### 2020-02-12 src/CCFE_visit1.tex
Add tex notes and pdf for CCFE Visit 1, 05 Feb 2020

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{extsizes}
\usepackage{parskip}

\usepackage{geometry}
\geometry{a4paper, portrait, margin=1in}

% Set up the images/graphics package
\usepackage{graphicx}
\setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
\graphicspath{{figures/}}

% Make prettier tables.
\usepackage{booktabs}

% The units package provides nice, non-stacked fractions and better spacing
% for units.
%\usepackage{units}

% The fancyvrb package lets us customize the formatting of verbatim
% environments.  We use a slightly smaller font.
\usepackage{fancyvrb}

% Small sections of multiple columns
\usepackage{multicol}

\title{Visit to CCFE, 05 Feb 2020}
\author{Graham Van Goffrier}

%%% Custom Commands
%---------------------------------------------------------------------------
% Concise referencing
\newcommand{\eqnref}[1]{\eqref{#1}}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\lemref}[1]{Lemma \ref{#1}}
\newcommand{\corref}[1]{Corollary \ref{#1}}
\newcommand{\thmref}[1]{Theorem \ref{#1}}
% Real numbers
\newcommand{\Real}[1]{\mathbb{R}^{#1}}
% Complex numbers
\newcommand{\Complex}[1]{\mathbb{C}^{#1}}
% Integers
\newcommand{\Integer}[1]{\mathbb{Z}^{#1}}
% Rank operator
\DeclareMathOperator{\rank}{\textnormal{rank}}
% Vec operator
\newcommand{\vecop}{\textnormal{vec}}
% Norm
\newcommand{\norm}[1]{\left|\left|#1\right|\right|}
% Trace
\newcommand{\trace}{\textnormal{tr}}
% Range
\newcommand{\range}{\textnormal{range}}
% Partial derivative
\newcommand{\pd}[2]{\dfrac{\partial #1}{\partial #2}}
% Complete derivative
\newcommand{\dd}[2]{\dfrac{d #1}{d #2}}
% Complete derivative, second order
\newcommand{\dds}[2]{\dfrac{d^2 #1}{d {#2}^2}}
% Limit to N / N
\newcommand{\limover}[1]{\lim_{#1 \rightarrow \infty} \dfrac{1}{#1}}
% Display style sum
\newcommand{\dsum}{\displaystyle\sum}
% arg min and arg max
\newcommand{\argmax}[1]{\underset{#1}{\operatorname{arg~max}}}
\newcommand{\argmin}[1]{\underset{#1}{\operatorname{arg~min}}}
%---------------------------------------------------------------------------
\newtheorem{theorem}{Theorem}

\begin{document}

\maketitle

%\begin{abstract}
%\noindent Begin abstract
%\end{abstract}

\section{The Model}

We discussed the simplified spherical model as presented in the Docker files to which we have been given access. Neutrons are sourced from the centre of the sphere with a Gaussian energy spread about 14 MeV. All these parameters are described in the help document for the Docker container, so I will not duplicate the description here, except to mention that certain noteworthy parameters are not included in the Docker model (e.g. temperature). More complex toroidal models, which take asymmetric plasma forms into account, come with a D=35 parameter space.

Monte Carlo n-Particle (MCNP) is the general descriptor for methods where neutron tracks through the geometric structure of the reactor are repeatedly modelled and observables such as the Tritium breeding ratio (TBR) are calculated. These geometries have long been represented in constructive solid geometry (CSG) format, but computer-aided design (CAD) geometry has now developed to the stage of providing increased efficiency for neutronics modelling. MCNP calculations are massively paralellisable, and generally follow a rectangular-wave pattern in core usage, where only one core is used to load the model followed by full core usage for the simulation.

The softwares in common use have been OpenMC for particle transport and DAGMC for CAD, while Chinese McCAD and German MCsen have been gaining prominence.
(see more: https://pdfs.semanticscholar.org/9f5c/07526173d6db29b6200e694a23835c0aa3f1.pdf)

\section{Project Planning}

The general scope of our literature review must include methods of building surrogate models from existing models.

F1000 Research was mentioned as an open-source publishing platform which allows for easy sharing of data in diverse formats -- however publishing via this platform does seem to exclude the possibility of publishing the same work in more traditional / renowned journals.

Effective quadratures were mentioned as a potentially useful method of polyfitting on undersampled regions.

\end{document}

### 2020-03-13 final_report/tbr_final_report-metadata.tex
add authors and report name

%-------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers if needed.
%-------------------------------------------------------------------------

% Partner Logo
% put the name of the logo image file found in graphics path
%\DISPartnerLogo{path/to/logo/image}

% Title
\DISTitle{Results from TBR Group Project}

% Draft version:
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\DISVersion{0}

% Abstract - % directly after { is important for correct indentation
\DISAbstract{%
  The abstract of my report.
}

% Authors and list of contributors to the analysis
\usepackage{authblk}
\author[a]{Petr Mánek}
\author[a]{Graham Van Goffrier}
\affil[a]{University College London}

% DIS reference code if ever used
\DISRefCode{UCLCDTDIS-2019-XX}

### 2020-04-18 final_report/data.tex
Update report outline

Data

\subsection{Data Description and Initial Sampling}
\label{sec:datadescription}

\subsection{Dimensionality Reduction}
\label{sec:dimred}

\subsubsection{Principal Component Analysis}

\subsubsection{Variogram Computations}

\subsubsection{Autoencoders}

### 2020-04-18 final_report/introduction.tex
Update report outline

Introduction

\subsection{Problem Description}
\label{sec:problemdescription}

### 2020-04-18 final_report/methodology.tex
Update report outline

Methodology

\subsection{Model Comparisons}
\label{sec:model}

\subsection{Adaptive Sampling}
\label{sec:adaptive}

### 2020-04-18 final_report/results.tex
Update report outline

Results

\subsection{Results of Model Comparisons}
\label{sec:modelres}

\subsection{Results of Adaptive Sampling}
\label{sec:adaptiveres}

### 2020-04-19 final_report/introduction.tex
Progress on introduction
Full draft of introduction.

@@
-Introduction
+The analysis of massive datasets has become a necessary component of virtually all technical fields, as well as the social and humanistic sciences, in recent years.
+Given that rapid improvements in sensing and processing hardware have gone hand in hand with the data explosion, it is unsurprising that software for the generation and interpretation of this data has also attained a new frontier in complexity.
+In particular, simulation procedures such as Monte Carlo (MC) event generation can perform physics predictions even for theoretical regimes which are not analytically soluble.
+The bottleneck for such procedures, as is often the case, lies in the computational time and power which they necessitate.
+
+Surrogate models, or metamodels, can resolve this limitation by replacing a resource-expensive procedure with a much cheaper approximation [1].
+They are especially useful in applications where numerous evaluations of an expensive procedure are required over the same or similar domains, e.g.
+in the parameter optimisation of a theoretical model.
+The term "metamodel" proves especially meaningful in this case, when the surrogate model approximates a computational process which is itself a model for a (perhaps unknown) physical process [2].
+There exists a spectrum between "physical" surrogates which are constructed with some contextual knowledge in hand, and "empirical" surrogates which are derived purely from the underlying expensive model.
+
+In this internship project, in coordination with the UK Atomic Energy Authority (UKAEA) and Culham Centre for Fusion Energy (CCFE), we sought to develop a surrogate model for the tritium breeding ratio (TBR) in a Tokamak-class nuclear fusion reactor.
+Our expensive model was a MC-based neutronics simulation [3], itself a spherical approximation of the Joint European Torus (JET) at CCFE, which returns a prediction of the TBR for a given reactor configuration.
+We took an empirical approach to the construction of this surrogate, and no results described here are explicitly dependent on prior physics knowledge.
+
+For the remainder of Section 1, we will define the TBR and set the context of this work within the goals of the UKAEA and CCFE.
+In Section 2 we will describe our datasets generated from the expensive model for training and validation purposes, and the dimensionality reduction methods employed to develop our understanding of the parameter domain.
+In Section 3 we will present our methodologies for the comparison testing of a wide variety of surrogate modelling techniques, as well as a novel adaptive sampling procedure suited to this application.
+After delivering the results of these approaches in Section 4, we will give our final conclusions and recommendations for further work.
 
@@
 \label{sec:problemdescription}
+
+- Introduce nuclear fusion via tokamak [4][5]
+
+- details of JET / CCFE [6]
+
+-------------------------------------------------------------------------------------
+
+- Describe tritium breeding [4]
+    - Modelling of reactor geometries [7]
+
+[1] Sondergaard 2003
+[2] Myers and Montgomery 2002
+[3] Collaboration with Jonathan 2020
+
+[4] Hernandez 2018
+[5] Tokamak wikipedia 
+[6] Keilhacker 1999
+[7] Coleman 2019

### 2020-04-19 final_report/methodology.tex
add basic methodology definitions, compare supervised and unsupervised learning

@@
-Methodology
+Assuming that input has been appropriately treated to eliminate redundant
+features, we may turn to characterise proposed surrogate models and the criteria
+used for their evaluation. The task all presented surrogates strive to solve can be
+formulated using the language of conventional regression problems. In the scope
+of this work, we explore various possible choices available to us in the
+scheme of supervised and unsupervised learning.
+
+Labeling the expensive Monte Carlo simulation $f(x)$, a surrogate is a mapping
+$\tilde{f}(x)$ that yields similar images as $f(x)$. In other words, $f(x)$ and
+$\tilde{f}(x)$ minimise a selected similarity metric. Furthermore, in order to
+be considered \textit{viable}, surrogates are required to achieve expected evaluation time
+that does not exceed the expected evaluation time of $f(x)$.
+
+In the supervised learning setting, we first gather a sufficiently large
+training set of samples $\mathcal{T}=\left\{\left( x^{(i)},f\left(x^{(i)}\right) \right)\right\}_{i=1}^N$
+to describe the behaviour of $f(x)$ across its domain.
+Depending on specific model class and appropriate choice of its
+hyperparameters, surrogate models $\tilde{f}(x)$ are trained to minimise
+empirical risk with respect to $\mathcal{T}$ and a model-specific
+loss function $\mathcal{L}$, where empirical risk is defined as
+
+\begin{align}
+	R_{\text{emp.}}(\tilde{f}\mid\mathcal{T},\mathcal{L})
+	=\frac{1}{N}\sum_{i=1}^N
+	\mathcal{L}\left(\tilde{f}(x^{(i)}),f(x^{(i)})\right).
+\end{align}
+
+The unsupervised setting can be viewed as an extension of this procedure.
+Rather than fixing the training set $\mathcal{T}$ for the entire duration of
+training, the points of evaluation $\{x^{(i)}\}_{i=1}^N$ that determine the set
+are first initialised randomly, and continuously extended throughout training. This
+permits the learning algorithm to motivate the choice of new points following the
+evaluation of surrogates trained thus far by appropriately biasing the
+proposal distribution, in order to better focus on problematic regions within
+the domain.
 

### 2020-04-19 final_report/methodology.tex
add section on metrics

@@
 
+\subsection{Metrics}
+\label{sec:metrics}
+
+Aiming to provide objective comparison of a diverse set of surrogate model
+classes, we define a multitude of metrics to be tracked during experiments.
+Following the motivation of this work, we are primarily interested in two
+properties of surrogates: (i) their capability to approximate the expensive
+model well and (ii) their time of evaluation. We strive to maximise the former
+while minimising the latter.
+
+To prevent undesirable bias in results due to training set selection, both
+properties are collected using $k$-fold cross-validation with a standard choice
+of $k=5$. Herein, a sample set is subdivided into 5 disjoint
+folds which are repeatedly interpreted as training and testing sets, maintaining
+a constant ratio of samples. In each such interpretation experiments are
+repeated, and the overall value of each metric of interest is given by the mean
+across all folds.
+
+The remainder of this section provides exhaustive list and description of
+regression performance and evaluation time metrics recorded in the experiments.
+
+\subsubsection{Regression Performance Metrics}
+\label{sec:perf-metrics}
+
+TODO: provide formal definition of each of the following metrics
+
+\begin{description}
+	\item[Mean absolute error]
+	\item[$R^2$ ratio]
+	\item[Adjusted $R^2$ ratio]
+	\item[Standard error of regression]
+\end{description}
+
+\subsubsection{Evaluation Time Metrics}
+\label{sec:time-metrics}
+
+TODO: provide formal definition of each of the following metrics
+
+\begin{description}
+	\item[Training time per sample]
+	\item[Prediction time per sample]
+\end{description}
+
 \subsection{Model Comparisons}

### 2020-04-20 final_report/introduction.tex
Complete introduction and problem description draft

@@
 
-In this internship project, in coordination with the UK Atomic Energy Authority (UKAEA) and Culham Centre for Fusion Energy (CCFE), we sought to develop a surrogate model for the tritium breeding ratio (TBR) in a Tokamak-class nuclear fusion reactor.
+In this internship project, in coordination with the UK Atomic Energy Authority (UKAEA) and Culham Centre for Fusion Energy (CCFE), we sought to develop a surrogate model for the tritium breeding ratio (TBR) in a Tokamak nuclear fusion reactor.
 Our expensive model was a MC-based neutronics simulation [3], itself a spherical approximation of the Joint European Torus (JET) at CCFE, which returns a prediction of the TBR for a given reactor configuration.
@@
 
-- Introduce nuclear fusion via tokamak [4][5]
+Nuclear fusion technology relies on the production and containment of an extremely hot and dense plasma.
+In this environment, by design similar to that of a star, hydrogen atoms attain energies sufficient to overcome their usual electrostatic repulsion and fuse to form helium [4].
+Early prototype reactors made use of the deuterium ($^2H$) isotope of hydrogen in order to achieve fusion under more accessible conditions, but achieved limited success.
+The current frontier generation of fusion reactors, such as JET and the under-construction International Thermonuclear Experimental Reactor (ITER), make use of tritium ($^3H$) fuel for further efficiency gain.
+Experimentation at JET dating back to 1997 [5] has made significant headway in validating deuterium-tritium (D-T) operations and constraining the technology which will be employed in ITER in a scaled up form.
 
-- details of JET / CCFE [6]
+However, tritium is much less readily available as a fuel source than deuterium.
+While at least one deuterium atom occurs for every 5000 molecules of naturally-sourced water, and may be easily distilled, tritium is extremely rare in nature.
+It may be produced indirectly through irradiation of heavy water (deuterium oxide) during nuclear fission, but only at very low rates which could never sustain industrial-scale fusion power.
 
--------------------------------------------------------------------------------------
+Instead, modern D-T reactors rely on tritium breeding blankets, specialised layers of material which partially line the reactor and produce tritium upon neutron bombardment, e.g. by
 
-- Describe tritium breeding [4]
-    - Modelling of reactor geometries [7]
+\begin{equation}
+    ^1_0n + \hspace{3pt} ^6_3Li \rightarrow \hspace{3pt} ^3_1T + \hspace{3pt} ^4_2He
+\end{equation}
+\begin{equation}
+    ^1_0n + \hspace{3pt} ^7_3Li  \rightarrow \hspace{3pt} ^3_1T + \hspace{3pt} ^4_2He + \hspace{3pt} ^1_0n
+\end{equation}
+\begin{wrapfigure}{r}{0.4\textwidth}
+  \begin{center}
+    \includegraphics[width=0.48\textwidth]{fig1_tokamakdiagram.png}
+  \end{center}
+  \caption{Typical single-null reactor configuration as specified by BLUEPRINT [6]: 1 — plasma,
+2 — breeding blankets }
+\end{wrapfigure}
 
-[1] Sondergaard 2003
-[2] Myers and Montgomery 2002
-[3] Collaboration with Jonathan 2020
+where T represents tritium and $^7Li$, $^6Li$ are the more and less frequently occurring isotopes of lithium, respectively.
+$^6Li$ has the greatest tritium breeding cross-section of all tested isotopes [4], but due to magnetohydrodynamic instability of liquid lithium in the reactor environment, a variety of solid lithium compounds are preferred.
 
-[4] Hernandez 2018
-[5] Tokamak wikipedia 
-[6] Keilhacker 1999
-[7] Coleman 2019
+The TBR is defined as the ratio between tritium generation in the breeding blanket per unit time and tritium fuel consumption in the reactor.
+The MC neutronics simulations previously mentioned therefore must account for both the internal plasma dynamics of the fusion reactor and the resultant interactions of neutrons with breeding blanket materials.
+Neutron paths are traced through a CAD model (e.g.
+Figure 1) of a reactor with modifiable geometry.
+
+The input parameters of the computationally-expensive TBR model therefore fall into two classes.
+Continuous parameters, including material thicknesses and packing ratios, describe the geometry of a given reactor configuration.
+Discrete categorical parameters further specify all relevant material sections, including coolants, armours, and neutron multipliers.
+One notable exception is the enrichment ratio denoting the presence of $^6Li$, a continuous parameter.
+Our challenge, put simply, was to produce a TBR function which takes these same input parameters and approximates the MC TBR model with the greatest achievable accuracy.

### 2020-04-20 final_report/methodology.tex

@@
 
-The unsupervised setting can be viewed as an extension of this procedure.
+The unsupervised setting can be viewed as an extension of this method.
 Rather than fixing the training set $\mathcal{T}$ for the entire duration of
-training, the points of evaluation $\{x^{(i)}\}_{i=1}^N$ that determine the set
-are first initialised randomly, and continuously extended throughout training. This
-permits the learning algorithm to motivate the choice of new points following the
-evaluation of surrogates trained thus far by appropriately biasing the
-proposal distribution, in order to better focus on problematic regions within
-the domain.
+training, multiple sets $\{\mathcal{T}_k\}_{k=0}^K$ are used, such that
+$\mathcal{T}_{k-1}\subset\mathcal{T}_k$ for all $k$. The first set
+$\mathcal{T}_0$ is initialised randomly to provide a \textit{burn-in}, and is
+repeatedly extended in epochs. In each epoch, a new surrogate is trained on
+$\mathcal{T}_k$ using the supervised learning procedure, and evaluated.
+This permits the learning algorithm to motivate the choice of new points following the
+evaluation of surrogates trained thus far by appropriately biasing a
+proposal distribution, in order to focus on improvement of complex regions
+within the domain.
 

### 2020-04-20 final_report/methodology.tex
minor edits in the metrics section, change f tilde to f hat

--- 2020-04-19 final_report/methodology.tex
@@
 Labeling the expensive Monte Carlo simulation $f(x)$, a surrogate is a mapping
-$\tilde{f}(x)$ that yields similar images as $f(x)$. In other words, $f(x)$ and
-$\tilde{f}(x)$ minimise a selected similarity metric. Furthermore, in order to
+$\hat{f}(x)$ that yields similar images as $f(x)$. In other words, $f(x)$ and
+$\hat{f}(x)$ minimise a selected similarity metric. Furthermore, in order to
 be considered \textit{viable}, surrogates are required to achieve expected evaluation time
@@
 Depending on specific model class and appropriate choice of its
-hyperparameters, surrogate models $\tilde{f}(x)$ are trained to minimise
+hyperparameters, surrogate models $\hat{f}(x)$ are trained to minimise
 empirical risk with respect to $\mathcal{T}$ and a model-specific
@@
 \begin{align}
-	R_{\text{emp.}}(\tilde{f}\mid\mathcal{T},\mathcal{L})
+	R_{\text{emp.}}(\hat{f}\mid\mathcal{T},\mathcal{L})
 	=\frac{1}{N}\sum_{i=1}^N
-	\mathcal{L}\left(\tilde{f}(x^{(i)}),f(x^{(i)})\right).
+	\mathcal{L}\left(\hat{f}(x^{(i)}),f(x^{(i)})\right).
 \end{align}
 
-The unsupervised setting can be viewed as an extension of this procedure.
+The unsupervised setting can be viewed as an extension of this method.
 Rather than fixing the training set $\mathcal{T}$ for the entire duration of
-training, the points of evaluation $\{x^{(i)}\}_{i=1}^N$ that determine the set
-are first initialised randomly, and continuously extended throughout training. This
-permits the learning algorithm to motivate the choice of new points following the
-evaluation of surrogates trained thus far by appropriately biasing the
-proposal distribution, in order to better focus on problematic regions within
-the domain.
+training, multiple sets $\{\mathcal{T}_k\}_{k=0}^K$ are used, such that
+$\mathcal{T}_{k-1}\subset\mathcal{T}_k$ for all $k>1$. The first set
+$\mathcal{T}_0$ is initialised randomly to provide a \textit{burn-in}, and is
+repeatedly extended in epochs, whereby each epoch trains a new surrogate on
+$\mathcal{T}_k$ using the supervised learning procedure, evaluates its
+performance, and forms a new set $\mathcal{T}_{k+1}$ by adding more samples to
+$\mathcal{T}_k$. This permits the learning algorithm to condition the selection
+of new samples by the results of evaluation in order to focus on improvement of
+surrogate performance in complex regions within the domain.
+
+\subsection{Metrics}
+\label{sec:metrics}
+
+Aiming to provide objective comparison of a diverse set of surrogate model
+classes, we define a multitude of metrics to be tracked during experiments.
+Following the motivation of this work, two desirable properties of surrogates
+arise: (i) their capability to approximate the expensive
+model well and (ii) their time of evaluation. An ideal surrogate would maximise
+the former while minimising the latter.
+
+To prevent undesirable bias in results due to training set selection, metrics
+related to both properties are collected using $k$-fold cross-validation with a
+standard choice of $k=5$. Herein, a sample set is subdivided into 5 disjoint
+folds which are repeatedly interpreted as training and testing sets, maintaining
+a constant ratio of samples between the two. In each such interpretation experiments are
+repeated, and the overall value of each metric of interest is reported as the mean
+across all folds.
+
+\Cref{tbl:metrics} provides exhaustive list and description of
+regression performance and evaluation time metrics recorded in the experiments.
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{lll}
+	\toprule
+	Regression performance metrics	& Mathematical formulation / description & Ideal value \\
+	\midrule
+	Mean absolute error	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0 [TBR] \\
+	$R^2$ ratio (coefficient of determination)	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
+	\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 [rel.] \\
+	Adjusted $R^2$ ratio	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 [rel.] \\
+	Standard error of regression	& $\text{StdDev}_{i=1}^N\left( |y^{(i)} -
+	\hat{y}^{(i)}| \right) $	 & 0 [TBR] \\
+	\midrule
+	Evaluation time metrics	& {} & {} \\
+	\midrule
+	Mean sample training time	& $(\text{wall training time of $\hat{f}(x)$})/N_0$ 	& 0 [ms] \\
+	Mean sample prediction time	& $(\text{wall evaluation time of $\hat{f}(x)$})/N$	& 0 [ms] \\
+	\bottomrule
+	\end{tabular}
+	\caption{Metrics recorded in supervised learning experiments. In
+	formulations, we work with training set of size $N_0$ and testing set of
+size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
+denote images of the $i$th sample in the expensive model and the surrogate
+respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
+number of input features.}
+	\label{tbl:metrics}
+\end{table}
 

### 2020-04-20 final_report/methodology.tex
add one more paragraph on metrics

@@
 
-To prevent undesirable bias in results due to training set selection, metrics
-related to both properties are collected using $k$-fold cross-validation with a
-standard choice of $k=5$. Herein, a sample set is subdivided into 5 disjoint
-folds which are repeatedly interpreted as training and testing sets, maintaining
-a constant ratio of samples between the two. In each such interpretation experiments are
-repeated, and the overall value of each metric of interest is reported as the mean
-across all folds.
-
-\Cref{tbl:metrics} provides exhaustive list and description of
-regression performance and evaluation time metrics recorded in the experiments.
+\Cref{tbl:metrics} provides exhaustive list and description of metrics recorded
+in the experiments. For regression performance analysis, we include a selection
+of absolute metrics to assess the approximation capability of surrogates, and set
+practical bounds on the expected accuracy of their predictions. In addition, we also track
+relative measures that are better-suited for model comparison between works as
+they maintain invariance with respect to the domain and image space.
 
@@
 	\midrule
-	Mean absolute error	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0 [TBR] \\
+	Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
+	[TBR] \\
+	Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left( |y^{(i)} -
+	\hat{y}^{(i)}| \right) $	 & 0 [TBR] \\
 	$R^2$ ratio (coefficient of determination)	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
@@
 	Adjusted $R^2$ ratio	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 [rel.] \\
-	Standard error of regression	& $\text{StdDev}_{i=1}^N\left( |y^{(i)} -
-	\hat{y}^{(i)}| \right) $	 & 0 [TBR] \\
 	\midrule
@@
 	\midrule
-	Mean sample training time	& $(\text{wall training time of $\hat{f}(x)$})/N_0$ 	& 0 [ms] \\
-	Mean sample prediction time	& $(\text{wall evaluation time of $\hat{f}(x)$})/N$	& 0 [ms] \\
+	Mean sample training time	& $(\text{wall training time of
+	$\hat{f}(x)$})/N_0$ 	& 0 [ms] \\
+	Mean sample prediction time	& $(\text{wall evaluation time of
+	$\hat{f}(x)$})/N$	& 0 [ms] \\
 	\bottomrule
@@
 size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
-denote images of the $i$th sample in the expensive model and the surrogate
+denote images of the $i$th testing sample in the expensive model and the surrogate
 respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
@@
 \end{table}
+
+To prevent undesirable bias in results due to training set selection, all metrics
+collected in the scheme of $k$-fold cross-validation with a standard choice of
+$k=5$. Herein, a sample set is subdivided into 5 disjoint folds which are
+repeatedly interpreted as training and testing sets, maintaining a constant
+ratio of samples between the two. In each such interpretation experiments are
+repeated, and the overall value of each metric of interest is reported as the
+mean across all folds.
 

### 2020-04-20 final_report/methodology.tex
add (hopefully) last bit on metrics, and speedup

@@
 
-\Cref{tbl:metrics} provides exhaustive list and description of metrics recorded
+\Cref{tbl:metrics} provides exhaustive listing and description of metrics recorded
 in the experiments. For regression performance analysis, we include a selection
@@
 relative measures that are better-suited for model comparison between works as
-they maintain invariance with respect to the domain and image space.
+they maintain invariance with respect to the selected domain and image space.
+For analysis of evaluation time, surrogates are assessed in terms of wall time
+elapsed during training and predicition. This closely models the practical use
+case, in which they are trained and used as drop-in replacements for the
+expensive model. Since training set sizes remain to be determined, all times are
+reported per a single sample. Even though some surrogates support acceleration
+by means of parallelisation, measures were taken to ensure sequential
+processing of samples to achieve comparability between considered models.
 
@@
 	\midrule
-	Mean sample training time	& $(\text{wall training time of
+	Mean sample training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
 	$\hat{f}(x)$})/N_0$ 	& 0 [ms] \\
-	Mean sample prediction time	& $(\text{wall evaluation time of
+	Mean sample prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
 	$\hat{f}(x)$})/N$	& 0 [ms] \\
+	Relative speedup	& $(\text{wall evaluation time of $f(x)$}) /
+	(N\overline{t}_{\text{pred.}})$	&
+	$\to\infty$ [rel.] \\
 	\bottomrule

### 2020-04-20 final_report/methodology.tex
ensure table 1 fits the page width

@@
 	\centering
-	\begin{tabular}{lll}
+	\begin{tabular}{llrl}
 	\toprule
-	Regression performance metrics	& Mathematical formulation / description & Ideal value \\
+	Regression performance metrics	& Mathematical formulation / description &
+	\multicolumn{2}{c}{Ideal value} \\
 	\midrule
 	Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
-	[TBR] \\
-	Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left( |y^{(i)} -
-	\hat{y}^{(i)}| \right) $	 & 0 [TBR] \\
-	$R^2$ ratio (coefficient of determination)	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
-	\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 [rel.] \\
-	Adjusted $R^2$ ratio	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 [rel.] \\
+								& [TBR] \\
+	Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
+	\hat{y}^{(i)}| \right\} $	 & 0 & [TBR] \\
+	$R^2$ (coefficient of determination)	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
+	\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 & [rel.] \\
+	Adjusted $R^2$	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 & [rel.] \\
 	\midrule
-	Evaluation time metrics	& {} & {} \\
+	Evaluation time metrics	& {} & {} & {} \\
 	\midrule
-	Mean sample training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
-	$\hat{f}(x)$})/N_0$ 	& 0 [ms] \\
-	Mean sample prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
-	$\hat{f}(x)$})/N$	& 0 [ms] \\
+	Mean training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
+	$\hat{f}(x)$})/N_0$ 	& 0 & [ms] \\
+	Mean prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
+	$\hat{f}(x)$})/N$	& 0 & [ms] \\
 	Relative speedup	& $(\text{wall evaluation time of $f(x)$}) /
 	(N\overline{t}_{\text{pred.}})$	&
-	$\to\infty$ [rel.] \\
+	$\to\infty$ & [rel.] \\
 	\bottomrule

### 2020-04-20 final_report/data.tex
Complete draft of dimensionality reduction: pca and variograms

@@
 
+\newpage
+
 \subsection{Dimensionality Reduction}
@@
 
+Model training over high-dimensional parameter spaces may be facilitated by carefully reducing the number of variables used to describe the space.
+For many applications, feature selection strategies succeed in identifying a sufficiently representative subset of the original input variables; however, all given variables were assumed to be physically relevant to the MC TBR model.
+Feature extraction methods, on the other hand, aim to identify a transformation from the parameter space which decreases dimensionality; even if no individual parameter is separable from the space, some linear combinations of parameters or nonlinear functions of parameters may be.
+
+\begin{figure}[h]
+  \centering
+    \includegraphics[width=0.6\linewidth]{fig2_pca.jpg}
+    \caption{Cumulative variance for optimal features identified by PCA}
+  \label{fig:pca}
+\end{figure}
+
+\begin{wrapfigure}{r}{0.5\textwidth}
+  \vspace{-55pt}
+  \begin{center}
+    \hspace*{-.3\columnsep}\includegraphics[width=0.58\textwidth]{fig3_allvar.jpg}
+    \caption{Semivariograms for MC TBR data with coolant materials: (a) $He$, (b) $H_2O$, (c) $D_2O$}
+    \label{fig:var}
+  \end{center}
+  \vspace{-110pt}
+\end{wrapfigure}
+
 \subsubsection{Principal Component Analysis}
+
+To pursue linear feature extraction, principal component analysis (PCA) was performed via scikit-learn on a set of 300,000 uniform samples of the MC TBR model.
+
+Figure \ref{fig:pca} shows the resultant cumulative variance of the feature vectors identified by PCA.
+The similar share of variance among all eleven features demonstrated irreducibility of the TBR model by linear methods.
 
@@
 
+Kriging, or Gaussian process regression, is a geostatistical surrogate modelling technique which relies on correlation functions over distance (lag) in the paramater space [2].
+Although kriging performed poorly for our use case due to high dimensionality, these correlation measures gave insight into similarities between discrete-parameter slices of the data.
+
+Figure \ref{fig:var} shows the Matheron semivariance [3] for three discrete slices with coolant material varied, but all other discrete parameters fixed.
+Fits [4] to the Matérn covariance model confirmed numerically that the coolant material is the discrete parameter with the greatest distinguishability in the MC TBR model.
+
+** Make sure discrete slices are mentioned before this **
+
 \subsubsection{Autoencoders}
+
+Question: is it accurate to say this represents nonlinear feature extraction? re my intro paragraph
+
+\newpage

### 2020-04-20 final_report/introduction.tex
Complete draft of dimensionality reduction: pca and variograms

@@
 Instead, modern D-T reactors rely on tritium breeding blankets, specialised layers of material which partially line the reactor and produce tritium upon neutron bombardment, e.g. by 
-
-\begin{equation}
-    ^1_0n + \hspace{3pt} ^6_3Li \rightarrow \hspace{3pt} ^3_1T + \hspace{3pt} ^4_2He
-\end{equation}
-\begin{equation}
-    ^1_0n + \hspace{3pt} ^7_3Li  \rightarrow \hspace{3pt} ^3_1T + \hspace{3pt} ^4_2He + \hspace{3pt} ^1_0n
-\end{equation}
-\begin{wrapfigure}{r}{0.4\textwidth}
+\begin{align}
+    ^1_0n + \hspace{3pt} ^6_3Li &\rightarrow \hspace{3pt} ^3_1T + \hspace{3pt} ^4_2He \\
+    ^1_0n + \hspace{3pt} ^7_3Li &\rightarrow \hspace{3pt} ^3_1T + \hspace{3pt} ^4_2He + \hspace{3pt} ^1_0n
+\end{align}
+\begin{wrapfigure}{r}{0.45\textwidth}
+  \vspace{-20pt}
   \begin{center}
@@
 2 — breeding blankets }
+\label{fig:tokamak}
 \end{wrapfigure}
-
 where T represents tritium and $^7Li$, $^6Li$ are the more and less frequently occurring isotopes of lithium, respectively.
@@
 Neutron paths are traced through a CAD model (e.g.
-Figure 1) of a reactor with modifiable geometry.
+Figure \ref{fig:tokamak}) of a reactor with modifiable geometry.
 
@@
 Discrete categorical parameters further specify all relevant material sections, including coolants, armours, and neutron multipliers.
-One notable exception is the enrichment ratio denoting the presence of $^6Li$, a continuous parameter.
+One notable exception is the enrichment ratio, a continuous parameter denoting the presence of $^6Li$.
 Our challenge, put simply, was to produce a TBR function which takes these same input parameters and approximates the MC TBR model with the greatest achievable accuracy.

### 2020-04-20 final_report/methodology.tex
add two more subsections
reorder words in table
add outline for supervised learning experiments

@@
 	\hat{y}^{(i)}| \right\} $	 & 0 & [TBR] \\
-	$R^2$ (coefficient of determination)	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
+	Coefficient of determination $R^2$	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
 	\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 & [rel.] \\
@@
 
-\subsection{Model Comparisons}
-\label{sec:model}
+\subsection{Supervised Learning Experiments}
+\label{sec:supervised}
+
+\subsubsection{Considered Surrogates}
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{llll}
+	\toprule
+	Surrogate & Acronym & Implementation & Hyperparameters \\
+	\midrule
+	Support vector machines	& SVM & SciKit Learn & TODO \\
+	Gradient boosted trees	& GBT & SciKit Learn & TODO \\
+	Extremely random trees	& ERT & SciKit Learn & TODO \\
+	AdaBoost	& AB & SciKit Learn & TODO \\
+	Gaussian process regression	& GPR & SciKit Learn & TODO \\
+	$k$ nearest neighbours	& KNN & SciKit Learn & TODO \\
+	Neural networks	& NN & Keras (TensorFlow) & TODO \\
+	Inverse distance weighing & IDW & SMT & TODO \\
+	Radial basis functions & RBF & SMT & TODO \\
+	Stochastic gradient descent & SGD & SciKit Learn & TODO \\
+	Ridge regression & RR & SciKit Learn & TODO \\
+	Kriging & KRG & SMT & TODO \\
+	\bottomrule
+	\end{tabular}
+	\caption{TODO}
+	\label{tbl:surrogates}
+\end{table}
+
+TODO: describe classes of surrogates
+
+TODO: reference implementations and original papers
+
+TODO: define NN architectures
+
+\subsubsection{Experiments}
+
+TODO: single slice hyperparameter optimisation
+
+TODO: multislice (mixed) hyperparameter optimisation
+
+TODO: retraining for scaling benchmark
+
+TODO: retraining on large set
 

### 2020-04-20 final_report/methodology.tex
compress expression in methodology intro

@@
 loss function $\mathcal{L}$, where empirical risk is defined as
-
-\begin{align}
-	R_{\text{emp.}}(\hat{f}\mid\mathcal{T},\mathcal{L})
+$R_{\text{emp.}}(\hat{f}\mid\mathcal{T},\mathcal{L})
 	=\frac{1}{N}\sum_{i=1}^N
-	\mathcal{L}\left(\hat{f}(x^{(i)}),f(x^{(i)})\right).
-\end{align}
+	\mathcal{L}\left(\hat{f}(x^{(i)}),f(x^{(i)})\right)$.
 

### 2020-04-20 final_report/methodology.tex
add diagrams of neural net architectures
Finished draft of methodology - adaptive sampling section.

@@
 
+\newpage
+
 \subsection{Adaptive Sampling}
 \label{sec:adaptive}
+
+All of the surrogate modelling techniques studied in this project face a shared challenge: their accuracy is limited by the quantity of training samples which are available from the expensive MC model.
+Adaptive sampling procedures can improve upon this limitation by taking advantage of statistical information which is accumulated during the training of any surrogate model.
+Rather than training the surrogate on a single sample set generated according to a fixed strategy, sample locations are chosen incrementally so as to best suit the model under consideration.
+
+Adaptive sampling techniques are widespread in the literature and have been specialised for surrogate modelling.
+Garud's [1] "Smart Sampling Algorithm" achieved notable success by incorporating surrogate quality and crowding distance scoring to identify optimal new samples, but was only tested on a single-parameter domain.
+We theorised that a nondeterministic sample generation approach, built around Markov Chain Monte Carlo methods (MCMC), would fare better for high-dimensional models by more thoroughly exploring all local optima in the parameter space.
+MCMC produces a progressive chain of sample points, each drawn according to the same symmetric proposal distribution from the prior point.
+These sample points will converge to a desired posterior distribution, so long as the acceptance probability for these draws has a particular functional dependence on that posterior value (see [2] for a review).
+
+Many researchers have embedded surrogate methods into MCMC strategies for parameter optimisation [3][4], in particular the ASMO-PODE algorithm [5] which makes use of MCMC-based adaptive sampling to attain greater surrogate precision around prospective optima.
+Our novel approach draws inspiration from ASMO-PODE, but instead uses MCMC to generate samples which increase surrogate precision throughout the entire parameter space.
+
+\begin{wrapfigure}{r}{0.5\textwidth}
+  \vspace{-35pt}
+  \begin{center}
+    \includegraphics[width=0.6\textwidth]{fig4_qassplan.png}
+    \caption{Schematic of QASS algorithm}
+    \label{fig:qassplan}
+  \end{center}
+  \vspace{-20pt}
+\end{wrapfigure}
+
+We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS) to iteratively increment the training set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) [6] in parameter space.
+On each iteration following an initial training of the surrogate on $N$ uniformly random samples, test error values were calculated according to the representative error defined in [1].
+MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points.
+The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the primary training set, beginning another training epoch.
+An adaptive MCMC technique [7], which tunes an ellipsoidal proposal distribution to best fit the proposal distribution, was also implemented.
+
+Literature review:
+
+other MC-based surrogate approaches
+
+Smart-Sampling Algorithm [1]
+
+Single MCMC [2]
+
+Reverse [3][4] ASMO-PODE [5]
+
+CDM [6]
+
+Adaptive MCMC [7]
+
+[1] Garud, 2016
+[2] Zhou, 2018
+[3] Zhang, 2020
+[4] Gong, 2017
+
+[5] Ginting, 2011
+[6] Solonen, 2012
+[7] Zhang, 2012

### 2020-04-20 final_report/methodology.tex
fix typo

@@
 To prevent undesirable bias in results due to training set selection, all metrics
-collected in the scheme of $k$-fold cross-validation with a standard choice of
+are collected in the scheme of $k$-fold cross-validation with a standard choice of
 $k=5$. Herein, a sample set is subdivided into 5 disjoint folds which are
@@
 TODO: define NN architectures
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[b]{0.20\textwidth}
+		\centering
+		{\footnotesize \incfigscale{0.62}{1h3f}}
+		\caption{$\text{1h3f}(W)$}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.15\textwidth}
+		\centering
+		{\footnotesize \incfigscale{0.62}{kf}}
+		\caption{$\text{df}(D,W)$}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.15\textwidth}
+		\centering
+		{\footnotesize \incfigscale{0.62}{3pyramid}}
+		\caption{$\text{3pyr}(W)$}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.20\textwidth}
+		\centering
+		{\footnotesize \incfigscale{0.62}{5diam}}
+		\caption{$\text{5diam}(W)$}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.20\textwidth}
+		\centering
+		{\footnotesize \incfigscale{0.62}{kf}} % TODO
+		\caption{$\text{6sym}(W)$}
+	\end{subfigure}
+
+	\caption{TODO}
+	\label{fig:neural-net-architectures}
+\end{figure}
 

### 2020-04-20 final_report/methodology.tex
Add QASS result plots

@@
 To prevent undesirable bias in results due to training set selection, all metrics
-are collected in the scheme of $k$-fold cross-validation with a standard choice of
+collected in the scheme of $k$-fold cross-validation with a standard choice of
 $k=5$. Herein, a sample set is subdivided into 5 disjoint folds which are
@@
 
-\begin{wrapfigure}{r}{0.5\textwidth}
+\begin{wrapfigure}{r}{0.55\textwidth}
   \vspace{-35pt}
   \begin{center}
-    \includegraphics[width=0.6\textwidth]{fig4_qassplan.png}
+    \includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
     \caption{Schematic of QASS algorithm}
@@
   \end{center}
-  \vspace{-20pt}
+  \vspace{-80pt}
 \end{wrapfigure}
 
-We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS) to iteratively increment the training set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) [6] in parameter space.
-On each iteration following an initial training of the surrogate on $N$ uniformly random samples, test error values were calculated according to the representative error defined in [1].
+We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS) to iteratively increment the training/test set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) [6] in parameter space.
+On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and AE calculated for .
 MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points.
-The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the primary training set, beginning another training epoch.
-An adaptive MCMC technique [7], which tunes an ellipsoidal proposal distribution to best fit the proposal distribution, was also implemented.
-
-Literature review:
-
-other MC-based surrogate approaches
-
-Smart-Sampling Algorithm [1]
-
-Single MCMC [2]
-
-Reverse [3][4] ASMO-PODE [5]
-
-CDM [6]
-
-Adaptive MCMC [7]
-
-[1] Garud, 2016
-[2] Zhou, 2018
-[3] Zhang, 2020
-[4] Gong, 2017
-
-[5] Ginting, 2011
-[6] Solonen, 2012
-[7] Zhang, 2012
+The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the training/test set, beginning another training epoch.
+Validation was also performed during each iteration on independent, uniformly-random sample sets.

### 2020-04-20 final_report/results.tex
Add QASS result plots

@@
-Results
-
 \subsection{Results of Model Comparisons}
@@
 
+\newpage
+
 \subsection{Results of Adaptive Sampling}
 \label{sec:adaptiveres}
+
+Define sinusoidal toy model and justify
+
+Explain hyperparameter tests: initsamples, stepsamples, MCMC length
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=1.1\linewidth]{fig5_qassincrsamp.png}
+        \caption{QASS absolute training error over total sample quantity}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=1.1\linewidth]{fig6_qassincrtime.png}
+        \caption{QASS absolute training error over number of iterations}
+    \end{subfigure}
+    \caption{Caption place holder}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+    \includegraphics[width=0.8\linewidth]{fig7_qasssampling.png}
+    \caption{Absolute training error for QASS, uniform random scheme, and mixed scheme}
+  \label{fig:pca}
+\end{figure}

### 2020-04-20 final_report/methodology.tex
write experiments section

@@
 
-TODO: single slice hyperparameter optimisation
+The presented surrogate candidates are evaluated in four experimental cases:
 
-TODO: multislice (mixed) hyperparameter optimisation
+\begin{enumerate}
 
-TODO: retraining for scaling benchmark
+	\item Hyperparameter tuning in simplified domain,
 
-TODO: retraining on large set
+	\item Hyperparameter tuning in full domain,
 
-\newpage
+	\item Scaling benchmark,
+
+	\item Competitive surrogate training.
+\end{enumerate}
+
+The aim of the initial experiments is to use a relatively small subset of
+collected TBR samples to determine hyperparameters of considered surrogates.
+Since this process requires learning the behaviour of an unknown, possibly
+expensive mapping---here a function that assigns cross-validated metrics to a
+point in the hyperparameter domain---it in many aspects mirrors
+the primary task of this work with the notable extension of added utility
+to optimise. In order to avoid undesirable exponential slowdown in exhaustive
+searches of a possibly high-dimensional parameter space, Bayesian
+optimisation is employed as standard hyperparameter tuning algorithm that is considered
+efficient for this purpose. We set its objective to maximise $R^2$.
+
+In the first experiment, efforts are made to maximise the possibility of success
+in surrogates that are prone to suboptimal performance in discontinuous spaces.
+This follows the notion that, if desired, accuracy of such models may be
+replicated at large scale by decomposing the TBR domain into continuous subsets,
+and learning ensemble surrogate comprised of models that are trained on each
+subset independently, incurring exponential complexity penalty in the process.
+To this end, training samples are filtered to only contain a single assignment
+of discrete features that are subsequently completely withheld from evaluated
+surrogates. This is repeated four times to investigate variance in behaviour
+under different feature assignments.
+
+The second experiment conventionally measures surrogate performance on the full
+TBR regression task. In extension of the previous case, surrogates work with
+unfiltered samples comprised of discrete as well as continuous features.
+
+The goal of the last two experiments is to exploit the information gathered by
+hyperparameter tuning for study of scaling properties. In
+the third experiment, the best-performing hyperparameter choices of each class
+are used to learn surrogates using progressively larger training sets. Following
+that, the fourth experiment attempts to produce competitive surrogates by
+retraining several selected well-scaling models on the largest available data set.
 

### 2020-04-20 final_report/methodology.tex
write supervised learning section

@@
 
-\subsection{Supervised Learning Experiments}
+\subsection{Evaluation of Supervised Learning Surrogates}
 \label{sec:supervised}
 
-\subsubsection{Considered Surrogates}
+In our experiments, we evaluate and compare surrogates in effort to
+optimise against metrics described in \cref{sec:metrics}. To attain meaningful
+and practically usable results, we require a sufficiently large and diverse pool
+of surrogate classes to draw from. This is described by the listing in
+\cref{tbl:surrogates}. The presented selection of models includes basic
+techniques suitable for linear regression enhanced by the kernel trick or dimension
+lifting, methods driven by decision trees, instance-based learning models,
+ensemble regressors, randomized algorithms, neural networks and mathematical approaches
+developed specifically for the purposes of surrogate modelling. For each of
+these classes, a state-of-the-art implementation was selected and adapted to
+operate with TBR samples.
 
@@
 	\end{tabular}
-	\caption{TODO}
+	\caption{Considered surrogate model classes.}
 	\label{tbl:surrogates}
@@
 
-TODO: describe classes of surrogates
-
-TODO: reference implementations and original papers
-
-TODO: define NN architectures
+In some rows of the table, a single class in reality represents a multitude of
+fundamentally similar approaches. Good examples of this are kriging methods and neural
+networks. In the case of the former, multiple algorithms such as kriging based on
+partial least squares and gradient-enhanced kriging are considered. In the
+latter, a host of parametric graphs are defined to realise simplistic network
+architecture search (see \cref{fig:nn-archs} for details). Discrimination
+between such options is considered an additional hyperparameter of the
+corresponding surrogate class.
 
@@
 
-	\caption{TODO}
-	\label{fig:neural-net-architectures}
+	\caption{Various considered parametric neural architectures. All layers use ReLU
+		activation and random initialisation. Information flow is indicated by
+		arrows. Conections between neurons are omitted for clarity.}
+	\label{fig:nn-archs}
 \end{figure}

### 2020-04-20 final_report/methodology.tex
make tables smaller to clear space

@@
 	\centering
+	{\footnotesize
 		\begin{tabular}{llrl}
@@
 		\end{tabular}
+	}
 	\caption{Metrics recorded in supervised learning experiments. In
@@
 	\centering
+	{\footnotesize
 		\begin{tabular}{llll}
@@
 		Gradient boosted trees	& GBT & SciKit Learn & TODO \\
-	Extremely random trees	& ERT & SciKit Learn & TODO \\
-	AdaBoost	& AB & SciKit Learn & TODO \\
+		Extremely randomized trees	& ERT & SciKit Learn & TODO \\
+		AdaBoosted decision trees	& AB & SciKit Learn & TODO \\
 		Gaussian process regression	& GPR & SciKit Learn & TODO \\
@@
 		\end{tabular}
+	}
 	\caption{Considered surrogate model classes.}

### 2020-04-20 final_report/methodology.tex
nicer neural network figure
fill in hyperparam counts

@@
 		\midrule
-		Support vector machines	& SVM & SciKit Learn & TODO \\
-		Gradient boosted trees	& GBT & SciKit Learn & TODO \\
-		Extremely randomized trees	& ERT & SciKit Learn & TODO \\
-		AdaBoosted decision trees	& AB & SciKit Learn & TODO \\
-		Gaussian process regression	& GPR & SciKit Learn & TODO \\
-		$k$ nearest neighbours	& KNN & SciKit Learn & TODO \\
-		Neural networks	& NN & Keras (TensorFlow) & TODO \\
-		Inverse distance weighing & IDW & SMT & TODO \\
-		Radial basis functions & RBF & SMT & TODO \\
-		Stochastic gradient descent & SGD & SciKit Learn & TODO \\
-		Ridge regression & RR & SciKit Learn & TODO \\
-		Kriging & KRG & SMT & TODO \\
+		Support vector machines	& SVM & SciKit Learn & 3 \\
+		Gradient boosted trees	& GBT & SciKit Learn & 11 \\
+		Extremely randomized trees	& ERT & SciKit Learn & 7 \\
+		AdaBoosted decision trees	& AB & SciKit Learn & 3 \\
+		Gaussian process regression	& GPR & SciKit Learn & 2 \\
+		$k$ nearest neighbours	& KNN & SciKit Learn & 3 \\
+		Neural networks	& NN & Keras (TensorFlow) & 2 \\
+		Inverse distance weighing & IDW & SMT & 1 \\
+		Radial basis functions & RBF & SMT & 3 \\
+		Stochastic gradient descent & SGD & SciKit Learn & 13 \\
+		Ridge regression & RR & SciKit Learn & 4 \\
+		Kriging & KRG & SMT & 4 \\
 		\bottomrule
@@
 	\centering
-	\begin{subfigure}[b]{0.20\textwidth}
+	\begin{subfigure}[b]{0.25\textwidth}
 		\centering
-		{\footnotesize \incfigscale{0.62}{1h3f}}
+		{\scriptsize \incfigscale{0.6}{1h3f}}
 		\caption{$\text{1h3f}(W)$}
 	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.15\textwidth}
+	\begin{subfigure}[b]{0.25\textwidth}
 		\centering
-		{\footnotesize \incfigscale{0.62}{kf}}
+		{\scriptsize \incfigscale{0.6}{kf}}
 		\caption{$\text{df}(D,W)$}
 	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.15\textwidth}
+	\begin{subfigure}[b]{0.25\textwidth}
 		\centering
-		{\footnotesize \incfigscale{0.62}{3pyramid}}
+		{\scriptsize \incfigscale{0.6}{3pyramid}}
 		\caption{$\text{3pyr}(W)$}
 	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.20\textwidth}
+	\begin{subfigure}[b]{0.25\textwidth}
 		\centering
-		{\footnotesize \incfigscale{0.62}{5diam}}
+		{\scriptsize \incfigscale{0.6}{5diam}}
 		\caption{$\text{5diam}(W)$}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.20\textwidth}
-		\centering
-		{\footnotesize \incfigscale{0.62}{kf}} % TODO
-		\caption{$\text{6sym}(W)$}
 	\end{subfigure}
 
-	\caption{Various considered parametric neural architectures. All layers use ReLU
-		activation and random initialisation. Information flow is indicated by
+	\caption{Selected parametric neural network architectures. All layers except
+		the last use ReLU activation. Prediction information flow is indicated by
 		arrows. Conections between neurons are omitted for clarity.}

### 2020-04-20 final_report/data.tex
add TODOs for the data section
rename sections to better reflect their content
redistribute more TODOs, rename sections (again)

@@
 
-\subsection{Data Description and Initial Sampling}
-\label{sec:datadescription}
+\subsection{Feature Description}
+\label{sec:feature-description}
 
-\newpage
+TODO
+\begin{enumerate}
+	\item about single sphere OpenMC sim
+	\item parameter listing
+	\item continuous vs discrete features
+	\item discrete embedding
+\end{enumerate}
+
+\subsection{Dataset Generation}
+\label{sec:dataset-generation}
+
+TODO
+\begin{enumerate}
+	\item grid search vs random sampling
+	\item from a set of sampled points to evaluated TBR values
+	\item tech deployed at Hypatia: dockerised sampler \& dataframe-driven querying
+	\item run 0, 1, 2 parameters
+\end{enumerate}
+
+\subsection{Preprocessing}
+\label{sec:preprocessing}
+
+TODO
+\begin{enumerate}
+	\item discrete feature embedding
+	\item standardisation
+\end{enumerate}
 
@@
 
-** Make sure discrete slices are mentioned before this **
+** TODO: Make sure discrete slices are mentioned before this **
 
@@
 
-Question: is it accurate to say this represents nonlinear feature extraction? re my intro paragraph
+TODO: Question: is it accurate to say this represents nonlinear feature extraction? re my intro paragraph
 
-\newpage
+TODO
+\begin{enumerate}
+	\item working principle
+	\item application on single slice
+	\item application on mixed slice data
+\end{enumerate}

### 2020-04-21 final_report/data.tex
add model description section

@@
-Data
+The initial step of our work is the study of the existing MC TBR model and its
+behaviour. Following the examination of its features (simulation parameters), we
+present efficient means of evaluating this model on large sets of points in HPC
+environment, preprocessing techniques designed to adapt collected datasets for
+surrogate modelling, and our attempts at feature space reduction to achieve the
+lowest possible number of dimensions.
 
-\subsection{Feature Description}
-\label{sec:feature-description}
+\subsection{Expensive Model Description}
+\label{sec:expensive-model-description}
 
-TODO
-\begin{enumerate}
-	\item about single sphere OpenMC sim
-	\item parameter listing
-	\item continuous vs discrete features
-	\item discrete embedding
-\end{enumerate}
+The MC TBR model that we understand to be the expensive function for our
+surrogate modelling is fundamentally a Monte Carlo simulation based on the OpenMC
+framework. At input the software expects a set of 19~parameters, discrete and
+continuous, that are fully listed in~\cref{tbl:params}. Following a brief period of
+time (usually on the order of tens of seconds), during which a fixed number of events is simulated, the software outputs the
+mean and the standard deviation of the TBR aggregated over the simulated run. The
+former of these two outputs we accept to be the output TBR value that is subject
+to approximation.
+
+\begin{table}[h]
+	\centering
+	{\footnotesize
+		\begin{tabular}{llll}
+		\toprule
+		Parameter name & Type & Domain & Description\\
+		\midrule
+		TODO & TODO & TODO & TODO\\
+		\bottomrule
+		\end{tabular}
+	}
+	\caption{Input parameters supplied to the MC TBR simulation.}
+	\label{tbl:params}
+\end{table}
+
+In our work, we often reference TBR points or samples. These are simply vectors
+in the feature space generated by Cartesian product of domains of all
+features---parameters from~\cref{tbl:params}.
+
+Since most surrogate models
+that we employ assume overall continuous inputs, we take steps to unify our
+feature interface in order to attain this property. In particular, we eliminate
+discrete features by embedding each such feature into a finite multitude of
+continuous features using standard one-hot encoding. This option is available to
+us since discrete domains that generate our feature space are finite in
+cardinality and relatively small in size. And while it renders all features continuous, the
+modification comes at the expense of increasing the dimensionality of the
+feature space, which is comprised of 27 features from this point on.
 

### 2020-04-21 final_report/data.tex
fill in param table

@@
 	{\footnotesize
-		\begin{tabular}{llll}
+		\begin{tabular}{l|llll}
 		\toprule
-		Parameter name & Type & Domain & Description\\
+		{} & Parameter name & Type & Domain & Description\\
 		\midrule
-		TODO & TODO & TODO & TODO\\
+		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{Blanket}}}
+		& Breeder fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & TODO\\
+		& Breeder \isotope[6]{Li} enrichment fraction & Continuous & $[0,1]$ & {}\\
+		& Breeder material & Discrete & $\{\ce{Li2TiO3}, \ce{Li4SiO4}\}$ & {}\\
+		& Breeder packing fraction & Continuous & $[0,1]$ & {}\\
+		& Coolant fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
+		& Coolant material & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
+		& Multiplier fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
+		& Multiplier material & Discrete & $\{\ce{Be}, \ce{Be12Ti}\}$ & {}\\
+		& Multiplier packing fraction & Continuous & $[0,1]$ & {}\\
+		& Structural fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
+		& Structural material & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
+		& Thickness & Continuous & $[0,500]$ & {}\\
+		\midrule
+		\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{First wall}}}
+		& Armour fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
+		& Armour material & Discrete & $\{\text{tungsten}\}$ & {}\\
+		& Coolant fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
+		& Coolant material & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
+		& Structural fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
+		& Structural material & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
+		& Thickness & Continuous & $[0,20]$ & {}\\
 		\bottomrule
@@
 	}
-	\caption{Input parameters supplied to the MC TBR simulation.}
+	\caption{Input parameters supplied to the MC TBR simulation in alphabetical
+		order. Fractions marked with superscripts\textsuperscript{\textdagger
+		\textdaggerdbl} are independently required to sum to one.}
 	\label{tbl:params}

### 2020-04-21 final_report/data.tex
finish data generation section

@@
 behaviour. Following the examination of its features (simulation parameters), we
-present efficient means of evaluating this model on large sets of points in HPC
-environment, preprocessing techniques designed to adapt collected datasets for
-surrogate modelling, and our attempts at feature space reduction to achieve the
-lowest possible number of dimensions.
+present efficient means of evaluating this model on large sets of points in
+high-performance computing (HPC) environment, preprocessing techniques designed
+to adapt collected datasets for surrogate modelling, and our attempts at feature
+space reduction to achieve the lowest possible number of dimensions.
 
@@
 modification comes at the expense of increasing the dimensionality of the
-feature space, which is comprised of 27 features from this point on.
+feature space to 27 features in total.
 
@@
 
-TODO
-\begin{enumerate}
-	\item grid search vs random sampling
-	\item from a set of sampled points to evaluated TBR values
-	\item tech deployed at Hypatia: dockerised sampler \& dataframe-driven querying
-	\item run 0, 1, 2 parameters
-\end{enumerate}
+While we deliberately make no assumptions about the internal properties of the
+MC TBR simulation, effectively treating it as a black box model, our means of
+studying its behaviour are limited to inspection of its outputs at various
+points in the feature space, and inference thereof. We thus require to
+gather sufficiently large and representative quantities of samples to ensure
+statistical significance of our findings.
+
+With grid search in high-dimensional domain clearly intractable, we decided to
+implement uniform pseudo-random sampling to generate large amounts of feature
+configurations that we consider to be independent and unbiased. For evaluation
+of the expensive MC TBR model, we utilise parallelisation offered by
+the HPC infrastructure available at UCL computing facilities. To this end, we
+implemented the Approximate TBR Evaluator---a Python software package capable of
+sequential evaluation of the multi-threaded OpenMC simulation on batches of
+previously generated points in the feature space.
+We deployed ATE at the UCL Hypatia cluster RCIF partition, which consists of
+4~homogeneous nodes, each containing 40 cores. We completed three data
+generation runs, which are summarised in~\cref{tbl:sampling-runs}.
+
+\begin{table}[h]
+	\centering
+	{\footnotesize
+		\begin{tabular}{rllll}
+		\toprule
+		\#	& Sample count & Job division & Run time (incl. waiting) & Description \\
+		\midrule
+		0 & \num{100000} & $\num{100}\times\num{1000}$ & 2~days, 23~hours &
+		Testing run using older MC TBR version.\\
+		1 & \num{500000} & $\num{500}\times\num{1000}$ & 13~days, 20~hours &
+		Fully uniform sampling in the entire domain.\\
+		2 & \num{400000} & $\num{400}\times\num{1000}$ & 10~days &
+		Mixed sampling, discrete features fixed.\\
+		\bottomrule
+		\end{tabular}
+	}
+	\caption{Parameters of sampling runs.}
+	\label{tbl:sampling-runs}
+\end{table}
+
+Skipping run zero, which was performed using older, fundamentally different
+version of the MC TBR software, and was thus treated as a technical
+proof-of-concept, we generated the total of~\num{900000} samples in two runs.
+While the first run featured fully uniform sampling of the unrestricted feature
+space, the second run used more elaborate strategy. Interested in further study
+of relationships between discrete and continuous features, we selected four
+assignments of discrete features and fixed them for all points, effectively
+slicing the feature space into four corresponding subspaces. In order to achieve
+comparability between these \textit{slices}, the remaining unassigned features
+were sampled only in the first slice, and reused in the other three.
 

### 2020-04-21 final_report/data.tex
add table of slice feature assignments

@@
 	{\footnotesize
-		\begin{tabular}{l|llll}
+		\begin{tabular}{l|lllll}
 		\toprule
-		{} & Parameter name & Type & Domain & Description\\
+		{} & Parameter name & Acronym & Type & Domain & Description\\
 		\midrule
 		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{Blanket}}}
-		& Breeder fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & TODO\\
-		& Breeder \isotope[6]{Li} enrichment fraction & Continuous & $[0,1]$ & {}\\
-		& Breeder material & Discrete & $\{\ce{Li2TiO3}, \ce{Li4SiO4}\}$ & {}\\
-		& Breeder packing fraction & Continuous & $[0,1]$ & {}\\
-		& Coolant fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
-		& Coolant material & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
-		& Multiplier fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
-		& Multiplier material & Discrete & $\{\ce{Be}, \ce{Be12Ti}\}$ & {}\\
-		& Multiplier packing fraction & Continuous & $[0,1]$ & {}\\
-		& Structural fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
-		& Structural material & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
-		& Thickness & Continuous & $[0,500]$ & {}\\
+		   & Breeder fraction\textsuperscript{\textdagger} & BBF & Continuous & $[0,1]$ & TODO\\
+		   & Breeder \isotope[6]{Li} enrichment fraction & BBLEF & Continuous & $[0,1]$ & {}\\
+		   & Breeder material & BBM & Discrete & $\{\ce{Li2TiO3}, \ce{Li4SiO4}\}$ & {}\\
+		   & Breeder packing fraction & BBPF & Continuous & $[0,1]$ & {}\\
+		   & Coolant fraction\textsuperscript{\textdagger} & BCF & Continuous & $[0,1]$ & {}\\
+		   & Coolant material & BCM & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
+		   & Multiplier fraction\textsuperscript{\textdagger} & BMF & Continuous & $[0,1]$ & {}\\
+		   & Multiplier material & BMM & Discrete & $\{\ce{Be}, \ce{Be12Ti}\}$ & {}\\
+		   & Multiplier packing fraction & BMPF & Continuous & $[0,1]$ & {}\\
+		   & Structural fraction\textsuperscript{\textdagger} & BSF & Continuous & $[0,1]$ & {}\\
+		   & Structural material & BSM & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
+		   & Thickness & BT & Continuous & $[0,500]$ & {}\\
 		\midrule
 		\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{First wall}}}
-		& Armour fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
-		& Armour material & Discrete & $\{\text{tungsten}\}$ & {}\\
-		& Coolant fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
-		& Coolant material & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
-		& Structural fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
-		& Structural material & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
-		& Thickness & Continuous & $[0,20]$ & {}\\
+		   & Armour fraction\textsuperscript{\textdaggerdbl} & FAF & Continuous & $[0,1]$ & {}\\
+		   & Armour material & FAM & Discrete & $\{\text{tungsten}\}$ & {}\\
+		   & Coolant fraction\textsuperscript{\textdaggerdbl} & FCF & Continuous & $[0,1]$ & {}\\
+		   & Coolant material & FCM & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
+		   & Structural fraction\textsuperscript{\textdaggerdbl} & FSF & Continuous & $[0,1]$ & {}\\
+		   & Structural material & FSM & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
+		   & Thickness & FT & Continuous & $[0,20]$ & {}\\
 		\bottomrule
@@
 of relationships between discrete and continuous features, we selected four
-assignments of discrete features and fixed them for all points, effectively
-slicing the feature space into four corresponding subspaces. In order to achieve
-comparability between these \textit{slices}, the remaining unassigned features
-were sampled only in the first slice, and reused in the other three.
+assignments of discrete features (listed in~\cref{tbl:slices}) and fixed them
+for all points, effectively slicing the feature space into four corresponding
+subspaces. In order to achieve comparability between these \textit{slices}, the
+remaining unassigned features were uniformly sampled only in the first slice,
+and reused in the other three.
+
+\begin{table}[h]
+	\centering
+	{\footnotesize
+		\begin{tabular}{r|lllllll}
+		\toprule
+		{} & \multicolumn{7}{c}{Discrete feature assignment}\\
+		Jobs & BBM & BCM & BMM & BSM & FAM & FCM & FSM \\
+		\midrule
+		0-99 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
+		100-199 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
+		200-299 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
+		300-399 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
+		\bottomrule
+		\end{tabular}
+	}
+	\caption{Selected discrete feature assignments corresponding to slices in run~2.}
+	\label{tbl:slices}
+\end{table}
 

### 2020-04-21 final_report/data.tex
add section on standardisation

@@
 
-\subsection{Preprocessing}
-\label{sec:preprocessing}
-
-TODO
-\begin{enumerate}
-	\item discrete feature embedding
-	\item standardisation
-\end{enumerate}
+Since some methods applied in this work are not scale-invariant or
+perform suboptimally when presented with arbitrarily scaled problems, all results
+produced in the sampling runs were standardised prior to further use. In this
+commonly used statistical procedure, features and regression outputs are
+independently scaled and offset to attain zero mean and unit variance.
 

### 2020-04-21 final_report/data.tex
add reference to dimensional reduction
add section on autoencoders

@@
 modification comes at the expense of increasing the dimensionality of the
-feature space to 27 features in total.
+feature space to 27 features in total. This is further discussed
+in~\cref{sec:dimred}.
 
@@
 
-** TODO: Make sure discrete slices are mentioned before this **
-
 \subsubsection{Autoencoders}
 
-TODO: Question: is it accurate to say this represents nonlinear feature extraction? re my intro paragraph
+\begin{wrapfigure}{r}{0.25\textwidth}
+	\centering
+	\vspace{-3ex}
+	{\footnotesize \incfigscale{0.8}{autoencoder}}
+	\caption{Autoencoder with input width~$W_0$ and bottleneck width~$W_1$.}
+	\label{fig:autoencoder}
+\end{wrapfigure}
 
-TODO
-\begin{enumerate}
-	\item working principle
-	\item application on single slice
-	\item application on mixed slice data
-\end{enumerate}
+Autoencoders are a family of approaches to feature extraction driven by neural
+networks. Faced with many possible alternatives, we implemented a conventional
+autoencoder, which relies on a three-layer network that is trained to replicate
+the identity mapping. While it follows that the input and output layers of such
+network are sized to accommodate the analysed dataset, the
+hidden layer---also called the bottleneck---allows for variable number of
+neurons that represent a smaller subspace. By scanning
+over a range of bottleneck widths and investigating relative changes in the
+validation loss, we assess the potential for dimensional reduction.
+
+This approach was applied to two sets of samples: (i) a subset of data obtained
+from run~1 and (ii) a subset of a single slice obtained from run~2. Our
+expectation was that while the former case would provide meaningful insight into
+correlations within the feature space, the latter would validate our
+autoencoder implementation by analysing a set of points that are trivially
+reducible due to a number of fixed features.
+
+\begin{wrapfigure}{l}{0.4\textwidth}
+	\centering
+	\vspace{-3ex}
+	% TODO: placeholders only, regenerate when time is available
+	\begin{subfigure}[b]{\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{ae_plot_all_slices_combined}
+	\end{subfigure}
+	\begin{subfigure}[b]{\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{ae_plot_single_slice}
+	\end{subfigure}
+	\caption{Autoencoder loss in two considered cases of dimensional reduction.}
+	\label{fig:autoencoder-loss}
+\end{wrapfigure}
+
+The results of both experiments are shown in~\cref{fig:autoencoder-loss}.
+Consistent with our motivation, in each plot we can clearly identify a constant
+plateau in the region of large dimensionality followed by a point, from which a
+steep increase in loss is observed towards lower dimension counts. We consider
+this critical point to correspond with the largest viable dimensional reduction
+without significant information loss.
+With this methodology we find that the autoencoder was able to reduce the
+datasets into a subspace of 17~dimensions in the first case and 10~dimensions in
+the second case.
+
+Confirming our expectation that in the latter, trivially reducible case the
+autoencoder should achieve stricter dimensional reduction, we are
+encouraged to believe that our implementation is indeed efficient. However, we
+must also conclude that in both examined cases this method failed to produce a
+reduction that would be dominate a naïve approach, in which we eliminate
+7~dimensions due to overdetermined one-hot-encoded features, 2~dimensions due to
+sum-to-one constraints, and in the latter case 7~additional dimensions due to
+artificially fixed features. This supports the findings from PCA as well as the
+presented semivariograms.
+
+% TODO: Question: is it accurate to say this represents nonlinear feature extraction? re my intro paragraph

### 2020-04-21 final_report/results.tex
add some placeholder plots, sketch outline of the results section

@@
-\subsection{Results of Model Comparisons}
+\subsection{Supervised Model Evaluation}
 \label{sec:modelres}
 
-\newpage
+TODO
+
+\subsubsection{Hyperparameter Tuning}
+
+TODO
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{exp1_time_vs_reg}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Experiment 1 (single slice)}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{exp1_time_vs_reg}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Experiment 2 (full dataset)}
+	\end{subfigure}
+	\caption{Regression performance (as $R^2$) plotted against mean
+	prediction time for the best $N$~models of each surrogate class.} % TODO. fill N
+	\label{fig:time-vs-reg}
+\end{figure}
+
+\subsubsection{Scaling Benchmark}
+
+TODO
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[b]{0.333\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{scaling_metric_r2}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Regression performance (as $R^2$)}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.333\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{scaling_time_train}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Mean training time}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.333\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{scaling_time_pred}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Mean prediction time}
+	\end{subfigure}
+	\caption{Various metrics collected during experiment 3 (scaling
+	benchmark) displayed as a function of training set size.}
+	\label{fig:scaling}
+\end{figure}
+
+\subsubsection{Competitive Training}
+
+TODO
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[b]{0.333\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Model 1}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.333\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Model 2}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.333\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Model 3}
+	\end{subfigure}
+
+	\vspace{0.75ex}
+
+	\begin{subfigure}[b]{0.333\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Model 1}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.333\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Model 2}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.333\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Model 3}
+	\end{subfigure}
+	\caption{Regression performance of the best models trained in experiment~4.}
+	\label{fig:reg-performance}
+\end{figure}
 

### 2020-04-21 final_report/results.tex
add section on scaling

@@
-\subsection{Supervised Model Evaluation}
+\subsection{Evaluation of Supervised Learning Surrogates}
 \label{sec:modelres}
@@
 
-TODO
+In the next experiment we examine surrogate scaling properties correlating
+metrics of interest with progressively increasing training set size. The results
+shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
+methods based on decision trees and neural networks offer the best accuracy on
+larger sets overall. This is a curious extension of previous findings, where
+gradient boosted trees were observed to significantly dominate over the rest of
+the examined methods. With increasing training set size, their relative advantage is
+clearly gradually diminished.
 
@@
 
-\subsubsection{Competitive Training}
+According to our experiment, the lowest mean training time is generally achieved
+by instance-based learning methods, which seem to offer near-constant scaling
+characterists at the expense of significant performance increase later during
+prediction. Following that, we observe that the majority of tree-based methods also exhibit
+desirable properties. The notable exception here appear to be neural networks,
+which are the only model to utilise parallelisation. As such, their constant
+synchronisation overhead overall hinders performance on small training sets,
+producing misleading results when divided by the number of samples.
+
+In terms of mean prediction time, all tested surrogates except previously mentioned
+instance-based learning methods scale exceptionally well. Tree-based generally
+models appear to perform the fastest.
+
+\subsubsection{Competitive Surrogate Training}
 

### 2020-04-21 final_report/introduction.tex

@@
 
-Nuclear fusion technology relies on the production and containment of an extremely hot and dense plasma.
-In this environment, by design similar to that of a star, hydrogen atoms attain energies sufficient to overcome their usual electrostatic repulsion and fuse to form helium [4].
-Early prototype reactors made use of the deuterium ($^2H$) isotope of hydrogen in order to achieve fusion under more accessible conditions, but achieved limited success.
-The current frontier generation of fusion reactors, such as JET and the under-construction International Thermonuclear Experimental Reactor (ITER), make use of tritium ($^3H$) fuel for further efficiency gain.
-Experimentation at JET dating back to 1997 [5] has made significant headway in validating deuterium-tritium (D-T) operations and constraining the technology which will be employed in ITER in a scaled up form.
+Nuclear fusion technology relies on the production and containment of an
+extremely hot and dense plasma. In this environment, by design similar to that
+of a star, hydrogen atoms attain energies sufficient to overcome their usual
+electrostatic repulsion and fuse to form helium [4]. Early prototype reactors
+made use of the deuterium (\isotope[2]{H}) isotope of hydrogen in order to
+achieve fusion under more accessible conditions, but achieved limited success.
+The current frontier generation of fusion reactors, such as JET and the
+under-construction International Thermonuclear Experimental Reactor (ITER), make
+use of tritium (\isotope[3]{H}) fuel for further efficiency gain.
+Experimentation at JET dating back to 1997 [5] has made significant headway in
+validating deuterium-tritium (D-T) operations and constraining the technology
+which will be employed in ITER in a scaled up form.
 
 However, tritium is much less readily available as a fuel source than deuterium.
-While at least one deuterium atom occurs for every 5000 molecules of naturally-sourced water, and may be easily distilled, tritium is extremely rare in nature.
-It may be produced indirectly through irradiation of heavy water (deuterium oxide) during nuclear fission, but only at very low rates which could never sustain industrial-scale fusion power.
+While at least one deuterium atom occurs for every 5000 molecules of
+naturally-sourced water, and may be easily distilled, tritium is extremely rare
+in nature. It may be produced indirectly through irradiation of heavy water
+(deuterium oxide) during nuclear fission, but only at very low rates which could
+never sustain industrial-scale fusion power.
 
-Instead, modern D-T reactors rely on tritium breeding blankets, specialised layers of material which partially line the reactor and produce tritium upon neutron bombardment, e.g. by 
+Instead, modern D-T reactors rely on tritium breeding blankets, specialised
+layers of material which partially line the reactor and produce tritium upon
+neutron bombardment, e.g. by 
 \begin{align}
-    ^1_0n + \hspace{3pt} ^6_3Li &\rightarrow \hspace{3pt} ^3_1T + \hspace{3pt} ^4_2He \\
-    ^1_0n + \hspace{3pt} ^7_3Li &\rightarrow \hspace{3pt} ^3_1T + \hspace{3pt} ^4_2He + \hspace{3pt} ^1_0n
+	\isotope[1][0]{n} + \hspace{3pt} \isotope[6][3]{Li} 
+	&\longrightarrow \hspace{3pt} 
+	\isotope[3][1]{T} + \hspace{3pt}\isotope[4][2]{He} \\
+	\isotope[1][0]{n} + \hspace{3pt} \isotope[7][3]{Li} 
+	&\longrightarrow \hspace{3pt} 
+	\isotope[3][1]{T} + \hspace{3pt} \isotope[4][2]{He} + \hspace{3pt} \isotope[1][0]{n}
 \end{align}
@@
 \end{wrapfigure}
-where T represents tritium and $^7Li$, $^6Li$ are the more and less frequently occurring isotopes of lithium, respectively.
-$^6Li$ has the greatest tritium breeding cross-section of all tested isotopes [4], but due to magnetohydrodynamic instability of liquid lithium in the reactor environment, a variety of solid lithium compounds are preferred.
+where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
+less frequently occurring isotopes of lithium, respectively. \isotope[6]{Li} has
+the greatest tritium breeding cross-section of all tested isotopes [4], but due
+to magnetohydrodynamic instability of liquid lithium in the reactor environment,
+a variety of solid lithium compounds are preferred.
 
-The TBR is defined as the ratio between tritium generation in the breeding blanket per unit time and tritium fuel consumption in the reactor.
-The MC neutronics simulations previously mentioned therefore must account for both the internal plasma dynamics of the fusion reactor and the resultant interactions of neutrons with breeding blanket materials.
-Neutron paths are traced through a CAD model (e.g.
-Figure \ref{fig:tokamak}) of a reactor with modifiable geometry.
+The TBR is defined as the ratio between tritium generation in the breeding
+blanket per unit time and tritium fuel consumption in the reactor. The MC
+neutronics simulations previously mentioned therefore must account for both the
+internal plasma dynamics of the fusion reactor and the resultant interactions of
+neutrons with breeding blanket materials. Neutron paths are traced through a CAD
+model (e.g. \cref{fig:tokamak}) of a reactor with modifiable geometry.
 
-The input parameters of the computationally-expensive TBR model therefore fall into two classes.
-Continuous parameters, including material thicknesses and packing ratios, describe the geometry of a given reactor configuration.
-Discrete categorical parameters further specify all relevant material sections, including coolants, armours, and neutron multipliers.
-One notable exception is the enrichment ratio, a continuous parameter denoting the presence of $^6Li$.
-Our challenge, put simply, was to produce a TBR function which takes these same input parameters and approximates the MC TBR model with the greatest achievable accuracy.
+The input parameters of the computationally-expensive TBR model therefore fall
+into two classes. Continuous parameters, including material thicknesses and
+packing ratios, describe the geometry of a given reactor configuration. Discrete
+categorical parameters further specify all relevant material sections, including
+coolants, armours, and neutron multipliers. One notable exception is the
+enrichment ratio, a continuous parameter denoting the presence of
+\isotope[6]{Li}. Our challenge, put simply, was to produce a TBR function which
+takes these same input parameters and approximates the MC TBR model with the
+greatest achievable accuracy.

### 2020-04-21 final_report/results.tex
Added bibliography .bib file
add supervised learning result intro

@@
+TODO
+
 \subsection{Evaluation of Supervised Learning Surrogates}
@@
 
-TODO
+We begin by evaluating a diverse set of surrogate classes that we proposed
+earlier. In particular, we aim to study considered models in terms of regression
+performance and evaluation complexity.
+Following~\cref{sec:experiment-methodology}, where we proposed four experiments
+that accomplish this task, we present and discuss our results in the following
+sections.
 

### 2020-04-21 final_report/results.tex
more revisions to the results section, change competitive plot

@@
 Following~\cref{sec:experiment-methodology}, where we proposed four experiments
-that accomplish this task, we present and discuss our results in the following
-sections.
+that accomplish this task, we present and discuss our results in the next
+several sections.
 
@@
 	\centering
-	\begin{subfigure}[b]{0.333\textwidth}
+	\begin{subfigure}[b]{0.25\textwidth}
 		\centering
@@
 		% TODO: only a placeholder, regenerate when data becomes available
-		\caption{Model 1}
 	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.333\textwidth}
+	\begin{subfigure}[b]{0.25\textwidth}
 		\centering
@@
 		% TODO: only a placeholder, regenerate when data becomes available
-		\caption{Model 2}
 	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.333\textwidth}
+	\begin{subfigure}[b]{0.25\textwidth}
 		\centering
@@
 		% TODO: only a placeholder, regenerate when data becomes available
-		\caption{Model 3}
-	\end{subfigure}
-
-	\vspace{0.75ex}
-
-	\begin{subfigure}[b]{0.333\textwidth}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.25\textwidth}
 		\centering
@@
 		% TODO: only a placeholder, regenerate when data becomes available
-		\caption{Model 1}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.333\textwidth}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.25\textwidth}
 		\centering
@@
 		% TODO: only a placeholder, regenerate when data becomes available
-		\caption{Model 3}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.25\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
+		% TODO: only a placeholder, regenerate when data becomes available
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.25\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
+		% TODO: only a placeholder, regenerate when data becomes available
 	\end{subfigure}

### 2020-04-21 final_report/results.tex
add two paragraphs about hyperparameter tuning results

@@
 
-TODO
+The first two experiments perform Bayesian optimisation to maximise~$R^2$ in
+cross-validated setting as a function of model hyperparameters. While in the
+first experiment we limit ourselves to the scope of a single slice of the
+domain, in the second experiment we extend the process to the full feature
+space.
+
+The results displayed in~\cref{fig:time-vs-reg} indicate that in the first
+experiment, gradient boosted trees clearly appear to be the most accurate as
+well as the fastest surrogate class in terms of mean prediction time. Following
+that, we note that extremely randomised trees, support vector machines and
+neural networks also achieved satisfactory results in both examined metrics.
+While the remainder of tested surrogate classes does not exhibit problems in
+complexity, its regression performance falls below average.
+
+% TODO: multislice description
 

### 2020-04-21 final_report/results.tex
nicer, more realistic results of the first experiment; remove old placeholder plots

@@
 
-The results displayed in~\cref{fig:time-vs-reg} indicate that in the first
+The results displayed in~\cref{fig:exp1-time-vs-reg} indicate that in the first
 experiment, gradient boosted trees clearly appear to be the most accurate as
@@
 
-% TODO: multislice description
-
 \begin{figure}[h]
 	\centering
-	\begin{subfigure}[b]{0.5\textwidth}
+	\begin{subfigure}[b]{0.333\textwidth}
 		\centering
-		\includegraphics[width=\linewidth]{exp1_time_vs_reg}
+		\includegraphics[width=\linewidth]{exp1_slice0}
 		% TODO: only a placeholder, regenerate when data becomes available
-		\caption{Experiment 1 (single slice)}
+		\caption{Run 2, batches 0-3}
 	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.5\textwidth}
+	\begin{subfigure}[b]{0.333\textwidth}
 		\centering
-		\includegraphics[width=\linewidth]{exp1_time_vs_reg}
+		\includegraphics[width=\linewidth]{exp1_slice1}
 		% TODO: only a placeholder, regenerate when data becomes available
-		\caption{Experiment 2 (full dataset)}
+		\caption{Run 2, batches 100-103}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.333\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{exp1_slice2}
+		% TODO: only a placeholder, regenerate when data becomes available
+		\caption{Run 2, batches 200-203}
 	\end{subfigure}
-	\caption{Regression performance (as $R^2$) plotted against mean
-	prediction time for the best $N$~models of each surrogate class.} % TODO. fill N
-	\label{fig:time-vs-reg}
+	\caption{20~best-performing surrogates per each considered class, plotted in
+	terms of mean prediction time and regression performance (as~$R^2$) on
+	selected slices of run~2, evaluated in experiment~1.}
+	\label{fig:exp1-time-vs-reg}
 \end{figure}
+
+\begin{wrapfigure}{r}{0.333\textwidth}
+	\centering
+	\vspace{-3ex}
+	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
+	% TODO: only a placeholder, regenerate when data becomes available
+	\caption{Results of experiment~2, plotted analogously
+	to~\cref{fig:exp1-time-vs-reg}.}
+	\label{fig:exp2-time-vs-reg}
+\end{wrapfigure}
+
+% TODO: multislice description
+TODO: multislice description
 

### 2020-04-21 final_report/data.tex
add tbr vs. feature plot
use chemical package in H2O in figure description
LaTeXify autoencoder plots

@@
 		\toprule
-		\#	& Sample count & Job division & Run time (incl. waiting) & Description \\
+		\#	& Sample count & Batch division & Run time (incl. waiting) & Description \\
 		\midrule
@@
 		{} & \multicolumn{7}{c}{Discrete feature assignment}\\
-		Jobs & BBM & BCM & BMM & BSM & FAM & FCM & FSM \\
+		Batches & BBM & BCM & BMM & BSM & FAM & FCM & FSM \\
 		\midrule
@@
 	\centering
+	\includegraphics[width=\linewidth]{run1_400k_tbr_vs_feat}
+	% TODO: placeholder only, turn into vector
+	\caption{Marginalised dependence of TBR on the choice of continuous
+	features.}
+  \label{fig:tbr-vs-features}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
     \includegraphics[width=0.6\linewidth]{fig2_pca.jpg}
@@
     \hspace*{-.3\columnsep}\includegraphics[width=0.58\textwidth]{fig3_allvar.jpg}
-    \caption{Semivariograms for MC TBR data with coolant materials: (a) $He$, (b) $H_2O$, (c) $D_2O$}
+	\caption{Semivariograms for MC TBR data with coolant materials: (a) \ce{He},
+	(b) \ce{H2O}, (c) \ce{D2O}}
     \label{fig:var}
@@
 		\centering
-		\includegraphics[width=\linewidth]{ae_plot_all_slices_combined}
+		\includegraphics[width=\linewidth]{ae_all_slices}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=\linewidth]{ae_plot_single_slice}
+		\includegraphics[width=\linewidth]{ae_single_slice}
 	\end{subfigure}

### 2020-04-21 final_report/data.tex
Updated citations and image wrapping.

--- 2020-04-21 final_report/data.tex
@@
 	\centering
+	\includegraphics[width=\linewidth]{run1_400k_tbr_vs_feat}
+	% TODO: placeholder only, turn into vector
+	\caption{Marginalised dependence of TBR on the choice of continuous
+	features.}
+  \label{fig:tbr-vs-features}
+\end{figure}
+
+\subsubsection{Principal Component Analysis}
+
+To pursue linear feature extraction, principal component analysis (PCA) \cite{Jolliffe2016} was performed via scikit-learn on a set of 300,000 uniform samples of the MC TBR model.
+
+Figure \cref{fig:pca} shows the resultant cumulative variance of the feature vectors identified by PCA.
+The similar share of variance among all eleven features demonstrated irreducibility of the TBR model by linear methods.
+
+\begin{figure}[h]
+  \centering
     \includegraphics[width=0.6\linewidth]{fig2_pca.jpg}
@@
 \begin{wrapfigure}{r}{0.5\textwidth}
-  \vspace{-55pt}
+  \vspace{-30pt}
   \begin{center}
     \hspace*{-.3\columnsep}\includegraphics[width=0.58\textwidth]{fig3_allvar.jpg}
-    \caption{Semivariograms for MC TBR data with coolant materials: (a) $He$, (b) $H_2O$, (c) $D_2O$}
+	\caption{Semivariograms for MC TBR data with coolant materials: (a) \ce{He},
+	(b) \ce{H2O}, (c) \ce{D2O}}
     \label{fig:var}
   \end{center}
-  \vspace{-110pt}
+  \vspace{-50pt}
 \end{wrapfigure}
-
-\subsubsection{Principal Component Analysis}
-
-To pursue linear feature extraction, principal component analysis (PCA) was performed via scikit-learn on a set of 300,000 uniform samples of the MC TBR model.
-
-Figure \ref{fig:pca} shows the resultant cumulative variance of the feature vectors identified by PCA.
-The similar share of variance among all eleven features demonstrated irreducibility of the TBR model by linear methods.
 
@@
 
-Kriging, or Gaussian process regression, is a geostatistical surrogate modelling technique which relies on correlation functions over distance (lag) in the paramater space [2].
+Kriging, or Gaussian process regression, is a geostatistical surrogate modelling technique which relies on correlation functions over distance (lag) in the paramater space \cite{Bouhlel2018}.
 Although kriging performed poorly for our use case due to high dimensionality, these correlation measures gave insight into similarities between discrete-parameter slices of the data.
 
-Figure \ref{fig:var} shows the Matheron semivariance [3] for three discrete slices with coolant material varied, but all other discrete parameters fixed.
-Fits [4] to the Matérn covariance model confirmed numerically that the coolant material is the discrete parameter with the greatest distinguishability in the MC TBR model.
+Figure \cref{fig:var} shows the Matheron semivariance \cite{Matheron1963} for three discrete slices with coolant material varied, but all other discrete parameters fixed.
+Fits \cite{KrigingFig} to the Matérn covariance model confirmed numerically that the coolant material is the discrete parameter with the greatest distinguishability in the MC TBR model.
 
@@
 	\centering
-	\vspace{-3ex}
+	\vspace{-5ex}
 	{\footnotesize \incfigscale{0.8}{autoencoder}}
@@
 	\label{fig:autoencoder}
+	\vspace{-9ex}
 \end{wrapfigure}
@@
 	\centering
-	\vspace{-3ex}
+	\vspace{-1ex}
 	% TODO: placeholders only, regenerate when time is available
@@
 	\label{fig:autoencoder-loss}
+	\vspace{-6ex}
 \end{wrapfigure}

### 2020-04-21 final_report/introduction.tex
Updated citations and image wrapping.

@@
 
-Surrogate models, or metamodels, can resolve this limitation by replacing a resource-expensive procedure with a much cheaper approximation [1].
+Surrogate models, or metamodels, can resolve this limitation by replacing a resource-expensive procedure with a much cheaper approximation \cite{Sondergaard2003}.
 They are especially useful in applications where numerous evaluations of an expensive procedure are required over the same or similar domains, e.g.
 in the parameter optimisation of a theoretical model.
-The term "metamodel" proves especially meaningful in this case, when the surrogate model approximates a computational process which is itself a model for a (perhaps unknown) physical process [2].
+The term "metamodel" proves especially meaningful in this case, when the surrogate model approximates a computational process which is itself a model for a (perhaps unknown) physical process \cite{Myers2002}.
 There exists a spectrum between "physical" surrogates which are constructed with some contextual knowledge in hand, and "empirical" surrogates which are derived purely from the underlying expensive model.
@@
 In this internship project, in coordination with the UK Atomic Energy Authority (UKAEA) and Culham Centre for Fusion Energy (CCFE), we sought to develop a surrogate model for the tritium breeding ratio (TBR) in a Tokamak nuclear fusion reactor.
-Our expensive model was a MC-based neutronics simulation [3], itself a spherical approximation of the Joint European Torus (JET) at CCFE, which returns a prediction of the TBR for a given reactor configuration.
+Our expensive model was a MC-based neutronics simulation \cite{JonathanCollab}, itself a spherical approximation of the Joint European Torus (JET) at CCFE, which returns a prediction of the TBR for a given reactor configuration.
 We took an empirical approach to the construction of this surrogate, and no results described here are explicitly dependent on prior physics knowledge.
@@
 of a star, hydrogen atoms attain energies sufficient to overcome their usual
-electrostatic repulsion and fuse to form helium [4]. Early prototype reactors
+electrostatic repulsion and fuse to form helium \cite{Hernandez2018}. Early prototype reactors
 made use of the deuterium (\isotope[2]{H}) isotope of hydrogen in order to
@@
 use of tritium (\isotope[3]{H}) fuel for further efficiency gain.
-Experimentation at JET dating back to 1997 [5] has made significant headway in
+Experimentation at JET dating back to 1997 \cite{Keilhacker1999} has made significant headway in
 validating deuterium-tritium (D-T) operations and constraining the technology
@@
   \end{center}
-  \caption{Typical single-null reactor configuration as specified by BLUEPRINT [6]: 1 — plasma,
+  \caption{Typical single-null reactor configuration as specified by BLUEPRINT \cite{Coleman2019}: 1 — plasma,
 2 — breeding blankets }
@@
 less frequently occurring isotopes of lithium, respectively. \isotope[6]{Li} has
-the greatest tritium breeding cross-section of all tested isotopes [4], but due
+the greatest tritium breeding cross-section of all tested isotopes \cite{Hernandez2018}, but due
 to magnetohydrodynamic instability of liquid lithium in the reactor environment,

### 2020-04-21 final_report/methodology.tex
add supervised learning result intro
Updated citations and image wrapping.

@@
 		Regression performance metrics	& Mathematical formulation / description &
-		\multicolumn{2}{c}{Ideal value} \\
+		\multicolumn{2}{c}{Ideal value [units]} \\
 		\midrule
@@
 \subsubsection{Experiments}
+\label{sec:experiment-methodology}
 
@@
 Adaptive sampling techniques are widespread in the literature and have been specialised for surrogate modelling.
-Garud's [1] "Smart Sampling Algorithm" achieved notable success by incorporating surrogate quality and crowding distance scoring to identify optimal new samples, but was only tested on a single-parameter domain.
+Garud's \cite{Garud2016} "Smart Sampling Algorithm" achieved notable success by incorporating surrogate quality and crowding distance scoring to identify optimal new samples, but was only tested on a single-parameter domain.
 We theorised that a nondeterministic sample generation approach, built around Markov Chain Monte Carlo methods (MCMC), would fare better for high-dimensional models by more thoroughly exploring all local optima in the parameter space.
 MCMC produces a progressive chain of sample points, each drawn according to the same symmetric proposal distribution from the prior point.
-These sample points will converge to a desired posterior distribution, so long as the acceptance probability for these draws has a particular functional dependence on that posterior value (see [2] for a review).
+These sample points will converge to a desired posterior distribution, so long as the acceptance probability for these draws has a particular functional dependence on that posterior value (see \cite{Zhou2018} for a review).
 
-Many researchers have embedded surrogate methods into MCMC strategies for parameter optimisation [3][4], in particular the ASMO-PODE algorithm [5] which makes use of MCMC-based adaptive sampling to attain greater surrogate precision around prospective optima.
+Many researchers have embedded surrogate methods into MCMC strategies for parameter optimisation \cite{Zhang2020}\cite{Gong2017}, in particular the ASMO-PODE algorithm \cite{Ginting2011} which makes use of MCMC-based adaptive sampling to attain greater surrogate precision around prospective optima.
 Our novel approach draws inspiration from ASMO-PODE, but instead uses MCMC to generate samples which increase surrogate precision throughout the entire parameter space.
@@
 
-We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS) to iteratively increment the training/test set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) [6] in parameter space.
-On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and AE calculated for .
+We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS) to iteratively increment the training/test set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) \cite{Solonen2012} in parameter space.
+On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and AE calculated.
 MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points.
@@
 Validation was also performed during each iteration on independent, uniformly-random sample sets.
+
+ADD FIG REFERENCE
+
+% Adaptive multi-chain MCMC: \cite{Zhang2012}

### 2020-04-21 final_report/methodology.tex
add some references

@@
 		\midrule
-		Support vector machines	& SVM & SciKit Learn & 3 \\
+		Support vector machines	& SVM & SciKit Learn~\cite{scikit-learn} & 3 \\
 		Gradient boosted trees	& GBT & SciKit Learn & 11 \\
@@
 		$k$ nearest neighbours	& KNN & SciKit Learn & 3 \\
-		Neural networks	& NN & Keras (TensorFlow) & 2 \\
-		Inverse distance weighing & IDW & SMT & 1 \\
+		Neural networks	& NN & Keras (TensorFlow)~\cite{chollet2015keras} & 2 \\
+		Inverse distance weighing & IDW & SMT~\cite{SMT2019} & 1 \\
 		Radial basis functions & RBF & SMT & 3 \\

### 2020-04-22 final_report/data.tex
add some references
intermediate replacement of the AE plots, some minor edits

@@
 
-Autoencoders are a family of approaches to feature extraction driven by neural
+Autoencoders~\cite{SCHMIDHUBER201585} are a family of approaches to feature extraction driven by neural
 networks. Faced with many possible alternatives, we implemented a conventional
@@
 
-This approach was applied to two sets of samples: (i) a subset of data obtained
+This approach was applied to two sets\footnote{Each set contained
+\num{100000}~samples from batches 0-99 of the corresponding runs.} of samples: (i) a subset of data obtained
 from run~1 and (ii) a subset of a single slice obtained from run~2. Our
-expectation was that while the former case would provide meaningful insight into
+expectation was that while the former case would provide meaningful insights into
 correlations within the feature space, the latter would validate our
 autoencoder implementation by analysing a set of points that are trivially
-reducible due to a number of fixed features.
+reducible due to a number of fixed discrete features.
 
-\begin{wrapfigure}{l}{0.4\textwidth}
+\begin{wrapfigure}{l}{0.4\textwidth} % TODO: regenerate both plots as described
 	\centering
 	\vspace{-1ex}
-	% TODO: placeholders only, regenerate when time is available
 	\begin{subfigure}[b]{\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{ae_all_slices}
+		\includegraphics[width=\linewidth,trim={0 48px 0 0},clip]{ae_mixed}
 	\end{subfigure}
+
+	\vspace{-0.2ex}
+
 	\begin{subfigure}[b]{\linewidth}
-		\centering
 		\includegraphics[width=\linewidth]{ae_single_slice}
 	\end{subfigure}
-	\caption{Autoencoder loss in two considered cases of dimensional reduction.}
+
+	\caption{Autoencoder loss scan on the full feature space (top) and a single slice
+		(bottom). Dimensional reduction is indicated by a green arrow.}
 	\label{fig:autoencoder-loss}
@@
 Consistent with our motivation, in each plot we can clearly identify a constant
-plateau in the region of large dimensionality followed by a point, from which a
-steep increase in loss is observed towards lower dimension counts. We consider
-this critical point to correspond with the largest viable dimensional reduction
-without significant information loss.
-With this methodology we find that the autoencoder was able to reduce the
-datasets into a subspace of 17~dimensions in the first case and 10~dimensions in
+plateau of low error in the region of large dimensionality followed by a point,
+from which a steep increase is observed.
+We consider this \textit{critical point} to mark the largest viable
+dimensional reduction without significant information loss.
+With this approach we find that the autoencoder was able to reduce the
+datasets into a subspace of 18~dimensions in the first case and 10~dimensions in
 the second case.
@@
 Confirming our expectation that in the latter, trivially reducible case the
-autoencoder should achieve stricter dimensional reduction, we are
-encouraged to believe that our implementation is indeed efficient. However, we
+autoencoder should achieve greater dimensional reduction, we are inclined to
+believe that our implementation is indeed efficient. However, we
 must also conclude that in both examined cases this method failed to produce a
-reduction that would be dominate a naïve approach, in which we eliminate
-7~dimensions due to overdetermined one-hot-encoded features, 2~dimensions due to
-sum-to-one constraints, and in the latter case 7~additional dimensions due to
-artificially fixed features. This supports the findings from PCA as well as the
+reduction that would be superior to a naïve approach.\footnote{In both tested cases we
+	can trivially eliminate 7~dimensions due to overdetermined one-hot-encoded
+	features and 2~dimensions due to sum-to-one constraints. Furthermore, in the
+	single slice case we may omit 7~additional dimensions due to artificially fixed
+features.} This supports the findings from PCA as well as the
 presented semivariograms.

### 2020-04-22 final_report/data.tex
add some TODOs and sklearn ref

@@
 
+% TODO: here maybe mention desirable effects of dim. red. (e.g. speedup,
+% simplification of the problem, better convergence...)
+
 Model training over high-dimensional parameter spaces may be facilitated by carefully reducing the number of variables used to describe the space.
@@
 
-To pursue linear feature extraction, principal component analysis (PCA) \cite{Jolliffe2016} was performed via scikit-learn on a set of 300,000 uniform samples of the MC TBR model.
+To pursue linear feature extraction, principal component analysis (PCA)
+\cite{Jolliffe2016} was performed via SciKit Learn~\cite{scikit-learn} on a set
+of \num{300000} uniform samples of the MC TBR model. % TODO:which run? batch range?
 

### 2020-04-22 final_report/data.tex
more edits to the autoencoder section

@@
 
+% TODO: in results, we feature both Kriging and GPR with differing results -
+% clarify their interchangeability here
+
 Kriging, or Gaussian process regression, is a geostatistical surrogate modelling technique which relies on correlation functions over distance (lag) in the paramater space \cite{Bouhlel2018}.
@@
 
-Figure \cref{fig:var} shows the Matheron semivariance \cite{Matheron1963} for three discrete slices with coolant material varied, but all other discrete parameters fixed.
+\Cref{fig:var} shows the Matheron semivariance \cite{Matheron1963} for three discrete slices with coolant material varied, but all other discrete parameters fixed.
 Fits \cite{KrigingFig} to the Matérn covariance model confirmed numerically that the coolant material is the discrete parameter with the greatest distinguishability in the MC TBR model.
@@
 network are sized to accommodate the analysed dataset, the
-hidden layer---also called the bottleneck---allows for variable number of
+hidden layer, also called the bottleneck, allows for variable number of
 neurons that represent a smaller subspace. By scanning
@@
 
-This approach was applied to two sets\footnote{Each set contained
+In particular, we consider two equally-sized sets\footnote{Each set contained
 \num{100000}~samples from batches 0-99 of the corresponding runs.} of samples: (i) a subset of data obtained
@@
 autoencoder should achieve greater dimensional reduction, we are inclined to
-believe that our implementation is indeed efficient. However, we
+believe that our implementation is indeed operating as intended. However, we
 must also conclude that in both examined cases this method failed to produce a
@@
 	single slice case we may omit 7~additional dimensions due to artificially fixed
-features.} This supports the findings from PCA as well as the
-presented semivariograms.
+features.} This is consistent with previous results obtained by PCA and kriging.
 

### 2020-04-22 final_report/data.tex
Image arranging.

--- 2020-04-22 final_report/data.tex
@@
 		\toprule
-		{} & Parameter name & Acronym & Type & Domain & Description\\
+		{} & Parameter Name & Acronym & Type & Domain & Description\\
 		\midrule
@@
 
-Autoencoders~\cite{SCHMIDHUBER201585} are a family of approaches to feature extraction driven by neural
+Autoencoders are a family of approaches to feature extraction driven by neural
 networks. Faced with many possible alternatives, we implemented a conventional
@@
 
-This approach was applied to two sets\footnote{Each set contained
-\num{100000}~samples from batches 0-99 of the corresponding runs.} of samples: (i) a subset of data obtained
+This approach was applied to two sets of samples: (i) a subset of data obtained
 from run~1 and (ii) a subset of a single slice obtained from run~2. Our
-expectation was that while the former case would provide meaningful insights into
+expectation was that while the former case would provide meaningful insight into
 correlations within the feature space, the latter would validate our
 autoencoder implementation by analysing a set of points that are trivially
-reducible due to a number of fixed discrete features.
+reducible due to a number of fixed features.
 
-\begin{wrapfigure}{l}{0.4\textwidth} % TODO: regenerate both plots as described
+\begin{wrapfigure}{l}{0.4\textwidth}
 	\centering
 	\vspace{-1ex}
+	% TODO: placeholders only, regenerate when time is available
 	\begin{subfigure}[b]{\linewidth}
-		\includegraphics[width=\linewidth,trim={0 48px 0 0},clip]{ae_mixed}
+		\centering
+		\includegraphics[width=\linewidth]{ae_all_slices}
 	\end{subfigure}
-
-	\vspace{-0.2ex}
-
 	\begin{subfigure}[b]{\linewidth}
+		\centering
 		\includegraphics[width=\linewidth]{ae_single_slice}
 	\end{subfigure}
-
-	\caption{Autoencoder loss scan on the full feature space (top) and a single slice
-		(bottom). Dimensional reduction is indicated by a green arrow.}
+	\caption{Autoencoder loss in two considered cases of dimensional reduction.}
 	\label{fig:autoencoder-loss}
@@
 Consistent with our motivation, in each plot we can clearly identify a constant
-plateau of low error in the region of large dimensionality followed by a point,
-from which a steep increase is observed.
-We consider this \textit{critical point} to mark the largest viable
-dimensional reduction without significant information loss.
-With this approach we find that the autoencoder was able to reduce the
-datasets into a subspace of 18~dimensions in the first case and 10~dimensions in
+plateau in the region of large dimensionality followed by a point, from which a
+steep increase in loss is observed towards lower dimension counts. We consider
+this critical point to correspond with the largest viable dimensional reduction
+without significant information loss.
+With this methodology we find that the autoencoder was able to reduce the
+datasets into a subspace of 17~dimensions in the first case and 10~dimensions in
 the second case.
@@
 Confirming our expectation that in the latter, trivially reducible case the
-autoencoder should achieve greater dimensional reduction, we are inclined to
-believe that our implementation is indeed efficient. However, we
+autoencoder should achieve stricter dimensional reduction, we are
+encouraged to believe that our implementation is indeed efficient. However, we
 must also conclude that in both examined cases this method failed to produce a
-reduction that would be superior to a naïve approach.\footnote{In both tested cases we
-	can trivially eliminate 7~dimensions due to overdetermined one-hot-encoded
-	features and 2~dimensions due to sum-to-one constraints. Furthermore, in the
-	single slice case we may omit 7~additional dimensions due to artificially fixed
-features.} This supports the findings from PCA as well as the
+reduction that would be dominate a naïve approach, in which we eliminate
+7~dimensions due to overdetermined one-hot-encoded features, 2~dimensions due to
+sum-to-one constraints, and in the latter case 7~additional dimensions due to
+artificially fixed features. This supports the findings from PCA as well as the
 presented semivariograms.

### 2020-04-22 final_report/methodology.tex
minor edits
Complete draft of adaptive sampling results section.

@@
 		{\scriptsize \incfigscale{0.6}{3pyramid}}
-		\caption{$\text{3pyr}(W)$}
+		\caption{$\text{3pyramid}(W)$}
 	\end{subfigure}\hfill%
@@
 		{\scriptsize \incfigscale{0.6}{5diam}}
-		\caption{$\text{5diam}(W)$}
+		\caption{$\text{5diamond}(W)$}
 	\end{subfigure}
@@
 
-We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS) to iteratively increment the training/test set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) \cite{Solonen2012} in parameter space.
+We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, Figure \label{fig:qassplan}) to iteratively increment the training/test set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) \cite{Solonen2012} in parameter space.
 On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and AE calculated.
@@
 
-ADD FIG REFERENCE
-
 % Adaptive multi-chain MCMC: \cite{Zhang2012}

### 2020-04-22 final_report/results.tex
Updated citations and image wrapping.
Complete draft of adaptive sampling results section.

@@
 	\label{fig:exp2-time-vs-reg}
+	\vspace{-4ex}
 \end{wrapfigure}
@@
 
+\begin{wrapfigure}{r}{0.4\textwidth}
+  \vspace{-60pt}
+  \begin{center}
+    \includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
+	\caption{Sinusoidal toy TBR model with two continuous parameters, wavenumber 1}
+    \label{fig:sintoy}
+  \end{center}
+  \vspace{-30pt}
+\end{wrapfigure}
+
 \subsection{Results of Adaptive Sampling}
@@
 
-Define sinusoidal toy model and justify
+In order to test our QASS prototype, several functional toy theories for TBR were developed as alternatives to the expensive MC model.
+By far the most robust of these was the following sinusoidal theory with adjustable wavenumber parameter $n$:
 
-Explain hyperparameter tests: initsamples, stepsamples, MCMC length
+\begin{equation}
+    TBR = mean_{i \in C} \left[ \frac{1 + sin(2*pi*n*(x_i - 1/2)) }{2} \right]
+\end{equation}
 
-\begin{figure}[h]
+plotted in Figure \ref{fig:sintoy} for $n=1$ and two continuous parameters $C$.
+ANNs trained on this model demonstrated similar performance to those on the expensive MC model.
+QASS performance was verified by training a 1h3f-256 ANN on the sinusoidal theory for varied quantities of initial, incremental, and MCMC candidate samples.
+Although the scope of this project did not include thorough searches of this hyperparameter domain, sufficient runs were made to identify some likely trends.
+
+An increase in MCMC candidate samples was seen to have a positive but very weak effect on final surrogate precision, suggesting that the runtime of MCMC on each iteration can be limited for increased efficiency.
+-- Awaiting test results on initial sample quantity --.
+The most complex dynamics arose with the adjustment of sample increment, shown in Figure \ref{fig:qassincr}.
+For each tested initial sample quantity N, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$; the plotted error trends suggest that incremental samples larger than this optimum give slower model improvement on both the training and evaluation sets, and a larger minimum error on the evaluation set.
+This performance distinction is predicted to be even more significant when trained on the expensive MC model, where the number of sample evaluations will serve as the primary bottleneck for computation time.
+\begin{figure}[h!]
     \centering
@@
         \centering
-        \includegraphics[width=1.1\linewidth]{fig5_qassincrsamp.png}
-        \caption{QASS absolute training error over total sample quantity}
+        \includegraphics[width=1.1\linewidth]{fig6a_qassincrsamp.pdf}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=1.1\linewidth]{fig6_qassincrtime.png}
-        \caption{QASS absolute training error over number of iterations}
+        \includegraphics[width=1.1\linewidth]{fig6b_qassincrtime.pdf}
     \end{subfigure}
-    \caption{Caption place holder}
+    \caption{QASS absolute training error over total sample quantity (left) and number of iterations (right).
+MAE represents surrogate error on the adaptively-sampled training/test set, and E\_MAE on the independent evaluation sets.}
+    \label{fig:qassincr}
 \end{figure}
+
+The plateau effect in surrogate error on the evaluation set, seen in Figure \ref{fig:qassincr}, was universal to all configurations and thought to warrant further investigation.
+At first this was suspected to be a residual effect of retraining the same ANN instance without adjustment to data normalisation; a "Goldilocks scheme" for checking normalisation drift was implemented and tested, but did not affect QASS performance.
+Schemes in which the ANN is periodically retrained were also discarded, as the retention of network weights from one iteration to the next was demonstrated to greatly benefit QASS efficiency.
+Further insight came from direct comparison between QASS and a baseline scheme with uniformly random incremental samples, shown in Figure \ref{fig:qasssampling}.
 
@@
   \centering
-    \includegraphics[width=0.8\linewidth]{fig7_qasssampling.png}
+    \includegraphics[width=0.8\linewidth]{fig7_qasssampling.pdf}
     \caption{Absolute training error for QASS, uniform random scheme, and mixed scheme}
-  \label{fig:pca}
+  \label{fig:qasssampling}
 \end{figure}
+
+Such tests revealed that while QASS has unmatched performance on its own adaptively-sampled training set, it is outperformed by the baseline scheme on uniformly random evaluation sets.
+We suspected that while QASS excels in learning the most strongly peaked regions of the TBR theory, this comes at the expense of precision in broader, smoother regions where uniformly random sampling suffices.
+Therefore a mixed scheme was implemented, with half MCMC samples and half uniformly random samples incremented on each iteration, and is also shown in Figure \ref{fig:qasssampling}.

### 2020-04-22 final_report/sinmodel_TBR.m

@@ -1,0 +1,17 @@
+wn=1
+
+f=@(x,y) sin(wn*2*pi*(x-0.5))/2 + sin(wn*2*pi*(y-0.5))/2 + 1;
+[X,Y]=meshgrid(0:0.001:1);
+z=f(X,Y);
+[C,h] = contourf(X,Y,z,9);   
+clabel(C,h,'FontSize',15)
+set(gca,'fontsize', 24)
+
+set(gca,'xtick',[0,1])
+set(gca,'xticklabel',[0,1])
+
+set(gca,'ytick',[0,1])
+set(gca,'yticklabel',[0,1])
+
+xlabel('Continuous parameter A')
+ylabel('Continuous parameter B')

### 2020-04-22 final_report/data.tex
Remove URLS and DOI from visible bibliography.

--- 2020-04-22 final_report/data.tex
@@
 
-Kriging, or Gaussian process regression, is a geostatistical surrogate modelling technique which relies on correlation functions over distance (lag) in the paramater space \cite{Bouhlel2018}.
+Kriging is a geostatistical surrogate modelling technique which relies on correlation functions over distance (lag) in the paramater space \cite{Bouhlel2018}.
 Although kriging performed poorly for our use case due to high dimensionality, these correlation measures gave insight into similarities between discrete-parameter slices of the data.

### 2020-04-22 final_report/methodology.tex
Remove URLS and DOI from visible bibliography.

@@
 We theorised that a nondeterministic sample generation approach, built around Markov Chain Monte Carlo methods (MCMC), would fare better for high-dimensional models by more thoroughly exploring all local optima in the parameter space.
-MCMC produces a progressive chain of sample points, each drawn according to the same symmetric proposal distribution from the prior point.
+MCMC produces a progressive chain of sample points, each drawn according to the same symmetric proposal distribution\footnote{An adaptive MCMC procedure \cite{Zhang2012}, which adjusts an ellipsoidal proposal distribution to fit the posterior, was also implemented but not fully tested.} from the prior point.
 These sample points will converge to a desired posterior distribution, so long as the acceptance probability for these draws has a particular functional dependence on that posterior value (see \cite{Zhou2018} for a review).
@@
 
-We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, Figure \label{fig:qassplan}) to iteratively increment the training/test set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) \cite{Solonen2012} in parameter space.
+We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, \cref{fig:qassplan}) to iteratively increment the training/test set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) \cite{Solonen2012} in parameter space.
 On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and AE calculated.

### 2020-04-22 final_report/results.tex
Remove URLS and DOI from visible bibliography.

@@
     \includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
-	\caption{Sinusoidal toy TBR model with two continuous parameters, wavenumber 1}
+	\caption{Sinusoidal toy TBR theory over two continuous parameters, wavenumber 1}
     \label{fig:sintoy}
@@
     \includegraphics[width=0.8\linewidth]{fig7_qasssampling.pdf}
-    \caption{Absolute training error for QASS, uniform random scheme, and mixed scheme}
+    \caption{Absolute training error for QASS, baseline scheme, and mixed scheme}
   \label{fig:qasssampling}
@@
 We suspected that while QASS excels in learning the most strongly peaked regions of the TBR theory, this comes at the expense of precision in broader, smoother regions where uniformly random sampling suffices.
-Therefore a mixed scheme was implemented, with half MCMC samples and half uniformly random samples incremented on each iteration, and is also shown in Figure \ref{fig:qasssampling}.
+Therefore a mixed scheme was implemented, with half MCMC samples and half uniformly random samples incremented on each iteration, which is also shown in Figure \ref{fig:qasssampling}.

### 2020-04-22 final_report/methodology.tex
harmonize references in favour of \cref

@@
 In our experiments, we evaluate and compare surrogates in effort to
-optimise against metrics described in \cref{sec:metrics}. To attain meaningful
+optimise against metrics described in~\cref{sec:metrics}. To attain meaningful
 and practically usable results, we require a sufficiently large and diverse pool
-of surrogate classes to draw from. This is described by the listing in
-\cref{tbl:surrogates}. The presented selection of models includes basic
+of surrogate classes to draw from. This is described by the listing in~\cref{tbl:surrogates}. The presented selection of models includes basic
 techniques suitable for linear regression enhanced by the kernel trick or dimension
@@
 latter, a host of parametric graphs are defined to realise simplistic network
-architecture search (see \cref{fig:nn-archs} for details). Discrimination
+architecture search (see~\cref{fig:nn-archs} for details). Discrimination
 between such options is considered an additional hyperparameter of the

### 2020-04-22 final_report/results.tex
harmonize references in favour of \cref

@@
 
-plotted in Figure \ref{fig:sintoy} for $n=1$ and two continuous parameters $C$.
+plotted in~\cref{fig:sintoy} for $n=1$ and two continuous parameters $C$.
 ANNs trained on this model demonstrated similar performance to those on the expensive MC model.
@@
 
-An increase in MCMC candidate samples was seen to have a positive but very weak effect on final surrogate precision, suggesting that the runtime of MCMC on each iteration can be limited for increased efficiency.
--- Awaiting test results on initial sample quantity --.
-The most complex dynamics arose with the adjustment of sample increment, shown in Figure \ref{fig:qassincr}.
+An increase in MCMC candidate samples was seen to have a positive but very weak
+effect on final surrogate precision, suggesting that the runtime of MCMC on each
+iteration can be limited for increased efficiency. -- Awaiting test results on
+initial sample quantity --. The most complex dynamics arose with the adjustment
+of sample increment, shown in~\cref{fig:qassincr}.
 For each tested initial sample quantity N, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$; the plotted error trends suggest that incremental samples larger than this optimum give slower model improvement on both the training and evaluation sets, and a larger minimum error on the evaluation set.
@@
 
-The plateau effect in surrogate error on the evaluation set, seen in Figure \ref{fig:qassincr}, was universal to all configurations and thought to warrant further investigation.
-At first this was suspected to be a residual effect of retraining the same ANN instance without adjustment to data normalisation; a "Goldilocks scheme" for checking normalisation drift was implemented and tested, but did not affect QASS performance.
-Schemes in which the ANN is periodically retrained were also discarded, as the retention of network weights from one iteration to the next was demonstrated to greatly benefit QASS efficiency.
-Further insight came from direct comparison between QASS and a baseline scheme with uniformly random incremental samples, shown in Figure \ref{fig:qasssampling}.
+The plateau effect in surrogate error on the evaluation set, seen
+in~\cref{fig:qassincr}, was universal to all configurations and thought to
+warrant further investigation. At first this was suspected to be a residual
+effect of retraining the same ANN instance without adjustment to data
+normalisation; a "Goldilocks scheme" for checking normalisation drift was
+implemented and tested, but did not affect QASS performance. Schemes in which
+the ANN is periodically retrained were also discarded, as the retention of
+network weights from one iteration to the next was demonstrated to greatly
+benefit QASS efficiency. Further insight came from direct comparison between
+QASS and a baseline scheme with uniformly random incremental samples, shown
+in~\cref{fig:qasssampling}.
 
@@
 
-Such tests revealed that while QASS has unmatched performance on its own adaptively-sampled training set, it is outperformed by the baseline scheme on uniformly random evaluation sets.
-We suspected that while QASS excels in learning the most strongly peaked regions of the TBR theory, this comes at the expense of precision in broader, smoother regions where uniformly random sampling suffices.
-Therefore a mixed scheme was implemented, with half MCMC samples and half uniformly random samples incremented on each iteration, which is also shown in Figure \ref{fig:qasssampling}.
+Such tests revealed that while QASS has unmatched performance on its own
+adaptively-sampled training set, it is outperformed by the baseline scheme on
+uniformly random evaluation sets. We suspected that while QASS excels in
+learning the most strongly peaked regions of the TBR theory, this comes at the
+expense of precision in broader, smoother regions where uniformly random
+sampling suffices. Therefore a mixed scheme was implemented, with half MCMC
+samples and half uniformly random samples incremented on each iteration, which
+is also shown in~\cref{fig:qasssampling}.

### 2020-04-22 final_report/data.tex
harmonize references in favour of \cref
minor edits to data

@@
 The MC TBR model that we understand to be the expensive function for our
-surrogate modelling is fundamentally a Monte Carlo simulation based on the OpenMC
-framework. At input the software expects a set of 19~parameters, discrete and
+surrogate modelling is fundamentally a Monte Carlo simulation based on the
+OpenMC framework~\cite{ROMANO201590}. At input the software expects a set of 19~parameters, discrete and
 continuous, that are fully listed in~\cref{tbl:params}. Following a brief period of
-time (usually on the order of tens of seconds), during which a fixed number of events is simulated, the software outputs the
+time (usually on the order of tens of seconds), during which a fixed number of
+events is generated, the simulation outputs the
 mean and the standard deviation of the TBR aggregated over the simulated run. The
-former of these two outputs we accept to be the output TBR value that is subject
+former of these two we accept to be the output TBR value that is subject
 to approximation.
@@
 studying its behaviour are limited to inspection of its outputs at various
-points in the feature space, and inference thereof. We thus require to
-gather sufficiently large and representative quantities of samples to ensure
+points in the feature space, and inference thereof. We thus require
+sufficiently large and representative quantities of samples to ensure
 statistical significance of our findings.
 
-With grid search in high-dimensional domain clearly intractable, we decided to
-implement uniform pseudo-random sampling to generate large amounts of feature
+With grid search in high-dimensional domain clearly intractable, we
+selected uniform pseudo-random sampling to generate large amounts of feature
 configurations that we consider to be independent and unbiased. For evaluation
@@
 the HPC infrastructure available at UCL computing facilities. To this end, we
-implemented the Approximate TBR Evaluator---a Python software package capable of
+designed and implemented the Approximate TBR Evaluator---a Python software package capable of
 sequential evaluation of the multi-threaded OpenMC simulation on batches of
@@
 
-Since some methods applied in this work are not scale-invariant or
-perform suboptimally when presented with arbitrarily scaled problems, all results
-produced in the sampling runs were standardised prior to further use. In this
-commonly used statistical procedure, features and regression outputs are
-independently scaled and offset to attain zero mean and unit variance.
+Since some surrogate modelling methods applied in this work are not scale-invariant or
+perform suboptimally with arbitrarily scaled problems, all run results
+were standardised prior to further use. In this commonly used statistical
+procedure, features and regression outputs are independently scaled and offset
+to attain zero mean and unit variance.
 
@@
 
-Model training over high-dimensional parameter spaces may be facilitated by carefully reducing the number of variables used to describe the space.
+Model training over high-dimensional parameter spaces may be improved in many
+aspects by carefully reducing the number of variables used to describe the space.
 For many applications, feature selection strategies succeed in identifying a sufficiently representative subset of the original input variables; however, all given variables were assumed to be physically relevant to the MC TBR model.
@@
 
-Figure \cref{fig:pca} shows the resultant cumulative variance of the feature vectors identified by PCA.
-The similar share of variance among all eleven features demonstrated irreducibility of the TBR model by linear methods.
+\Cref{fig:pca} shows the resultant cumulative variance of the feature vectors
+identified by PCA. The similar share of variance among all eleven features
+demonstrates irreducibility of the TBR model by linear methods.
 
@@
 
-Kriging is a geostatistical surrogate modelling technique which relies on correlation functions over distance (lag) in the paramater space \cite{Bouhlel2018}.
+Kriging is a geostatistical surrogate modelling technique which relies on
+correlation functions over distance (lag) in the feature space \cite{Bouhlel2018}.
 Although kriging performed poorly for our use case due to high dimensionality, these correlation measures gave insight into similarities between discrete-parameter slices of the data.
@@
 
-Autoencoders~\cite{SCHMIDHUBER201585} are a family of approaches to feature extraction driven by neural
-networks. Faced with many possible alternatives, we implemented a conventional
+Autoencoders~\cite{SCHMIDHUBER201585} are a family of approaches to
+dimensionality reduction driven by neural
+networks. Faced with many possible alternatives, we utilised a conventional
 autoencoder, which relies on a three-layer network that is trained to replicate
@@
 network are sized to accommodate the analysed dataset, the
-hidden layer, also called the bottleneck, allows for variable number of
+hidden layer, also called \textit{the bottleneck}, allows for variable number of
 neurons that represent a smaller subspace. By scanning
@@
 autoencoder implementation by analysing a set of points that are trivially
-reducible due to a number of fixed discrete features.
+reducible in dimensionality due to a number of fixed discrete features.
 
@@
 
-Confirming our expectation that in the latter, trivially reducible case the
+Confirming our expectation that in the latter, trivial case the
 autoencoder should achieve greater dimensional reduction, we are inclined to

### 2020-04-22 final_report/methodology.tex
minor edits to methodology

@@
-Assuming that input has been appropriately treated to eliminate redundant
-features, we may turn to characterise proposed surrogate models and the criteria
+Assuming that data is appropriately treated to eliminate redundant
+features, we proceed to propose surrogate models and criteria
 used for their evaluation. The task all presented surrogates strive to solve can be
-formulated using the language of conventional regression problems. In the scope
-of this work, we explore various possible choices available to us in the
-scheme of supervised and unsupervised learning.
+formulated using the language of conventional regression problems. In this section,
+we focus on interpretation in the scheme of supervised and unsupervised learning.
 
-Labeling the expensive Monte Carlo simulation $f(x)$, a surrogate is a mapping
+Labeling the expensive MC TBR model $f(x)$, a surrogate is a mapping
 $\hat{f}(x)$ that yields similar images as $f(x)$. In other words, $f(x)$ and
@@
 be considered \textit{viable}, surrogates are required to achieve expected evaluation time
-that does not exceed the expected evaluation time of $f(x)$.
+lower than that of $f(x)$.
 
@@
 $\mathcal{T}_k$. This permits the learning algorithm to condition the selection
-of new samples by the results of evaluation in order to focus on improvement of
-surrogate performance in complex regions within the domain.
+of new samples on the evaluation results in order to maximise improvement of
+surrogate performance over complex regions within the domain.
 
@@
 Following the motivation of this work, two desirable properties of surrogates
-arise: (i) their capability to approximate the expensive
-model well and (ii) their time of evaluation. An ideal surrogate would maximise
+arise: (i) their capability to approximate the TBR MC model well and (ii) their time of evaluation. An ideal surrogate would maximise
 the former while minimising the latter.
@@
 For analysis of evaluation time, surrogates are assessed in terms of wall time
-elapsed during training and predicition. This closely models the practical use
-case, in which they are trained and used as drop-in replacements for the
-expensive model. Since training set sizes remain to be determined, all times are
+elapsed during training and predicition. This is motivated by common practical use
+cases of our work, where models are trained and used as drop-in replacements for the
+expensive MC TBR model. Since training set sizes remain to be determined, all times are
 reported per a single sample. Even though some surrogates support acceleration
 by means of parallelisation, measures were taken to ensure sequential
-processing of samples to achieve comparability between considered models.
+processing of samples to achieve comparability between considered
+models.\footnote{The only exception to this are artificial neural networks, which are
+notoriously slow to train on conventional CPU architectures in serialised
+setting.}
 
@@
 repeatedly interpreted as training and testing sets, maintaining a constant
-ratio of samples between the two. In each such interpretation experiments are
-repeated, and the overall value of each metric of interest is reported as the
-mean across all folds.
+ratio of samples between the two.\footnote{Unless explicitly stated otherwise, we use 1
+fold for testing and the $k-1$ remaining folds for training. This gives 80\% to
+20\% train-test ratio.} In each such interpretation experiments are
+repeated, and the overall value of each metric is reported as the mean across all folds.
 
@@
 
-In some rows of the table, a single class in reality represents a multitude of
-fundamentally similar approaches. Good examples of this are kriging methods and neural
+In some rows of~\cref{tbl:surrogates}, a single class in reality represents a
+family of fundamentally similar approaches. Good examples of this are kriging methods and neural
 networks. In the case of the former, multiple algorithms such as kriging based on
@@
 		the last use ReLU activation. Prediction information flow is indicated by
-		arrows. Conections between neurons are omitted for clarity.}
+		arrows. Connections between neurons are omitted for clarity.}
 	\label{fig:nn-archs}
@@
 
-The presented surrogate candidates are evaluated in four experimental cases:
-
+The presented surrogate candidates are evaluated in four experimental cases:%
 \begin{enumerate}
-
 	\item Hyperparameter tuning in simplified domain,
@@
 searches of a possibly high-dimensional parameter space, Bayesian
-optimisation is employed as standard hyperparameter tuning algorithm that is considered
-efficient for this purpose. We set its objective to maximise $R^2$.
+optimisation is employed as a standard hyperparameter tuning algorithm. We set
+its objective to maximise $R^2$ and perform 1000~iterations.\footnote{Tuning of
+	each surrogate class was artificially terminated after 2~days. Instances
+	which reached this limit are marked in the results.}
+
+% TODO: mark instances that timed out in results
 
@@
 replicated at large scale by decomposing the TBR domain into continuous subsets,
-and learning ensemble surrogate comprised of models that are trained on each
+and learning ensemble surrogate comprised of identical models that are trained on each
 subset independently, incurring exponential complexity penalty in the process.
-To this end, training samples are filtered to only contain a single assignment
-of discrete features that are subsequently completely withheld from evaluated
-surrogates. This is repeated four times to investigate variance in behaviour
-under different feature assignments.
+To this end, data are limited to a single slice from run~2, and discrete
+features are completely withheld from evaluated
+surrogates. This is repeated for each of the four available slices to
+investigate variance in behaviour under different discrete feature assignments.
 
 The second experiment conventionally measures surrogate performance on the full
-TBR regression task. In extension of the previous case, surrogates work with
-unfiltered samples comprised of discrete as well as continuous features.
+feature space. Here, in extension of the previous case, surrogates work with
+samples comprised of discrete as well as continuous features.
 
@@
 hyperparameter tuning for study of scaling properties. In
-the third experiment, the best-performing hyperparameter choices of each class
-are used to learn surrogates using progressively larger training sets. Following
+the third experiment, 20~best-performing hyperparameter choices of each class
+(in $R^2$) are used to learn surrogates using progressively larger training sets. Following
 that, the fourth experiment attempts to produce competitive surrogates by
@@
 
-All of the surrogate modelling techniques studied in this project face a shared challenge: their accuracy is limited by the quantity of training samples which are available from the expensive MC model.
-Adaptive sampling procedures can improve upon this limitation by taking advantage of statistical information which is accumulated during the training of any surrogate model.
-Rather than training the surrogate on a single sample set generated according to a fixed strategy, sample locations are chosen incrementally so as to best suit the model under consideration.
+All of the surrogate modelling techniques studied in this project face a shared
+challenge: their accuracy is limited by the quantity of training samples which
+are available from the expensive MC TBR model. Adaptive sampling procedures can
+improve upon this limitation by taking advantage of statistical information
+which is accumulated during the training of any surrogate model. Rather than
+training the surrogate on a single sample set generated according to a fixed
+strategy, sample locations are chosen incrementally so as to best suit the model
+under consideration.
 
-Adaptive sampling techniques are widespread in the literature and have been specialised for surrogate modelling.
-Garud's \cite{Garud2016} "Smart Sampling Algorithm" achieved notable success by incorporating surrogate quality and crowding distance scoring to identify optimal new samples, but was only tested on a single-parameter domain.
-We theorised that a nondeterministic sample generation approach, built around Markov Chain Monte Carlo methods (MCMC), would fare better for high-dimensional models by more thoroughly exploring all local optima in the parameter space.
-MCMC produces a progressive chain of sample points, each drawn according to the same symmetric proposal distribution\footnote{An adaptive MCMC procedure \cite{Zhang2012}, which adjusts an ellipsoidal proposal distribution to fit the posterior, was also implemented but not fully tested.} from the prior point.
-These sample points will converge to a desired posterior distribution, so long as the acceptance probability for these draws has a particular functional dependence on that posterior value (see \cite{Zhou2018} for a review).
+Adaptive sampling techniques are widespread in the literature and have been
+specialised for surrogate modelling. Garud's \cite{Garud2016} "Smart Sampling
+Algorithm" achieved notable success by incorporating surrogate quality and
+crowding distance scoring to identify optimal new samples, but was only tested
+on a single-parameter domain. We theorised that a nondeterministic sample
+generation approach, built around Markov Chain Monte Carlo methods (MCMC), would
+fare better for high-dimensional models by more thoroughly exploring all local
+optima in the feature space. MCMC produces a progressive chain of sample points,
+each drawn according to the same symmetric proposal distribution\footnote{An
+adaptive MCMC procedure \cite{Zhang2012}, which adjusts an ellipsoidal proposal
+distribution to fit the posterior, was also implemented but not fully tested.}
+from the prior point. These sample points will converge to a desired posterior
+distribution, so long as the acceptance probability for these draws has a
+particular functional dependence on that posterior value (see \cite{Zhou2018}
+for a review).
 
-Many researchers have embedded surrogate methods into MCMC strategies for parameter optimisation \cite{Zhang2020}\cite{Gong2017}, in particular the ASMO-PODE algorithm \cite{Ginting2011} which makes use of MCMC-based adaptive sampling to attain greater surrogate precision around prospective optima.
-Our novel approach draws inspiration from ASMO-PODE, but instead uses MCMC to generate samples which increase surrogate precision throughout the entire parameter space.
+Many researchers have embedded surrogate methods into MCMC strategies for
+parameter optimisation \cite{Zhang2020,Gong2017}, in particular the ASMO-PODE
+algorithm \cite{Ginting2011} which makes use of MCMC-based adaptive sampling to
+attain greater surrogate precision around prospective optima. Our novel approach
+draws inspiration from ASMO-PODE, but instead uses MCMC to generate samples
+which increase surrogate precision throughout the entire parameter space.
 
@@
 
-We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, \cref{fig:qassplan}) to iteratively increment the training/test set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) \cite{Solonen2012} in parameter space.
+% TODO: explain AE
+
+We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS,
+\cref{fig:qassplan}) to iteratively increment the training/test set with sample
+points which maximise surrogate error and minimise a crowding distance metric
+(CDM) \cite{Solonen2012} in feature space.
 On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and AE calculated.

### 2020-04-22 final_report/results.tex
minor edits to results

@@
 cross-validated setting as a function of model hyperparameters. While in the
-first experiment we limit ourselves to the scope of a single slice of the
-domain, in the second experiment we extend the process to the full feature
-space.
+first experiment we limit training and testing sets to the scope of four slices of the
+feature space, in the second experiment we lift this restriction.
 
@@
 that, we note that extremely randomised trees, support vector machines and
-neural networks also achieved satisfactory results in both examined metrics.
+neural networks also achieved satisfactory results with respect to both examined metrics.
 While the remainder of tested surrogate classes does not exhibit problems in
@@
 methods based on decision trees and neural networks offer the best accuracy on
-larger sets overall. This is a curious extension of previous findings, where
+larger sets overall. This is a curious extension of the previous findings, where
 gradient boosted trees were observed to significantly dominate over the rest of
@@
 by instance-based learning methods, which seem to offer near-constant scaling
-characterists at the expense of significant performance increase later during
+characteristics at the expense of significant performance increase later during
 prediction. Following that, we observe that the majority of tree-based methods also exhibit
@@
 which are the only model to utilise parallelisation. As such, their constant
-synchronisation overhead overall hinders performance on small training sets,
+synchronisation overhead presumably hinders performance on small training sets,
 producing misleading results when divided by the number of samples.
@@
 	\end{subfigure}
-	\caption{Regression performance of the best models trained in experiment~4.}
+	\caption{Regression performance of selected best-performing models trained in experiment~4.}
 	\label{fig:reg-performance}
@@
 \begin{equation}
-    TBR = mean_{i \in C} \left[ \frac{1 + sin(2*pi*n*(x_i - 1/2)) }{2} \right]
+	\text{TBR} = \text{Mean}_{i \in C} \left[ \frac{1 + \sin(2\pi n (x_i - 1/2)) }{2} \right]
 \end{equation}
 
-plotted in~\cref{fig:sintoy} for $n=1$ and two continuous parameters $C$.
-ANNs trained on this model demonstrated similar performance to those on the expensive MC model.
-QASS performance was verified by training a 1h3f-256 ANN on the sinusoidal theory for varied quantities of initial, incremental, and MCMC candidate samples.
-Although the scope of this project did not include thorough searches of this hyperparameter domain, sufficient runs were made to identify some likely trends.
+plotted in~\cref{fig:sintoy} for $n=1$ and two continuous parameters $C$. ANNs
+trained on this model demonstrated similar performance to those on the expensive
+MC model. QASS performance was verified by training a $\text{1h3f}(256)$ ANN on
+the sinusoidal theory for varied quantities of initial, incremental, and MCMC
+candidate samples. Although the scope of this project did not include thorough
+searches of this hyperparameter domain, sufficient runs were made to identify
+some likely trends.
 

### 2020-04-22 final_report/methodology.tex
refer to NNs as ANNs

@@
 lifting, methods driven by decision trees, instance-based learning models,
-ensemble regressors, randomized algorithms, neural networks and mathematical approaches
+ensemble regressors, randomized algorithms, artificial neural networks and mathematical approaches
 developed specifically for the purposes of surrogate modelling. For each of
@@
 		$k$ nearest neighbours	& KNN & SciKit Learn & 3 \\
-		Neural networks	& NN & Keras (TensorFlow)~\cite{chollet2015keras} & 2 \\
+		Artificial neural networks	& ANN & Keras (TensorFlow)~\cite{chollet2015keras} & 2 \\
 		Inverse distance weighing & IDW & SMT~\cite{SMT2019} & 1 \\

### 2020-04-22 final_report/results.tex
refer to NNs as ANNs

@@
 that, we note that extremely randomised trees, support vector machines and
-neural networks also achieved satisfactory results with respect to both examined metrics.
+artificial neural networks also achieved satisfactory results with respect to both examined metrics.
 While the remainder of tested surrogate classes does not exhibit problems in
@@
 shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
-methods based on decision trees and neural networks offer the best accuracy on
+methods based on decision trees and artificial neural networks offer the best accuracy on
 larger sets overall. This is a curious extension of the previous findings, where
@@
 prediction. Following that, we observe that the majority of tree-based methods also exhibit
-desirable properties. The notable exception here appear to be neural networks,
+desirable properties. The notable exception here appear to be artificial neural networks,
 which are the only model to utilise parallelisation. As such, their constant

### 2020-04-22 final_report/conclusion.tex
fill in preliminary result points

---

---

From Petr:

\begin{enumerate}
	\item Generated 900K samples,
	\item Investigated possibilities for simplification: there appear to be no
		obvious ones,
	\item Reviewed $N$ surrogate models (fill in $N$), examined their behaviour
		on (un)constrained feature space and their scaling properties,
	\item Retrained some of the best-performing surrogates on large scale,
		achieved best accuracy $X$ and mean prediction time $X$, this amounts to
		relative speedup $X$ with respect to TBR MC model,
	\item All code is open-source; generated data, intermediate results and
		trained models are available online at $X$
\end{enumerate}

---

TODO: further work

\newpage

### 2020-04-22 final_report/conclusion.tex
Conclusion draft

@@
+Over the course of this internship project, we employed a broad spectrum of data analysis and machine learning techniques to develop fast and high-quality surrogate models for a MC TBR model in use at UKAEA.
 ---
@@
 ---
-
-From Petr:
-
-\begin{enumerate}
-	\item Generated 900K samples,
-	\item Investigated possibilities for simplification: there appear to be no
-		obvious ones,
-	\item Reviewed $N$ surrogate models (fill in $N$), examined their behaviour
-		on (un)constrained feature space and their scaling properties,
-	\item Retrained some of the best-performing surrogates on large scale,
-		achieved best accuracy $X$ and mean prediction time $X$, this amounts to
-		relative speedup $X$ with respect to TBR MC model,
-	\item All code is open-source; generated data, intermediate results and
-		trained models are available online at $X$
-\end{enumerate}
-
----
-
-TODO: further work
+After a thorough review of the literature, we developed a novel adaptive sampling algorithm, QASS, capable of interfacing with any of the individual studied models.
+Preliminary testing on a toy theory, qualitatively comparable to the MC TBR model, demonstrated the effectiveness of QASS and behavioral trends over its hyperparameters which are consistent with the design of the algorithm.
 

### 2020-04-22 final_report/results.tex
fill in preliminary result points
Conclusion draft

--- 2020-04-22 final_report/results.tex
@@
 
+\newpage
+
 \begin{wrapfigure}{r}{0.4\textwidth}
@@
 
-plotted in~\cref{fig:sintoy} for $n=1$ and two continuous parameters $C$.
+plotted in Figure \ref{fig:sintoy} for $n=1$ and two continuous parameters $C$.
 ANNs trained on this model demonstrated similar performance to those on the expensive MC model.
@@
 
-An increase in MCMC candidate samples was seen to have a positive but very weak
-effect on final surrogate precision, suggesting that the runtime of MCMC on each
-iteration can be limited for increased efficiency. -- Awaiting test results on
-initial sample quantity --. The most complex dynamics arose with the adjustment
-of sample increment, shown in~\cref{fig:qassincr}.
+An increase in MCMC candidate samples was seen to have a positive but very weak effect on final surrogate precision, suggesting that the runtime of MCMC on each iteration can be limited for increased efficiency.
+-- Awaiting test results on initial sample quantity --.
+The most complex dynamics arose with the adjustment of sample increment, shown in Figure \ref{fig:qassincr}.
 For each tested initial sample quantity N, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$; the plotted error trends suggest that incremental samples larger than this optimum give slower model improvement on both the training and evaluation sets, and a larger minimum error on the evaluation set.
@@
 
-The plateau effect in surrogate error on the evaluation set, seen
-in~\cref{fig:qassincr}, was universal to all configurations and thought to
-warrant further investigation. At first this was suspected to be a residual
-effect of retraining the same ANN instance without adjustment to data
-normalisation; a "Goldilocks scheme" for checking normalisation drift was
-implemented and tested, but did not affect QASS performance. Schemes in which
-the ANN is periodically retrained were also discarded, as the retention of
-network weights from one iteration to the next was demonstrated to greatly
-benefit QASS efficiency. Further insight came from direct comparison between
-QASS and a baseline scheme with uniformly random incremental samples, shown
-in~\cref{fig:qasssampling}.
+The plateau effect in surrogate error on the evaluation set, seen in Figure \ref{fig:qassincr}, was universal to all configurations and thought to warrant further investigation.
+At first this was suspected to be a residual effect of retraining the same ANN instance without adjustment to data normalisation; a ``Goldilocks scheme" for checking normalisation drift was implemented and tested, but did not affect QASS performance.
+Schemes in which the ANN is periodically retrained were also discarded, as the retention of network weights from one iteration to the next was demonstrated to greatly benefit QASS efficiency.
+Further insight came from direct comparison between QASS and a baseline scheme with uniformly random incremental samples, shown in Figure \ref{fig:qasssampling}.
 
@@
 
-Such tests revealed that while QASS has unmatched performance on its own
-adaptively-sampled training set, it is outperformed by the baseline scheme on
-uniformly random evaluation sets. We suspected that while QASS excels in
-learning the most strongly peaked regions of the TBR theory, this comes at the
-expense of precision in broader, smoother regions where uniformly random
-sampling suffices. Therefore a mixed scheme was implemented, with half MCMC
-samples and half uniformly random samples incremented on each iteration, which
-is also shown in~\cref{fig:qasssampling}.
+Such tests revealed that while QASS has unmatched performance on its own adaptively-sampled training set, it is outperformed by the baseline scheme on uniformly random evaluation sets.
+We suspected that while QASS excels in learning the most strongly peaked regions of the TBR theory, this comes at the expense of precision in broader, smoother regions where uniformly random sampling suffices.
+Therefore a mixed scheme was implemented, with half MCMC samples and half uniformly random samples incremented on each iteration, which is also shown in Figure \ref{fig:qasssampling}.

### 2020-04-22 final_report/data.tex
refer to NNs as ANNs
fill in preliminary result points
Conclusion draft
regenerate autoencoder plots (hopefully for the last time)

@@
 
+% TODO: find a way to mention average time per sample and std
+
 Skipping run zero, which was performed using older, fundamentally different
@@
 
+% TODO: tie the figure above to the paragraph above
+
 \subsubsection{Principal Component Analysis}
@@
 Autoencoders~\cite{SCHMIDHUBER201585} are a family of approaches to
-dimensionality reduction driven by neural
-networks. Faced with many possible alternatives, we utilised a conventional
+dimensionality reduction driven by artificial neural
+networks (ANNs). Faced with many possible alternatives, we utilised a conventional
 autoencoder, which relies on a three-layer network that is trained to replicate
@@
 
-\begin{wrapfigure}{l}{0.4\textwidth} % TODO: regenerate both plots as described
+\begin{wrapfigure}{l}{0.4\textwidth}
 	\centering

### 2020-04-22 final_report/data.tex
include MET in run table

@@
 \begin{table}[h]
+	\sisetup{round-mode=places,round-precision=2}
 	\centering
 	{\footnotesize
-		\begin{tabular}{rllll}
+		\begin{tabular}{rlllll}
 		\toprule
-		\#	& Sample count & Batch division & Run time (incl. waiting) & Description \\
+		\#	& Samples & Batch division & Total run time & MET [\si{\second}] & Description \\
 		\midrule
-		0 & \num{100000} & $\num{100}\times\num{1000}$ & 2~days, 23~hours &
+		0 & \num{100000} & $\num{100}\times\num{1000}$ & 2~days, 23~h 
+		  & $\num{7.877122043981347} \pm \num{2.749485948560108}$ &
 		Testing run using older MC TBR version.\\
-		1 & \num{500000} & $\num{500}\times\num{1000}$ & 13~days, 20~hours &
+		1 & \num{500000} & $\num{500}\times\num{1000}$ & 13~days, 20~h
+		  & $\num{7.777049573054314} \pm \num{2.8103592103930337}$ &
 		Fully uniform sampling in the entire domain.\\
-		2 & \num{400000} & $\num{400}\times\num{1000}$ & 10~days &
+		2 & \num{400000} & $\num{400}\times\num{1000}$ & 10~days 
+		  & $\num{7.944379778103232} \pm \num{2.601428571503671}$ &
 		Mixed sampling, discrete features fixed.\\
@@
 	}
-	\caption{Parameters of sampling runs.}
+	\caption{Parameters of sampling runs. Total run time includes waiting in
+	the processing queue. MET stands for mean evaluation time (per single
+	sampled point).}
 	\label{tbl:sampling-runs}
 \end{table}
-
-% TODO: find a way to mention average time per sample and std
 

### 2020-04-22 final_report/conclusion.tex

@@
 Over the course of this internship project, we employed a broad spectrum of data analysis and machine learning techniques to develop fast and high-quality surrogate models for a MC TBR model in use at UKAEA.
----
+We generated 900,000 samples for training and test purposes, evaluated on this expensive MC model.
+We investigated possibilities for simplification of the parameter space, and concluded that no straightforward reduction was possible.
+After reviewing $N$ surrogate models (fill in $N$), and examining their behaviour on (un)constrained feature space and scaling properties, we retrained some of the best-performing surrogates on the full parameter space.
+The optimum results obtained were an accuracy of $X$ and a mean prediction time of $X$, representing a relative speedup $X$ with respect to the MC model.
 
----
-After a thorough review of the literature, we developed a novel adaptive sampling algorithm, QASS, capable of interfacing with any of the individual studied models.
-Preliminary testing on a toy theory, qualitatively comparable to the MC TBR model, demonstrated the effectiveness of QASS and behavioral trends over its hyperparameters which are consistent with the design of the algorithm.
+After a thorough review of the literature, we also developed a novel adaptive sampling algorithm, QASS, capable of interfacing with any of the individual studied models.
+Preliminary testing on a toy theory, qualitatively comparable to the MC TBR model, demonstrated the effectiveness of QASS and behavioural trends consistent with the design of the algorithm.
+$Insert numerical results for QASS.$ Further optimisation over the hyperparameter space has strong potential to increase this performance, allowing for future deployment of QASS on the MC TBR model in coalition with any of the most effective identified surrogate models.
 

### 2020-04-22 final_report/introduction.tex
harmonize references in favour of \cref

@@
 electrostatic repulsion and fuse to form helium \cite{Hernandez2018}. Early prototype reactors
-made use of the deuterium (\isotope[2]{H}) isotope of hydrogen in order to
-achieve fusion under more accessible conditions, but achieved limited success.
+made use of the deuterium (\isotope[2]{H}, or \isotope{D}) isotope of hydrogen in order to
+achieve fusion under more accessible conditions, but lead to limited success.
 The current frontier generation of fusion reactors, such as JET and the
 under-construction International Thermonuclear Experimental Reactor (ITER), make
-use of tritium (\isotope[3]{H}) fuel for further efficiency gain.
+use of tritium (\isotope[3]{H}, or \isotope{T}) fuel for further efficiency gain.
 Experimentation at JET dating back to 1997 \cite{Keilhacker1999} has made significant headway in
@@
 However, tritium is much less readily available as a fuel source than deuterium.
-While at least one deuterium atom occurs for every 5000 molecules of
+While at least one deuterium atom occurs for every \num{5000} molecules of
 naturally-sourced water, and may be easily distilled, tritium is extremely rare
 in nature. It may be produced indirectly through irradiation of heavy water
-(deuterium oxide) during nuclear fission, but only at very low rates which could
+(\ce{D2O}) during nuclear fission, but only at very low rates which could
 never sustain industrial-scale fusion power.
@@
 neutrons with breeding blanket materials. Neutron paths are traced through a CAD
-model (e.g. \cref{fig:tokamak}) of a reactor with modifiable geometry.
+model (e.g.~\cref{fig:tokamak}) of a reactor with modifiable geometry.
 

### 2020-04-22 final_report/tbr_final_report-metadata.tex
Added bibliography .bib file
Remove URLS and DOI from visible bibliography.
add bitmap ukaea logo placeholder, enable draft mode

@@
 % put the name of the logo image file found in graphics path
-%\DISPartnerLogo{path/to/logo/image}
+% TODO: make this a vector logo, wait for reply from Vignesh
+\DISPartnerLogo{ukaea_logo}
 
 % Title
-\DISTitle{Results from TBR Group Project}
+\DISTitle{Surrogate Modelling of\\the Tritium Breeding Ratio}
 
@@
 % and line numbers.
-% Comment or remove in final version.
+% TODO: Comment or remove in final version.
 \DISVersion{0}
@@
 \DISAbstract{%
-  The abstract of my report.
+  Surrogate modelling techniques have been employed in diverse areas of research to resolve the limitations of resource-expensive procedure with significantly cheaper approximations.
+In this internship project, we sought to develop a fast and high-quality surrogate model for simulations of the tritium breeding ratio (TBR) for under-design Tokamak nuclear fusion reactors.
+We investigated possibilities for dimensional reduction on the parameter space of a Monte Carlo TBR model in use at the UK Atomic Energy Authority.
+We investigated possibilities for dimensional reduction on the parameter space of this model, and reviewed $N$ classes of surrogate models for potential applicability.
+Here we present the performance and scaling properties of these surrogate models, the best of which demonstrated an accuracy of $X$ and a mean prediction time of $X$, representing a relative speedup $X$ with respect to the MC model.
+We further present a novel adaptive sampling algorithm, QASS, capable of interfacing with any of the individual studied models.
+Our preliminary testing on a toy TBR theory has demonstrated the efficacy of this algorithm for speeding up the surrogate modelling process.
 }
@@
 % DIS reference code if ever used
-\DISRefCode{UCLCDTDIS-2019-XX}
+%\DISRefCode{UCLCDTDIS-2019-XX}

### 2020-04-22 final_report/tbr_final_report-metadata.tex
Remake abstract

@@
 \DISAbstract{%
-  Surrogate modelling techniques have been employed in diverse areas of research to resolve the limitations of resource-expensive procedure with significantly cheaper approximations.
-In this internship project, we sought to develop a fast and high-quality surrogate model for simulations of the tritium breeding ratio (TBR) for under-design Tokamak nuclear fusion reactors.
-We investigated possibilities for dimensional reduction on the parameter space of a Monte Carlo TBR model in use at the UK Atomic Energy Authority.
+ The tritium breeding ratio (TBR) is an essential quantity for the design of modern and next-generation Tokamak nuclear fusion reactors.
+Representing the ratio between tritium fuel generated in breeding blankets at the boundary of the reactor, and fuel consumed during reactor runtime, the TBR depends in a complex manner on reactor geometry and material properties.
+We explored the training of surrogate models to produce a cheap but high-quality approximations for a Monte Carlo TBR model in use at the UK Atomic Energy Authority.
 We investigated possibilities for dimensional reduction on the parameter space of this model, and reviewed $N$ classes of surrogate models for potential applicability.

### 2020-04-22 final_report/conclusion.tex
Repaired images and conclusion formatting.

@@
 Preliminary testing on a toy theory, qualitatively comparable to the MC TBR model, demonstrated the effectiveness of QASS and behavioural trends consistent with the design of the algorithm.
-$Insert numerical results for QASS.$ Further optimisation over the hyperparameter space has strong potential to increase this performance, allowing for future deployment of QASS on the MC TBR model in coalition with any of the most effective identified surrogate models.
+\textit{[Insert numerical results for QASS.]} Further optimisation over the hyperparameter space has strong potential to increase this performance, allowing for future deployment of QASS on the MC TBR model in coalition with any of the most effective identified surrogate models.
 

### 2020-04-22 final_report/data.tex
Repaired images and conclusion formatting.

@@
 
-\Cref{fig:pca} shows the resultant cumulative variance of the feature vectors
-identified by PCA. The similar share of variance among all eleven features
-demonstrates irreducibility of the TBR model by linear methods.
+\Cref{fig:pca} shows the resultant cumulative variance of PCA-identified feature vectors. The similar share of variance among all features
+reveals irreducibility of the TBR model by linear methods.
 
@@
 
-\begin{wrapfigure}{l}{0.4\textwidth}
+\begin{wrapfigure}{r}{0.4\textwidth} % TODO: regenerate both plots as described
 	\centering
@@
 	\label{fig:autoencoder-loss}
-	\vspace{-6ex}
+	\vspace{-10ex}
 \end{wrapfigure}

### 2020-04-22 final_report/methodology.tex
Repaired images and conclusion formatting.

@@
 optima in the feature space. MCMC produces a progressive chain of sample points,
-each drawn according to the same symmetric proposal distribution\footnote{An
-adaptive MCMC procedure \cite{Zhang2012}, which adjusts an ellipsoidal proposal
-distribution to fit the posterior, was also implemented but not fully tested.}
+each drawn according to the same symmetric proposal distribution
 from the prior point. These sample points will converge to a desired posterior
@@
 for a review).
+
+%\footnote{An
+%adaptive MCMC procedure \cite{Zhang2012}, which adjusts an ellipsoidal proposal
+%distribution to fit the posterior, was also implemented but not fully tested.}
 

### 2020-04-23 final_report/appendix_online.tex
add outline of appendix B

TODO: point reader to various online repositories, briefly describe them

\begin{enumerate}
	\item data repository
	\item sampling repository
	\item regression repository
	\item hyperopt repository
	\item docs repository
\end{enumerate}

### 2020-04-23 final_report/methodology.tex
blow up tables, finalise appendix A layout

@@
 		$\hat{f}(x)$})/N$	& 0 & [ms] \\
-		Relative speedup	& $(\text{wall evaluation time of $f(x)$}) /
+		Relative speedup $\sigma$	& $(\text{wall evaluation time of $f(x)$}) /
 		(N\overline{t}_{\text{pred.}})$	&

### 2020-04-23 final_report/data.tex
harmonise run time notation

@@
 		\toprule
-		\#	& Samples & Batch division & Total run time & MET [\si{\second}] & Description \\
+		\#	& Samples & Batch division & $t_{\text{run}} $ 
+			& $\overline{t}_{\text{eval.}}$ [\si{\second}] & Description \\
 		\midrule
@@
 	}
-	\caption{Parameters of sampling runs. Total run time includes waiting in
-	the processing queue. MET stands for mean evaluation time (per single
+	\caption{Parameters of sampling runs. Here, $t_{\text{run}}$ denotes the total run
+		time (including waiting in the processing queue), and
+		$\overline{t}_{\text{eval.}}$ is the mean evaluation time of MC TBR (per single
 		sampled point).}
@@
 	{\footnotesize
-		\begin{tabular}{r|lllllll}
+		\begin{tabular}{rlllllll}
 		\toprule
 		{} & \multicolumn{7}{c}{Discrete feature assignment}\\
+		\cmidrule(lr){2-8}
 		Batches & BBM & BCM & BMM & BSM & FAM & FCM & FSM \\

### 2020-04-25 final_report/methodology.tex
more detailed figure 9 and 10

@@
 Following the motivation of this work, two desirable properties of surrogates
-arise: (i) their capability to approximate the TBR MC model well and (ii) their time of evaluation. An ideal surrogate would maximise
+arise: (i) their capability to approximate the TBR MC model well and (ii) their
+complexity. An ideal surrogate would maximise
 the former while minimising the latter.
@@
 they maintain invariance with respect to the selected domain and image space.
-For analysis of evaluation time, surrogates are assessed in terms of wall time
+For complexity analysis, surrogates are assessed in terms of wall time
 elapsed during training and predicition. This is motivated by common practical use
@@
 		\midrule
-		Evaluation time metrics	& {} & {} & {} \\
+		Complexity metrics	& {} & {} & {} \\
 		\midrule

### 2020-04-25 final_report/results.tex
Repaired images and conclusion formatting.
more detailed figure 9 and 10

--- 2020-04-22 final_report/results.tex
@@
 	\caption{20~best-performing surrogates per each considered class, plotted in
-	terms of mean prediction time and regression performance (as~$R^2$) on
-	selected slices of run~2, evaluated in experiment~1.}
+		terms of complexity (as $\overline{t}_{\text{pred.}}$) and regression
+		performance (as~$R^2$) on selected slices of run~2, evaluated in experiment~1.}
 	\label{fig:exp1-time-vs-reg}
@@
 
+% TODO: add table here or in appendix with hard numbers, for each class take 20
+% best performing models from each slice, concatenate and calculate mean and std
+% for each metric
+
+% TODO: do the same thing for the second experiment
+\newpage
 \begin{wrapfigure}{r}{0.333\textwidth}
@@
 
+% TODO: add tables here or in appendix with scaling results; for each metric
+% create a table with rows = classes, columns = training set size, cells = mean +/- std
+% it may be a lot, decide on placement and layout!
+
 \subsubsection{Competitive Surrogate Training}
@@
   \end{center}
-  \vspace{-30pt}
+  \vspace{-10pt}
 \end{wrapfigure}

### 2020-04-25 final_report/data.tex
add hardware information about hypatia nodes

@@
 We deployed ATE at the UCL Hypatia cluster RCIF partition, which consists of
-4~homogeneous nodes, each containing 40 cores. We completed three data
+4~homogeneous nodes, each containing 40 cores.\footnote{Hypatia RCIF nodes use
+Intel\textsuperscript{\textregistered} Xeon\textsuperscript{\textregistered}
+Gold 6148 CPU with frequency 2.40~GHz and 376 GB RAM.} We completed three data
 generation runs, which are summarised in~\cref{tbl:sampling-runs}.

### 2020-04-26 final_report/methodology.tex
add some more SMT references

@@
 		Artificial neural networks	& ANN & Keras (TensorFlow)~\cite{chollet2015keras} & 2 \\
-		Inverse distance weighing & IDW & SMT~\cite{SMT2019} & 1 \\
+		Inverse distance weighing~\cite{shepard1968two} & IDW & SMT~\cite{SMT2019} & 1 \\
 		Radial basis functions & RBF & SMT & 3 \\
@@
 		Ridge regression & RR & SciKit Learn & 4 \\
-		Kriging & KRG & SMT & 4 \\
+		Kriging~\cite{sacks1989designs,wold1975soft,bouhlel2016improving,bouhlel2016improved} & KRG & SMT & 4 \\
 		\bottomrule

### 2020-04-26 final_report/results.tex
more detailed figure 11
update fig. 12 caption

@@
 		% TODO: only a placeholder, regenerate when data becomes available
-		\caption{Mean training time}
+		\caption{Complexity (as~$\overline{t}_{\text{trn.}}$)}
 	\end{subfigure}\hfill%
@@
 		% TODO: only a placeholder, regenerate when data becomes available
-		\caption{Mean prediction time}
+		\caption{Complexity (as~$\overline{t}_{\text{pred.}}$)}
 	\end{subfigure}
@@
 	\end{subfigure}
-	\caption{Regression performance of selected best-performing models trained in experiment~4.}
+	\caption{Regression performance of models 1-4 (row 1, from the left) and 5-8
+		(row 2) trained in experiment~4 (competitive surrogate training), viewed
+		as true vs. predicted TBR on a test set of a selected cross-validation
+		fold. Due to large set sizes, points are randomly subsampled and coloured by density.}
 	\label{fig:reg-performance}

### 2020-04-26 final_report/methodology.tex
add sklearn references, decrease bibliography font size

--- 2020-04-25 final_report/methodology.tex
@@
 		\midrule
-		Support vector machines	& SVM & SciKit Learn~\cite{scikit-learn} & 3 \\
-		Gradient boosted trees	& GBT & SciKit Learn & 11 \\
-		Extremely randomized trees	& ERT & SciKit Learn & 7 \\
-		AdaBoosted decision trees	& AB & SciKit Learn & 3 \\
-		Gaussian process regression	& GPR & SciKit Learn & 2 \\
+		Support vector machines~\cite{fan2008liblinear}	& SVM & SciKit Learn~\cite{scikit-learn} & 3 \\
+		Gradient boosted trees~\cite{friedman2001greedy,friedman1999stochastic,hastie2009elements}	& GBT & SciKit Learn & 11 \\
+		Extremely randomized trees~\cite{geurts2006extremely}	& ERT & SciKit Learn & 7 \\
+		AdaBoosted decision trees~\cite{drucker1997improving}	& ABT & SciKit Learn & 3 \\
+		Gaussian process regression~\cite{williams2006gaussian}	& GPR & SciKit Learn & 2 \\
 		$k$ nearest neighbours	& KNN & SciKit Learn & 3 \\
 		Artificial neural networks	& ANN & Keras (TensorFlow)~\cite{chollet2015keras} & 2 \\
-		Inverse distance weighing & IDW & SMT~\cite{SMT2019} & 1 \\
+		Inverse distance weighing~\cite{shepard1968two} & IDW & SMT~\cite{SMT2019} & 1 \\
 		Radial basis functions & RBF & SMT & 3 \\
-		Stochastic gradient descent & SGD & SciKit Learn & 13 \\
-		Ridge regression & RR & SciKit Learn & 4 \\
-		Kriging & KRG & SMT & 4 \\
+		Kriging~\cite{sacks1989designs,wold1975soft,bouhlel2016improving,bouhlel2016improved} & KRG & SMT & 4 \\
 		\bottomrule

### 2020-04-28 final_report/methodology.tex
add final figure 10

--- 2020-04-25 final_report/methodology.tex
@@
 		\midrule
-		Support vector machines	& SVM & SciKit Learn~\cite{scikit-learn} & 3 \\
-		Gradient boosted trees	& GBT & SciKit Learn & 11 \\
-		Extremely randomized trees	& ERT & SciKit Learn & 7 \\
-		AdaBoosted decision trees	& AB & SciKit Learn & 3 \\
-		Gaussian process regression	& GPR & SciKit Learn & 2 \\
+		Support vector machines~\cite{fan2008liblinear}	& SVM & SciKit Learn~\cite{scikit-learn} & 3 \\
+		Gradient boosted trees~\cite{friedman2001greedy,friedman1999stochastic,hastie2009elements}	& GBT & SciKit Learn & 11 \\
+		Extremely randomized trees~\cite{geurts2006extremely}	& ERT & SciKit Learn & 7 \\
+		AdaBoosted decision trees~\cite{drucker1997improving}	& ABT & SciKit Learn & 3 \\
+		Gaussian process regression~\cite{williams2006gaussian}	& GPR & SciKit Learn & 2 \\
 		$k$ nearest neighbours	& KNN & SciKit Learn & 3 \\
 		Artificial neural networks	& ANN & Keras (TensorFlow)~\cite{chollet2015keras} & 2 \\
-		Inverse distance weighing & IDW & SMT~\cite{SMT2019} & 1 \\
+		Inverse distance weighing~\cite{shepard1968two} & IDW & SMT~\cite{SMT2019} & 1 \\
 		Radial basis functions & RBF & SMT & 3 \\
-		Stochastic gradient descent & SGD & SciKit Learn & 13 \\
-		Ridge regression & RR & SciKit Learn & 4 \\
-		Kriging & KRG & SMT & 4 \\
 		\bottomrule

### 2020-04-28 final_report/data.tex
implement simple comments from Nikos

@@
 surrogate modelling is fundamentally a Monte Carlo simulation based on the
-OpenMC framework~\cite{ROMANO201590}. At input the software expects a set of 19~parameters, discrete and
+OpenMC framework~\cite{ROMANO201590}. As input the software expects a set of 19~parameters, discrete and
 continuous, that are fully listed in~\cref{tbl:params}. Following a brief period of
-time (usually on the order of tens of seconds), during which a fixed number of
+time (usually of the order of tens of seconds), during which a fixed number of
 events is generated, the simulation outputs the
@@
 		   & Armour fraction\textsuperscript{\textdaggerdbl} & FAF & Continuous & $[0,1]$ & {}\\
-		   & Armour material & FAM & Discrete & $\{\text{tungsten}\}$ & {}\\
 		   & Coolant fraction\textsuperscript{\textdaggerdbl} & FCF & Continuous & $[0,1]$ & {}\\
@@
 	\caption{Input parameters supplied to the MC TBR simulation in alphabetical
-		order. Fractions marked with superscripts\textsuperscript{\textdagger
+		order. Groups of fractions marked\textsuperscript{\textdagger
 		\textdaggerdbl} are independently required to sum to one.}
@@
 
-With grid search in high-dimensional domain clearly intractable, we
+With grid search in such a high-dimensional domain clearly intractable, we
 selected uniform pseudo-random sampling to generate large amounts of feature
@@
 		  & $\num{7.877122043981347} \pm \num{2.749485948560108}$ &
-		Testing run using older MC TBR version.\\
+		Testing run using old MC TBR version.\\
 		1 & \num{500000} & $\num{500}\times\num{1000}$ & 13~days, 20~h
@@
 
-Skipping run zero, which was performed using older, fundamentally different
+Skipping run zero, which was performed using an older, fundamentally different
 version of the MC TBR software, and was thus treated as a technical
-proof-of-concept, we generated the total of~\num{900000} samples in two runs.
+proof-of-concept, we generated a total of~\num{900000} samples in two runs.
 While the first run featured fully uniform sampling of the unrestricted feature
-space, the second run used more elaborate strategy. Interested in further study
+space, the second run used a more elaborate strategy. Interested in further study
 of relationships between discrete and continuous features, we selected four
@@
 Since some surrogate modelling methods applied in this work are not scale-invariant or
-perform suboptimally with arbitrarily scaled problems, all run results
-were standardised prior to further use. In this commonly used statistical
-procedure, features and regression outputs are independently scaled and offset
-to attain zero mean and unit variance.
+perform suboptimally with arbitrarily scaled inputs, all obtained TBR~samples
+(features and TBR~values) were standardised prior to further use. In this
+commonly used statistical procedure, features and regression outputs are
+independently scaled and offset to attain zero mean and unit variance.
 
@@
 Model training over high-dimensional parameter spaces may be improved in many
-aspects by carefully reducing the number of variables used to describe the space.
-For many applications, feature selection strategies succeed in identifying a sufficiently representative subset of the original input variables; however, all given variables were assumed to be physically relevant to the MC TBR model.
-Feature extraction methods, on the other hand, aim to identify a transformation from the parameter space which decreases dimensionality; even if no individual parameter is separable from the space, some linear combinations of parameters or nonlinear functions of parameters may be.
+aspects by carefully reducing the number of variables used to describe the
+space. For many applications, feature selection strategies succeed in
+identifying a sufficiently representative subset of the original input
+variables; however, all given variables were assumed to be physically relevant
+to the MC TBR model. Feature extraction methods, on the other hand, aim to
+identify a transformation of the parameter space which decreases dimensionality; even if no individual parameter is separable from the space, some linear combinations of parameters or nonlinear functions of parameters may be.
 

### 2020-04-28 final_report/methodology.tex
implement simple comments from Nikos

@@
 $\hat{f}(x)$ that yields similar images as $f(x)$. In other words, $f(x)$ and
-$\hat{f}(x)$ minimise a selected similarity metric. Furthermore, in order to
+$\hat{f}(x)$ minimise a selected dissimilarity metric. Furthermore, in order to
 be considered \textit{viable}, surrogates are required to achieve expected evaluation time
@@
 hyperparameters, surrogate models $\hat{f}(x)$ are trained to minimise
-empirical risk with respect to $\mathcal{T}$ and a model-specific
-loss function $\mathcal{L}$, where empirical risk is defined as
+the empirical risk~$R_{\text{emp.}}$ with respect to $\mathcal{T}$ and a model-specific
+loss function $\mathcal{L}$, where the empirical risk is defined as
 $R_{\text{emp.}}(\hat{f}\mid\mathcal{T},\mathcal{L})
@@
 
-The unsupervised setting can be viewed as an extension of this method.
+The unsupervised setting can be viewed as a more general problem.
 Rather than fixing the training set $\mathcal{T}$ for the entire duration of
@@
 
-\Cref{tbl:metrics} provides exhaustive listing and description of metrics recorded
+\Cref{tbl:metrics} provides an exhaustive listing and description of metrics recorded
 in the experiments. For regression performance analysis, we include a selection
@@
 expensive MC TBR model. Since training set sizes remain to be determined, all times are
-reported per a single sample. Even though some surrogates support acceleration
+reported per a single datapoint. Even though some surrogates support acceleration
 by means of parallelisation, measures were taken to ensure sequential
@@
 	\caption{Metrics recorded in supervised learning experiments. In
-	formulations, we work with training set of size $N_0$ and testing set of
+	formulations, we work with a training set of size $N_0$ and a test set of
 size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
@@
 are collected in the scheme of $k$-fold cross-validation with a standard choice of
-$k=5$. Herein, a sample set is subdivided into 5 disjoint folds which are
-repeatedly interpreted as training and testing sets, maintaining a constant
-ratio of samples between the two.\footnote{Unless explicitly stated otherwise, we use 1
+$k=5$. Herein, a sample set is subdivided into 5 disjoint foldsi, each of which
+is used as a test set for the model trained on the remaining 4.\footnote{Unless explicitly stated otherwise, we use 1
 fold for testing and the $k-1$ remaining folds for training. This gives 80\% to
-20\% train-test ratio.} In each such interpretation experiments are
-repeated, and the overall value of each metric is reported as the mean across all folds.
+20\% train-test ratio.} In each such run experiments are
+repeated, and the overall value of each metric is reported as the mean and
+standard deviation over all folds.
 
@@
 and practically usable results, we require a sufficiently large and diverse pool
-of surrogate classes to draw from. This is described by the listing in~\cref{tbl:surrogates}. The presented selection of models includes basic
+of surrogate families to draw from. This is described by the listing in~\cref{tbl:surrogates}. The presented selection of models includes basic
 techniques suitable for linear regression enhanced by the kernel trick or dimension
@@
 developed specifically for the purposes of surrogate modelling. For each of
-these classes, a state-of-the-art implementation was selected and adapted to
+these families, a state-of-the-art implementation was selected and adapted to
 operate with TBR samples.
@@
 	}
-	\caption{Considered surrogate model classes.}
+	\caption{Considered surrogate model families.}
 	\label{tbl:surrogates}
@@
 \begin{enumerate}
-	\item Hyperparameter tuning in simplified domain,
+	\item Hyperparameter tuning in a simplified domain.
 
-	\item Hyperparameter tuning in full domain,
+	\item Hyperparameter tuning in full domain.
 
-	\item Scaling benchmark,
+	\item Scaling benchmark.
 
@@
 The goal of the last two experiments is to exploit the information gathered by
-hyperparameter tuning for study of scaling properties. In
-the third experiment, 20~best-performing hyperparameter choices of each class
+hyperparameter tuning to investigate scaling properties. In
+the third experiment, the 20~best-performing hyperparameter choices of each class
 (in $R^2$) are used to learn surrogates using progressively larger training sets. Following

### 2020-04-28 final_report/results.tex
add first competitive model and table 11
add model 2 (rbf)
add model 3 (gbt)
add model 4 (ert)
add model 5 (ert)
add model 6 (ann)
add model 7 (ann)
remove clause about subsampling
add final figure 10
implement simple comments from Nikos

@@
 earlier. In particular, we aim to study considered models in terms of regression
-performance and evaluation complexity.
+performance and prediction time.
 Following~\cref{sec:experiment-methodology}, where we proposed four experiments
 that accomplish this task, we present and discuss our results in the next
-several sections.
+sections.
 
@@
 The first two experiments perform Bayesian optimisation to maximise~$R^2$ in
-cross-validated setting as a function of model hyperparameters. While in the
+a cross-validation setting as a function of model hyperparameters. While in the
 first experiment we limit training and testing sets to the scope of four slices of the
@@
 
-% TODO: add table here or in appendix with hard numbers, for each class take 20
-% best performing models from each slice, concatenate and calculate mean and std
-% for each metric
-
 % TODO: do the same thing for the second experiment
@@
 	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
-	% TODO: only a placeholder, regenerate when data becomes available
 	\caption{Results of experiment~2, plotted analogously
@@
 		\centering
-		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
-		% TODO: only a placeholder, regenerate when data becomes available
+		\includegraphics[width=\linewidth]{exp4_model1}
 	\end{subfigure}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
-		% TODO: only a placeholder, regenerate when data becomes available
+		\includegraphics[width=\linewidth]{exp4_model2}
 	\end{subfigure}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
-		% TODO: only a placeholder, regenerate when data becomes available
+		\includegraphics[width=\linewidth]{exp4_model3}
 	\end{subfigure}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
-		% TODO: only a placeholder, regenerate when data becomes available
+		\includegraphics[width=\linewidth]{exp4_model4}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
-		% TODO: only a placeholder, regenerate when data becomes available
+		\includegraphics[width=\linewidth]{exp4_model5}
 	\end{subfigure}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
-		% TODO: only a placeholder, regenerate when data becomes available
+		\includegraphics[width=\linewidth]{exp4_model6}
 	\end{subfigure}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
-		% TODO: only a placeholder, regenerate when data becomes available
+		\includegraphics[width=\linewidth]{exp4_model7}
 	\end{subfigure}\hfill%
@@
 		as true vs. predicted TBR on a test set of a selected cross-validation
-		fold. Due to large set sizes, points are randomly subsampled and coloured by density.}
+		fold. Points are coloured by density.}
 	\label{fig:reg-performance}

### 2020-04-28 final_report/tbr_final_report-metadata.tex
use vector version of the UKAEA logo
disable draft mode
implement simple comments from Nikos

@@
 % put the name of the logo image file found in graphics path
-% TODO: make this a vector logo, wait for reply from Vignesh
 \DISPartnerLogo{ukaea_logo}
@@
 % and line numbers.
-% TODO: Comment or remove in final version.
-\DISVersion{0}
+%\DISVersion{0}
 
@@
 \DISAbstract{%
- The tritium breeding ratio (TBR) is an essential quantity for the design of modern and next-generation Tokamak nuclear fusion reactors.
-Representing the ratio between tritium fuel generated in breeding blankets at the boundary of the reactor, and fuel consumed during reactor runtime, the TBR depends in a complex manner on reactor geometry and material properties.
-We explored the training of surrogate models to produce a cheap but high-quality approximations for a Monte Carlo TBR model in use at the UK Atomic Energy Authority.
-We investigated possibilities for dimensional reduction on the parameter space of this model, and reviewed $N$ classes of surrogate models for potential applicability.
-Here we present the performance and scaling properties of these surrogate models, the best of which demonstrated an accuracy of $X$ and a mean prediction time of $X$, representing a relative speedup $X$ with respect to the MC model.
-We further present a novel adaptive sampling algorithm, QASS, capable of interfacing with any of the individual studied models.
-Our preliminary testing on a toy TBR theory has demonstrated the efficacy of this algorithm for speeding up the surrogate modelling process.
+ The tritium breeding ratio (TBR) is an essential quantity for the design of
+ modern and next-generation Tokamak nuclear fusion reactors. Representing the
+ ratio between tritium fuel generated in breeding blankets at the boundary of
+ the reactor, and fuel consumed during reactor runtime, the TBR depends in a
+ complex manner on reactor geometry and material properties. We explored the
+ training of surrogate models to produce a cheap but high-quality approximation
+ for a Monte Carlo TBR model in use at the UK Atomic Energy Authority. We
+ investigated possibilities for dimensional reduction on the parameter space of
+ this model, and reviewed $N$ classes of surrogate models for potential % TODO
+ applicability. Here we present the performance and scaling properties of these
+ surrogate models, the best of which demonstrated an accuracy of $X$ and a mean % TODO
+ prediction time of $X$, representing a relative speedup $X$ with respect to the % TODO
+ MC model. We further present a novel adaptive sampling algorithm, QASS, capable
+ of interfacing with any of the individual studied models. Our preliminary
+ testing on a toy TBR theory has demonstrated the efficacy of this algorithm for
+ speeding up the surrogate modelling process.
 }

### 2020-04-28 final_report/data.tex
implement simple comments from Vignesh

@@
 With grid search in such a high-dimensional domain clearly intractable, we
-selected uniform pseudo-random sampling to generate large amounts of feature
+selected uniform pseudo-random sampling\footnote{Continuous and discrete
+parameters are drawn from a corresponding uniform distribution over their
+domain, as defined in~\cref{tbl:params}. For reproducibility, each run uses a seed equal to its number.} to generate large amounts of feature
 configurations that we consider to be independent and unbiased. For evaluation

### 2020-04-28 final_report/appendix_online.tex
fill online appendix

@@
-TODO: point reader to various online repositories, briefly describe them
+In this appendix, we provide a brief overview of datasets, open-source
+software, documentation resources and other materials available online for
+public use. All files related to this project are hosted by GitHub in
+a group at \url{https://github.com/ucl-tbr-group-project}, organised in the
+following repositories:
+\begin{description}
+	\item[\href{https://github.com/ucl-tbr-group-project/simple-sphere-study}{Simple Sphere Study}]
+		OpenMC TBR simulation software used to generate TBR values.
+	\item[\href{https://github.com/ucl-tbr-group-project/sampling}{Sampling}]
+		Python implementation of the Approximate TBR Evaluator.
+	\item[\href{https://github.com/ucl-tbr-group-project/data}{Data}]
+		Over \num{900000}~datapoints and TBR values generated in sampling runs 0-2.
+	\item[\href{https://github.com/ucl-tbr-group-project/regression}{Regression}]
+		Python implementation of the surrogate models presented in this work as
+		well as various pre-processing, plotting and evaluation tools.
+	\item[\href{https://github.com/ucl-tbr-group-project/hyperopt}{Hyperparameter Optimisation}]
+		Results of experiments 1-4, including performance plots and software
+		commands used to produce them.
+	\item[\href{https://github.com/ucl-tbr-group-project/documentation}{Documentation}]
+		Project notes, extended bibliography, a digital version of this
+		\LaTeX\  document and source files for all presented figures and
+		tables.
+\end{description}
 
-\begin{enumerate}
-	\item data repository
-	\item sampling repository
-	\item regression repository
-	\item hyperopt repository
-	\item docs repository
-\end{enumerate}
+Unless specified otherwise, permission to use these materials is hereby granted
+in accordance with the MIT~Licence.

### 2020-04-28 final_report/data.tex
remove FAM from discrete feature assignment

@@
 	{\footnotesize
-		\begin{tabular}{rlllllll}
+		\begin{tabular}{rllllll}
 		\toprule
-		{} & \multicolumn{7}{c}{Discrete feature assignment}\\
-		\cmidrule(lr){2-8}
-		Batches & BBM & BCM & BMM & BSM & FAM & FCM & FSM \\
+		{} & \multicolumn{6}{c}{Discrete feature assignment}\\
+		\cmidrule(lr){2-7}
+		Batches & BBM & BCM & BMM & BSM & FCM & FSM \\
 		\midrule
-		0-99 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
-		100-199 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{H2O} & eurofer\\
-		200-299 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
-		300-399 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & tungsten & \ce{He} & eurofer\\
+		0-99 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & \ce{H2O} & eurofer\\
+		100-199 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & \ce{H2O} & eurofer\\
+		200-299 & \ce{Li4SiO4} & \ce{H2O} & \ce{Be12Ti} & eurofer & \ce{He} & eurofer\\
+		300-399 & \ce{Li4SiO4} & \ce{He} & \ce{Be12Ti} & eurofer & \ce{He} & eurofer\\
 		\bottomrule

### 2020-04-28 final_report/data.tex
replace figure 2 with vector
more Nikos comments implemented

@@
 points in the feature space, and inference thereof. We thus require
-sufficiently large and representative quantities of samples to ensure
-statistical significance of our findings.
+sufficiently large and representative quantities of samples to ensure that
+surrogates can be trained to approximate the MC TBR model.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{run1_400k_tbr_vs_feat}
-	% TODO: placeholder only, turn into vector
+	\includegraphics[width=\linewidth]{run1_500k_tbr_vs_feat}
 	\caption{Marginalised dependence of TBR on the choice of continuous
@@
 
-% TODO: in results, we feature both Kriging and GPR with differing results -
-% clarify their interchangeability here
-
 Kriging is a geostatistical surrogate modelling technique which relies on
@@
 dimensionality reduction driven by artificial neural
-networks (ANNs). Faced with many possible alternatives, we utilised a conventional
-autoencoder, which relies on a three-layer network that is trained to replicate
-the identity mapping. While it follows that the input and output layers of such
+networks (ANNs). Faced with a broad selection of alternatives, we opted for a
+conventional autoencoder architecture with a single hidden layer. While it
+follows that the input and output layers of such
 network are sized to accommodate the analysed dataset, the

### 2020-04-28 final_report/methodology.tex
more Nikos comments implemented

@@
 formulated using the language of conventional regression problems. In this section,
-we focus on interpretation in the scheme of supervised and unsupervised learning.
+we focus on interpretation in the scheme of supervised learning with decoupled
+and adaptive sampling.
 
@@
 
-In the supervised learning setting, we first gather a sufficiently large
+In the decoupled sampling approach that is further described
+in~\cref{sec:supervised}, we first gather a sufficiently large
 training set of samples $\mathcal{T}=\left\{\left( x^{(i)},f\left(x^{(i)}\right) \right)\right\}_{i=1}^N$
@@
 
-The unsupervised setting can be viewed as a more general problem.
+The adaptive sampling approach that we characterise in~\cref{sec:adaptive} can be viewed as a more general problem.
 Rather than fixing the training set $\mathcal{T}$ for the entire duration of
@@
 arise: (i) their capability to approximate the TBR MC model well and (ii) their
-complexity. An ideal surrogate would maximise
+prediction time. An ideal surrogate would maximise
 the former while minimising the latter.
@@
 practical bounds on the expected accuracy of their predictions. In addition, we also track
-relative measures that are better-suited for model comparison between works as
+relative measures that are better-suited for comparison between this work and others, as
 they maintain invariance with respect to the selected domain and image space.
@@
 
-\subsection{Evaluation of Supervised Learning Surrogates}
+\subsection{Decoupled Sampling}
 \label{sec:supervised}

### 2020-04-28 final_report/results.tex
more Nikos comments implemented

@@
 
-\subsection{Evaluation of Supervised Learning Surrogates}
+\subsection{Results of Decoupled Sampling}
 \label{sec:modelres}
@@
 		\includegraphics[width=\linewidth]{exp1_slice0}
-		% TODO: only a placeholder, regenerate when data becomes available
 		\caption{Run 2, batches 0-3}
@@
 		\includegraphics[width=\linewidth]{exp1_slice1}
-		% TODO: only a placeholder, regenerate when data becomes available
 		\caption{Run 2, batches 100-103}
@@
 		\includegraphics[width=\linewidth]{exp1_slice2}
-		% TODO: only a placeholder, regenerate when data becomes available
 		\caption{Run 2, batches 200-203}
@@
 		terms of complexity (as $\overline{t}_{\text{pred.}}$) and regression
-		performance (as~$R^2$) on selected slices of run~2, evaluated in experiment~1.}
+		performance (as~$R^2$) on selected slices of run~2, evaluated in
+	experiment~1. Here, batches refer to subsets of training and test datasets that
+	may be matched to slices using~\cref{tbl:slices}.}
 	\label{fig:exp1-time-vs-reg}

### 2020-04-28 final_report/data.tex
even better figures, more comments from Nikos implemented

@@
 	{\footnotesize
-		\begin{tabular}{l|lllll}
+		\begin{tabular}{l|llll}
 		\toprule
-		{} & Parameter Name & Acronym & Type & Domain & Description\\
+		{} & Parameter Name & Acronym & Type & Domain\\
 		\midrule
 		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{Blanket}}}
-		   & Breeder fraction\textsuperscript{\textdagger} & BBF & Continuous & $[0,1]$ & TODO\\
-		   & Breeder \isotope[6]{Li} enrichment fraction & BBLEF & Continuous & $[0,1]$ & {}\\
-		   & Breeder material & BBM & Discrete & $\{\ce{Li2TiO3}, \ce{Li4SiO4}\}$ & {}\\
-		   & Breeder packing fraction & BBPF & Continuous & $[0,1]$ & {}\\
-		   & Coolant fraction\textsuperscript{\textdagger} & BCF & Continuous & $[0,1]$ & {}\\
-		   & Coolant material & BCM & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
-		   & Multiplier fraction\textsuperscript{\textdagger} & BMF & Continuous & $[0,1]$ & {}\\
-		   & Multiplier material & BMM & Discrete & $\{\ce{Be}, \ce{Be12Ti}\}$ & {}\\
-		   & Multiplier packing fraction & BMPF & Continuous & $[0,1]$ & {}\\
-		   & Structural fraction\textsuperscript{\textdagger} & BSF & Continuous & $[0,1]$ & {}\\
-		   & Structural material & BSM & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
-		   & Thickness & BT & Continuous & $[0,500]$ & {}\\
+		   & Breeder fraction\textsuperscript{\textdagger} & BBF & Continuous & $[0,1]$\\
+		   & Breeder \isotope[6]{Li} enrichment fraction & BBLEF & Continuous & $[0,1]$\\
+		   & Breeder material & BBM & Discrete & $\{\ce{Li2TiO3}, \ce{Li4SiO4}\}$\\
+		   & Breeder packing fraction & BBPF & Continuous & $[0,1]$\\
+		   & Coolant fraction\textsuperscript{\textdagger} & BCF & Continuous & $[0,1]$\\
+		   & Coolant material & BCM & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$\\
+		   & Multiplier fraction\textsuperscript{\textdagger} & BMF & Continuous & $[0,1]$\\
+		   & Multiplier material & BMM & Discrete & $\{\ce{Be}, \ce{Be12Ti}\}$\\
+		   & Multiplier packing fraction & BMPF & Continuous & $[0,1]$\\
+		   & Structural fraction\textsuperscript{\textdagger} & BSF & Continuous & $[0,1]$\\
+		   & Structural material & BSM & Discrete & $\{\ce{SiC}, \text{eurofer}\}$\\
+		   & Thickness & BT & Continuous & $[0,500]$\\
 		\midrule
 		\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{First wall}}}
-		   & Armour fraction\textsuperscript{\textdaggerdbl} & FAF & Continuous & $[0,1]$ & {}\\
-		   & Coolant fraction\textsuperscript{\textdaggerdbl} & FCF & Continuous & $[0,1]$ & {}\\
-		   & Coolant material & FCM & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
-		   & Structural fraction\textsuperscript{\textdaggerdbl} & FSF & Continuous & $[0,1]$ & {}\\
-		   & Structural material & FSM & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
-		   & Thickness & FT & Continuous & $[0,20]$ & {}\\
+		   & Armour fraction\textsuperscript{\textdaggerdbl} & FAF & Continuous & $[0,1]$\\
+		   & Coolant fraction\textsuperscript{\textdaggerdbl} & FCF & Continuous & $[0,1]$\\
+		   & Coolant material & FCM & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$\\
+		   & Structural fraction\textsuperscript{\textdaggerdbl} & FSF & Continuous & $[0,1]$\\
+		   & Structural material & FSM & Discrete & $\{\ce{SiC}, \text{eurofer}\}$\\
+		   & Thickness & FT & Continuous & $[0,20]$\\
 		\bottomrule
@@
 Since most surrogate models
-that we employ assume overall continuous inputs, we take steps to unify our
-feature interface in order to attain this property. In particular, we eliminate
-discrete features by embedding each such feature into a finite multitude of
-continuous features using standard one-hot encoding. This option is available to
+that we employ assume overall continuous numerical inputs, we take steps to unify our
+feature interface in order to attain this property. In particular, we transform
+discrete features by embedding each such feature using standard one-hot
+encoding. This option is available to
 us since discrete domains that generate our feature space are finite in
-cardinality and relatively small in size. And while it renders all features continuous, the
-modification comes at the expense of increasing the dimensionality of the
-feature space to 27 features in total. This is further discussed
-in~\cref{sec:dimred}.
+cardinality and relatively small in size. And while it helps us towards
+unification, this step comes at the expense of increasing the dimensionality of the
+feature space. This is further discussed in~\cref{sec:dimred}.
 
@@
 for all points, effectively slicing the feature space into four corresponding
-subspaces. In order to achieve comparability between these \textit{slices}, the
-remaining unassigned features were uniformly sampled only in the first slice,
-and reused in the other three.
+subspaces. In order to achieve comparability, all such \textit{slices} use the
+same samples for the values of continuous features.
 
@@
 	{\footnotesize \incfigscale{0.8}{autoencoder}}
-	\caption{Autoencoder with input width~$W_0$ and bottleneck width~$W_1$.}
+	\caption{Autoencoder with input width~$W_0$ and bottleneck width~$W_1$.
+	Here, $\text{Dense}(N)$ denotes a fully-connected layer of $N$ neurons.}
 	\label{fig:autoencoder}

### 2020-04-29 final_report/methodology.tex
even better figures, more comments from Nikos implemented
implement more Vignesh comments

@@
 		the last use ReLU activation. Prediction information flow is indicated by
-		arrows. Connections between neurons are omitted for clarity.}
+		arrows.}
 	\label{fig:nn-archs}
@@
 optimisation is employed as a standard hyperparameter tuning algorithm. We set
-its objective to maximise $R^2$ and perform 1000~iterations.\footnote{Tuning of
-	each surrogate class was artificially terminated after 2~days. Instances
-	which reached this limit are marked in the results.}
-
-% TODO: mark instances that timed out in results
+its objective to maximise $R^2$ and perform
+1000~iterations.\footnote{Hyperparameter tuning of each surrogate family was
+	terminated after 2~days. Instances that reached this limit may be identified
+	in~\cref{tbl:exp1-detailed-results,tbl:exp2-detailed-results}.}
 
@@
 This follows the notion that, if desired, accuracy of such models may be
-replicated at large scale by decomposing the TBR domain into continuous subsets,
-and learning ensemble surrogate comprised of identical models that are trained on each
-subset independently, incurring exponential complexity penalty in the process.
+replicated by training separate instances to model each continuous subregion of
+the domain independently.
 To this end, data are limited to a single slice from run~2, and discrete

### 2020-04-29 final_report/introduction.tex
replace accuracy with regression performance (mostly)

@@
 takes these same input parameters and approximates the MC TBR model with the
-greatest achievable accuracy.
+greatest achievable regression performance.

### 2020-04-29 final_report/methodology.tex
replace accuracy with regression performance (mostly)

@@
 of absolute metrics to assess the approximation capability of surrogates, and set
-practical bounds on the expected accuracy of their predictions. In addition, we also track
+practical bounds on the expected uncertainty of their predictions. In addition, we also track
 relative measures that are better-suited for comparison between this work and others, as
@@
 in surrogates that are prone to suboptimal performance in discontinuous spaces.
-This follows the notion that, if desired, accuracy of such models may be
+This follows the notion that, if desired, performance of such models may be
 replicated by training separate instances to model each continuous subregion of

### 2020-04-29 final_report/results.tex
replace accuracy with regression performance (mostly)

@@
 shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
-methods based on decision trees and artificial neural networks offer the best accuracy on
+methods based on decision trees and artificial neural networks offer the best regression performance on
 larger sets overall. This is a curious extension of the previous findings, where

### 2020-04-29 final_report/methodology.tex
replace competitive training with model comparison

@@
 
-	\item Competitive surrogate training.
+	\item Model comparison.
 \end{enumerate}
@@
 (in $R^2$) are used to learn surrogates using progressively larger training sets. Following
-that, the fourth experiment attempts to produce competitive surrogates by
-retraining several selected well-scaling models on the largest available data set.
+that, the fourth experiment aims to produce surrogates for practical use by
+retraining selected well-scaling models to further optimise their properties.
 

### 2020-04-29 final_report/results.tex
replace competitive training with model comparison

@@
 
-\subsubsection{Competitive Surrogate Training}
+\subsubsection{Model Comparison}
 
@@
 	\caption{Regression performance of models 1-4 (row 1, from the left) and 5-8
-		(row 2) trained in experiment~4 (competitive surrogate training), viewed
+		(row 2) trained in experiment~4 (model comparison), viewed
 		as true vs. predicted TBR on a test set of a selected cross-validation

### 2020-04-29 final_report/methodology.tex
replace model class with model family

@@
 to describe the behaviour of $f(x)$ across its domain.
-Depending on specific model class and appropriate choice of its
+Depending on specific model family and appropriate choice of its
 hyperparameters, surrogate models $\hat{f}(x)$ are trained to minimise
@@
 Aiming to provide objective comparison of a diverse set of surrogate model
-classes, we define a multitude of metrics to be tracked during experiments.
+families, we define a multitude of metrics to be tracked during experiments.
 Following the motivation of this work, two desirable properties of surrogates
@@
 
-In some rows of~\cref{tbl:surrogates}, a single class in reality represents a
-family of fundamentally similar approaches. Good examples of this are kriging methods and neural
-networks. In the case of the former, multiple algorithms such as kriging based on
-partial least squares and gradient-enhanced kriging are considered. In the
-latter, a host of parametric graphs are defined to realise simplistic network
-architecture search (see~\cref{fig:nn-archs} for details). Discrimination
-between such options is considered an additional hyperparameter of the
-corresponding surrogate class.
+While some of the presented model families are clearly determined by an explicit
+choice of a learning algorithm, others may vary considerably depending on
+hyperparameter configuration. A good example of the latter group are artificial neural
+networks, which in addition to conventional hyperparameters enable to control network
+architecture through selection from various parametric graph templates
+(see~\cref{fig:nn-archs} for details). This allows us to realise a simplistic
+network architecture search during the hyperparameter optimisation procedure.
 
@@
 hyperparameter tuning to investigate scaling properties. In
-the third experiment, the 20~best-performing hyperparameter choices of each class
+the third experiment, the 20~best-performing hyperparameter choices of each family
 (in $R^2$) are used to learn surrogates using progressively larger training sets. Following

### 2020-04-29 final_report/results.tex
replace model class with model family

@@
 
-We begin by evaluating a diverse set of surrogate classes that we proposed
+We begin by evaluating a diverse set of surrogate families that we proposed
 earlier. In particular, we aim to study considered models in terms of regression
@@
 experiment, gradient boosted trees clearly appear to be the most accurate as
-well as the fastest surrogate class in terms of mean prediction time. Following
+well as the fastest surrogate family in terms of mean prediction time. Following
 that, we note that extremely randomised trees, support vector machines and
 artificial neural networks also achieved satisfactory results with respect to both examined metrics.
-While the remainder of tested surrogate classes does not exhibit problems in
+While the remainder of tested surrogate families does not exhibit problems in
 complexity, its regression performance falls below average.
@@
 	\end{subfigure}
-	\caption{20~best-performing surrogates per each considered class, plotted in
+	\caption{20~best-performing surrogates per each considered family, plotted in
 		terms of complexity (as $\overline{t}_{\text{pred.}}$) and regression
@@
 models appear to perform the fastest.
-
-% TODO: add tables here or in appendix with scaling results; for each metric
-% create a table with rows = classes, columns = training set size, cells = mean +/- std
-% it may be a lot, decide on placement and layout!
 

### 2020-04-29 final_report/tbr_final_report-metadata.tex
replace model class with model family

@@
  investigated possibilities for dimensional reduction on the parameter space of
- this model, and reviewed $N$ classes of surrogate models for potential % TODO
+ this model, and reviewed $N$ families of surrogate models for potential % TODO
  applicability. Here we present the performance and scaling properties of these

### 2020-04-29 final_report/results.tex
add multislice (exp2) description

@@
 
-We begin by evaluating a diverse set of surrogate families that we proposed
-earlier. In particular, we aim to study considered models in terms of regression
-performance and prediction time.
-Following~\cref{sec:experiment-methodology}, where we proposed four experiments
-that accomplish this task, we present and discuss our results in the next
-sections.
+We begin by comparing a diverse set of surrogate families that we proposed
+to evaluate on previously collected samples of the expensive MC TBR model.
+Through the four experimental cases described
+in~\cref{sec:experiment-methodology}, we aim to study properties of the
+considered models in terms of regression performance, training and prediction
+time. In the next sections, we present and discuss our results.
 
@@
 a cross-validation setting as a function of model hyperparameters. While in the
-first experiment we limit training and testing sets to the scope of four slices of the
-feature space, in the second experiment we lift this restriction.
+first experiment we limit training and test sets to the scope of four selected
+slices of the feature space, in the second experiment we lift this restriction.
 
@@
 
-% TODO: do the same thing for the second experiment
-\newpage
 \begin{wrapfigure}{r}{0.333\textwidth}
@@
 
-% TODO: multislice description
-TODO: multislice description
+The results of the second experiment, shown in~\cref{fig:exp2-time-vs-reg},
+seem to confirm our expectations. Compared to the previous experiment, we observe
+that many surrogate families consistently achieved worse regression
+performance and prediction times in a more complex, unrestricted domain. The least
+affected models appear to be gradient boosted trees, artificial neural networks and extremely
+randomised trees, which are known to be capable of capturing relationships
+involving mixed feature types that were deliberately withheld in the first
+experiment. With only negligible differences, the first two of these families
+appear to be tied for the best performance as well as the shortest prediction
+time. While extremely randomised trees and radial basis functions also
+demonstrated satisfactory properties, other families failed to achieve
+comparable regression performance, and in some cases also prediction time.
 

### 2020-04-29 final_report/results.tex
revise second experiment

@@
 The results of the second experiment, shown in~\cref{fig:exp2-time-vs-reg},
-seem to confirm our expectations. Compared to the previous experiment, we observe
+seem to confirm our expectations. Compared to the previous case, we observe
 that many surrogate families consistently achieved worse regression
@@
 appear to be tied for the best performance as well as the shortest prediction
-time. While extremely randomised trees and radial basis functions also
-demonstrated satisfactory properties, other families failed to achieve
-comparable regression performance, and in some cases also prediction time.
+time. We observe that extremely randomised trees and radial basis functions also
+demonstrated satisfactory results, outperforming the remaining surrogates in
+terms of regression performance, and in some cases also in prediction time.
 

### 2020-04-29 final_report/results.tex
revise scaling benchmark results

@@
 
+Following both hyperparameter tuning experiments, we conclude that while domain
+restrictions employed in the first case have proven effective in improving the
+regression performance of some methods, this result has fluctuated considerably
+depending on the selected slices. Furthermore, in all instances the best
+results were achieved by families of surrogates that were nearly unaffected by
+this modification.
+
 \subsubsection{Scaling Benchmark}
 
-In the next experiment we examine surrogate scaling properties correlating
-metrics of interest with progressively increasing training set size. The results
-shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
-methods based on decision trees and artificial neural networks offer the best regression performance on
-larger sets overall. This is a curious extension of the previous findings, where
-gradient boosted trees were observed to significantly dominate over the rest of
-the examined methods. With increasing training set size, their relative advantage is
-clearly gradually diminished.
+In the third experiment we examine surrogate scaling properties by correlating
+metrics of interest with training set size. First, the results shown 
+in~\cref{fig:scaling-r2} suggest that the most accurate families from the previous experiments
+consistently maintain their relative advantage over others, even as we introduce
+more training data. While such families achieve nearly comparable regression
+performance on the largest dataset, in the opposite case methods based on
+decision trees clearly outperform neural networks. This can be observed
+particularly on training sets of sizes up to~\num{6000}.
 
@@
 		\includegraphics[width=\linewidth]{scaling_metric_r2}
-		% TODO: only a placeholder, regenerate when data becomes available
 		\caption{Regression performance (as $R^2$)}
+		\label{fig:scaling-r2}
 	\end{subfigure}\hfill%
@@
 		\includegraphics[width=\linewidth]{scaling_time_train}
-		% TODO: only a placeholder, regenerate when data becomes available
 		\caption{Complexity (as~$\overline{t}_{\text{trn.}}$)}
+		\label{fig:scaling-trn}
 	\end{subfigure}\hfill%
@@
 		\includegraphics[width=\linewidth]{scaling_time_pred}
-		% TODO: only a placeholder, regenerate when data becomes available
 		\caption{Complexity (as~$\overline{t}_{\text{pred.}}$)}
+		\label{fig:scaling-pred}
 	\end{subfigure}
@@
 
-According to our experiment, the lowest mean training time is generally achieved
-by instance-based learning methods, which seem to offer near-constant scaling
-characteristics at the expense of significant performance increase later during
-prediction. Following that, we observe that the majority of tree-based methods also exhibit
-desirable properties. The notable exception here appear to be artificial neural networks,
-which are the only model to utilise parallelisation. As such, their constant
-synchronisation overhead presumably hinders performance on small training sets,
-producing misleading results when divided by the number of samples.
+Next, we examine scaling behaviour in terms of the mean training time (displayed
+in~\cref{fig:scaling-trn}). Consistent with our expectation, the shortest times
+were achieved by instance-based learning methods (e.g. KNN, IDW) that
+are trained trivially at the expense of increased lookup complexity later during prediction.
+Furthermore, we observe that the majority of tree-based algorithms also exhibit
+desirable properties unlike radial basis functions and gaussian process
+regression, which appear to scale superlinearly. We note that artificial neural networks,
+which are the only family to utilise parallelisation during training, show an
+inverse scaling characteristic. Our conjecture is that this effect may be caused
+by a constant multi-threading overhead that possibly dominates the training process
+on relatively small training sets.
 
-In terms of mean prediction time, all tested surrogates except previously mentioned
-instance-based learning methods scale exceptionally well. Tree-based generally
-models appear to perform the fastest.
+Lastly, we study scaling with respect to the mean prediction time (shown
+in~\cref{fig:scaling-pred}). Our initial observation is that all tested
+surrogate families with the exception of previously mentioned instance-based
+learning methods offer desirable characteristics overall. Analogous to previous
+experiments, gradient boosted trees and artificial neural networks again
+appear to be tied, as they not only exhibit comparable times but also similar
+scaling slopes.
 

### 2020-04-29 final_report/results.tex
finalise results of experiments 3-4

@@
 
-TODO
+In the fourth and final experiment, we exploit previously collected information
+to produce surrogates with desirable properties for practical use. We
+aim to create models that yield: (i)~the best regression performance regardless
+of other features, (ii)~acceptable performance with the shortest mean
+prediction time, or (iii)~acceptable performance with the smallest training set.
+To this end, we trained 8~surrogates that are presented in~\cref{fig:reg-performance}
+(more details are given in~\cref{tbl:exp4-detailed-results} in the Appendix).
 
@@
 
-\newpage
+Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of the
+experiments~2-3, we utilised the best-performing hyperparameter
+assignments and training sets of varying sizes. In attempts to satisfy
+goals~(i) and~(ii) within cross-validation setting, our best surrogate
+achieved~$R^2=\num{0.998}$ and mean prediction
+time~$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$. These correspond
+to the standard error of regression~$S=\num{0.013}$ and a relative speedup~$\sigma=\num{8659251} \times$
+with respect to the MC TBR evaluation baseline measured during run~1
+(see~\cref{tbl:sampling-runs} for details). While this particular surrogate
+used the entire available set of~\num{500000} datapoints, in attempts to satisfy
+goal~(iii) we also learned a more simplified model that achieved~$R^2=\num{0.913}$,
+$\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\sigma=\num{1269777} \times$
+using only a set of size~\num{10000}.
+
+Overall we found that due to their excellent performance, boosted tree-based
+approaches seem to be advantageous for fast surrogate modelling on relatively small training
+sets (up to the order of~$10^4$). Conversely, while neural networks perform
+poorly in such a setting, both their regression performance and prediction times
+have proven superior on larger training sets (at least of the order of~$10^5$).
+
+\subsection{Results of Adaptive Sampling}
+\label{sec:adaptiveres}
 
@@
 \end{wrapfigure}
-
-\subsection{Results of Adaptive Sampling}
-\label{sec:adaptiveres}
 

### 2020-04-30 final_report/conclusion.tex
add acknowledgements section and nearly finals tables 8-10
promote acknowledgements heading size
add acknowledgements
finalise 1st paragraph of conclusion

@@
-Over the course of this internship project, we employed a broad spectrum of data analysis and machine learning techniques to develop fast and high-quality surrogate models for a MC TBR model in use at UKAEA.
-We generated 900,000 samples for training and test purposes, evaluated on this expensive MC model.
-We investigated possibilities for simplification of the parameter space, and concluded that no straightforward reduction was possible.
-After reviewing $N$ surrogate models (fill in $N$), and examining their behaviour on (un)constrained feature space and scaling properties, we retrained some of the best-performing surrogates on the full parameter space.
-The optimum results obtained were an accuracy of $X$ and a mean prediction time of $X$, representing a relative speedup $X$ with respect to the MC model.
+Over the course of this internship project, we employed a broad spectrum of data
+analysis and machine learning techniques to develop fast and high-quality
+surrogates for a~MC TBR model in use at~UKAEA. We generated over~\num{900000}
+samples for training and test purposes, evaluated on this expensive MC~model. We
+investigated possibilities for simplification of the parameter space, and
+concluded that no straightforward reduction was possible. After reviewing
+9~surrogate model families, examining their behaviour on constrained and
+unrestricted feature space, and studying their scaling properties, we retrained
+some of the best-performing instances to produce properties desirable for
+practical use. The best approximator, trained on~\num{500000} datapoints,
+featured~$R^2=\num{0.998}$ with mean prediction time
+of~$\SI{0.898}{\micro\second}$, representing a relative
+speedup~$\num{8659251} \times$ with respect to the MC model. Alternatively, we
+also demonstrated the possibility of achieving comparable results using only a
+training set of size~\num{10000}.
 
-After a thorough review of the literature, we also developed a novel adaptive sampling algorithm, QASS, capable of interfacing with any of the individual studied models.
-Preliminary testing on a toy theory, qualitatively comparable to the MC TBR model, demonstrated the effectiveness of QASS and behavioural trends consistent with the design of the algorithm.
-\textit{[Insert numerical results for QASS.]} Further optimisation over the hyperparameter space has strong potential to increase this performance, allowing for future deployment of QASS on the MC TBR model in coalition with any of the most effective identified surrogate models.
+After a thorough review of the literature, we developed a novel adaptive
+sampling algorithm, QASS, capable of interfacing with any of the individual
+studied models. Preliminary testing on a toy theory, qualitatively comparable to
+the MC TBR model, demonstrated the effectiveness of QASS and behavioural trends
+consistent with the design of the algorithm. \textit{[Insert numerical results
+for QASS.]} Further optimisation over the hyperparameter space has strong
+potential to increase this performance, allowing for future deployment of QASS
+on the MC TBR model in coalition with any of the most effective identified
+surrogate models.
 
-\newpage
+\section*{Acknowledgements}
+
+The authors would like to thank Vignesh Gopakumar, Prof.~Nikolaos
+Konstantinidis, Nikos Nikolaou, Prof.~Emily Nurse, Jonathan Shimwell and Ingo
+Waldmann for their supervision and valuable suggestions related to this work.

### 2020-04-30 final_report/methodology.tex
finalise results of experiments 3-4
more edits

@@
 are collected in the scheme of $k$-fold cross-validation with a standard choice of
-$k=5$. Herein, a sample set is subdivided into 5 disjoint foldsi, each of which
+$k=5$. Herein, a sample set is subdivided into 5 disjoint folds, each of which
 is used as a test set for the model trained on the remaining 4.\footnote{Unless explicitly stated otherwise, we use 1
-fold for testing and the $k-1$ remaining folds for training. This gives 80\% to
+fold for testing and the 4 remaining folds for training. This gives 80\% to
 20\% train-test ratio.} In each such run experiments are
@@
 investigate variance in behaviour under different discrete feature assignments.
-
 The second experiment conventionally measures surrogate performance on the full

### 2020-04-30 final_report/results.tex
more edits

@@
 The results displayed in~\cref{fig:exp1-time-vs-reg} indicate that in the first
-experiment, gradient boosted trees clearly appear to be the most accurate as
+experiment, GBTs clearly appear to be the most accurate as
 well as the fastest surrogate family in terms of mean prediction time. Following
-that, we note that extremely randomised trees, support vector machines and
-artificial neural networks also achieved satisfactory results with respect to both examined metrics.
+that, we note that ERTs, SVMs and ANNs also achieved satisfactory results with respect to both examined metrics.
 While the remainder of tested surrogate families does not exhibit problems in
@@
 performance and prediction times in a more complex, unrestricted domain. The least
-affected models appear to be gradient boosted trees, artificial neural networks and extremely
-randomised trees, which are known to be capable of capturing relationships
+affected models appear to be GBTs, ANNs and ERTs, which are known to be capable of capturing relationships
 involving mixed feature types that were deliberately withheld in the first
@@
 appear to be tied for the best performance as well as the shortest prediction
-time. We observe that extremely randomised trees and radial basis functions also
+time. We observe that ERTs trees and RBFs also
 demonstrated satisfactory results, outperforming the remaining surrogates in
@@
 Furthermore, we observe that the majority of tree-based algorithms also exhibit
-desirable properties unlike radial basis functions and gaussian process
-regression, which appear to scale superlinearly. We note that artificial neural networks,
+desirable properties unlike RBFs and gaussian process
+regression, which appear to scale superlinearly. We note that ANNs,
 which are the only family to utilise parallelisation during training, show an
@@
 learning methods offer desirable characteristics overall. Analogous to previous
-experiments, gradient boosted trees and artificial neural networks again
+experiments, GBTs and ANNs again
 appear to be tied, as they not only exhibit comparable times but also similar

### 2020-04-30 final_report/methodology.tex
remove negative space from wrapped figures
rename sigma to omega to prevent confusion with std. deviation

@@
 		$\hat{f}(x)$})/N$	& 0 & [ms] \\
-		Relative speedup $\sigma$	& $(\text{wall evaluation time of $f(x)$}) /
+		Relative speedup $\omega$	& $(\text{wall evaluation time of $f(x)$}) /
 		(N\overline{t}_{\text{pred.}})$	&
@@
 \begin{wrapfigure}{r}{0.55\textwidth}
-  \vspace{-35pt}
-  \begin{center}
+	\centering
 	\includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
@@
 	\label{fig:qassplan}
-  \end{center}
-  \vspace{-80pt}
 \end{wrapfigure}

### 2020-04-30 final_report/results.tex
write lead in for the results section
remove negative space from wrapped figures
rename sigma to omega to prevent confusion with std. deviation

@@
-TODO
+Having outlined a variety of models and metrics tracked for the
+purposes of their objective comparison, we proceed to present and discuss our
+results in the next sections.
 
@@
 considered models in terms of regression performance, training and prediction
-time. In the next sections, we present and discuss our results.
+time.
 
@@
 		\includegraphics[width=\linewidth]{exp1_slice0}
-		\caption{Run 2, batches 0-3}
+		\caption{Run 2, batches 0-2}
 	\end{subfigure}\hfill%
@@
 		\includegraphics[width=\linewidth]{exp1_slice1}
-		\caption{Run 2, batches 100-103}
+		\caption{Run 2, batches 100-102}
 	\end{subfigure}\hfill%
@@
 		\includegraphics[width=\linewidth]{exp1_slice2}
-		\caption{Run 2, batches 200-203}
+		\caption{Run 2, batches 200-202}
 	\end{subfigure}
@@
 	\centering
-	\vspace{-3ex}
 	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
@@
 	\label{fig:exp2-time-vs-reg}
-	\vspace{-4ex}
 \end{wrapfigure}
@@
 time~$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$. These correspond
-to the standard error of regression~$S=\num{0.013}$ and a relative speedup~$\sigma=\num{8659251} \times$
+to the standard error of regression~$S=\num{0.013}$ and a relative speedup~$\omega=\num{8659251} \times$
 with respect to the MC TBR evaluation baseline measured during run~1
@@
 goal~(iii) we also learned a more simplified model that achieved~$R^2=\num{0.913}$,
-$\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\sigma=\num{1269777} \times$
+$\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
 using only a set of size~\num{10000}.
@@
 \begin{wrapfigure}{r}{0.4\textwidth}
-  \vspace{-60pt}
-  \begin{center}
+	\centering
 	\includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
@@
 	\label{fig:sintoy}
-  \end{center}
-  \vspace{-10pt}
 \end{wrapfigure}

### 2020-04-30 final_report/results.tex
change 'used' to 'was trained on'

@@
 (see~\cref{tbl:sampling-runs} for details). While this particular surrogate
-used the entire available set of~\num{500000} datapoints, in attempts to satisfy
+was trained on the entire available set of~\num{500000} datapoints, in attempts to satisfy
 goal~(iii) we also learned a more simplified model that achieved~$R^2=\num{0.913}$,
 $\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
-using only a set of size~\num{10000}.
+with only a set of size~\num{10000}.
 

### 2020-04-30 final_report/methodology.tex
change 'learn' to 'train'

@@
 the third experiment, the 20~best-performing hyperparameter choices of each family
-(in $R^2$) are used to learn surrogates using progressively larger training sets. Following
+(in $R^2$) are used to train surrogates using progressively larger training sets. Following
 that, the fourth experiment aims to produce surrogates for practical use by

### 2020-04-30 final_report/results.tex
change 'learn' to 'train'

--- 2020-04-30 final_report/results.tex
@@
 (see~\cref{tbl:sampling-runs} for details). While this particular surrogate
-used the entire available set of~\num{500000} datapoints, in attempts to satisfy
-goal~(iii) we also learned a more simplified model that achieved~$R^2=\num{0.913}$,
+was trained on the entire available set of~\num{500000} datapoints, in attempts to satisfy
+goal~(iii) we also trained a more simplified model that achieved~$R^2=\num{0.913}$,
 $\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
-using only a set of size~\num{10000}.
+with only a set of size~\num{10000}.
 

### 2020-04-30 final_report/conclusion.tex
rename Nikos in acknowledgements

@@
 The authors would like to thank Vignesh Gopakumar, Prof.~Nikolaos
-Konstantinidis, Nikos Nikolaou, Prof.~Emily Nurse, Jonathan Shimwell and Ingo
+Konstantinidis, Nikolaos Nikolaou, Prof.~Emily Nurse, Jonathan Shimwell and Ingo
 Waldmann for their supervision and valuable suggestions related to this work.

### 2020-04-30 final_report/data.tex
remove negative space from wrapped figures
improve typesetting

@@
 
-\begin{wrapfigure}{r}{0.5\textwidth}
-  \vspace{-30pt}
-  \begin{center}
+\begin{wrapfigure}[30]{r}{0.5\textwidth}
+	\centering
 	\hspace*{-.3\columnsep}\includegraphics[width=0.58\textwidth]{fig3_allvar.jpg}
@@
 	\label{fig:var}
-  \end{center}
-  \vspace{-50pt}
 \end{wrapfigure}
@@
 
-\begin{wrapfigure}{r}{0.25\textwidth}
-	\centering
-	\vspace{-5ex}
-	{\footnotesize \incfigscale{0.8}{autoencoder}}
-	\caption{Autoencoder with input width~$W_0$ and bottleneck width~$W_1$.
-	Here, $\text{Dense}(N)$ denotes a fully-connected layer of $N$ neurons.}
-	\label{fig:autoencoder}
-	\vspace{-9ex}
-\end{wrapfigure}
-
 Autoencoders~\cite{SCHMIDHUBER201585} are a family of approaches to
@@
 
+\begin{wrapfigure}[15]{l}{0.25\textwidth}
+	\centering
+	{\footnotesize \incfigscale{0.8}{autoencoder}}
+	\caption{Autoencoder with input width~$W_0$ and bottleneck width~$W_1$.
+	Here, $\text{Dense}(N)$ denotes a fully-connected layer of $N$ neurons.}
+	\label{fig:autoencoder}
+\end{wrapfigure}
+
 In particular, we consider two equally-sized sets\footnote{Each set contained
-\num{100000}~samples from batches 0-99 of the corresponding runs.} of samples: (i) a subset of data obtained
-from run~1 and (ii) a subset of a single slice obtained from run~2. Our
+\num{100000}~samples from batches 0-99 of the corresponding runs.} of samples:
+(i)~a subset of data obtained
+from run~1 and (ii)~a subset of a single slice obtained from run~2. Our
 expectation was that while the former case would provide meaningful insights into
@@
 
-\begin{wrapfigure}{r}{0.4\textwidth} % TODO: regenerate both plots as described
+\begin{wrapfigure}[22]{r}{0.4\textwidth}
 	\centering
-	\vspace{-1ex}
+	\vspace{-4ex}
+
 	\begin{subfigure}[b]{\linewidth}
@@
 	\label{fig:autoencoder-loss}
-	\vspace{-10ex}
 \end{wrapfigure}

### 2020-04-30 final_report/results.tex
improve typesetting
nicer figure 9

@@
 	\caption{20~best-performing surrogates per each considered family, plotted in
-		terms of complexity (as $\overline{t}_{\text{pred.}}$) and regression
+		terms of complexity (as~$\overline{t}_{\text{pred.}}$) and regression
 		performance (as~$R^2$) on selected slices of run~2, evaluated in
@@
 \end{figure}
-
-\begin{wrapfigure}{r}{0.333\textwidth}
-	\centering
-	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
-	\caption{Results of experiment~2, plotted analogously
-	to~\cref{fig:exp1-time-vs-reg}.}
-	\label{fig:exp2-time-vs-reg}
-\end{wrapfigure}
 
@@
 terms of regression performance, and in some cases also in prediction time.
+
+\begin{wrapfigure}[10]{r}{0.333\textwidth}
+	\centering
+	\vspace{-2ex}
+	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
+	\caption{Results of experiment~2, plotted analogously
+	to~\cref{fig:exp1-time-vs-reg}.}
+	\label{fig:exp2-time-vs-reg}
+\end{wrapfigure}
 
@@
 
-\subsection{Results of Adaptive Sampling}
-\label{sec:adaptiveres}
-
-\begin{wrapfigure}{r}{0.4\textwidth}
+\begin{wrapfigure}[13]{r}{0.4\textwidth}
 	\centering
+	\vspace{-12ex}
 	\includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
@@
 \end{wrapfigure}
+
+\subsection{Results of Adaptive Sampling}
+\label{sec:adaptiveres}
 
@@
     \end{subfigure}%
-    ~ 
+    \hfill
     \begin{subfigure}[t]{0.5\textwidth}
@@
   \centering
-    \includegraphics[width=0.8\linewidth]{fig7_qasssampling.pdf}
+    \includegraphics[width=0.78\linewidth]{fig7_qasssampling.pdf}
     \caption{Absolute training error for QASS, baseline scheme, and mixed scheme}

### 2020-04-30 final_report/appendix_online.tex
sort out appendix

@@
-In this appendix, we provide a brief overview of datasets, open-source
-software, documentation resources and other materials available online for
-public use. All files related to this project are hosted by GitHub in
-a group at \url{https://github.com/ucl-tbr-group-project}, organised in the
-following repositories:
+In this appendix, we provide a brief overview of datasets, software, documentation 
+and other resources available online for public use. All files related to this
+project are hosted by GitHub in a group at
+\url{https://github.com/ucl-tbr-group-project}, organised as follows:
 \begin{description}
@@
 	\item[\href{https://github.com/ucl-tbr-group-project/hyperopt}{Hyperparameter Optimisation}]
-		Results of experiments 1-4, including performance plots and software
-		commands used to produce them.
+		Results, plots and software commands used to produce them.
 	\item[\href{https://github.com/ucl-tbr-group-project/documentation}{Documentation}]
-		Project notes, extended bibliography, a digital version of this
-		\LaTeX\  document and source files for all presented figures and
-		tables.
+		Notes, extended bibliography, this \LaTeX\  document and source files.
 \end{description}
 
-Unless specified otherwise, permission to use these materials is hereby granted
-in accordance with the MIT~Licence.
+Unless specified otherwise, these materials are shared in accordance with the MIT~Licence.

### 2020-04-30 final_report/conclusion.tex
Followed comments from Nikos and Vignesh.

--- 2020-04-22 final_report/conclusion.tex
@@
 We investigated possibilities for simplification of the parameter space, and concluded that no straightforward reduction was possible.
-After reviewing $N$ surrogate models (fill in $N$), and examining their behaviour on (un)constrained feature space and scaling properties, we retrained some of the best-performing surrogates on the full parameter space.
-The optimum results obtained were an accuracy of $X$ and a mean prediction time of $X$, representing a relative speedup $X$ with respect to the MC model.
+After reviewing $N$ surrogate models (fill in $N$), and examining their behaviour and scaling properties on the (un)constrained feature space, we retrained some of the best-performing surrogates on the full parameter space.
+The optimal models obtained had an accuracy of $X$ and a mean prediction time of $X$, representing a relative speedup $X$ with respect to the MC model.
 
@@
 
-\newpage
+\section*{Acknowledgements}
+
+The authors would like to thank Vignesh Gopakumar, Prof.~Nikolaos
+Konstantinidis, Nikos Nikolaou, Prof.~Emily Nurse, Jonathan Shimwell and Ingo
+Waldmann for their supervision and valuable suggestions related to this work.

### 2020-04-30 final_report/introduction.tex
Followed comments from Nikos and Vignesh.

@@
 Given that rapid improvements in sensing and processing hardware have gone hand in hand with the data explosion, it is unsurprising that software for the generation and interpretation of this data has also attained a new frontier in complexity.
-In particular, simulation procedures such as Monte Carlo (MC) event generation can perform physics predictions even for theoretical regimes which are not analytically soluble.
+In particular, simulation procedures such as Monte Carlo (MC) event generation can perform physics predictions even for theoretical regimes which are not analytically tractable.
 The bottleneck for such procedures, as is often the case, lies in the computational time and power which they necessitate.
@@
 in the parameter optimisation of a theoretical model.
-The term "metamodel" proves especially meaningful in this case, when the surrogate model approximates a computational process which is itself a model for a (perhaps unknown) physical process \cite{Myers2002}.
-There exists a spectrum between "physical" surrogates which are constructed with some contextual knowledge in hand, and "empirical" surrogates which are derived purely from the underlying expensive model.
+The term ``metamodel" proves especially meaningful in this case, when the surrogate model approximates a computational process which is itself a model for a (perhaps unknown) physical process \cite{Myers2002}.
+There exists a spectrum between ``physical" surrogates which are constructed with some contextual knowledge in hand, and ``empirical" surrogates which are derived purely from samples of the underlying expensive model.
 
-In this internship project, in coordination with the UK Atomic Energy Authority (UKAEA) and Culham Centre for Fusion Energy (CCFE), we sought to develop a surrogate model for the tritium breeding ratio (TBR) in a Tokamak nuclear fusion reactor.
-Our expensive model was a MC-based neutronics simulation \cite{JonathanCollab}, itself a spherical approximation of the Joint European Torus (JET) at CCFE, which returns a prediction of the TBR for a given reactor configuration.
+In this internship project, in coordination with the UK Atomic Energy Authority (UKAEA), we sought to develop a surrogate model for the tritium breeding ratio (TBR) in a Tokamak nuclear fusion reactor.
+Our expensive model was an MC-based neutronics simulation, \textit{Paramak} \footnote{Provided by collaborator Jonathan Shimwell, at UKAEA.}, which returns a prediction of the TBR for a given configuration of a spherical Tokamak.
 We took an empirical approach to the construction of this surrogate, and no results described here are explicitly dependent on prior physics knowledge.
 
-For the remainder of Section 1, we will define the TBR and set the context of this work within the goals of the UKAEA and CCFE.
+For the remainder of Section 1, we will define the TBR and set the context of this work within the goals of the UKAEA.
 In Section 2 we will describe our datasets generated from the expensive model for training and validation purposes, and the dimensionality reduction methods employed to develop our understanding of the parameter domain.
@@
 achieve fusion under more accessible conditions, but lead to limited success.
-The current frontier generation of fusion reactors, such as JET and the
+The current frontier generation of fusion reactors, such as the Joint European Torus (JET) and the
 under-construction International Thermonuclear Experimental Reactor (ITER), make
@@
 validating deuterium-tritium (D-T) operations and constraining the technology
-which will be employed in ITER in a scaled up form.
+which will be employed in ITER in a scaled-up form.
 

### 2020-04-30 final_report/methodology.tex
improve typesetting
Followed comments from Nikos and Vignesh.

--- 2020-04-30 final_report/methodology.tex
@@
 are collected in the scheme of $k$-fold cross-validation with a standard choice of
-$k=5$. Herein, a sample set is subdivided into 5 disjoint folds, each of which
+$k=5$. Herein, a sample set is subdivided into 5 disjoint foldsi, each of which
 is used as a test set for the model trained on the remaining 4.\footnote{Unless explicitly stated otherwise, we use 1
-fold for testing and the 4 remaining folds for training. This gives 80\% to
+fold for testing and the $k-1$ remaining folds for training. This gives 80\% to
 20\% train-test ratio.} In each such run experiments are
@@
 investigate variance in behaviour under different discrete feature assignments.
+
 The second experiment conventionally measures surrogate performance on the full
@@
 training the surrogate on a single sample set generated according to a fixed
-strategy, sample locations are chosen incrementally so as to best suit the model
+strategy, sample locations are chosen periodically during training so as to best suit the model
 under consideration.
@@
 
-% TODO: explain AE
-
 We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS,
@@
 (CDM) \cite{Solonen2012} in feature space.
-On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and AE calculated.
+On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and absolute error calculated.
 MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points.

### 2020-04-30 final_report/results.tex
Followed comments from Nikos and Vignesh.

--- 2020-04-30 final_report/results.tex
@@
-Having outlined a variety of models and metrics tracked for the
-purposes of their objective comparison, we proceed to present and discuss our
-results in the next sections.
+TODO
 
@@
 considered models in terms of regression performance, training and prediction
-time.
+time. In the next sections, we present and discuss our results.
 
@@
 The results displayed in~\cref{fig:exp1-time-vs-reg} indicate that in the first
-experiment, GBTs clearly appear to be the most accurate as
+experiment, gradient boosted trees clearly appear to be the most accurate as
 well as the fastest surrogate family in terms of mean prediction time. Following
-that, we note that ERTs, SVMs and ANNs also achieved satisfactory results with respect to both examined metrics.
+that, we note that extremely randomised trees, support vector machines and
+artificial neural networks also achieved satisfactory results with respect to both examined metrics.
 While the remainder of tested surrogate families does not exhibit problems in
@@
 		\includegraphics[width=\linewidth]{exp1_slice0}
-		\caption{Run 2, batches 0-2}
+		\caption{Run 2, batches 0-3}
 	\end{subfigure}\hfill%
@@
 		\includegraphics[width=\linewidth]{exp1_slice1}
-		\caption{Run 2, batches 100-102}
+		\caption{Run 2, batches 100-103}
 	\end{subfigure}\hfill%
@@
 		\includegraphics[width=\linewidth]{exp1_slice2}
-		\caption{Run 2, batches 200-202}
+		\caption{Run 2, batches 200-203}
 	\end{subfigure}
@@
 	\centering
+	\vspace{-3ex}
 	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
@@
 The results of the second experiment, shown in~\cref{fig:exp2-time-vs-reg},
-seem to confirm our expectations. Compared to the previous case, we observe
+seem to confirm our expectations. Compared to the previous experiment, we observe
 that many surrogate families consistently achieved worse regression
 performance and prediction times in a more complex, unrestricted domain. The least
-affected models appear to be GBTs, ANNs and ERTs, which are known to be capable of capturing relationships
+affected models appear to be gradient boosted trees, artificial neural networks and extremely
+randomised trees, which are known to be capable of capturing relationships
 involving mixed feature types that were deliberately withheld in the first
@@
 appear to be tied for the best performance as well as the shortest prediction
-time. We observe that ERTs trees and RBFs also
-demonstrated satisfactory results, outperforming the remaining surrogates in
-terms of regression performance, and in some cases also in prediction time.
-
-Following both hyperparameter tuning experiments, we conclude that while domain
-restrictions employed in the first case have proven effective in improving the
-regression performance of some methods, this result has fluctuated considerably
-depending on the selected slices. Furthermore, in all instances the best
-results were achieved by families of surrogates that were nearly unaffected by
-this modification.
+time. While extremely randomised trees and radial basis functions also
+demonstrated satisfactory properties, other families failed to achieve
+comparable regression performance, and in some cases also prediction time.
 
@@
 
-In the third experiment we examine surrogate scaling properties by correlating
-metrics of interest with training set size. First, the results shown 
-in~\cref{fig:scaling-r2} suggest that the most accurate families from the previous experiments
-consistently maintain their relative advantage over others, even as we introduce
-more training data. While such families achieve nearly comparable regression
-performance on the largest dataset, in the opposite case methods based on
-decision trees clearly outperform neural networks. This can be observed
-particularly on training sets of sizes up to~\num{6000}.
+In the next experiment we examine surrogate scaling properties correlating
+metrics of interest with progressively increasing training set size. The results
+shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
+methods based on decision trees and artificial neural networks offer the best regression performance on
+larger sets overall. This is a curious extension of the previous findings, where
+gradient boosted trees were observed to significantly dominate over the rest of
+the examined methods. With increasing training set size, their relative advantage is
+clearly gradually diminished.
 
@@
 		\includegraphics[width=\linewidth]{scaling_metric_r2}
+		% TODO: only a placeholder, regenerate when data becomes available
 		\caption{Regression performance (as $R^2$)}
-		\label{fig:scaling-r2}
 	\end{subfigure}\hfill%
@@
 		\includegraphics[width=\linewidth]{scaling_time_train}
+		% TODO: only a placeholder, regenerate when data becomes available
 		\caption{Complexity (as~$\overline{t}_{\text{trn.}}$)}
-		\label{fig:scaling-trn}
 	\end{subfigure}\hfill%
@@
 		\includegraphics[width=\linewidth]{scaling_time_pred}
+		% TODO: only a placeholder, regenerate when data becomes available
 		\caption{Complexity (as~$\overline{t}_{\text{pred.}}$)}
-		\label{fig:scaling-pred}
 	\end{subfigure}
@@
 
-Next, we examine scaling behaviour in terms of the mean training time (displayed
-in~\cref{fig:scaling-trn}). Consistent with our expectation, the shortest times
-were achieved by instance-based learning methods (e.g. KNN, IDW) that
-are trained trivially at the expense of increased lookup complexity later during prediction.
-Furthermore, we observe that the majority of tree-based algorithms also exhibit
-desirable properties unlike RBFs and gaussian process
-regression, which appear to scale superlinearly. We note that ANNs,
-which are the only family to utilise parallelisation during training, show an
-inverse scaling characteristic. Our conjecture is that this effect may be caused
-by a constant multi-threading overhead that possibly dominates the training process
-on relatively small training sets.
+According to our experiment, the lowest mean training time is generally achieved
+by instance-based learning methods, which seem to offer near-constant scaling
+characteristics at the expense of significant performance increase later during
+prediction. Following that, we observe that the majority of tree-based methods also exhibit
+desirable properties. The notable exception here appear to be artificial neural networks,
+which are the only model to utilise parallelisation. As such, their constant
+synchronisation overhead presumably hinders performance on small training sets,
+producing misleading results when divided by the number of samples.
 
-Lastly, we study scaling with respect to the mean prediction time (shown
-in~\cref{fig:scaling-pred}). Our initial observation is that all tested
-surrogate families with the exception of previously mentioned instance-based
-learning methods offer desirable characteristics overall. Analogous to previous
-experiments, GBTs and ANNs again
-appear to be tied, as they not only exhibit comparable times but also similar
-scaling slopes.
+In terms of mean prediction time, all tested surrogates except previously mentioned
+instance-based learning methods scale exceptionally well. Tree-based generally
+models appear to perform the fastest.
 
@@
 
-In the fourth and final experiment, we exploit previously collected information
-to produce surrogates with desirable properties for practical use. We
-aim to create models that yield: (i)~the best regression performance regardless
-of other features, (ii)~acceptable performance with the shortest mean
-prediction time, or (iii)~acceptable performance with the smallest training set.
-To this end, we trained 8~surrogates that are presented in~\cref{fig:reg-performance}
-(more details are given in~\cref{tbl:exp4-detailed-results} in the Appendix).
+TODO
 
@@
 
-Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of the
-experiments~2-3, we utilised the best-performing hyperparameter
-assignments and training sets of varying sizes. In attempts to satisfy
-goals~(i) and~(ii) within cross-validation setting, our best surrogate
-achieved~$R^2=\num{0.998}$ and mean prediction
-time~$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$. These correspond
-to the standard error of regression~$S=\num{0.013}$ and a relative speedup~$\omega=\num{8659251} \times$
-with respect to the MC TBR evaluation baseline measured during run~1
-(see~\cref{tbl:sampling-runs} for details). While this particular surrogate
-was trained on the entire available set of~\num{500000} datapoints, in attempts to satisfy
-goal~(iii) we also trained a more simplified model that achieved~$R^2=\num{0.913}$,
-$\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
-with only a set of size~\num{10000}.
+\newpage
 
-Overall we found that due to their excellent performance, boosted tree-based
-approaches seem to be advantageous for fast surrogate modelling on relatively small training
-sets (up to the order of~$10^4$). Conversely, while neural networks perform
-poorly in such a setting, both their regression performance and prediction times
-have proven superior on larger training sets (at least of the order of~$10^5$).
+\begin{wrapfigure}{r}{0.4\textwidth}
+  \vspace{-60pt}
+  \begin{center}
+    \includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
+	\caption{Sinusoidal toy TBR theory over two continuous parameters, wavenumber 1}
+    \label{fig:sintoy}
+  \end{center}
+  \vspace{-10pt}
+\end{wrapfigure}
 
@@
 \label{sec:adaptiveres}
-
-\begin{wrapfigure}{r}{0.4\textwidth}
-	\centering
-	\includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
-	\caption{Sinusoidal toy TBR theory over two continuous parameters, wavenumber 1}
-	\label{fig:sintoy}
-\end{wrapfigure}
 
@@
 adaptively-sampled training set, it is outperformed by the baseline scheme on
-uniformly random evaluation sets. We suspected that while QASS excels in
+uniformly-random evaluation sets. We suspected that while QASS excels in
 learning the most strongly peaked regions of the TBR theory, this comes at the

### 2020-04-30 final_report/conclusion.tex

--- 2020-04-30 final_report/conclusion.tex
@@
+<<<<<<< HEAD
+Over the course of this internship project, we employed a broad spectrum of data analysis and machine learning techniques to develop fast and high-quality surrogate models for a MC TBR model in use at UKAEA.
+We generated 900,000 samples for training and test purposes, evaluated on this expensive MC model.
+We investigated possibilities for simplification of the parameter space, and concluded that no straightforward reduction was possible.
+After reviewing $N$ surrogate models (fill in $N$), and examining their behaviour and scaling properties on the (un)constrained feature space, we retrained some of the best-performing surrogates on the full parameter space.
+The optimal models obtained had an accuracy of $X$ and a mean prediction time of $X$, representing a relative speedup $X$ with respect to the MC model.
+=======
 Over the course of this internship project, we employed a broad spectrum of data
@@
 training set of size~\num{10000}.
+>>>>>>> a8aa361ad44249d94cd86fe2d10a7f27c74ef277
 

### 2020-04-30 final_report/tbr_final_report-metadata.tex

--- 2020-04-28 final_report/tbr_final_report-metadata.tex
@@
  modern and next-generation Tokamak nuclear fusion reactors. Representing the
- ratio between tritium fuel generated in breeding blankets at the boundary of
- the reactor, and fuel consumed during reactor runtime, the TBR depends in a
+ ratio between tritium fuel generated in breeding blankets and fuel consumed
+ during reactor runtime, the TBR depends in a
  complex manner on reactor geometry and material properties. We explored the
@@
  for a Monte Carlo TBR model in use at the UK Atomic Energy Authority. We
- investigated possibilities for dimensional reduction on the parameter space of
- this model, and reviewed $N$ classes of surrogate models for potential % TODO
- applicability. Here we present the performance and scaling properties of these
- surrogate models, the best of which demonstrated an accuracy of $X$ and a mean % TODO
- prediction time of $X$, representing a relative speedup $X$ with respect to the % TODO
- MC model. We further present a novel adaptive sampling algorithm, QASS, capable
+ investigated possibilities for dimensional reduction on the feature space of
+ this model, reviewed 9~families of surrogate models for potential
+ applicability and performed hyperparameter optimisation. Here we present the
+ performance and scaling properties of these
+ models, the best of which demonstrated~$R^2=\num{0.998}$ and a mean
+ prediction time of~$\SI{0.898}{\micro\second}$, representing a relative speedup~$\num{8659251} \times$
+ with respect to the expensive MC model. We further present a novel adaptive
+ sampling algorithm, QASS, capable
  of interfacing with any of the individual studied models. Our preliminary
  testing on a toy TBR theory has demonstrated the efficacy of this algorithm for
- speeding up the surrogate modelling process.
+ accelerating the surrogate modelling process.
 }

### 2020-04-30 final_report/methodology.tex
resolve committed merge conflicts (why were they committed in the first place?)

--- 2020-04-30 final_report/methodology.tex
@@
 
+\begin{wrapfigure}[22]{r}{0.55\textwidth}
+	\centering
+	\vspace{-5ex}
+	\includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
+	\caption{Schematic of QASS algorithm}
+	\label{fig:qassplan}
+\end{wrapfigure}
+
 Many researchers have embedded surrogate methods into MCMC strategies for
@@
 
-\begin{wrapfigure}{r}{0.55\textwidth}
-	\centering
-	\includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
-	\caption{Schematic of QASS algorithm}
-	\label{fig:qassplan}
-\end{wrapfigure}
-
 % TODO: explain AE

### 2020-04-30 final_report/results.tex
link appendix figures from results, shorten paragraphs to maintain typesetting

@@
 
-The results displayed in~\cref{fig:exp1-time-vs-reg} indicate that in the first
+The results displayed in~\cref{fig:exp1-time-vs-reg} (and listed
+in~\cref{tbl:exp1-detailed-results} in the Appendix) indicate that in the first
 experiment, GBTs clearly appear to be the most accurate as
@@
 
-The results of the second experiment, shown in~\cref{fig:exp2-time-vs-reg},
+The results of the second experiment, shown in~\cref{fig:exp2-time-vs-reg} (and listed
+in~\cref{tbl:exp2-detailed-results} in the Appendix),
 seem to confirm our expectations. Compared to the previous case, we observe
@@
 metrics of interest with training set size. First, the results shown 
-in~\cref{fig:scaling-r2} suggest that the most accurate families from the previous experiments
+in~\cref{fig:scaling-r2} (and listed in~\cref{tbl:exp3-detailed-results-r2} in
+the Appendix) suggest that the most accurate families from the previous experiments
 consistently maintain their relative advantage over others, even as we introduce
@@
 Next, we examine scaling behaviour in terms of the mean training time (displayed
-in~\cref{fig:scaling-trn}). Consistent with our expectation, the shortest times
+in~\cref{fig:scaling-trn} and listed in~\cref{tbl:exp3-detailed-results-t-train} in
+the Appendix). Consistent with our expectation, the shortest times
 were achieved by instance-based learning methods (e.g. KNN, IDW) that
@@
 Lastly, we study scaling with respect to the mean prediction time (shown
-in~\cref{fig:scaling-pred}). Our initial observation is that all tested
+in~\cref{fig:scaling-pred} and listed in~\cref{tbl:exp3-detailed-results-t-pred} in
+the Appendix). Our initial observation is that all tested
 surrogate families with the exception of previously mentioned instance-based
@@
 
-In the fourth and final experiment, we exploit previously collected information
+In the fourth experiment, we exploit previously collected information
 to produce surrogates with desirable properties for practical use. We
@@
 To this end, we trained 8~surrogates that are presented in~\cref{fig:reg-performance}
-(more details are given in~\cref{tbl:exp4-detailed-results} in the Appendix).
+(and listed in~\cref{tbl:exp4-detailed-results} in the Appendix).
 
@@
 effect on final surrogate precision, suggesting that the runtime of MCMC on each
-iteration can be limited for increased efficiency. -- Awaiting test results on
+iteration can be limited for increased efficiency. -- Awaiting test results on % TODO
 initial sample quantity --. The most complex dynamics arose with the adjustment

### 2020-04-30 final_report/methodology.tex
add bayesian optimisation reference

@@
 searches of a possibly high-dimensional parameter space, Bayesian
-optimisation is employed as a standard hyperparameter tuning algorithm. We set
+optimisation~\cite{movckus1975bayesian} is employed as a standard hyperparameter tuning algorithm. We set
 its objective to maximise $R^2$ and perform

### 2020-04-30 final_report/methodology.tex
use '-ise' instead of '-ize'

@@
 lifting, methods driven by decision trees, instance-based learning models,
-ensemble regressors, randomized algorithms, artificial neural networks and mathematical approaches
+ensemble regressors, randomised algorithms, artificial neural networks and mathematical approaches
 developed specifically for the purposes of surrogate modelling. For each of
@@
 		Gradient boosted trees~\cite{friedman2001greedy,friedman1999stochastic,hastie2009elements}	& GBT & SciKit Learn & 11 \\
-		Extremely randomized trees~\cite{geurts2006extremely}	& ERT & SciKit Learn & 7 \\
+		Extremely randomised trees~\cite{geurts2006extremely}	& ERT & SciKit Learn & 7 \\
 		AdaBoosted decision trees~\cite{drucker1997improving}	& ABT & SciKit Learn & 3 \\

### 2020-04-30 final_report/data.tex
Followed comments from Nikos and Vignesh.
update Hypatia footnote to reflect CPU count

@@
 4~homogeneous nodes, each containing 40 cores.\footnote{Hypatia RCIF nodes use
-Intel\textsuperscript{\textregistered} Xeon\textsuperscript{\textregistered}
-Gold 6148 CPU with frequency 2.40~GHz and 376 GB RAM.} We completed three data
+40~Intel\textsuperscript{\textregistered} Xeon\textsuperscript{\textregistered}
+Gold 6148 CPUs with frequency 2.40~GHz and 376 GB RAM.} We completed three data
 generation runs, which are summarised in~\cref{tbl:sampling-runs}.
@@
 
-\Cref{fig:pca} shows the resultant cumulative variance of PCA-identified feature vectors. The similar share of variance among all features
+\Cref{fig:pca} shows the resultant cumulative variance of the 11 principal components. The similar share of variance among all features
 reveals irreducibility of the TBR model by linear methods.

### 2020-04-30 final_report/data.tex
get figure 2 sorted

@@
 
-Model training over high-dimensional parameter spaces may be improved in many
+Model training over high-dimensional parameter spaces (illustrated
+in~\cref{fig:tbr-vs-features}) may be improved in many
 aspects by carefully reducing the number of variables used to describe the
@@
 	\caption{Marginalised dependence of TBR on the choice of continuous
-	features.}
+	features in \num{500000}~points collected in run~1. Points are coloured by density.}
   \label{fig:tbr-vs-features}
 \end{figure}
-
-% TODO: tie the figure above to the paragraph above
 

### 2020-04-30 final_report/conclusion.tex
Change speedup value formatting.

--- 2020-04-30 final_report/conclusion.tex
@@
 of~$\SI{0.898}{\micro\second}$, representing a relative
-speedup~$\num{8659251} \times$ with respect to the MC model. Alternatively, we
+speedup of $8\cdot 10^6$ with respect to the MC model. Alternatively, we
 also demonstrated the possibility of achieving comparable results using only a

### 2020-04-30 final_report/tbr_final_report-metadata.tex
Change speedup value formatting.

@@
  models, the best of which demonstrated~$R^2=\num{0.998}$ and a mean
- prediction time of~$\SI{0.898}{\micro\second}$, representing a relative speedup~$\num{8659251} \times$
+ prediction time of~$\SI{0.898}{\micro\second}$, representing a relative speedup of $8\cdot 10^6$
  with respect to the expensive MC model. We further present a novel adaptive

### 2020-04-30 final_report/sinmodel_TBR.m
Vectorised sin toy model figure.

@@ -13,5 +13,5 @@ set(gca,'xticklabel',[0,1])
 set(gca,'ytick',[0,1])
 set(gca,'yticklabel',[0,1])
 
-xlabel('Continuous parameter A')
-ylabel('Continuous parameter B')
+xlabel('Continuous parameter x_1')
+ylabel('Continuous parameter x_2')

### 2020-04-30 final_report/methodology.tex
Vectorised sin toy model figure.
.fig file for sin toy model, some figure placement adjustments.

@@
 
+\begin{wrapfigure}[25]{r}{0.55\textwidth}
+	\centering
+	\vspace{-3ex}
+	\includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
+	\caption{Schematic of QASS algorithm}
+	\label{fig:qassplan}
+\end{wrapfigure}
+
 All of the surrogate modelling techniques studied in this project face a shared
@@
 
-Adaptive sampling techniques are widespread in the literature and have been
+Adaptive sampling techniques appear frequently in the literature and have been
 specialised for surrogate modelling. Garud's \cite{Garud2016} "Smart Sampling
@@
 optima in the feature space. MCMC produces a progressive chain of sample points,
-each drawn according to the same symmetric proposal distribution
+each drawn according to the same symmetric proposal distribution\footnote{An
+adaptive MCMC procedure \cite{Zhang2012}, which adjusts an ellipsoidal proposal
+distribution to fit the posterior, was also implemented but not fully tested.}
 from the prior point. These sample points will converge to a desired posterior
@@
 for a review).
-
-%\footnote{An
-%adaptive MCMC procedure \cite{Zhang2012}, which adjusts an ellipsoidal proposal
-%distribution to fit the posterior, was also implemented but not fully tested.}
-
-\begin{wrapfigure}[22]{r}{0.55\textwidth}
-	\centering
-	\vspace{-5ex}
-	\includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
-	\caption{Schematic of QASS algorithm}
-	\label{fig:qassplan}
-\end{wrapfigure}
 

### 2020-04-30 final_report/sinmodel_TBR.m
intermediate update

@@ -1,3 +1,6 @@
+pos = get(gca, 'Position');
+set(gca, 'Position', [pos(1) pos(2)+0.01 pos(3) pos(4)-0.01]);
+
 wn=1
 
 f=@(x,y) sin(wn*2*pi*(x-0.5))/2 + sin(wn*2*pi*(y-0.5))/2 + 1;
@@ -15,3 +18,5 @@ set(gca,'yticklabel',[0,1])
 
 xlabel('Continuous parameter x_1')
 ylabel('Continuous parameter x_2')
+
+savefig('asd.pdf')

### 2020-04-30 final_report/sinmodel_TBR.m
regenerate figure 13

@@ -1,14 +1,11 @@
-pos = get(gca, 'Position');
-set(gca, 'Position', [pos(1) pos(2)+0.01 pos(3) pos(4)-0.01]);
-
 wn=1
 
 f=@(x,y) sin(wn*2*pi*(x-0.5))/2 + sin(wn*2*pi*(y-0.5))/2 + 1;
 [X,Y]=meshgrid(0:0.001:1);
 z=f(X,Y);
 [C,h] = contourf(X,Y,z,9);   
-clabel(C,h,'FontSize',15)
-set(gca,'fontsize', 24)
+clabel(C,h,'FontSize',11)
+%set(gca,'fontsize', 24)
 
 set(gca,'xtick',[0,1])
 set(gca,'xticklabel',[0,1])
@@ -18,5 +15,3 @@ set(gca,'yticklabel',[0,1])
 
 xlabel('Continuous parameter x_1')
 ylabel('Continuous parameter x_2')
-
-savefig('asd.pdf')

### 2020-04-30 final_report/introduction.tex
correct quotation marks

@@
 
-Surrogate models, or metamodels, can resolve this limitation by replacing a resource-expensive procedure with a much cheaper approximation \cite{Sondergaard2003}.
-They are especially useful in applications where numerous evaluations of an expensive procedure are required over the same or similar domains, e.g.
-in the parameter optimisation of a theoretical model.
-The term ``metamodel" proves especially meaningful in this case, when the surrogate model approximates a computational process which is itself a model for a (perhaps unknown) physical process \cite{Myers2002}.
-There exists a spectrum between ``physical" surrogates which are constructed with some contextual knowledge in hand, and ``empirical" surrogates which are derived purely from samples of the underlying expensive model.
+Surrogate models, or metamodels, can resolve this limitation by replacing a
+resource-expensive procedure with a much cheaper approximation
+\cite{Sondergaard2003}. They are especially useful in applications where
+numerous evaluations of an expensive procedure are required over the same or
+similar domains, e.g. in the parameter optimisation of a theoretical model. The
+term ``metamodel'' proves especially meaningful in this case, when the surrogate
+model approximates a computational process which is itself a model for a
+(perhaps unknown) physical process \cite{Myers2002}. There exists a spectrum
+between ``physical'' surrogates which are constructed with some contextual
+knowledge in hand, and ``empirical'' surrogates which are derived purely from
+samples of the underlying expensive model.
 

### 2020-04-30 final_report/methodology.tex
correct quotation marks

@@
 Adaptive sampling techniques appear frequently in the literature and have been
-specialised for surrogate modelling. Garud's \cite{Garud2016} "Smart Sampling
-Algorithm" achieved notable success by incorporating surrogate quality and
+specialised for surrogate modelling. Garud's \cite{Garud2016} ``Smart Sampling
+Algorithm'' achieved notable success by incorporating surrogate quality and
 crowding distance scoring to identify optimal new samples, but was only tested

### 2020-04-30 final_report/results.tex
finalise model 8 in figure 12
reorder experiment 4 models (only in TeX, not in files)
.fig file for sin toy model, some figure placement adjustments.
intermediate update
regenerate figure 13
correct quotation marks

@@
 
-\begin{wrapfigure}[10]{r}{0.333\textwidth}
+\begin{wrapfigure}[12]{r}{0.333\textwidth}
 	\centering
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model1}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{exp4_model2}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{exp4_model3}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{exp4_model4}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.25\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{exp4_model5}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
-		\centering
 		\includegraphics[width=\linewidth]{exp4_model6}
@@
 		\centering
-		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
-		% TODO: only a placeholder, regenerate when data becomes available
+		\includegraphics[width=\linewidth]{exp4_model1}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.25\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{exp4_model3}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.25\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{exp4_model4}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.25\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{exp4_model5}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.25\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{exp4_model2}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.25\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{exp4_model8}
 	\end{subfigure}
@@
 
-\begin{wrapfigure}[13]{r}{0.4\textwidth}
+\begin{wrapfigure}[11]{r}{0.42\textwidth}
 	\centering
-	\vspace{-12ex}
-	\includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
-	\caption{Sinusoidal toy TBR theory over two continuous parameters, wavenumber 1}
+	\vspace{-13ex}
+	\includegraphics[width=0.42\textwidth]{fig5_sintoy}
+	\caption{Sinusoidal toy TBR theory over two continuous parameters,
+	$n=1$.}
 	\label{fig:sintoy}
@@
 effect of retraining the same ANN instance without adjustment to data
-normalisation; a "Goldilocks scheme" for checking normalisation drift was
+normalisation; a ``Goldilocks scheme'' for checking normalisation drift was
 implemented and tested, but did not affect QASS performance. Schemes in which

### 2020-05-01 final_report/conclusion.tex
integrate Sim's comments

@@
-Over the course of this internship project, we employed a broad spectrum of data
+Over the course of this project, we employed a broad spectrum of data
 analysis and machine learning techniques to develop fast and high-quality
-surrogates for a~MC TBR model in use at~UKAEA. We generated over~\num{900000}
-samples for training and test purposes, evaluated on this expensive MC~model. We
+surrogates for a~MC TBR simulation in use at~UKAEA. Having implemented a sampling
+software to efficiently evaluate this expensive MC~model, we deployed it on a
+high performance cluster to generate over~\num{900000}
+datapoints for training and test purposes. We
 investigated possibilities for simplification of the parameter space, and
@@
 unrestricted feature space, and studying their scaling properties, we retrained
-some of the best-performing instances to produce properties desirable for
-practical use. The best approximator, trained on~\num{500000} datapoints,
-featured~$R^2=\num{0.998}$ with mean prediction time
+the best-performing instances to produce properties desirable for
+practical use. The fastest surrogate, an artificial neural network trained
+on~\num{500000} datapoints, featured~$R^2=\num{0.985}$ with mean prediction time
 of~$\SI{0.898}{\micro\second}$, representing a relative
@@
 After a thorough review of the literature, we developed a novel adaptive
-sampling algorithm, QASS, capable of interfacing with any of the individual
-studied models. Preliminary testing on a toy theory, qualitatively comparable to
+sampling algorithm, QASS, capable of interfacing with any of the studied
+surrogates. Preliminary testing on a toy theory, qualitatively comparable to
 the MC TBR model, demonstrated the effectiveness of QASS and behavioural trends
-consistent with the design of the algorithm. \textit{[Insert numerical results
+consistent with the design of the algorithm. \textit{[Insert numerical results % TODO
 for QASS.]} Further optimisation over the hyperparameter space has strong
 potential to increase this performance, allowing for future deployment of QASS
-on the MC TBR model in coalition with any of the most effective identified
-surrogate models.
+in coalition with any of the most effective identified surrogates to facilitate
+learning during evaluation of the MC TBR model.
 
@@
 
-The authors would like to thank Vignesh Gopakumar, Prof.~Nikolaos
+The authors would like to thank Simeon Bash, Vignesh Gopakumar, Prof.~Nikolaos
 Konstantinidis, Nikolaos Nikolaou, Prof.~Emily Nurse, Jonathan Shimwell and Ingo

### 2020-05-01 final_report/introduction.tex
integrate Sim's comments

@@
 model approximates a computational process which is itself a model for a
-(perhaps unknown) physical process \cite{Myers2002}. There exists a spectrum
+(perhaps unknown) physical process~\cite{Myers2002}. There exists a spectrum
 between ``physical'' surrogates which are constructed with some contextual
@@
 In this internship project, in coordination with the UK Atomic Energy Authority (UKAEA), we sought to develop a surrogate model for the tritium breeding ratio (TBR) in a Tokamak nuclear fusion reactor.
-Our expensive model was an MC-based neutronics simulation, \textit{Paramak} \footnote{Provided by collaborator Jonathan Shimwell, at UKAEA.}, which returns a prediction of the TBR for a given configuration of a spherical Tokamak.
+Our expensive model was an MC-based neutronics simulation, \textit{Paramak}\footnote{Provided by collaborator Jonathan Shimwell, at UKAEA.}, which returns a prediction of the TBR for a given configuration of a spherical Tokamak.
 We took an empirical approach to the construction of this surrogate, and no results described here are explicitly dependent on prior physics knowledge.
@@
 of a star, hydrogen atoms attain energies sufficient to overcome their usual
-electrostatic repulsion and fuse to form helium \cite{Hernandez2018}. Early prototype reactors
+electrostatic repulsion and fuse to form helium~\cite{Hernandez2018}. Early prototype reactors
 made use of the deuterium (\isotope[2]{H}, or \isotope{D}) isotope of hydrogen in order to
@@
 use of tritium (\isotope[3]{H}, or \isotope{T}) fuel for further efficiency gain.
-Experimentation at JET dating back to 1997 \cite{Keilhacker1999} has made significant headway in
+Experimentation at JET dating back to 1997~\cite{Keilhacker1999} has made significant headway in
 validating deuterium-tritium (D-T) operations and constraining the technology
@@
   \end{center}
-  \caption{Typical single-null reactor configuration as specified by BLUEPRINT \cite{Coleman2019}: 1 — plasma,
+  \caption{Typical single-null reactor configuration as specified by BLUEPRINT~\cite{Coleman2019}: 1 — plasma,
 2 — breeding blankets }
@@
 less frequently occurring isotopes of lithium, respectively. \isotope[6]{Li} has
-the greatest tritium breeding cross-section of all tested isotopes \cite{Hernandez2018}, but due
+the greatest tritium breeding cross-section of all tested isotopes~\cite{Hernandez2018}, but due
 to magnetohydrodynamic instability of liquid lithium in the reactor environment,

### 2020-05-01 final_report/methodology.tex
integrate Sim's comments

--- 2020-04-30 final_report/methodology.tex
@@
 Following the motivation of this work, two desirable properties of surrogates
-arise: (i) their capability to approximate the TBR MC model well and (ii) their
+arise: (a) their capability to approximate the TBR MC model well and (b) their
 prediction time. An ideal surrogate would maximise
@@
 To prevent undesirable bias in results due to training set selection, all metrics
-are collected in the scheme of $k$-fold cross-validation with a standard choice of
-$k=5$. Herein, a sample set is subdivided into 5 disjoint folds, each of which
+are collected in the scheme of $k$-fold cross-validation with a conventional choice of
+$k=5$. In this setting, a sample set is divided into 5 disjoint folds, each of which
 is used as a test set for the model trained on the remaining 4.\footnote{Unless explicitly stated otherwise, we use 1
@@
 Since this process requires learning the behaviour of an unknown, possibly
-expensive mapping---here a function that assigns cross-validated metrics to a
-point in the hyperparameter domain---it in many aspects mirrors
+expensive mapping -- here a function that assigns cross-validated metrics to a
+point in the hyperparameter domain -- it in many aspects mirrors
 the primary task of this work with the notable extension of added utility
@@
 	terminated after 2~days. Instances that reached this limit may be identified
-	in~\cref{tbl:exp1-detailed-results,tbl:exp2-detailed-results}.}
+	in~\cref{tbl:exp1-detailed-results,tbl:exp2-detailed-results} in the
+	Appendix.}
 
@@
 
-All of the surrogate modelling techniques studied in this project face a shared
+All of the surrogate modelling techniques studied in this project face a common
 challenge: their accuracy is limited by the quantity of training samples which
@@
 Adaptive sampling techniques appear frequently in the literature and have been
-specialised for surrogate modelling. Garud's \cite{Garud2016} "Smart Sampling
-Algorithm" achieved notable success by incorporating surrogate quality and
+specialised for surrogate modelling. Garud's~\cite{Garud2016} ``Smart Sampling
+Algorithm'' achieved notable success by incorporating surrogate quality and
 crowding distance scoring to identify optimal new samples, but was only tested
@@
 each drawn according to the same symmetric proposal distribution\footnote{An
-adaptive MCMC procedure \cite{Zhang2012}, which adjusts an ellipsoidal proposal
+adaptive MCMC procedure~\cite{Zhang2012}, which adjusts an ellipsoidal proposal
 distribution to fit the posterior, was also implemented but not fully tested.}
@@
 distribution, so long as the acceptance probability for these draws has a
-particular functional dependence on that posterior value (see \cite{Zhou2018}
+particular functional dependence on that posterior value (see~\cite{Zhou2018}
 for a review).
@@
 Many researchers have embedded surrogate methods into MCMC strategies for
-parameter optimisation \cite{Zhang2020,Gong2017}, in particular the ASMO-PODE
-algorithm \cite{Ginting2011} which makes use of MCMC-based adaptive sampling to
+parameter optimisation~\cite{Zhang2020,Gong2017}, in particular the ASMO-PODE
+algorithm~\cite{Ginting2011} which makes use of MCMC-based adaptive sampling to
 attain greater surrogate precision around prospective optima. Our novel approach
@@
 points which maximise surrogate error and minimise a crowding distance metric
-(CDM) \cite{Solonen2012} in feature space.
+(CDM)~\cite{Solonen2012} in feature space.
 On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and absolute error calculated.
@@
 
-% Adaptive multi-chain MCMC: \cite{Zhang2012}
+% Adaptive multi-chain MCMC:~\cite{Zhang2012}

### 2020-05-01 final_report/results.tex
integrate Sim's comments

@@
 In the third experiment we examine surrogate scaling properties by correlating
-metrics of interest with training set size. First, the results shown 
+metrics of interest with training set size. Firstly, the results shown 
 in~\cref{fig:scaling-r2} (and listed in~\cref{tbl:exp3-detailed-results-r2} in
@@
 Furthermore, we observe that the majority of tree-based algorithms also exhibit
-desirable properties unlike RBFs and gaussian process
-regression, which appear to scale superlinearly. We note that ANNs,
+desirable properties unlike RBFs and GPR, which appear to scale superlinearly. We note that ANNs,
 which are the only family to utilise parallelisation during training, show an
@@
 
-Lastly, we study scaling with respect to the mean prediction time (shown
+Finally, we study scaling with respect to the mean prediction time (shown
 in~\cref{fig:scaling-pred} and listed in~\cref{tbl:exp3-detailed-results-t-pred} in
@@
 learning methods offer desirable characteristics overall. Analogous to previous
-experiments, GBTs and ANNs again
-appear to be tied, as they not only exhibit comparable times but also similar
+experiments, GBTs and ANNs again appear to be tied, as they not only exhibit comparable times but also similar
 scaling slopes.
@@
 
-In the fourth experiment, we exploit previously collected information
+In the fourth experiment proposed
+in~\cref{sec:experiment-methodology}, we exploit previously collected information
 to produce surrogates with desirable properties for practical use. We
-aim to create models that yield: (i)~the best regression performance regardless
-of other features, (ii)~acceptable performance with the shortest mean
-prediction time, or (iii)~acceptable performance with the smallest training set.
+aim to create models that yield: (a)~the best regression performance regardless
+of other features, (b)~acceptable performance with the shortest mean
+prediction time, or (c)~acceptable performance with the smallest training set.
 To this end, we trained 8~surrogates that are presented in~\cref{fig:reg-performance}
-(and listed in~\cref{tbl:exp4-detailed-results} in the Appendix).
+and~\cref{tbl:exp4-detailed-results}.
 
@@
 		(row 2) trained in experiment~4 (model comparison), viewed
-		as true vs. predicted TBR on a test set of a selected cross-validation
+		as true vs.~predicted TBR on a test set of a selected cross-validation
 		fold. Points are coloured by density.}
@@
 
-Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of the
+Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
 experiments~2-3, we utilised the best-performing hyperparameter
-assignments and training sets of varying sizes. In attempts to satisfy
-goals~(i) and~(ii) within cross-validation setting, our best surrogate
-achieved~$R^2=\num{0.998}$ and mean prediction
-time~$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$. These correspond
-to the standard error of regression~$S=\num{0.013}$ and a relative speedup~$\omega=\num{8659251} \times$
+assignments. Trained to satisfy
+goal~(a), the best surrogate (no.~1,
+ANN) achieved~$R^2=\num{0.998}$ and mean prediction
+time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
+to standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
 with respect to the MC TBR evaluation baseline measured during run~1
-(see~\cref{tbl:sampling-runs} for details). While this particular surrogate
-was trained on the entire available set of~\num{500000} datapoints, in attempts to satisfy
-goal~(iii) we also trained a more simplified model that achieved~$R^2=\num{0.913}$,
+(see~\cref{tbl:sampling-runs} for details). Satisfying
+goal~(b), the fastest model (no.~2, ANN) features~$R^2=\num{0.985}$,
+$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
+and~$\omega=\num{8659251} \times$.
+While these surrogates
+were trained on the entire available set of~\num{500000} datapoints, pursuing
+goal~(c) we also trained a simplified model (no.~5, GBT) that achieved~$R^2=\num{0.913}$,
 $\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
@@
 
-Overall we found that due to their excellent performance, boosted tree-based
+\begin{table}[h]
+	\centering
+	\sisetup{round-mode=places,round-precision=3,detect-weight=true,detect-family=true}
+	\setlength\tabcolsep{2pt}
+	{\scriptsize
+		\begin{tabular}{lrrrrrrrr}
+		\toprule
+		{} & {} & \multicolumn{4}{c}{Regression performance} &
+		\multicolumn{3}{c}{Complexity}\\
+		\cmidrule(lr){3-6}
+		\cmidrule(lr){7-9}
+		Model & $|\mathcal{T}|$ & MAE [TBR] & $S$ [TBR] & $R^2$ [rel.] & $R^2_{\text{adj.}}$ [rel.]
+						& $\overline{t}_{\text{trn.}}$ [\si{\milli\second}] &
+		$\overline{t}_{\text{pred.}}$ [\si{\milli\second}] & $\omega$ [rel.]\\
+		\midrule
+		\input{tbl/table11}
+		\bottomrule
+		\end{tabular}
+	}
+	\caption{Results of experiment~4. Here, means and
+		standard deviations are reported over 5~cross-validation folds. In addition, we also give
+		cross-validation set size $|\mathcal{T}|$ (in thousands of datapoints)
+		and relative speedup $\omega$ with respect to the
+		MC TBR model mean evaluation time \SI{7.777049573054314}{\second} (per
+		sample) measured during run~1 (see~\cref{tbl:sampling-runs} for details).
+		The best-performing metrics are highlighted in bold.}
+	\label{tbl:exp4-detailed-results}
+\end{table}
+
+Overall we found that due to their superior performance, boosted tree-based
 approaches seem to be advantageous for fast surrogate modelling on relatively small training
 sets (up to the order of~$10^4$). Conversely, while neural networks perform
-poorly in such a setting, both their regression performance and prediction times
-have proven superior on larger training sets (at least of the order of~$10^5$).
+poorly in such a setting, they become dominant on larger training
+sets (at least of the order of~$10^5$) both in terms of regression performance
+and mean prediction time.
 
-\begin{wrapfigure}[11]{r}{0.42\textwidth}
+\subsection{Results of Adaptive Sampling}
+\label{sec:adaptiveres}
+\begin{wrapfigure}[10]{r}{0.42\textwidth}
 	\centering
@@
 
-\subsection{Results of Adaptive Sampling}
-\label{sec:adaptiveres}
-
 In order to test our QASS prototype, several functional toy theories for TBR were developed as alternatives to the expensive MC model.
@@
 \begin{equation}
-	\text{TBR} = \text{Mean}_{i \in C} \left[ \frac{1 + \sin(2\pi n (x_i - 1/2)) }{2} \right]
+	\text{TBR} = \frac{1}{|C|}\sum_{i \in C} \left[ \frac{1 + \sin(2\pi n (x_i - 1/2)) }{2} \right]
 \end{equation}
 
-plotted in~\cref{fig:sintoy} for $n=1$ and two continuous parameters $C$. ANNs
+plotted in~\cref{fig:sintoy} for $n=1$ and two continuous parameters $C$.
+
+ANNs
 trained on this model demonstrated similar performance to those on the expensive
@@
 initial sample quantity --. The most complex dynamics arose with the adjustment
-of sample increment, shown in~\cref{fig:qassincr}.
-For each tested initial sample quantity N, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$; the plotted error trends suggest that incremental samples larger than this optimum give slower model improvement on both the training and evaluation sets, and a larger minimum error on the evaluation set.
-This performance distinction is predicted to be even more significant when trained on the expensive MC model, where the number of sample evaluations will serve as the primary bottleneck for computation time.
+of sample increment, shown in~\cref{fig:qassincr}. For each tested initial
+sample quantity N, the optimal number of step samples was seen to be
+well-approximated by $\sqrt{N}$. The plotted error trends suggest that
+incremental samples larger than this optimum give slower model improvement on
+both the training and evaluation sets, and a larger minimum error on the
+evaluation set. This performance distinction is predicted to be even more
+significant when trained on the expensive MC model, where the number of sample
+evaluations will serve as the primary bottleneck for computation time.
 \begin{figure}[h!]
@@
 effect of retraining the same ANN instance without adjustment to data
-normalisation; a ``Goldilocks scheme'' for checking normalisation drift was
+normalisation. A ``Goldilocks scheme'' for checking normalisation drift was
 implemented and tested, but did not affect QASS performance. Schemes in which
@@
     \includegraphics[width=0.78\linewidth]{fig7_qasssampling.pdf}
-    \caption{Absolute training error for QASS, baseline scheme, and mixed scheme}
+    \caption{Absolute training error for QASS, baseline scheme, and mixed
+	scheme.}
   \label{fig:qasssampling}

### 2020-05-01 final_report/tbr_final_report-metadata.tex
put author names in alphabetical order
integrate Sim's comments

@@
  ratio between tritium fuel generated in breeding blankets and fuel consumed
- during reactor runtime, the TBR depends in a
- complex manner on reactor geometry and material properties. We explored the
+ during reactor runtime, the TBR depends on reactor geometry and material
+ properties in a complex manner. In this work, we explored the
  training of surrogate models to produce a cheap but high-quality approximation
  for a Monte Carlo TBR model in use at the UK Atomic Energy Authority. We
- investigated possibilities for dimensional reduction on the feature space of
- this model, reviewed 9~families of surrogate models for potential
- applicability and performed hyperparameter optimisation. Here we present the
+ investigated possibilities for dimensional reduction of its feature space, reviewed
+ 9~families of surrogate models for potential
+ applicability, and performed hyperparameter optimisation. Here we present the
  performance and scaling properties of these
- models, the best of which demonstrated~$R^2=\num{0.998}$ and a mean
+ models, the fastest of which, an artificial neural network,
+ demonstrated~$R^2=\num{0.985}$ and a mean
  prediction time of~$\SI{0.898}{\micro\second}$, representing a relative speedup of $8\cdot 10^6$
  with respect to the expensive MC model. We further present a novel adaptive
- sampling algorithm, QASS, capable
- of interfacing with any of the individual studied models. Our preliminary
+ sampling algorithm, Quality-Adaptive Surrogate Sampling, capable
+ of interfacing with any of the individually studied surrogates. Our preliminary
  testing on a toy TBR theory has demonstrated the efficacy of this algorithm for
@@
 \usepackage{authblk}
+\author[a]{Graham Van Goffrier}
 \author[a]{Petr Mánek}
-\author[a]{Graham Van Goffrier}
 \affil[a]{University College London}

### 2020-05-01 final_report/conclusion.tex

@@
 the MC TBR model, demonstrated the effectiveness of QASS and behavioural trends
-consistent with the design of the algorithm. \textit{[Insert numerical results % TODO
-for QASS.]} Further optimisation over the hyperparameter space has strong
-potential to increase this performance, allowing for future deployment of QASS
+consistent with the design of the algorithm.
+With~\num{100000} initial samples and 100 incremental samples per iteration, QASS achieved a ${\sim}60\%$ decrease in surrogate error as compared with a baseline random sampling scheme.
+Equivalently, the same surrogate error as the baseline could be achieved with ${\sim}6\%$ fewer total samples of the expensive theory.
+Further optimisation over the hyperparameter space has strong
+potential to increase this performance, in particular by decreasing the required quantity of initial samples. This will allow for future deployment of QASS
 in coalition with any of the most effective identified surrogates to facilitate

### 2020-05-01 final_report/data.tex

@@
 
-The MC TBR model that we understand to be the expensive function for our
-surrogate modelling is fundamentally a Monte Carlo simulation based on the
-OpenMC framework~\cite{ROMANO201590}. As input the software expects a set of 19~parameters, discrete and
-continuous, that are fully listed in~\cref{tbl:params}. Following a brief period of
-time (usually of the order of tens of seconds), during which a fixed number of
-events is generated, the simulation outputs the
-mean and the standard deviation of the TBR aggregated over the simulated run. The
-former of these two we accept to be the output TBR value that is subject
-to approximation.
+The expensive MC TBR model is fundamentally a Monte Carlo simulation based on the
+OpenMC framework~\cite{ROMANO201590}. As input the software expects 18~parameters, discrete and
+continuous, that are fully listed in~\cref{tbl:params}. During evaluation, which
+usually takes units of seconds, a fixed number of events is simulated, and the
+results are given in terms of the mean and the standard deviation of the~TBR aggregated
+over the simulated run. The former of these two we accept to be the output TBR
+value that is subject to approximation.
 
@@
 
-In our work, we often reference TBR points or samples. These are simply vectors
+In the following sections, we often reference TBR points or samples. These are simply vectors
 in the feature space generated by Cartesian product of domains of all
@@
 
-While we deliberately make no assumptions about the internal properties of the
-MC TBR simulation, effectively treating it as a black box model, our means of
-studying its behaviour are limited to inspection of its outputs at various
-points in the feature space, and inference thereof. We thus require
+In our work, we deliberately make no assumptions about the internal properties of the
+MC TBR simulation, effectively treating it as a black box model. This limits our
+means of studying its behaviour to inspection of its outputs at various
+points in the feature space. We therefore require
 sufficiently large and representative quantities of samples to ensure that
@@
 
-With grid search in such a high-dimensional domain clearly intractable, we
+With a grid search in such a high-dimensional domain clearly intractable, we
 selected uniform pseudo-random sampling\footnote{Continuous and discrete
@@
 previously generated points in the feature space.
-We deployed ATE at the UCL Hypatia cluster RCIF partition, which consists of
-4~homogeneous nodes, each containing 40 cores.\footnote{Hypatia RCIF nodes use
-40~Intel\textsuperscript{\textregistered} Xeon\textsuperscript{\textregistered}
-Gold 6148 CPUs with frequency 2.40~GHz and 376 GB RAM.} We completed three data
-generation runs, which are summarised in~\cref{tbl:sampling-runs}.
+Having deployed ATE at the UCL Hypatia cluster,\footnote{The Hypatia RCIF
+	partition is comprised of 4~homogeneous nodes. Each node is installed with
+	376~GB RAM and 40~Intel\textsuperscript{\textregistered}
+	Xeon\textsuperscript{\textregistered} Gold 6148 CPUs of clock frequency
+	2.40~GHz.} we completed 3~data
+generation runs that are summarised in~\cref{tbl:sampling-runs}.
 
@@
 identifying a sufficiently representative subset of the original input
-variables; however, all given variables were assumed to be physically relevant
-to the MC TBR model. Feature extraction methods, on the other hand, aim to
+variables. However, all given variables were assumed to be physically relevant
+to the MC TBR model. On the other hand, feature extraction methods aim to
 identify a transformation of the parameter space which decreases dimensionality; even if no individual parameter is separable from the space, some linear combinations of parameters or nonlinear functions of parameters may be.
@@
 Kriging is a geostatistical surrogate modelling technique which relies on
-correlation functions over distance (lag) in the feature space \cite{Bouhlel2018}.
+correlation functions over distance (lag) in the feature space~\cite{Bouhlel2018}.
 Although kriging performed poorly for our use case due to high dimensionality, these correlation measures gave insight into similarities between discrete-parameter slices of the data.
 
-\Cref{fig:var} shows the Matheron semivariance \cite{Matheron1963} for three discrete slices with coolant material varied, but all other discrete parameters fixed.
-Fits \cite{KrigingFig} to the Matérn covariance model confirmed numerically that the coolant material is the discrete parameter with the greatest distinguishability in the MC TBR model.
+\Cref{fig:var} shows the Matheron semivariance~\cite{Matheron1963} for three discrete slices with coolant material varied, but all other discrete parameters fixed.
+Fits~\cite{KrigingFig} to the Matérn covariance model confirmed numerically that the coolant material is the discrete parameter with the greatest distinguishability in the MC TBR model.
 
@@
 \num{100000}~samples from batches 0-99 of the corresponding runs.} of samples:
-(i)~a subset of data obtained
-from run~1 and (ii)~a subset of a single slice obtained from run~2. Our
+(a)~a subset of data obtained
+from run~1 and (B)~A SUBSet of a single slice obtained from run~2. Our
 expectation was that while the former case would provide meaningful insights into

### 2020-05-01 final_report/results.tex

@@
 
-An increase in MCMC candidate samples was seen to have a positive but very weak
-effect on final surrogate precision, suggesting that the runtime of MCMC on each
-iteration can be limited for increased efficiency. -- Awaiting test results on % TODO
-initial sample quantity --. The most complex dynamics arose with the adjustment
-of sample increment, shown in~\cref{fig:qassincr}. For each tested initial
-sample quantity N, the optimal number of step samples was seen to be
-well-approximated by $\sqrt{N}$. The plotted error trends suggest that
-incremental samples larger than this optimum give slower model improvement on
-both the training and evaluation sets, and a larger minimum error on the
-evaluation set. This performance distinction is predicted to be even more
-significant when trained on the expensive MC model, where the number of sample
-evaluations will serve as the primary bottleneck for computation time.
+An increase in initial samples with increment held constant had a strong impact on final surrogate precision, an early confirmation of basic functionality.
+An increase in MCMC candidate samples was seen to have a positive but very weak effect on final surrogate precision, suggesting that the runtime of MCMC on each iteration can be limited for increased efficiency.
+The most complex dynamics arose with the adjustment of sample increment, shown in~\cref{fig:qassincr}.
+For each tested initial sample quantity N, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$.
+The plotted error trends suggest that
+incremental samples larger than this optimum give slower model improvement on both the training and evaluation sets, and a larger minimum error on the evaluation set.
+This performance distinction is predicted to be even more significant when trained on the expensive MC model, where the number of sample evaluations will serve as the primary bottleneck for computation time.
 \begin{figure}[h!]
@@
 
+\begin{figure}[h]
+  \centering
+    \includegraphics[width=0.78\linewidth]{fig8_qasssampling100k.pdf}
+    \caption{Absolute training error for QASS and baseline scheme, with 100k initial samples.}
+  \label{fig:qasssampling100k}
+\end{figure}
+
 Such tests revealed that while QASS has unmatched performance on its own
@@
 is also shown in~\cref{fig:qasssampling}.
+An increase in initial sample size was observed to also resolve precision in these smooth regions of the toy theory, as the initial samples were obtained from a uniform random distribution.
+As shown in ~\cref{fig:qasssampling100k}, with~\num{100000} initial samples it was possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline scheme.
+Comparing at the point of termination for QASS, this corresponds to a ${\sim}6\%$ decrease in the number of total samples needed to train a surrogate with the same error.

### 2020-05-01 final_report/conclusion.tex
Final QASS results and plots.

@@
 consistent with the design of the algorithm.
-With~\num{100000} initial samples and 100 incremental samples per iteration, QASS achieved a ${\sim}60\%$ decrease in surrogate error as compared with a baseline random sampling scheme.
+With~\num{100000} initial samples and 100 incremental samples per iteration, QASS achieved a ${\sim}40\%$ decrease in surrogate error as compared with a baseline random sampling scheme.
 Equivalently, the same surrogate error as the baseline could be achieved with ${\sim}6\%$ fewer total samples of the expensive theory.

### 2020-05-01 final_report/results.tex
Final QASS results and plots.

@@
 An increase in initial sample size was observed to also resolve precision in these smooth regions of the toy theory, as the initial samples were obtained from a uniform random distribution.
-As shown in ~\cref{fig:qasssampling100k}, with~\num{100000} initial samples it was possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline scheme.
+As shown in ~\cref{fig:qasssampling100k}, with~\num{100000} initial samples it was possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline scheme, from 0.0025 to 0.0015 mean averaged error.
 Comparing at the point of termination for QASS, this corresponds to a ${\sim}6\%$ decrease in the number of total samples needed to train a surrogate with the same error.

### 2020-05-01 final_report/data.tex
more minor edits

@@
 continuous, that are fully listed in~\cref{tbl:params}. During evaluation, which
-usually takes units of seconds, a fixed number of events is simulated, and the
+usually takes units of seconds, a fixed number of neutron events is generated, and the
 results are given in terms of the mean and the standard deviation of the~TBR aggregated
@@
 sufficiently large and representative quantities of samples to ensure that
-surrogates can be trained to approximate the MC TBR model.
+surrogates can be trained to approximate the MC TBR model accurately.
 
@@
 previously generated points in the feature space.
-Having deployed ATE at the UCL Hypatia cluster,\footnote{The Hypatia RCIF
+Having deployed ATE at the UCL Hypatia cluster\footnote{The Hypatia RCIF
 	partition is comprised of 4~homogeneous nodes. Each node is installed with
@@
 	Xeon\textsuperscript{\textregistered} Gold 6148 CPUs of clock frequency
-	2.40~GHz.} we completed 3~data
+	2.40~GHz.}, we completed three data
 generation runs that are summarised in~\cref{tbl:sampling-runs}.
@@
 		time (including waiting in the processing queue), and
-		$\overline{t}_{\text{eval.}}$ is the mean evaluation time of MC TBR (per single
-		sampled point).}
+		$\overline{t}_{\text{eval.}}$ is the mean evaluation time of the MC TBR
+		model (per single sampled point).}
 	\label{tbl:sampling-runs}
@@
 	\caption{Marginalised dependence of TBR on the choice of continuous
-	features in \num{500000}~points collected in run~1. Points are coloured by density.}
+	features in \num{500000}~points generated in run~1. Points are coloured by density.}
   \label{fig:tbr-vs-features}
@@
 	\caption{Autoencoder with input width~$W_0$ and bottleneck width~$W_1$.
-	Here, $\text{Dense}(N)$ denotes a fully-connected layer of $N$ neurons.}
+	Here, $\text{Dense}(N)$ denotes a fully-connected layer of $N$~neurons.}
 	\label{fig:autoencoder}
@@
 \num{100000}~samples from batches 0-99 of the corresponding runs.} of samples:
-(a)~a subset of data obtained
-from run~1 and (B)~A SUBSet of a single slice obtained from run~2. Our
+(a)~a~subset of data obtained
+from run~1 and (b)~a~subset of a single slice obtained from run~2. Our
 expectation was that while the former case would provide meaningful insights into
@@
 must also conclude that in both examined cases this method failed to produce a
-reduction that would be superior to a naïve approach.\footnote{In both tested cases we
-	can trivially eliminate 7~dimensions due to overdetermined one-hot-encoded
-	features and 2~dimensions due to sum-to-one constraints. Furthermore, in the
-	single slice case we may omit 7~additional dimensions due to artificially fixed
-features.} This is consistent with previous results obtained by PCA and kriging.
+reduction that would prove superior to a naïve approach.\footnote{In both tested cases we
+	can trivially eliminate 6~dimensions due to overdetermination of one-hot-encoded
+	categorical features, and 2~dimensions corresponding to sum-to-one constraints. Furthermore, in the
+	single slice case we may omit 6~additional dimensions due to fixed feature
+	assignment.} This is consistent with previous results obtained by PCA and kriging.
 

### 2020-05-01 final_report/introduction.tex
more minor edits

@@
 
-In this internship project, in coordination with the UK Atomic Energy Authority (UKAEA), we sought to develop a surrogate model for the tritium breeding ratio (TBR) in a Tokamak nuclear fusion reactor.
+In this project, in coordination with the UK Atomic Energy Authority (UKAEA), we sought to develop a surrogate model for the tritium breeding ratio (TBR) in a Tokamak nuclear fusion reactor.
 Our expensive model was an MC-based neutronics simulation, \textit{Paramak}\footnote{Provided by collaborator Jonathan Shimwell, at UKAEA.}, which returns a prediction of the TBR for a given configuration of a spherical Tokamak.
@@
 coolants, armours, and neutron multipliers. One notable exception is the
-enrichment ratio, a continuous parameter denoting the presence of
-\isotope[6]{Li}. Our challenge, put simply, was to produce a TBR function which
-takes these same input parameters and approximates the MC TBR model with the
-greatest achievable regression performance.
+enrichment ratio, a continuous parameter denoting the presence
+of~\isotope[6]{Li}. Our challenge, put simply, was to produce a fast TBR
+function which takes these same input parameters and approximates the MC TBR
+model with the greatest achievable regression performance.

### 2020-05-01 final_report/methodology.tex
more minor edits

@@
 to describe the behaviour of $f(x)$ across its domain.
-Depending on specific model family and appropriate choice of its
+Depending on a specific model family and appropriate choice of its
 hyperparameters, surrogate models $\hat{f}(x)$ are trained to minimise
@@
 $\mathcal{T}_0$ is initialised randomly to provide a \textit{burn-in}, and is
-repeatedly extended in epochs, whereby each epoch trains a new surrogate on
+repeatedly extended in epochs, whereby each epoch trains a new surrogate~$\hat{f}_k(x)$ on
 $\mathcal{T}_k$ using the supervised learning procedure, evaluates its
@@
 $\mathcal{T}_k$. This permits the learning algorithm to condition the selection
-of new samples on the evaluation results in order to maximise improvement of
-surrogate performance over complex regions within the domain.
+of new samples in~$\mathcal{T}_{k+1}$ on the evaluation results
+of~$\hat{f}_k(x)$ in order to maximise improvement of
+surrogate performance over complex regions within the feature space.
 
@@
 \Cref{tbl:metrics} provides an exhaustive listing and description of metrics recorded
-in the experiments. For regression performance analysis, we include a selection
+in our experiments. For regression performance analysis, we include a selection
 of absolute metrics to assess the approximation capability of surrogates, and set
@@
 they maintain invariance with respect to the selected domain and image space.
-For complexity analysis, surrogates are assessed in terms of wall time
+For complexity analysis, surrogates are assessed in terms of wall
+time\footnote{Real time elapsed during computation measured by a
+chronometer, here by means of the Python~\texttt{time} package.}
 elapsed during training and predicition. This is motivated by common practical use
@@
 reported per a single datapoint. Even though some surrogates support acceleration
-by means of parallelisation, measures were taken to ensure sequential
-processing of samples to achieve comparability between considered
-models.\footnote{The only exception to this are artificial neural networks, which are
-notoriously slow to train on conventional CPU architectures in serialised
-setting.}
+by means of parallelisation, sequential processing of samples was ensured to
+achieve comparability between considered
+models.\footnote{The only exception to this are artificial neural networks,
+	which require considerable amount of processing power for training on conventional CPU architectures.}
 
@@
 are collected in the scheme of $k$-fold cross-validation with a conventional choice of
-$k=5$. In this setting, a sample set is divided into 5 disjoint folds, each of which
-is used as a test set for the model trained on the remaining 4.\footnote{Unless explicitly stated otherwise, we use 1
+$k=5$. In this setting, a sample set is uniformly divided into 5 disjoint folds, each of which
+is used as a test set for models trained on the remaining 4.\footnote{Unless explicitly stated otherwise, we use 1
 fold for testing and the 4 remaining folds for training. This gives 80\% to
-20\% train-test ratio.} In each such run experiments are
-repeated, and the overall value of each metric is reported as the mean and
+20\% train-test ratio.} Having repeated the same experiment for each such run,
+the overall value of individual metrics is reported in terms of their mean and
 standard deviation over all folds.
@@
 and practically usable results, we require a sufficiently large and diverse pool
-of surrogate families to draw from. This is described by the listing in~\cref{tbl:surrogates}. The presented selection of models includes basic
+of surrogate families to review. This is described by the listing in~\cref{tbl:surrogates}. The presented selection of models includes basic
 techniques suitable for linear regression enhanced by the kernel trick or dimension
@@
 architecture through selection from various parametric graph templates
-(see~\cref{fig:nn-archs} for details). This allows us to realise a simplistic
-network architecture search during the hyperparameter optimisation procedure.
+(illustrated in~\cref{fig:nn-archs}). This allows us to realise a simplistic
+network architecture search during the hyperparameter tuning procedure.
 
@@
 
-The goal of the last two experiments is to exploit the information gathered by
-hyperparameter tuning to investigate scaling properties. In
-the third experiment, the 20~best-performing hyperparameter choices of each family
-(in $R^2$) are used to train surrogates using progressively larger training sets. Following
-that, the fourth experiment aims to produce surrogates for practical use by
-retraining selected well-scaling models to further optimise their properties.
+The objective of the last two experiments is to exploit the information gathered by
+hyperparameter tuning. In the third experiment, the 20~best-performing
+hyperparameter configurations of each family (with respect to~$R^2$) are used to
+perform training on progressively larger sets to investigate their scaling
+properties. Following that, the fourth experiment aims to produce surrogates
+suitable for practical use by retraining selected well-scaling instances on large
+training sets to satisfy the goals of this work.
 

### 2020-05-01 final_report/results.tex
more minor edits

@@
 We begin by comparing a diverse set of surrogate families that we proposed
-to evaluate on previously collected samples of the expensive MC TBR model.
+to evaluate on previously generated samples of the expensive MC TBR model.
 Through the four experimental cases described
@@
 first experiment we limit training and test sets to the scope of four selected
-slices of the feature space, in the second experiment we lift this restriction.
+slices of the feature space, in the second experiment we lift this restriction
+to examine surrogate capability to model a more complex domain.
 
@@
 that many surrogate families consistently achieved worse regression
-performance and prediction times in a more complex, unrestricted domain. The least
+performance and prediction times. The least
 affected models appear to be GBTs, ANNs and ERTs, which are known to be capable of capturing relationships
@@
 appear to be tied for the best performance as well as the shortest prediction
-time. We observe that ERTs trees and RBFs also
-demonstrated satisfactory results, outperforming the remaining surrogates in
+time. We observe that ERTs and RBFs also
+demonstrated satisfactory results, relatively outperforming the remaining surrogates in
 terms of regression performance, and in some cases also in prediction time.
 
-\begin{wrapfigure}[12]{r}{0.333\textwidth}
+\begin{wrapfigure}[10]{r}{0.333\textwidth}
 	\centering
@@
 consistently maintain their relative advantage over others, even as we introduce
-more training data. While such families achieve nearly comparable regression
+more training points. While such families achieve nearly comparable regression
 performance on the largest dataset, in the opposite case methods based on
 decision trees clearly outperform neural networks. This can be observed
-particularly on training sets of sizes up to~\num{6000}.
+particularly on sets of sizes up to~\num{6000}.
 
@@
 are trained trivially at the expense of increased lookup complexity later during prediction.
-Furthermore, we observe that the majority of tree-based algorithms also exhibit
-desirable properties unlike RBFs and GPR, which appear to scale superlinearly. We note that ANNs,
+Furthermore, we observe that the majority of tree-based algorithms also perform
+and scale well, unlike RBFs and GPR which appear to behave superlinearly. We note that ANNs,
 which are the only family to utilise parallelisation during training, show an
@@
 learning methods offer desirable characteristics overall. Analogous to previous
-experiments, GBTs and ANNs again appear to be tied, as they not only exhibit comparable times but also similar
-scaling slopes.
+experiments, GBTs, ABTs and ANNs appear to be tied, as they not only exhibit
+comparable times but also similar scaling slopes. Following that, we notice a
+clear hierarchy of ERTs, SVMs, GPR and RBFs, trailed by IDW and KNNs.
 
@@
 experiments~2-3, we utilised the best-performing hyperparameter
-assignments. Trained to satisfy
-goal~(a), the best surrogate (no.~1,
+assignments. In pursuit of goal~(a), the best approximator (no.~1,
 ANN) achieved~$R^2=\num{0.998}$ and mean prediction
 time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
-to standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
+to a standard error of regression~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
 with respect to the MC TBR evaluation baseline measured during run~1
@@
 While these surrogates
-were trained on the entire available set of~\num{500000} datapoints, pursuing
-goal~(c) we also trained a simplified model (no.~5, GBT) that achieved~$R^2=\num{0.913}$,
-$\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
+were trained on the entire available set of~\num{500000} datapoints, in our
+attempts to satisfy goal~(c) we also trained a more simplified model (no.~4, GBT)
+that achieved~$R^2=\num{0.913}$,
+$\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
 with only a set of size~\num{10000}.

### 2020-05-01 final_report/results.tex
incorporate both changesets
Minor changes

@@
 (see~\cref{tbl:sampling-runs} for details). Satisfying
-goal~(b), the fastest model (no.~2, ANN) features~$R^2=\num{0.985}$,
+goal~(b), the fastest model (no.~2, ANN) achieves~$R^2=\num{0.985}$,
 $\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
@@
 While these surrogates
-were trained on the entire available set of~\num{500000} datapoints, in our
-attempts to satisfy goal~(c) we also trained a more simplified model (no.~4, GBT)
+were trained on the entire available set of~\num{500000} datapoints, to satisfy goal~(c) we also trained a more simplified model (no.~4, GBT)
 that achieved~$R^2=\num{0.913}$,
 $\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
-with only a set of size~\num{10000}.
+with a set of size only~\num{10000}.
 
@@
 \begin{equation}
-	\text{TBR} = \frac{1}{|C|}\sum_{i \in C} \left[ \frac{1 + \sin(2\pi n (x_i - 1/2)) }{2} \right]
+	\text{TBR} = \frac{1}{|C|}\sum_{i \in C} \left[1 + \sin(2\pi n (x_i - 1/2)) \right]
 \end{equation}

### 2020-05-01 final_report/results.tex
Minor edits
fix typesetting again

@@
 
-We begin by comparing a diverse set of surrogate families that we proposed
-to evaluate on previously generated samples of the expensive MC TBR model.
+We begin by comparing the performance of a diverse set of surrogate families on previously generated samples of the expensive MC TBR model.
 Through the four experimental cases described
@@
 consistently maintain their relative advantage over others, even as we introduce
-more training points. While such families achieve nearly comparable regression
-performance on the largest dataset, in the opposite case methods based on
-decision trees clearly outperform neural networks. This can be observed
+more training points. While such families achieve nearly comparable
+performance on the largest dataset, in the opposite case tree-based approaches
+clearly outperform ANNs. This can be observed
 particularly on sets of sizes up to~\num{6000}.
@@
 the Appendix). Our initial observation is that all tested
-surrogate families with the exception of previously mentioned instance-based
-learning methods offer desirable characteristics overall. Analogous to previous
+families with the exception of previously mentioned instance-based
+models offer desirable characteristics overall. Analogous to previous
 experiments, GBTs, ABTs and ANNs appear to be tied, as they not only exhibit
@@
 Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
-experiments~2-3, we utilised the best-performing hyperparameter
-assignments. In pursuit of goal~(a), the best approximator (no.~1,
+experiments~2-3, we utilised the best-performing hyperparameters.
+In pursuit of goal~(a), the best approximator (no.~1,
 ANN) achieved~$R^2=\num{0.998}$ and mean prediction
 time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
-to a standard error of regression~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
+to a standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
 with respect to the MC TBR evaluation baseline measured during run~1
@@
 While these surrogates
-were trained on the entire available set of~\num{500000} datapoints, to satisfy goal~(c) we also trained a more simplified model (no.~4, GBT)
+were trained on the entire available set of~\num{500000} datapoints, to satisfy goal~(c) we also trained a simplified model (no.~4, GBT)
 that achieved~$R^2=\num{0.913}$,
@@
 	}
-	\caption{Results of experiment~4. Here, means and
-		standard deviations are reported over 5~cross-validation folds. In addition, we also give
-		cross-validation set size $|\mathcal{T}|$ (in thousands of datapoints)
-		and relative speedup $\omega$ with respect to the
-		MC TBR model mean evaluation time \SI{7.777049573054314}{\second} (per
-		sample) measured during run~1 (see~\cref{tbl:sampling-runs} for details).
+	\caption{Results of experiment~4. Here, figures are reported over 5~cross-validation folds,
+		$|\mathcal{T}|$~denotes cross-validation set size ($\times 10^3$)
+		and $\omega$ is a relative speedup with respect to
+		$\overline{t}_{\text{eval.}}=\SI{7.777049573054314}{\second}$
+		measured in the MC TBR model during run~1 (see~\cref{tbl:sampling-runs}).
 		The best-performing metrics are highlighted in bold.}
@@
 approaches seem to be advantageous for fast surrogate modelling on relatively small training
-sets (up to the order of~$10^4$). Conversely, while neural networks perform
-poorly in such a setting, they become dominant on larger training
-sets (at least of the order of~$10^5$) both in terms of regression performance
-and mean prediction time.
+sets (up to the order of~$10^4$). Conversely, while ANNs perform
+poorly in such a setting, they dominate on larger training sets (at least of the
+order of~$10^5$) both in terms of regression performance and mean prediction time.
 
-\subsection{Results of Adaptive Sampling}
-\label{sec:adaptiveres}
-\begin{wrapfigure}[10]{r}{0.42\textwidth}
+\begin{wrapfigure}[10]{r}{0.4\textwidth}
 	\centering
-	\vspace{-13ex}
-	\includegraphics[width=0.42\textwidth]{fig5_sintoy}
+	\vspace{-16ex}
+	\includegraphics[width=\linewidth]{fig5_sintoy}
 	\caption{Sinusoidal toy TBR theory over two continuous parameters,
@@
 
+\subsection{Results of Adaptive Sampling}
+\label{sec:adaptiveres}
 In order to test our QASS prototype, several functional toy theories for TBR were developed as alternatives to the expensive MC model.
@@
 plotted in~\cref{fig:sintoy} for $n=1$ and two continuous parameters $C$.
-
-ANNs
-trained on this model demonstrated similar performance to those on the expensive
+ANNs trained on this model demonstrated similar performance to those on the expensive
 MC model. QASS performance was verified by training a $\text{1h3f}(256)$ ANN on
@@
 
-An increase in initial samples with increment held constant had a strong impact on final surrogate precision, an early confirmation of basic functionality.
-An increase in MCMC candidate samples was seen to have a positive but very weak effect on final surrogate precision, suggesting that the runtime of MCMC on each iteration can be limited for increased efficiency.
-The most complex dynamics arose with the adjustment of sample increment, shown in~\cref{fig:qassincr}.
-For each tested initial sample quantity N, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$.
-The plotted error trends suggest that
+An increase in initial samples with increment held constant had a strong impact
+on final surrogate precision, an early confirmation of basic functionality. An
+increase in MCMC candidate samples was seen to have a positive but very weak
+effect on final surrogate precision, suggesting that the runtime of MCMC on each
+iteration can be limited for increased efficiency. The most complex dynamics
+arose with the adjustment of sample increment, shown in~\cref{fig:qassincr}. For
+each tested initial sample quantity $N$, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$. The plotted error trends suggest that
 incremental samples larger than this optimum give slower model improvement on both the training and evaluation sets, and a larger minimum error on the evaluation set.
@@
     \centering
+    \vspace{-1ex}
     \begin{subfigure}[t]{0.5\textwidth}
@@
     \end{subfigure}%
-    \hfill
+    \hfill%
     \begin{subfigure}[t]{0.5\textwidth}
@@
     \label{fig:qassincr}
+    \vspace{-1ex}
 \end{figure}
@@
 \centering
-    \includegraphics[width=0.78\linewidth]{fig7_qasssampling.pdf}
-    \caption{Absolute training error for QASS, baseline scheme, and mixed
-	scheme.}
+\begin{minipage}{.48\textwidth}
+  \centering
+  \includegraphics[width=1.1\linewidth]{fig7_qasssampling.pdf}
+  \captionof{figure}{Absolute training error for QASS, baseline scheme, and mixed scheme.}
   \label{fig:qasssampling}
-\end{figure}
-
-\begin{figure}[h]
+\end{minipage}%
+\hfill%
+\begin{minipage}{.48\textwidth}
   \centering
-    \includegraphics[width=0.78\linewidth]{fig8_qasssampling100k.pdf}
-    \caption{Absolute training error for QASS and baseline scheme, with 100k initial samples.}
+  \includegraphics[width=1.1\linewidth]{fig8_qasssampling100k.pdf}
+  \captionof{figure}{Absolute training error for QASS and baseline scheme, with 100k initial samples.}
   \label{fig:qasssampling100k}
+\end{minipage}
 \end{figure}

### 2020-05-01 final_report/appendix_online.tex
run spellcheck

@@
 		Python implementation of the surrogate models presented in this work as
-		well as various pre-processing, plotting and evaluation tools.
+		well as various preprocessing, plotting and evaluation tools.
 	\item[\href{https://github.com/ucl-tbr-group-project/hyperopt}{Hyperparameter Optimisation}]

### 2020-05-01 final_report/data.tex
run spellcheck

@@
 parameters are drawn from a corresponding uniform distribution over their
-domain, as defined in~\cref{tbl:params}. For reproducibility, each run uses a seed equal to its number.} to generate large amounts of feature
+domain, as defined in~\cref{tbl:params}. For repeatability, each run uses a seed equal to its number.} to generate large amounts of feature
 configurations that we consider to be independent and unbiased. For evaluation

### 2020-05-01 final_report/methodology.tex
run spellcheck

@@
 chronometer, here by means of the Python~\texttt{time} package.}
-elapsed during training and predicition. This is motivated by common practical use
+elapsed during training and prediction. This is motivated by common practical use
 cases of our work, where models are trained and used as drop-in replacements for the

### 2020-05-01 final_report/results.tex
carefully re-expand some contracted sentences

@@
 (see~\cref{tbl:sampling-runs} for details). Satisfying
-goal~(b), the fastest model (no.~2, ANN) achieves~$R^2=\num{0.985}$,
+goal~(b), the fastest model (no.~2, ANN) achieved~$R^2=\num{0.985}$,
 $\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
@@
 While these surrogates
-were trained on the entire available set of~\num{500000} datapoints, to satisfy goal~(c) we also trained a simplified model (no.~4, GBT)
+were trained on the entire available set of~\num{500000} datapoints, to satisfy
+goal~(c) we also trained a more simplified model (no.~4, GBT)
 that achieved~$R^2=\num{0.913}$,
@@
 approaches seem to be advantageous for fast surrogate modelling on relatively small training
-sets (up to the order of~$10^4$). Conversely, while ANNs perform
+sets (up to the order of~$10^4$). Conversely, while neural networks perform
 poorly in such a setting, they dominate on larger training sets (at least of the

### 2020-05-01 final_report/data.tex
final edits

@@
 	single slice case we may omit 6~additional dimensions due to fixed feature
-	assignment.} This is consistent with previous results obtained by PCA and kriging.
+	assignment.} This is consistent with the previous results obtained by PCA and kriging.
 

### 2020-05-04 elevator_pitch/elevator_pitch.tex
add elevator pitch boilerplate

--- 2020-05-01 final_report/tbr_final_report-metadata.tex
@@
-%-------------------------------------------------------------------------
-% This file contains the title, author and abstract.
-% It also contains all relevant document numbers if needed.
-%-------------------------------------------------------------------------
+\documentclass{article}
 
-% Partner Logo
-% put the name of the logo image file found in graphics path
-\DISPartnerLogo{ukaea_logo}
+\usepackage[margin=3cm]{geometry}
+\usepackage[utf8]{inputenc}
+\usepackage{siunitx}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
 
-% Title
-\DISTitle{Surrogate Modelling of\\the Tritium Breeding Ratio}
+\title{Surrogate Modelling of the Tritium Breeding Ratio}
+\date{2020\\ January -- April}
+\author{
+	Graham Van Goffrier, University College London\\
+	\and Petr Mánek, University College London
+}
 
-% Draft version:
-% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
-% and line numbers.
-%\DISVersion{0}
+\begin{document}
 
-% Abstract - % directly after { is important for correct indentation
-\DISAbstract{%
+\maketitle
+
 The tritium breeding ratio (TBR) is an essential quantity for the design of
@@
 accelerating the surrogate modelling process.
-}
 
-% Authors and list of contributors to the analysis
-\usepackage{authblk}
-\author[a]{Graham Van Goffrier}
-\author[a]{Petr Mánek}
-\affil[a]{University College London}
-
-% DIS reference code if ever used
-%\DISRefCode{UCLCDTDIS-2019-XX}
+\end{document}

### 2020-05-11 elevator_pitch/elevator_pitch.tex
add figure to elevator pitch
expand on the abstract using bits of the conclusion, mostly the part about dimensional reduction

@@
 
-\usepackage[margin=3cm]{geometry}
+\usepackage[margin=2cm]{geometry}
 \usepackage[utf8]{inputenc}
+\usepackage{graphicx}
 \usepackage{siunitx}
@@
 \usepackage{amsthm}
+
+\graphicspath{{fig/}}
 
@@
 training of surrogate models to produce a cheap but high-quality approximation
-for a Monte Carlo TBR model in use at the UK Atomic Energy Authority. We
-investigated possibilities for dimensional reduction of its feature space, reviewed
-9~families of surrogate models for potential
-applicability, and performed hyperparameter optimisation. Here we present the
+for a Monte Carlo TBR model in use at the UK Atomic Energy Authority.
+
+Having implemented and deployed our sampling software on a high performance cluster, we
+used the MC TBR model to generate over~$9\cdot 10^5$ datapoints for training and
+test purposes. On this set, we investigated possibilities for
+dimensional reduction using Principal Component Analysis, Kriging and
+autoencoders, and concluded that no straightforward reduction was possible
+without significant information loss. We reviewed 9~families of surrogate models for potential
+applicability, benchmarked their behaviour as a function of training set size and tuned their
+hyperparameters via Bayesian Optimisation.
+
+Here we present the
 performance and scaling properties of these
@@
 prediction time of~$\SI{0.898}{\micro\second}$, representing a relative speedup of $8\cdot 10^6$
-with respect to the expensive MC model. We further present a novel adaptive
+with respect to the expensive MC TBR model. We further present a novel adaptive
 sampling algorithm, Quality-Adaptive Surrogate Sampling, capable
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.6\textwidth]{exp4_model6}
+	\caption{Regression performance of the most accurate evaluated surrogate
+		(artificial neural network), viewed as true vs.~predicted TBR on a test
+		set of a selected cross-validation fold (out of 5). Points are coloured by density.}
+\end{figure}
+
 \end{document}

### 2020-05-11 paper/ucl_tbr_paper.tex
add IOP paper guidelines and template

\documentclass[12pt]{iopart}

\usepackage{iopams}

\providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}

\begin{document}
\title[The anomalous magnetic moment of the neutrino]{The anomalous magnetic moment of the neutrino and its relation to the solar neutrino problem}

\author{P J Smith$^1$, T M Collins$^2$, R J Jones$^3$\footnote{Present address: Department of Physics, University of Bristol, Tyndalls Park Road, Bristol BS8 1TS, UK.} and Janet Williams$^3$}

\address{$^1$ Mathematics Faculty, Open University, Milton Keynes MK7~6AA, UK}
\address{$^2$ Department of Mathematics, Imperial College, Prince Consort Road, London SW7~2BZ, UK}
\address{$^3$ Department of Computer Science, University College London, Gower Street, London WC1E~6BT, UK}
\ead{williams@ucl.ac.uk}

\begin{abstract}
...
\end{abstract}

\keywords{magnetic moment, solar neutrinos, astrophysics}
\submitto{\jpg}
\maketitle

\end{document}

### 2020-05-14 elevator_pitch/elevator_pitch.tex
add a bit about smaller models
remove page number, adjust margins
Edits to elevator pitch

@@
 
-\usepackage[margin=2cm]{geometry}
+\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm]{geometry}
 \usepackage[utf8]{inputenc}
@@
 \author{
-	Graham Van Goffrier, University College London\\
-	\and Petr Mánek, University College London
+	Petr Mánek, University College London\\
+	\and Graham Van Goffrier, University College London
 }
@@
 \maketitle
+\thispagestyle{empty}
 
@@
 Having implemented and deployed our sampling software on a high performance cluster, we
-used the MC TBR model to generate over~$9\cdot 10^5$ datapoints for training and
+used the MC TBR model to generate over~\num{900000} datapoints for training and
 test purposes. On this set, we investigated possibilities for
-dimensional reduction using Principal Component Analysis, Kriging and
+dimensional reduction using Principal Component Analysis, variograms and
 autoencoders, and concluded that no straightforward reduction was possible
@@
 
-Here we present the
-performance and scaling properties of these
+Here we present the performance and scaling properties of these
 models, the fastest of which, an artificial neural network,
@@
 prediction time of~$\SI{0.898}{\micro\second}$, representing a relative speedup of $8\cdot 10^6$
-with respect to the expensive MC TBR model. We further present a novel adaptive
-sampling algorithm, Quality-Adaptive Surrogate Sampling, capable
+with respect to the expensive MC TBR model. While this surrogate was trained on
+a set of size~\num{500000}, we demonstrated that comparable results can also be
+achieved using only~\num{10000} datapoints. We further present a novel adaptive
+sampling algorithm, Quality-Adaptive Surrogate Sampling, which applies Markov chain Monte Carlo methods to probe high-error regions of the surrogate during training, and is capable
 of interfacing with any of the individually studied surrogates. Our preliminary

### 2020-05-21 paper/ucl_tbr_paper.tex
add commenting package
add provisional title, institution addresses

@@
 \usepackage{iopams}
+\usepackage[colorinlistoftodos]{todonotes} % TODO: remove me before submitting
 
@@
 \begin{document}
-\title[The anomalous magnetic moment of the neutrino]{The anomalous magnetic moment of the neutrino and its relation to the solar neutrino problem}
+\title[Fast regression of the Tritium Breeding Ratio in Tokamaks]{Fast regression of the
+Tritium Breeding Ratio in Tokamak fusion reactors} % TODO: revise this
 
-\author{P J Smith$^1$, T M Collins$^2$, R J Jones$^3$\footnote{Present address: Department of Physics, University of Bristol, Tyndalls Park Road, Bristol BS8 1TS, UK.} and Janet Williams$^3$}
+\author{G~Van Goffrier$^1$ and P~Mánek$^{1,2}$, V~Gopakumar$^3$, N~Nikolau$^1$, J~Shimwell$^3$, I~Waldmann$^1$}
 
-\address{$^1$ Mathematics Faculty, Open University, Milton Keynes MK7~6AA, UK}
-\address{$^2$ Department of Mathematics, Imperial College, Prince Consort Road, London SW7~2BZ, UK}
-\address{$^3$ Department of Computer Science, University College London, Gower Street, London WC1E~6BT, UK}
+\address{$^1$ Department of Physics and Astronomy, University College London, Gower Street, London WC1E~6BT, UK}
+\address{$^2$ Institute of Experimental and Applied Physics, Czech Technical University, Husova 240/5, Prague 110~00, Czech Republic}
+\address{$^3$ UK Atomic Energy Authority, Culham Science Centre, OX14~3DB Abingdon, UK}
 \ead{williams@ucl.ac.uk}
@@
 \begin{abstract}
+% TODO: revise this
 ... 
@@
 
+\todo{This is a comment that will appear in the margin}
+
 \end{document}

### 2020-05-21 paper/ucl_tbr_paper.tex
add abstract from the report and author emails

@@
 \usepackage{iopams}
+\usepackage{siunitx}
 \usepackage[colorinlistoftodos]{todonotes} % TODO: remove me before submitting
@@
 \begin{document}
-\title[Fast regression of the Tritium Breeding Ratio in Tokamaks]{Fast regression of the
-Tritium Breeding Ratio in Tokamak fusion reactors} % TODO: revise this
+\title[Fast Regression of the Tritium Breeding Ratio in Tokamaks]{Fast Regression of the
+Tritium Breeding Ratio in Tokamak Fusion Reactors} % TODO: revise this
 
@@
 \address{$^3$ UK Atomic Energy Authority, Culham Science Centre, OX14~3DB Abingdon, UK}
-\ead{williams@ucl.ac.uk}
+
+% TODO: check if Graham can also have a shorter version of email
+\eads{\mailto{graham.vangoffrier.19@ucl.ac.uk}, \mailto{petr.manek@ucl.ac.uk}}
 
 \begin{abstract}
-% TODO: revise this
-... 
+	% TODO: this has been taken as is from the report, revise this
+	The tritium breeding ratio (TBR) is an essential quantity for the design of
+	modern and next-generation Tokamak nuclear fusion reactors. Representing the
+	ratio between tritium fuel generated in breeding blankets and fuel consumed
+	during reactor runtime, the TBR depends on reactor geometry and material
+	properties in a complex manner. In this work, we explored the
+	training of surrogate models to produce a cheap but high-quality approximation
+	for a Monte Carlo TBR model in use at the UK Atomic Energy Authority. We
+	investigated possibilities for dimensional reduction of its feature space, reviewed
+	9~families of surrogate models for potential
+	applicability, and performed hyperparameter optimisation. Here we present the
+	performance and scaling properties of these
+	models, the fastest of which, an artificial neural network,
+	demonstrated~$R^2=\num{0.985}$ and a mean
+	prediction time of~$\SI{0.898}{\micro\second}$, representing a relative speedup of $8\cdot 10^6$
+	with respect to the expensive MC model. We further present a novel adaptive
+	sampling algorithm, Quality-Adaptive Surrogate Sampling, capable
+	of interfacing with any of the individually studied surrogates. Our preliminary
+	testing on a toy TBR theory has demonstrated the efficacy of this algorithm for
+	accelerating the surrogate modelling process.
 \end{abstract}
 
+% TODO: revise these
 \keywords{magnetic moment, solar neutrinos, astrophysics}

### 2020-05-21 paper/introduction.tex
add full introduction from the final report, ignore .out files

--- 2020-05-01 final_report/introduction.tex
@@
 in nature. It may be produced indirectly through irradiation of heavy water
-(\ce{D2O}) during nuclear fission, but only at very low rates which could
+(\DDO) during nuclear fission, but only at very low rates which could
 never sustain industrial-scale fusion power.
@@
 neutron bombardment, e.g. by 
-\begin{align}
+\begin{eqnarray}
 	\isotope[1][0]{n} + \hspace{3pt} \isotope[6][3]{Li} 
@@
 	\isotope[3][1]{T} + \hspace{3pt} \isotope[4][2]{He} + \hspace{3pt} \isotope[1][0]{n}
-\end{align}
-\begin{wrapfigure}{r}{0.45\textwidth}
-  \vspace{-20pt}
-  \begin{center}
-    \includegraphics[width=0.48\textwidth]{fig1_tokamakdiagram.png}
-  \end{center}
+\end{eqnarray}
+\begin{figure}
+  \centering
+  % TODO: \includegraphics[width=0.48\textwidth]{fig1_tokamakdiagram.png}
   \caption{Typical single-null reactor configuration as specified by BLUEPRINT~\cite{Coleman2019}: 1 — plasma,
@@
 \label{fig:tokamak}
-\end{wrapfigure}
+\end{figure}
 where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
@@
 neutrons with breeding blanket materials. Neutron paths are traced through a CAD
-model (e.g.~\cref{fig:tokamak}) of a reactor with modifiable geometry.
+model (e.g. Figure~\ref{fig:tokamak}) of a reactor with modifiable geometry.
 

### 2020-05-21 paper/methodology.tex
add full methodology section from the report

--- 2020-05-01 final_report/methodology.tex
@@
 In the decoupled sampling approach that is further described
-in~\cref{sec:supervised}, we first gather a sufficiently large
+in Section~\ref{sec:supervised}, we first gather a sufficiently large
 training set of samples $\mathcal{T}=\left\{\left( x^{(i)},f\left(x^{(i)}\right) \right)\right\}_{i=1}^N$
@@
 
-The adaptive sampling approach that we characterise in~\cref{sec:adaptive} can be viewed as a more general problem.
+The adaptive sampling approach that we characterise in Section~\ref{sec:adaptive} can be viewed as a more general problem.
 Rather than fixing the training set $\mathcal{T}$ for the entire duration of
@@
 
-\Cref{tbl:metrics} provides an exhaustive listing and description of metrics recorded
+Table~\ref{tbl:metrics} provides an exhaustive listing and description of metrics recorded
 in our experiments. For regression performance analysis, we include a selection
@@
 In our experiments, we evaluate and compare surrogates in effort to
-optimise against metrics described in~\cref{sec:metrics}. To attain meaningful
+optimise against metrics described in Section~\ref{sec:metrics}. To attain meaningful
 and practically usable results, we require a sufficiently large and diverse pool
-of surrogate families to review. This is described by the listing in~\cref{tbl:surrogates}. The presented selection of models includes basic
+of surrogate families to review. This is described by the listing in Table~\ref{tbl:surrogates}. The presented selection of models includes basic
 techniques suitable for linear regression enhanced by the kernel trick or dimension
@@
 architecture through selection from various parametric graph templates
-(illustrated in~\cref{fig:nn-archs}). This allows us to realise a simplistic
+(illustrated in Figure~\ref{fig:nn-archs}). This allows us to realise a simplistic
 network architecture search during the hyperparameter tuning procedure.
@@
 	\centering
-	\begin{subfigure}[b]{0.25\textwidth}
-		\centering
-		{\scriptsize \incfigscale{0.6}{1h3f}}
-		\caption{$\text{1h3f}(W)$}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
-		\centering
-		{\scriptsize \incfigscale{0.6}{kf}}
-		\caption{$\text{df}(D,W)$}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
-		\centering
-		{\scriptsize \incfigscale{0.6}{3pyramid}}
-		\caption{$\text{3pyramid}(W)$}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
-		\centering
-		{\scriptsize \incfigscale{0.6}{5diam}}
-		\caption{$\text{5diamond}(W)$}
-	\end{subfigure}
+	Placeholder % TODO
+%	\begin{subfigure}[b]{0.25\textwidth}
+%		\centering
+%		{\scriptsize \incfigscale{0.6}{1h3f}}
+%		\caption{$\text{1h3f}(W)$}
+%	\end{subfigure}\hfill%
+%	\begin{subfigure}[b]{0.25\textwidth}
+%		\centering
+%		{\scriptsize \incfigscale{0.6}{kf}}
+%		\caption{$\text{df}(D,W)$}
+%	\end{subfigure}\hfill%
+%	\begin{subfigure}[b]{0.25\textwidth}
+%		\centering
+%		{\scriptsize \incfigscale{0.6}{3pyramid}}
+%		\caption{$\text{3pyramid}(W)$}
+%	\end{subfigure}\hfill%
+%	\begin{subfigure}[b]{0.25\textwidth}
+%		\centering
+%		{\scriptsize \incfigscale{0.6}{5diam}}
+%		\caption{$\text{5diamond}(W)$}
+%	\end{subfigure}
 
@@
 	terminated after 2~days. Instances that reached this limit may be identified
-	in~\cref{tbl:exp1-detailed-results,tbl:exp2-detailed-results} in the
+	in Table~\ref{tbl:exp1-detailed-results,tbl:exp2-detailed-results} in the
 	Appendix.}
@@
 
-\begin{wrapfigure}[25]{r}{0.55\textwidth}
+\begin{figure}[h]
 	\centering
-	\vspace{-3ex}
-	\includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
+	Placeholder % TODO: \includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
 	\caption{Schematic of QASS algorithm}
 	\label{fig:qassplan}
-\end{wrapfigure}
+\end{figure}
 
@@
 
-% TODO: explain AE
-
 We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS,
-\cref{fig:qassplan}) to iteratively increment the training/test set with sample
+Figure~\ref{fig:qassplan}) to iteratively increment the training/test set with sample
 points which maximise surrogate error and minimise a crowding distance metric

### 2020-05-25 paper/ucl_tbr_paper.tex
add outline
do not use shortened email
add full introduction from the final report, ignore .out files
remove data exploration section
add full methodology section from the report
add bibliography from the report, ignore byproducts
smaller todos

@@
 \usepackage{iopams}
+
+\makeatletter
+\@namedef{ver@amsmath.sty}{}
+\makeatother
+
 \usepackage{siunitx}
-\usepackage[colorinlistoftodos]{todonotes} % TODO: remove me before submitting
+\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % TODO: remove me before submitting
+\usepackage{isotope}
+\usepackage{fixltx2e}
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage{url}
 
 \providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}
+\newcommand{\DDO}{D\textsubscript{2}O}
 
 \begin{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% FRONT MATTER
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \title[Fast Regression of the Tritium Breeding Ratio in Tokamaks]{Fast Regression of the
@@
 
-% TODO: check if Graham can also have a shorter version of email
-\eads{\mailto{graham.vangoffrier.19@ucl.ac.uk}, \mailto{petr.manek@ucl.ac.uk}}
+\eads{\mailto{graham.vangoffrier.19@ucl.ac.uk}, \mailto{petr.manek.19@ucl.ac.uk}}
 
@@
 
-\todo{This is a comment that will appear in the margin}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% MAIN MATTER
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Introduction}
+\label{sec:introduction}
+\input{introduction}
+
+\section{Methodology}
+\label{sec:methodoglogy}
+\input{methodology}
+
+\section{Results}
+\label{sec:results}
+\input{results}
+
+\section{Conclusion}
+\label{sec:conclusion}
+\input{conclusion}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% BACK MATTER
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Acknowledgements}
+\label{sec:acknowledgements}
+\input{acknowledgements}
+
+\section{References}
+\label{sec:references}
+\bibliography{ucl_tbr_paper}
+\bibliographystyle{iopart-num}
 

### 2020-05-25 paper/methodology.tex
shorten methodolgy intro

@@
-Assuming that data is appropriately treated to eliminate redundant
-features, we proceed to propose surrogate models and criteria
-used for their evaluation. The task all presented surrogates strive to solve can be
-formulated using the language of conventional regression problems. In this section,
-we focus on interpretation in the scheme of supervised learning with decoupled
-and adaptive sampling.
+Labeling the expensive MC TBR model $f(x)$, a surrogate is a mapping
+$\hat{f}(x)$ such that $f(x)$ and $\hat{f}(x)$ minimise a selected dissimilarity
+metric. In order to be considered \textit{viable}, $\hat{f}(x)$ is required to
+achieve expected evaluation time lower than that of~$f(x)$. In this work, we
+consider two methods of producing viable surrogates: (1) a conventional decoupled
+approach, which evaluates $f(x)$ on a set of randomly sampled points and
+trains surrogates in a supervised scheme, and (2) an adaptive approach, which attempts to
+compensate for localised regression performance insuficiencies by interleaving
+multiple epochs of sampling and training.
 
-Labeling the expensive MC TBR model $f(x)$, a surrogate is a mapping
-$\hat{f}(x)$ that yields similar images as $f(x)$. In other words, $f(x)$ and
-$\hat{f}(x)$ minimise a selected dissimilarity metric. Furthermore, in order to
-be considered \textit{viable}, surrogates are required to achieve expected evaluation time
-lower than that of $f(x)$.
-
-In the decoupled sampling approach that is further described
-in Section~\ref{sec:supervised}, we first gather a sufficiently large
-training set of samples $\mathcal{T}=\left\{\left( x^{(i)},f\left(x^{(i)}\right) \right)\right\}_{i=1}^N$
-to describe the behaviour of $f(x)$ across its domain.
-Depending on a specific model family and appropriate choice of its
-hyperparameters, surrogate models $\hat{f}(x)$ are trained to minimise
-the empirical risk~$R_{\text{emp.}}$ with respect to $\mathcal{T}$ and a model-specific
-loss function $\mathcal{L}$, where the empirical risk is defined as
-$R_{\text{emp.}}(\hat{f}\mid\mathcal{T},\mathcal{L})
-	=\frac{1}{N}\sum_{i=1}^N
-	\mathcal{L}\left(\hat{f}(x^{(i)}),f(x^{(i)})\right)$.
-
-The adaptive sampling approach that we characterise in Section~\ref{sec:adaptive} can be viewed as a more general problem.
-Rather than fixing the training set $\mathcal{T}$ for the entire duration of
-training, multiple sets $\{\mathcal{T}_k\}_{k=0}^K$ are used, such that
-$\mathcal{T}_{k-1}\subset\mathcal{T}_k$ for all $k>1$. The first set
-$\mathcal{T}_0$ is initialised randomly to provide a \textit{burn-in}, and is
-repeatedly extended in epochs, whereby each epoch trains a new surrogate~$\hat{f}_k(x)$ on
-$\mathcal{T}_k$ using the supervised learning procedure, evaluates its
-performance, and forms a new set $\mathcal{T}_{k+1}$ by adding more samples to
-$\mathcal{T}_k$. This permits the learning algorithm to condition the selection
-of new samples in~$\mathcal{T}_{k+1}$ on the evaluation results
-of~$\hat{f}_k(x)$ in order to maximise improvement of
-surrogate performance over complex regions within the feature space.
-
-\subsection{Metrics}
-\label{sec:metrics}
-
-Aiming to provide objective comparison of a diverse set of surrogate model
-families, we define a multitude of metrics to be tracked during experiments.
-Following the motivation of this work, two desirable properties of surrogates
-arise: (a) their capability to approximate the TBR MC model well and (b) their
-prediction time. An ideal surrogate would maximise
-the former while minimising the latter.
-
-Table~\ref{tbl:metrics} provides an exhaustive listing and description of metrics recorded
-in our experiments. For regression performance analysis, we include a selection
-of absolute metrics to assess the approximation capability of surrogates, and set
-practical bounds on the expected uncertainty of their predictions. In addition, we also track
-relative measures that are better-suited for comparison between this work and others, as
-they maintain invariance with respect to the selected domain and image space.
-For complexity analysis, surrogates are assessed in terms of wall
-time\footnote{Real time elapsed during computation measured by a
-chronometer, here by means of the Python~\texttt{time} package.}
-elapsed during training and prediction. This is motivated by common practical use
-cases of our work, where models are trained and used as drop-in replacements for the
-expensive MC TBR model. Since training set sizes remain to be determined, all times are
-reported per a single datapoint. Even though some surrogates support acceleration
-by means of parallelisation, sequential processing of samples was ensured to
-achieve comparability between considered
-models.\footnote{The only exception to this are artificial neural networks,
-	which require considerable amount of processing power for training on conventional CPU architectures.}
+For both methods, we selected state-of-the-art regression algorithms to perform
+surrogate training on sampled point sets. Listed in~\tref{tbl:surrogates}, these
+implementations define 9~surrogate families that are later reviewed in~\sref{sec:results}.
+We note that each presented algorithm defines hyperparameters that may influence its
+performance. Since their optimal values for this problem are unknown, we explore
+their assignments prior to other experiments.
 
 \begin{table}[h]
-	\centering
-	{\footnotesize
-		\begin{tabular}{llrl}
+	\caption{\label{tbl:surrogates}Considered surrogate model families.
+	$\mathcal{H}$ denotes hyperparameter set.}
+	\begin{indented}
+	\item[]
+		\begin{tabular}{lllr}
 		\toprule
-		Regression performance metrics	& Mathematical formulation / description &
-		\multicolumn{2}{c}{Ideal value [units]} \\
-		\midrule
-		Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
-									& [TBR] \\
-		Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
-		\hat{y}^{(i)}| \right\} $	 & 0 & [TBR] \\
-		Coefficient of determination $R^2$	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
-		\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 & [rel.] \\
-		Adjusted $R^2$	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 & [rel.] \\
-		\midrule
-		Complexity metrics	& {} & {} & {} \\
-		\midrule
-		Mean training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
-		$\hat{f}(x)$})/N_0$ 	& 0 & [ms] \\
-		Mean prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
-		$\hat{f}(x)$})/N$	& 0 & [ms] \\
-		Relative speedup $\omega$	& $(\text{wall evaluation time of $f(x)$}) /
-		(N\overline{t}_{\text{pred.}})$	&
-		$\to\infty$ & [rel.] \\
-		\bottomrule
-		\end{tabular}
-	}
-	\caption{Metrics recorded in supervised learning experiments. In
-	formulations, we work with a training set of size $N_0$ and a test set of
-size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
-denote images of the $i$th testing sample in the expensive model and the surrogate
-respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
-number of input features.}
-	\label{tbl:metrics}
-\end{table}
-
-To prevent undesirable bias in results due to training set selection, all metrics
-are collected in the scheme of $k$-fold cross-validation with a conventional choice of
-$k=5$. In this setting, a sample set is uniformly divided into 5 disjoint folds, each of which
-is used as a test set for models trained on the remaining 4.\footnote{Unless explicitly stated otherwise, we use 1
-fold for testing and the 4 remaining folds for training. This gives 80\% to
-20\% train-test ratio.} Having repeated the same experiment for each such run,
-the overall value of individual metrics is reported in terms of their mean and
-standard deviation over all folds.
-
-\subsection{Decoupled Sampling}
-\label{sec:supervised}
-
-In our experiments, we evaluate and compare surrogates in effort to
-optimise against metrics described in Section~\ref{sec:metrics}. To attain meaningful
-and practically usable results, we require a sufficiently large and diverse pool
-of surrogate families to review. This is described by the listing in Table~\ref{tbl:surrogates}. The presented selection of models includes basic
-techniques suitable for linear regression enhanced by the kernel trick or dimension
-lifting, methods driven by decision trees, instance-based learning models,
-ensemble regressors, randomised algorithms, artificial neural networks and mathematical approaches
-developed specifically for the purposes of surrogate modelling. For each of
-these families, a state-of-the-art implementation was selected and adapted to
-operate with TBR samples.
-
-\begin{table}[h]
-	\centering
-	{\footnotesize
-		\begin{tabular}{llll}
-		\toprule
-		Surrogate & Acronym & Implementation & Hyperparameters \\
+		Surrogate & Acronym & Implementation & $|\mathcal{H}|$ \\
 		\midrule
@@
 		\end{tabular}
-	}
-	\caption{Considered surrogate model families.}
-	\label{tbl:surrogates}
+	\end{indented}
 \end{table}
 
-While some of the presented model families are clearly determined by an explicit
-choice of a learning algorithm, others may vary considerably depending on
-hyperparameter configuration. A good example of the latter group are artificial neural
-networks, which in addition to conventional hyperparameters enable to control network
-architecture through selection from various parametric graph templates
-(illustrated in Figure~\ref{fig:nn-archs}). This allows us to realise a simplistic
-network architecture search during the hyperparameter tuning procedure.
+To compare quality of produced surrogates, we define a number of metrics listed
+in~\tref{tbl:metrics}. For regression performance analysis, we include a
+selection of absolute metrics to assess their approximation capability and set
+practical bounds on the expected uncertainty of their predictions. In addition, we also track
+relative measures that are better-suited for comparison between this work and others as
+they maintain invariance with respect to the selected domain and image space.
+For complexity analysis, surrogates are assessed in terms of wall
+time (captured by the Python~\texttt{time} package). This is motivated by common practical use
+cases of our work, where models are trained and used as drop-in replacements for the
+expensive MC TBR model. Since training set sizes remain to be determined, all times are
+reported per a single datapoint. Even though some surrogates support acceleration
+by means of parallelisation, sequential processing of samples was ensured to
+achieve comparability between considered models. The only exception to this are
+ANNs, which require considerable amount of processing power for training on
+conventional CPU architectures. Lastly, to prevent undesirable bias by training set
+selection, all metrics are collected in the scheme of 5-fold cross-validation.
 
-\begin{figure}[h]
-	\centering
-	Placeholder % TODO
-%	\begin{subfigure}[b]{0.25\textwidth}
-%		\centering
-%		{\scriptsize \incfigscale{0.6}{1h3f}}
-%		\caption{$\text{1h3f}(W)$}
-%	\end{subfigure}\hfill%
-%	\begin{subfigure}[b]{0.25\textwidth}
-%		\centering
-%		{\scriptsize \incfigscale{0.6}{kf}}
-%		\caption{$\text{df}(D,W)$}
-%	\end{subfigure}\hfill%
-%	\begin{subfigure}[b]{0.25\textwidth}
-%		\centering
-%		{\scriptsize \incfigscale{0.6}{3pyramid}}
-%		\caption{$\text{3pyramid}(W)$}
-%	\end{subfigure}\hfill%
-%	\begin{subfigure}[b]{0.25\textwidth}
-%		\centering
-%		{\scriptsize \incfigscale{0.6}{5diam}}
-%		\caption{$\text{5diamond}(W)$}
-%	\end{subfigure}
+\begin{table}[h]
+	\caption{\label{tbl:metrics}Metrics recorded in experiments. In
+	formulations, we work with a training set of size $N_0$ and a test set of
+size $N$, values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
+denote images of the $i$th testing sample in the MC TBR model and the surrogate
+respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
+number of input features.}
+	\begin{indented}
+	\item[]
+		\begin{tabular}{lrl}
+		\toprule
+		Regression perf. metrics& Notation	& Mathematical formulation\\
+		\midrule
+		Mean absolute error	& MAE & $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ \\
+		Standard error of regression & $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
+		\hat{y}^{(i)}| \right\} $ \\
+			Coefficient of determination & $R^2$	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
+		\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ \\
+			Adjusted $R^2$ & $R^2_\text{adj.}$	& $1-(1-R^2)(N-1)/(N-P-1)$ \\
+		\midrule
+		Complexity metrics	& {}	& {} \\
+		\midrule
+		Mean training time & $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
+		$\hat{f}(x)$})/N_0$  \\
+			Mean prediction time & $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
+		$\hat{f}(x)$})/N$ \\
+				Relative speedup & $\omega$	& $(\text{wall evaluation time of $f(x)$}) /
+		(N\overline{t}_{\text{pred.}})$ \\
+		\bottomrule
+		\end{tabular}
+	\end{indented}
+\end{table}
 
-	\caption{Selected parametric neural network architectures. All layers except
-		the last use ReLU activation. Prediction information flow is indicated by
-		arrows.}
-	\label{fig:nn-archs}
-\end{figure}
-
-\subsubsection{Experiments}
+\subsection{Decoupled Sampling}
 \label{sec:experiment-methodology}
+\todo{This section needs to be shortened}
 
@@
 \label{sec:adaptive}
+\todo{This section needs to be shortened}
 

### 2020-05-25 paper/methodology.tex
remove large slashes to conform with journal guidelines

@@
 denote images of the $i$th testing sample in the MC TBR model and the surrogate
-respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
+respectively. Furthermore, the mean $\overline{y}=N^{-1}\sum_{i=1}^N y^{(i)}$ and $P$ is the
 number of input features.}
@@
 		\midrule
-		Mean absolute error	& MAE & $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ \\
+		Mean absolute error	& MAE & $N^{-1}\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|$ \\
 		Standard error of regression & $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
 		\hat{y}^{(i)}| \right\} $ \\
-			Coefficient of determination & $R^2$	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
-		\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ \\
-			Adjusted $R^2$ & $R^2_\text{adj.}$	& $1-(1-R^2)(N-1)/(N-P-1)$ \\
+			Coefficient of determination & $R^2$	& $1-\sum_{i=1}^N
+			\left(y^{(i)}-\hat{y}^{(i)} \right)^2\left[\sum_{i=1}^N \left(
+			y^{(i)}-\overline{y} \right)^2\right]^{-1} $ \\
+			Adjusted $R^2$ & $R^2_\text{adj.}$	& $1-(1-R^2)(N-1)(N-P-1)^{-1}$ \\
 		\midrule

### 2020-05-25 paper/methodology.tex
shorten decoupled methodology section

@@
 
-\subsection{Decoupled Sampling}
-\label{sec:experiment-methodology}
-\todo{This section needs to be shortened}
+\subsection{Decoupled Approach}\label{sec:experiment-methodology}
 
-The presented surrogate candidates are evaluated in four experimental cases:%
-\begin{enumerate}
-	\item Hyperparameter tuning in a simplified domain.
+Experiments related to the decoupled approach are organised in four parts,
+further described in this section. In summary, we aim to optimise hyperparameters of
+each surrogate family separately and later use the best found results to compare surrogate
+families among themselves.
 
-	\item Hyperparameter tuning in full domain.
+The objective of the first experiment is to simplify the regression task for
+surrogates prone to suboptimal performance in discontinuous spaces.
+To this end, training points are filtered to a single selected discrete feature
+assignment, and surrogates are trained only on the remaining continuous features.
+This is repeated for 4~distinct assignments to explore variances in behaviour.
+The second experiment conventionally measures surrogate performance on the full,
+unrestricted feature space. In both cases, hyperparameter tuning is
+facilitated by Bayesian optimisation~\cite{movckus1975bayesian}. We set its
+objective to maximise $R^2$ and terminate the process after 1000~iterations or
+2~days, whichever condition is satisfied first.
 
-	\item Scaling benchmark.
+In the third experiment, the 20~best-performing hyperparameter configurations
+per each family are used to train surrogates on sets of various sizes to
+investigate their scaling properties. Following that, the fourth experiment aims
+to produce surrogates suitable for practical use by retraining selected
+well-scaling instances on large training sets in order to satisfy the goals of this work.
 
-	\item Model comparison.
-\end{enumerate}
-
-The aim of the initial experiments is to use a relatively small subset of
-collected TBR samples to determine hyperparameters of considered surrogates.
-Since this process requires learning the behaviour of an unknown, possibly
-expensive mapping -- here a function that assigns cross-validated metrics to a
-point in the hyperparameter domain -- it in many aspects mirrors
-the primary task of this work with the notable extension of added utility
-to optimise. In order to avoid undesirable exponential slowdown in exhaustive
-searches of a possibly high-dimensional parameter space, Bayesian
-optimisation~\cite{movckus1975bayesian} is employed as a standard hyperparameter tuning algorithm. We set
-its objective to maximise $R^2$ and perform
-1000~iterations.\footnote{Hyperparameter tuning of each surrogate family was
-	terminated after 2~days. Instances that reached this limit may be identified
-	in Table~\ref{tbl:exp1-detailed-results,tbl:exp2-detailed-results} in the
-	Appendix.}
-
-In the first experiment, efforts are made to maximise the possibility of success
-in surrogates that are prone to suboptimal performance in discontinuous spaces.
-This follows the notion that, if desired, performance of such models may be
-replicated by training separate instances to model each continuous subregion of
-the domain independently.
-To this end, data are limited to a single slice from run~2, and discrete
-features are completely withheld from evaluated
-surrogates. This is repeated for each of the four available slices to
-investigate variance in behaviour under different discrete feature assignments.
-The second experiment conventionally measures surrogate performance on the full
-feature space. Here, in extension of the previous case, surrogates work with
-samples comprised of discrete as well as continuous features.
-
-The objective of the last two experiments is to exploit the information gathered by
-hyperparameter tuning. In the third experiment, the 20~best-performing
-hyperparameter configurations of each family (with respect to~$R^2$) are used to
-perform training on progressively larger sets to investigate their scaling
-properties. Following that, the fourth experiment aims to produce surrogates
-suitable for practical use by retraining selected well-scaling instances on large
-training sets to satisfy the goals of this work.
-
-\subsection{Adaptive Sampling}
-\label{sec:adaptive}
+\subsection{Adaptive Approach}\label{sec:adaptive}
 \todo{This section needs to be shortened}

### 2020-05-25 paper/methodology.tex
more edits to the methodology section to comply with journal guidelines

@@
 
-\begin{figure}[h]
+\begin{figure}
 	\centering
-	Placeholder % TODO: \includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
+	\includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
 	\caption{Schematic of QASS algorithm}
@@
 optima in the feature space. MCMC produces a progressive chain of sample points,
-each drawn according to the same symmetric proposal distribution\footnote{An
+each drawn according to the same symmetric proposal
+distribution\todo{Incorporate the footnote into the text.}\footnote{An
 adaptive MCMC procedure~\cite{Zhang2012}, which adjusts an ellipsoidal proposal
@@
 
-We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS,
-Figure~\ref{fig:qassplan}) to iteratively increment the training/test set with sample
+We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, \fref{fig:qassplan}) to iteratively increment the training/test set with sample
 points which maximise surrogate error and minimise a crowding distance metric

### 2020-05-25 paper/results.tex
add results section "as is" from the final report, link tables directory

--- 2020-05-01 final_report/results.tex
@@
+\todo{This entire section needs to be shortened.}
+
 Having outlined a variety of models and metrics tracked for the
@@
 Through the four experimental cases described
-in~\cref{sec:experiment-methodology}, we aim to study properties of the
+in~\sref{sec:experiment-methodology}, we aim to study properties of the
 considered models in terms of regression performance, training and prediction
@@
 
-The results displayed in~\cref{fig:exp1-time-vs-reg} (and listed
-in~\cref{tbl:exp1-detailed-results} in the Appendix) indicate that in the first
+The results displayed in~\fref{fig:exp1-time-vs-reg} (and listed
+in~\tref{tbl:exp1-detailed-results} in the Appendix) indicate that in the first
 experiment, GBTs clearly appear to be the most accurate as
@@
 	\centering
-	\begin{subfigure}[b]{0.333\textwidth}
-		\centering
+	\begin{minipage}{0.333\textwidth}
+		%\centering
 		\includegraphics[width=\linewidth]{exp1_slice0}
-		\caption{Run 2, batches 0-2}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.333\textwidth}
-		\centering
+		%\caption{Run 2, batches 0-2}
+	\end{minipage}\hfill%
+	\begin{minipage}{0.333\textwidth}
+		%\centering
 		\includegraphics[width=\linewidth]{exp1_slice1}
-		\caption{Run 2, batches 100-102}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.333\textwidth}
-		\centering
+		%\caption{Run 2, batches 100-102}
+	\end{minipage}\hfill%
+	\begin{minipage}{0.333\textwidth}
+		%\centering
 		\includegraphics[width=\linewidth]{exp1_slice2}
-		\caption{Run 2, batches 200-202}
-	\end{subfigure}
+		%\caption{Run 2, batches 200-202}
+	\end{minipage}
 	\caption{20~best-performing surrogates per each considered family, plotted in
@@
 	experiment~1. Here, batches refer to subsets of training and test datasets that
-	may be matched to slices using~\cref{tbl:slices}.}
+	may be matched to slices using~\tref{tbl:slices}.}
 	\label{fig:exp1-time-vs-reg}
@@
 
-The results of the second experiment, shown in~\cref{fig:exp2-time-vs-reg} (and listed
-in~\cref{tbl:exp2-detailed-results} in the Appendix),
+The results of the second experiment, shown in~\fref{fig:exp2-time-vs-reg} (and listed
+in~\tref{tbl:exp2-detailed-results} in the Appendix),
 seem to confirm our expectations. Compared to the previous case, we observe
@@
 
-\begin{wrapfigure}[10]{r}{0.333\textwidth}
+\begin{figure}
 	\centering
-	\vspace{-2ex}
 	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
 	\caption{Results of experiment~2, plotted analogously
-	to~\cref{fig:exp1-time-vs-reg}.}
+	to~\fref{fig:exp1-time-vs-reg}.}
 	\label{fig:exp2-time-vs-reg}
-\end{wrapfigure}
+\end{figure}
 
@@
 metrics of interest with training set size. Firstly, the results shown 
-in~\cref{fig:scaling-r2} (and listed in~\cref{tbl:exp3-detailed-results-r2} in
+in~\fref{fig:scaling-r2} (and listed in~\tref{tbl:exp3-detailed-results-r2} in
 the Appendix) suggest that the most accurate families from the previous experiments
@@
 	\centering
-	\begin{subfigure}[b]{0.333\textwidth}
-		\centering
+	\begin{minipage}{0.333\textwidth}
+		%\centering
 		\includegraphics[width=\linewidth]{scaling_metric_r2}
-		\caption{Regression performance (as $R^2$)}
-		\label{fig:scaling-r2}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.333\textwidth}
-		\centering
+		%\caption{Regression performance (as $R^2$)}
+		%\label{fig:scaling-r2}
+	\end{minipage}\hfill%
+	\begin{minipage}{0.333\textwidth}
+		%\centering
 		\includegraphics[width=\linewidth]{scaling_time_train}
-		\caption{Complexity (as~$\overline{t}_{\text{trn.}}$)}
-		\label{fig:scaling-trn}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.333\textwidth}
-		\centering
+		%\caption{Complexity (as~$\overline{t}_{\text{trn.}}$)}
+		%\label{fig:scaling-trn}
+	\end{minipage}\hfill%
+	\begin{minipage}{0.333\textwidth}
+		%\centering
 		\includegraphics[width=\linewidth]{scaling_time_pred}
-		\caption{Complexity (as~$\overline{t}_{\text{pred.}}$)}
-		\label{fig:scaling-pred}
-	\end{subfigure}
+		%\caption{Complexity (as~$\overline{t}_{\text{pred.}}$)}
+		%\label{fig:scaling-pred}
+	\end{minipage}
 	\caption{Various metrics collected during experiment 3 (scaling
@@
 Next, we examine scaling behaviour in terms of the mean training time (displayed
-in~\cref{fig:scaling-trn} and listed in~\cref{tbl:exp3-detailed-results-t-train} in
+in~\fref{fig:scaling-trn} and listed in~\tref{tbl:exp3-detailed-results-t-train} in
 the Appendix). Consistent with our expectation, the shortest times
@@
 Finally, we study scaling with respect to the mean prediction time (shown
-in~\cref{fig:scaling-pred} and listed in~\cref{tbl:exp3-detailed-results-t-pred} in
+in~\fref{fig:scaling-pred} and listed in~\tref{tbl:exp3-detailed-results-t-pred} in
 the Appendix). Our initial observation is that all tested
@@
 In the fourth experiment proposed
-in~\cref{sec:experiment-methodology}, we exploit previously collected information
+in~\sref{sec:experiment-methodology}, we exploit previously collected information
 to produce surrogates with desirable properties for practical use. We
@@
 prediction time, or (c)~acceptable performance with the smallest training set.
-To this end, we trained 8~surrogates that are presented in~\cref{fig:reg-performance}
-and~\cref{tbl:exp4-detailed-results}.
+To this end, we trained 8~surrogates that are presented in~\fref{fig:reg-performance}
+and~\tref{tbl:exp4-detailed-results}.
 
@@
 	\centering
-	\begin{subfigure}[b]{0.25\textwidth}
+	\begin{minipage}{0.25\textwidth}
 		\centering
 		\includegraphics[width=\linewidth]{exp4_model6}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
+	\end{minipage}\hfill%
+	\begin{minipage}{0.25\textwidth}
 		\centering
 		\includegraphics[width=\linewidth]{exp4_model7}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
+	\end{minipage}\hfill%
+	\begin{minipage}{0.25\textwidth}
 		\centering
 		\includegraphics[width=\linewidth]{exp4_model1}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
+	\end{minipage}\hfill%
+	\begin{minipage}{0.25\textwidth}
 		\centering
 		\includegraphics[width=\linewidth]{exp4_model3}
-	\end{subfigure}
+	\end{minipage}
 
-	\begin{subfigure}[b]{0.25\textwidth}
+	\begin{minipage}{0.25\textwidth}
 		\centering
 		\includegraphics[width=\linewidth]{exp4_model4}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
+	\end{minipage}\hfill%
+	\begin{minipage}{0.25\textwidth}
 		\centering
 		\includegraphics[width=\linewidth]{exp4_model5}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
+	\end{minipage}\hfill%
+	\begin{minipage}{0.25\textwidth}
 		\centering
 		\includegraphics[width=\linewidth]{exp4_model2}
-	\end{subfigure}\hfill%
-	\begin{subfigure}[b]{0.25\textwidth}
+	\end{minipage}\hfill%
+	\begin{minipage}{0.25\textwidth}
 		\centering
 		\includegraphics[width=\linewidth]{exp4_model8}
-	\end{subfigure}
+	\end{minipage}
 	\caption{Regression performance of models 1-4 (row 1, from the left) and 5-8
@@
 with respect to the MC TBR evaluation baseline measured during run~1
-(see~\cref{tbl:sampling-runs} for details). Satisfying
+(see~\tref{tbl:sampling-runs} for details). Satisfying
 goal~(b), the fastest model (no.~2, ANN) achieved~$R^2=\num{0.985}$,
@@
 		$\overline{t}_{\text{eval.}}=\SI{7.777049573054314}{\second}$
-		measured in the MC TBR model during run~1 (see~\cref{tbl:sampling-runs}).
+		measured in the MC TBR model during run~1 (see~\tref{tbl:sampling-runs}).
 		The best-performing metrics are highlighted in bold.}
@@
 
-\begin{wrapfigure}[10]{r}{0.4\textwidth}
+\begin{figure}
 	\centering
-	\vspace{-16ex}
 	\includegraphics[width=\linewidth]{fig5_sintoy}
@@
 	\label{fig:sintoy}
-\end{wrapfigure}
+\end{figure}
 
@@
 
-plotted in~\cref{fig:sintoy} for $n=1$ and two continuous parameters $C$.
+plotted in~\fref{fig:sintoy} for $n=1$ and two continuous parameters $C$.
 ANNs trained on this model demonstrated similar performance to those on the expensive
@@
 iteration can be limited for increased efficiency. The most complex dynamics
-arose with the adjustment of sample increment, shown in~\cref{fig:qassincr}. For
+arose with the adjustment of sample increment, shown in~\fref{fig:qassincr}. For
 each tested initial sample quantity $N$, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$. The plotted error trends suggest that
@@
     \centering
-    \vspace{-1ex}
-    \begin{subfigure}[t]{0.5\textwidth}
+    \begin{minipage}{0.5\textwidth}
         \centering
         \includegraphics[width=1.1\linewidth]{fig6a_qassincrsamp.pdf}
-    \end{subfigure}%
+    \end{minipage}%
     \hfill%
-    \begin{subfigure}[t]{0.5\textwidth}
+    \begin{minipage}{0.5\textwidth}
         \centering
         \includegraphics[width=1.1\linewidth]{fig6b_qassincrtime.pdf}
-    \end{subfigure}
+    \end{minipage}
     \caption{QASS absolute training error over total sample quantity (left) and number of iterations (right).
@@
     \label{fig:qassincr}
-    \vspace{-1ex}
 \end{figure}
@@
 The plateau effect in surrogate error on the evaluation set, seen
-in~\cref{fig:qassincr}, was universal to all configurations and thought to
+in~\fref{fig:qassincr}, was universal to all configurations and thought to
 warrant further investigation. At first this was suspected to be a residual
@@
 QASS and a baseline scheme with uniformly random incremental samples, shown
-in~\cref{fig:qasssampling}.
+in~\fref{fig:qasssampling}.
 
@@
 \begin{minipage}{.48\textwidth}
-  \centering
+  %\centering
   \includegraphics[width=1.1\linewidth]{fig7_qasssampling.pdf}
-  \captionof{figure}{Absolute training error for QASS, baseline scheme, and mixed scheme.}
-  \label{fig:qasssampling}
+  %\caption{Absolute training error for QASS, baseline scheme, and mixed scheme.}
+  %\label{fig:qasssampling}
 \end{minipage}%
@@
 \begin{minipage}{.48\textwidth}
-  \centering
+  %\centering
   \includegraphics[width=1.1\linewidth]{fig8_qasssampling100k.pdf}
-  \captionof{figure}{Absolute training error for QASS and baseline scheme, with 100k initial samples.}
-  \label{fig:qasssampling100k}
+  %\caption{Absolute training error for QASS and baseline scheme, with 100k initial samples.}
+  %\label{fig:qasssampling100k}
 \end{minipage}
@@
 samples and half uniformly random samples incremented on each iteration, which
-is also shown in~\cref{fig:qasssampling}.
-An increase in initial sample size was observed to also resolve precision in these smooth regions of the toy theory, as the initial samples were obtained from a uniform random distribution.
-As shown in ~\cref{fig:qasssampling100k}, with~\num{100000} initial samples it was possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline scheme, from 0.0025 to 0.0015 mean averaged error.
+is also shown in~\fref{fig:qasssampling}. An increase in initial sample size was
+observed to also resolve precision in these smooth regions of the toy theory, as
+the initial samples were obtained from a uniform random distribution. As shown
+in ~\fref{fig:qasssampling100k}, with~\num{100000} initial samples it was possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline scheme, from 0.0025 to 0.0015 mean averaged error.
 Comparing at the point of termination for QASS, this corresponds to a ${\sim}6\%$ decrease in the number of total samples needed to train a surrogate with the same error.

### 2020-05-25 paper/results.tex
shorten the first two results sections, transition to two-column layout

@@
-\todo{This entire section needs to be shortened.}
+\todo{Need any introduction here?}
 
-Having outlined a variety of models and metrics tracked for the
-purposes of their objective comparison, we proceed to present and discuss our
-results in the next sections.
-
-\subsection{Results of Decoupled Sampling}
+\subsection{Decoupled Approach}
 \label{sec:modelres}
-
-We begin by comparing the performance of a diverse set of surrogate families on previously generated samples of the expensive MC TBR model.
-Through the four experimental cases described
-in~\sref{sec:experiment-methodology}, we aim to study properties of the
-considered models in terms of regression performance, training and prediction
-time.
 
@@
 
-The first two experiments perform Bayesian optimisation to maximise~$R^2$ in
-a cross-validation setting as a function of model hyperparameters. While in the
-first experiment we limit training and test sets to the scope of four selected
-slices of the feature space, in the second experiment we lift this restriction
-to examine surrogate capability to model a more complex domain.
-
-The results displayed in~\fref{fig:exp1-time-vs-reg} (and listed
-in~\tref{tbl:exp1-detailed-results} in the Appendix) indicate that in the first
-experiment, GBTs clearly appear to be the most accurate as
+The results displayed in~\fref{fig:exp1-time-vs-reg} indicate that in the first,
+simplified case GBTs clearly appear to be the most accurate as
 well as the fastest surrogate family in terms of mean prediction time. Following
@@
 
-\begin{figure}[h]
+\begin{figure}
 	\centering
-	\begin{minipage}{0.333\textwidth}
-		%\centering
-		\includegraphics[width=\linewidth]{exp1_slice0}
-		%\caption{Run 2, batches 0-2}
-	\end{minipage}\hfill%
-	\begin{minipage}{0.333\textwidth}
-		%\centering
-		\includegraphics[width=\linewidth]{exp1_slice1}
-		%\caption{Run 2, batches 100-102}
-	\end{minipage}\hfill%
-	\begin{minipage}{0.333\textwidth}
-		%\centering
-		\includegraphics[width=\linewidth]{exp1_slice2}
-		%\caption{Run 2, batches 200-202}
-	\end{minipage}
-	\caption{20~best-performing surrogates per each considered family, plotted in
+	\includegraphics[width=0.9\linewidth]{exp1_slice0}
+	\includegraphics[width=0.9\linewidth]{exp1_slice1}
+	\includegraphics[width=0.9\linewidth]{exp1_slice2}
+	\caption{\label{fig:exp1-time-vs-reg}20~best-performing surrogates per each considered family, plotted in
 		terms of complexity (as~$\overline{t}_{\text{pred.}}$) and regression
-		performance (as~$R^2$) on selected slices of run~2, evaluated in
-	experiment~1. Here, batches refer to subsets of training and test datasets that
-	may be matched to slices using~\tref{tbl:slices}.}
-	\label{fig:exp1-time-vs-reg}
+		performance (as~$R^2$) with 3~selected discrete feature assignments.}
 \end{figure}
 
-The results of the second experiment, shown in~\fref{fig:exp2-time-vs-reg} (and listed
-in~\tref{tbl:exp2-detailed-results} in the Appendix),
-seem to confirm our expectations. Compared to the previous case, we observe
-that many surrogate families consistently achieved worse regression
-performance and prediction times. The least
+Comparing these results with those of the second, unrestricted experiment (shown
+in~\fref{fig:exp2-time-vs-reg}), we observe that many surrogate families
+consistently underperformed. The least
 affected models appear to be GBTs, ANNs and ERTs, which are known to be capable of capturing relationships
@@
 	\centering
-	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
-	\caption{Results of experiment~2, plotted analogously
+	\includegraphics[width=0.9\linewidth]{exp2_time_vs_reg}
+	\caption{\label{fig:exp2-time-vs-reg}Results of experiment~2, plotted analogously
 	to~\fref{fig:exp1-time-vs-reg}.}
-	\label{fig:exp2-time-vs-reg}
 \end{figure}
@@
 
-In the third experiment we examine surrogate scaling properties by correlating
-metrics of interest with training set size. Firstly, the results shown 
-in~\fref{fig:scaling-r2} (and listed in~\tref{tbl:exp3-detailed-results-r2} in
-the Appendix) suggest that the most accurate families from the previous experiments
+The results shown in~\fref{fig:scaling} suggest that in terms of regression
+performance the most accurate families from the previous experiments
 consistently maintain their relative advantage over others, even as we introduce
@@
 
-\begin{figure}[h]
+\begin{figure}
 	\centering
-	\begin{minipage}{0.333\textwidth}
-		%\centering
-		\includegraphics[width=\linewidth]{scaling_metric_r2}
-		%\caption{Regression performance (as $R^2$)}
-		%\label{fig:scaling-r2}
-	\end{minipage}\hfill%
-	\begin{minipage}{0.333\textwidth}
-		%\centering
-		\includegraphics[width=\linewidth]{scaling_time_train}
-		%\caption{Complexity (as~$\overline{t}_{\text{trn.}}$)}
-		%\label{fig:scaling-trn}
-	\end{minipage}\hfill%
-	\begin{minipage}{0.333\textwidth}
-		%\centering
-		\includegraphics[width=\linewidth]{scaling_time_pred}
-		%\caption{Complexity (as~$\overline{t}_{\text{pred.}}$)}
-		%\label{fig:scaling-pred}
-	\end{minipage}
-	\caption{Various metrics collected during experiment 3 (scaling
-	benchmark) displayed as a function of training set size.}
+	\includegraphics[width=0.9\linewidth]{scaling_metric_r2}
+	\includegraphics[width=0.9\linewidth]{scaling_time_train}
+	\includegraphics[width=0.9\linewidth]{scaling_time_pred}
+	\caption{Results of the scaling benchmark displayed as a function of
+	training set size. From top to bottom, regression performance (as $R^2$),
+	mean training time and mean prediction time.}
 	\label{fig:scaling}
@@
 
-Next, we examine scaling behaviour in terms of the mean training time (displayed
-in~\fref{fig:scaling-trn} and listed in~\tref{tbl:exp3-detailed-results-t-train} in
-the Appendix). Consistent with our expectation, the shortest times
-were achieved by instance-based learning methods (e.g. KNN, IDW) that
+Consistent with our expectation, the shortest training times were achieved by
+instance-based learning methods (e.g. KNN, IDW) that
 are trained trivially at the expense of increased lookup complexity later during prediction.
@@
 
-Finally, we study scaling with respect to the mean prediction time (shown
-in~\fref{fig:scaling-pred} and listed in~\tref{tbl:exp3-detailed-results-t-pred} in
-the Appendix). Our initial observation is that all tested
-families with the exception of previously mentioned instance-based
-models offer desirable characteristics overall. Analogous to previous
-experiments, GBTs, ABTs and ANNs appear to be tied, as they not only exhibit
-comparable times but also similar scaling slopes. Following that, we notice a
+Finally, all tested families with the exception of previously mentioned instance-based
+models offer desirable prediction times. Analogous to previous experiments,
+GBTs, ABTs and ANNs appear to be tied, as they not only exhibit
+comparable times but also similar scaling slopes. Following that, we note a
 clear hierarchy of ERTs, SVMs, GPR and RBFs, trailed by IDW and KNNs.
@@
 \subsubsection{Model Comparison}
+\todo{This section needs to be shortened.}
 
@@
 	\centering
-	\begin{minipage}{0.25\textwidth}
+	\begin{minipage}{0.5\linewidth}
 		\centering
@@
 	\end{minipage}\hfill%
-	\begin{minipage}{0.25\textwidth}
+	\begin{minipage}{0.5\linewidth}
 		\centering
 		\includegraphics[width=\linewidth]{exp4_model7}
-	\end{minipage}\hfill%
-	\begin{minipage}{0.25\textwidth}
+	\end{minipage}
+
+	\begin{minipage}{0.5\linewidth}
 		\centering
@@
 	\end{minipage}\hfill%
-	\begin{minipage}{0.25\textwidth}
+	\begin{minipage}{0.5\linewidth}
 		\centering
@@
 
-	\begin{minipage}{0.25\textwidth}
+	\begin{minipage}{0.5\linewidth}
 		\centering
@@
 	\end{minipage}\hfill%
-	\begin{minipage}{0.25\textwidth}
+	\begin{minipage}{0.5\linewidth}
 		\centering
 		\includegraphics[width=\linewidth]{exp4_model5}
-	\end{minipage}\hfill%
-	\begin{minipage}{0.25\textwidth}
+	\end{minipage}
+
+	\begin{minipage}{0.5\linewidth}
 		\centering
@@
 	\end{minipage}
+
 	\caption{Regression performance of models 1-4 (row 1, from the left) and 5-8
@@
 
-\begin{table}[h]
+\begin{table*}[t]
 	\centering
@@
 	\label{tbl:exp4-detailed-results}
-\end{table}
+\end{table*}
 
@@
 
-\subsection{Results of Adaptive Sampling}
-\label{sec:adaptiveres}
+\subsection{Adaptive Approach}\label{sec:adaptiveres}
+\todo{This section needs to be shortened.}
+
 In order to test our QASS prototype, several functional toy theories for TBR were developed as alternatives to the expensive MC model.
@@
 \begin{equation}
-	\text{TBR} = \frac{1}{|C|}\sum_{i \in C} \left[1 + \sin(2\pi n (x_i - 1/2)) \right]
+	\text{TBR} = |C|^{-1}\sum_{i \in C} \left[1 + \sin(2\pi n (x_i - 1/2)) \right]
 \end{equation}

### 2020-05-25 paper/methodology.tex
shorten the first two results sections, transition to two-column layout
more edits, add conclusion and acknowledgement, reformat QASS figures

@@
 
-\begin{table}[h]
-	\caption{\label{tbl:surrogates}Considered surrogate model families.
-	$\mathcal{H}$ denotes hyperparameter set.}
+\begin{table}[t]
+	\setlength\tabcolsep{2pt}
+	\caption{\label{tbl:surrogates}Considered surrogate model families, their
+		selected abbreviations and implementations. $\mathcal{H}$~denotes the
+		set of hyperparameters.}
 	\begin{indented}
@@
 		\toprule
-		Surrogate & Acronym & Implementation & $|\mathcal{H}|$ \\
+		Surrogate family & Abbr. & Impl. & $|\mathcal{H}|$ \\
 		\midrule
-		Support vector machines~\cite{fan2008liblinear}	& SVM & SciKit Learn~\cite{scikit-learn} & 3 \\
-		Gradient boosted trees~\cite{friedman2001greedy,friedman1999stochastic,hastie2009elements}	& GBT & SciKit Learn & 11 \\
-		Extremely randomised trees~\cite{geurts2006extremely}	& ERT & SciKit Learn & 7 \\
-		AdaBoosted decision trees~\cite{drucker1997improving}	& ABT & SciKit Learn & 3 \\
-		Gaussian process regression~\cite{williams2006gaussian}	& GPR & SciKit Learn & 2 \\
-		$k$ nearest neighbours	& KNN & SciKit Learn & 3 \\
-		Artificial neural networks	& ANN & Keras (TensorFlow)~\cite{chollet2015keras} & 2 \\
+		Support vector machines~\cite{fan2008liblinear}	& SVM & SciKit~\cite{scikit-learn} & 3 \\
+		Gradient boosted trees~\cite{friedman2001greedy,friedman1999stochastic,hastie2009elements}	& GBT & SciKit & 11 \\
+		Extremely randomised trees~\cite{geurts2006extremely}	& ERT & SciKit & 7 \\
+		AdaBoosted decision trees~\cite{drucker1997improving}	& ABT & SciKit & 3 \\
+		Gaussian process regression~\cite{williams2006gaussian}	& GPR & SciKit & 2 \\
+		$k$ nearest neighbours	& KNN & SciKit & 3 \\
+		Artificial neural networks	& ANN & Keras~\cite{chollet2015keras} & 2 \\
 		Inverse distance weighing~\cite{shepard1968two} & IDW & SMT~\cite{SMT2019} & 1 \\
@@
 
-\begin{table}[h]
+\begin{table*}[t]
 	\caption{\label{tbl:metrics}Metrics recorded in experiments. In
@@
 denote images of the $i$th testing sample in the MC TBR model and the surrogate
-respectively. Furthermore, the mean $\overline{y}=N^{-1}\sum_{i=1}^N y^{(i)}$ and $P$ is the
+respectively. The mean $\overline{y}=N^{-1}\sum_{i=1}^N y^{(i)}$ and $P$ is the
 number of input features.}
@@
 		\toprule
-		Regression perf. metrics& Notation	& Mathematical formulation\\
+		Regression performance metrics& Notation	& Mathematical formulation\\
 		\midrule
@@
 		Mean training time & $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
-		$\hat{f}(x)$})/N_0$  \\
+		$\hat{f}(x)$})N_0^{-1}$  \\
 			Mean prediction time & $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
-		$\hat{f}(x)$})/N$ \\
-				Relative speedup & $\omega$	& $(\text{wall evaluation time of $f(x)$}) /
-		(N\overline{t}_{\text{pred.}})$ \\
+			$\hat{f}(x)$})N^{-1}$ \\
+				Relative speedup & $\omega$	& $(\text{wall evaluation time of $f(x)$})
+				(N\overline{t}_{\text{pred.}})^{-1}$ \\
 		\bottomrule
@@
 	\end{indented}
-\end{table}
+\end{table*}
 
@@
 	\centering
-	\includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
-	\caption{Schematic of QASS algorithm}
-	\label{fig:qassplan}
+	\includegraphics[width=\linewidth]{fig4_qassplan.png}
+	\caption{\label{fig:qassplan}Schematic of QASS algorithm}
 \end{figure}

### 2020-05-29 elevator_pitch/elevator_pitch.tex
Elevator pitch updates

@@
 training of surrogate models to produce a cheap but high-quality approximation
-for a Monte Carlo TBR model in use at the UK Atomic Energy Authority.
+for a Monte Carlo (MC) TBR model in use at the UK Atomic Energy Authority.
 

### 2020-05-29 paper/acknowledgements.tex

PM was supported the STFC UCL Centre for Doctoral Training in Data Intensive
Science (grant no. ST/P006736/1).

### 2020-05-29 paper/results.tex

@@
 performance the most accurate families from the previous experiments
-consistently maintain their relative advantage over others, even as we introduce
-more training points. While such families achieve nearly comparable
+consistently maintain their relative advantage over others, even as
+more training points are introduced. While such families achieve nearly comparable
 performance on the largest dataset, in the opposite case tree-based approaches
@@
 Consistent with our expectation, the shortest training times were achieved by
-instance-based learning methods (e.g. KNN, IDW) that
+instance-based learning methods (KNN, IDW) that
 are trained trivially at the expense of increased lookup complexity later during prediction.
@@
 which are the only family to utilise parallelisation during training, show an
-inverse scaling characteristic. Our conjecture is that this effect may be caused
-by a constant multi-threading overhead that possibly dominates the training process
-on relatively small training sets.
+inverse scaling characteristic. We suspect that this effect may be caused
+by a constant multi-threading overhead that dominates the training process
+on relatively small sets.
 
@@
 \subsubsection{Model Comparison}
-\todo{This section needs to be shortened.}
-
-In the fourth experiment proposed
-in~\sref{sec:experiment-methodology}, we exploit previously collected information
-to produce surrogates with desirable properties for practical use. We
-aim to create models that yield: (a)~the best regression performance regardless
+In the fourth experiment, we aim to create models that yield:
+(a)~the best regression performance regardless
 of other features, (b)~acceptable performance with the shortest mean
@@
 and~\tref{tbl:exp4-detailed-results}.
+Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
+experiments~2-3, we utilised the best-performing hyperparameters.
+In pursuit of goal~(a), the best approximator (no.~1,
+ANN) achieved~$R^2=\num{0.998}$ and mean prediction
+time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
+to a standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
+with respect to the MC TBR evaluation baseline. Satisfying
+goal~(b), the fastest model (no.~2, ANN) achieved~$R^2=\num{0.985}$,
+$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
+and~$\omega=\num{8659251} \times$.
+While these surrogates
+were trained on the entire available set of~\num{500000} datapoints, to satisfy
+goal~(c) we also trained a more simplified model (no.~4, GBT)
+that achieved~$R^2=\num{0.913}$,
+$\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
+with a set of size only~\num{10000}.
 
-\begin{figure}[h]
+\begin{table*}
+	\centering
+	\sisetup{round-mode=places,round-precision=3,detect-weight=true,detect-family=true}
+	\caption{\label{tbl:exp4-detailed-results}Results of experiment~4. Here, figures are reported over 5~cross-validation folds,
+		$|\mathcal{T}|$~denotes cross-validation set size ($\times 10^3$)
+		and $\omega$ is a relative speedup with respect to
+		$\overline{t}_{\text{eval.}}=\SI{7.777049573054314}{\second}$
+		measured in the MC TBR model during run~1 (see~\tref{tbl:sampling-runs}).
+		The best-performing metrics are highlighted in bold.}
+	\setlength\tabcolsep{4pt}
+	\begin{indented}
+	\item[]
+		\scriptsize
+		\begin{tabular}{lrrrrrrrr}
+		\toprule
+		{} & {} & \multicolumn{4}{c}{Regression performance} &
+		\multicolumn{3}{c}{Complexity}\\
+		\cmidrule(lr){3-6}
+		\cmidrule(lr){7-9}
+		Model & $|\mathcal{T}|$ & MAE [TBR] & $S$ [TBR] & $R^2$ [rel.] & $R^2_{\text{adj.}}$ [rel.]
+						& $\overline{t}_{\text{trn.}}$ [\si{\milli\second}] &
+		$\overline{t}_{\text{pred.}}$ [\si{\milli\second}] & $\omega$ [rel.]\\
+		\midrule
+		\input{tbl/table11}
+		\bottomrule
+		\end{tabular}
+	\end{indented}
+\end{table*}
+
+\begin{figure}
 	\centering
@@
 
-	\caption{Regression performance of models 1-4 (row 1, from the left) and 5-8
-		(row 2) trained in experiment~4 (model comparison), viewed
+	\caption{Regression performance of models 1-8 (from left to right, top to
+		bottom) trained in the model comparison experiment, viewed
 		as true vs.~predicted TBR on a test set of a selected cross-validation
@@
 \end{figure}
-
-Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
-experiments~2-3, we utilised the best-performing hyperparameters.
-In pursuit of goal~(a), the best approximator (no.~1,
-ANN) achieved~$R^2=\num{0.998}$ and mean prediction
-time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
-to a standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
-with respect to the MC TBR evaluation baseline measured during run~1
-(see~\tref{tbl:sampling-runs} for details). Satisfying
-goal~(b), the fastest model (no.~2, ANN) achieved~$R^2=\num{0.985}$,
-$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
-and~$\omega=\num{8659251} \times$.
-While these surrogates
-were trained on the entire available set of~\num{500000} datapoints, to satisfy
-goal~(c) we also trained a more simplified model (no.~4, GBT)
-that achieved~$R^2=\num{0.913}$,
-$\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
-with a set of size only~\num{10000}.
-
-\begin{table*}[t]
-	\centering
-	\sisetup{round-mode=places,round-precision=3,detect-weight=true,detect-family=true}
-	\setlength\tabcolsep{2pt}
-	{\scriptsize
-		\begin{tabular}{lrrrrrrrr}
-		\toprule
-		{} & {} & \multicolumn{4}{c}{Regression performance} &
-		\multicolumn{3}{c}{Complexity}\\
-		\cmidrule(lr){3-6}
-		\cmidrule(lr){7-9}
-		Model & $|\mathcal{T}|$ & MAE [TBR] & $S$ [TBR] & $R^2$ [rel.] & $R^2_{\text{adj.}}$ [rel.]
-						& $\overline{t}_{\text{trn.}}$ [\si{\milli\second}] &
-		$\overline{t}_{\text{pred.}}$ [\si{\milli\second}] & $\omega$ [rel.]\\
-		\midrule
-		\input{tbl/table11}
-		\bottomrule
-		\end{tabular}
-	}
-	\caption{Results of experiment~4. Here, figures are reported over 5~cross-validation folds,
-		$|\mathcal{T}|$~denotes cross-validation set size ($\times 10^3$)
-		and $\omega$ is a relative speedup with respect to
-		$\overline{t}_{\text{eval.}}=\SI{7.777049573054314}{\second}$
-		measured in the MC TBR model during run~1 (see~\tref{tbl:sampling-runs}).
-		The best-performing metrics are highlighted in bold.}
-	\label{tbl:exp4-detailed-results}
-\end{table*}
 
@@
 
+\subsection{Adaptive Approach}\label{sec:adaptiveres}
+\todo{This section needs to be shortened.}
+
 \begin{figure}
 	\centering
-	\includegraphics[width=\linewidth]{fig5_sintoy}
-	\caption{Sinusoidal toy TBR theory over two continuous parameters,
+	\includegraphics[width=0.9\linewidth]{fig5_sintoy}
+	\caption{Sinusoidal toy TBR theory over 2 continuous parameters,
 	$n=1$.}
@@
 \end{figure}
-
-\subsection{Adaptive Approach}\label{sec:adaptiveres}
-\todo{This section needs to be shortened.}
 
@@
 each tested initial sample quantity $N$, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$. The plotted error trends suggest that
-incremental samples larger than this optimum give slower model improvement on both the training and evaluation sets, and a larger minimum error on the evaluation set.
-This performance distinction is predicted to be even more significant when trained on the expensive MC model, where the number of sample evaluations will serve as the primary bottleneck for computation time.
-\begin{figure}[h!]
+incremental samples larger than this optimum give slower model improvement on
+both the training and evaluation sets, and a larger minimum error on the
+evaluation set. This performance distinction is predicted to be even more
+significant when trained on the expensive MC model, where the number of sample
+evaluations will serve as the primary bottleneck for computation time.
+
+\begin{figure}
 	\centering
-    \begin{minipage}{0.5\textwidth}
-        \centering
-        \includegraphics[width=1.1\linewidth]{fig6a_qassincrsamp.pdf}
-    \end{minipage}%
-    \hfill%
-    \begin{minipage}{0.5\textwidth}
-        \centering
-        \includegraphics[width=1.1\linewidth]{fig6b_qassincrtime.pdf}
-    \end{minipage}
+	\includegraphics[width=\linewidth]{fig6a_qassincrsamp.pdf}
+	\includegraphics[width=\linewidth]{fig6b_qassincrtime.pdf}
     \caption{QASS absolute training error over total sample quantity (left) and number of iterations (right).
@@
 
-\begin{figure}[h]
+\begin{figure}
 	\centering
-\begin{minipage}{.48\textwidth}
-  %\centering
-  \includegraphics[width=1.1\linewidth]{fig7_qasssampling.pdf}
-  %\caption{Absolute training error for QASS, baseline scheme, and mixed scheme.}
-  %\label{fig:qasssampling}
-\end{minipage}%
-\hfill%
-\begin{minipage}{.48\textwidth}
-  %\centering
-  \includegraphics[width=1.1\linewidth]{fig8_qasssampling100k.pdf}
-  %\caption{Absolute training error for QASS and baseline scheme, with 100k initial samples.}
-  %\label{fig:qasssampling100k}
-\end{minipage}
+	\includegraphics[width=\linewidth]{fig7_qasssampling.pdf}
+	\caption{\label{fig:qasssampling}Absolute training error for QASS, baseline scheme, and mixed scheme.}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{fig8_qasssampling100k.pdf}
+	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and baseline scheme, with 100k initial samples.}
 \end{figure}
@@
 the initial samples were obtained from a uniform random distribution. As shown
-in ~\fref{fig:qasssampling100k}, with~\num{100000} initial samples it was possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline scheme, from 0.0025 to 0.0015 mean averaged error.
-Comparing at the point of termination for QASS, this corresponds to a ${\sim}6\%$ decrease in the number of total samples needed to train a surrogate with the same error.
+in ~\fref{fig:qasssampling100k}, with~\num{100000} initial samples it was
+possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline
+scheme, from 0.0025 to 0.0015 mean averaged error. Comparing at the point of
+termination for QASS, this corresponds to a ${\sim}6\%$ decrease in the number
+of total samples needed to train a surrogate with the same error.

### 2020-05-29 paper/conclusion.tex
more edits, add conclusion and acknowledgement, reformat QASS figures
Reduce introduction and adaptive sampling sections.

--- 2020-05-01 final_report/conclusion.tex
@@
-Over the course of this project, we employed a broad spectrum of data
+We employed a broad spectrum of data
 analysis and machine learning techniques to develop fast and high-quality
-surrogates for a~MC TBR simulation in use at~UKAEA. Having implemented a sampling
-software to efficiently evaluate this expensive MC~model, we deployed it on a
-high performance cluster to generate over~\num{900000}
-datapoints for training and test purposes. We
-investigated possibilities for simplification of the parameter space, and
-concluded that no straightforward reduction was possible. After reviewing
-9~surrogate model families, examining their behaviour on constrained and
+surrogates for the Paramak TBR model. After reviewing
+nine surrogate model families, examining their behaviour on constrained and
 unrestricted feature space, and studying their scaling properties, we retrained
@@
 of~$\SI{0.898}{\micro\second}$, representing a relative
-speedup of $8\cdot 10^6$ with respect to the MC model. Alternatively, we
-also demonstrated the possibility of achieving comparable results using only a
+speedup of $8\cdot 10^6$ with respect to the MC model. We demonstrated the possibility of achieving comparable results using only a
 training set of size~\num{10000}.
 
-After a thorough review of the literature, we developed a novel adaptive
+We further developed a novel adaptive
 sampling algorithm, QASS, capable of interfacing with any of the studied
@@
 With~\num{100000} initial samples and 100 incremental samples per iteration, QASS achieved a ${\sim}40\%$ decrease in surrogate error as compared with a baseline random sampling scheme.
-Equivalently, the same surrogate error as the baseline could be achieved with ${\sim}6\%$ fewer total samples of the expensive theory.
-Further optimisation over the hyperparameter space has strong
-potential to increase this performance, in particular by decreasing the required quantity of initial samples. This will allow for future deployment of QASS
-in coalition with any of the most effective identified surrogates to facilitate
-learning during evaluation of the MC TBR model.
-
-\section*{Acknowledgements}
-
-The authors would like to thank Simeon Bash, Vignesh Gopakumar, Prof.~Nikolaos
-Konstantinidis, Nikolaos Nikolaou, Prof.~Emily Nurse, Jonathan Shimwell and Ingo
-Waldmann for their supervision and valuable suggestions related to this work.
+Further optimisation over the hyperparameter space has strong potential to increase this performance, in particular by decreasing the required quantity of initial samples.
+This will allow for future deployment of QASS on the Paramak TBR model in coalition with any of the most effective identified surrogates.

### 2020-05-29 paper/introduction.tex
Reduce introduction and adaptive sampling sections.

@@
-The analysis of massive datasets has become a necessary component of virtually all technical fields, as well as the social and humanistic sciences, in recent years.
-Given that rapid improvements in sensing and processing hardware have gone hand in hand with the data explosion, it is unsurprising that software for the generation and interpretation of this data has also attained a new frontier in complexity.
-In particular, simulation procedures such as Monte Carlo (MC) event generation can perform physics predictions even for theoretical regimes which are not analytically tractable.
-The bottleneck for such procedures, as is often the case, lies in the computational time and power which they necessitate.
-
-Surrogate models, or metamodels, can resolve this limitation by replacing a
-resource-expensive procedure with a much cheaper approximation
+Surrogate models were developed to resolve computational limitations in the analysis of massive datasets by replacing a resource-expensive procedure with a much cheaper approximation
 \cite{Sondergaard2003}. They are especially useful in applications where
@@
 
-In this project, in coordination with the UK Atomic Energy Authority (UKAEA), we sought to develop a surrogate model for the tritium breeding ratio (TBR) in a Tokamak nuclear fusion reactor.
-Our expensive model was an MC-based neutronics simulation, \textit{Paramak}\footnote{Provided by collaborator Jonathan Shimwell, at UKAEA.}, which returns a prediction of the TBR for a given configuration of a spherical Tokamak.
-We took an empirical approach to the construction of this surrogate, and no results described here are explicitly dependent on prior physics knowledge.
+We sought to develop an empirical surrogate model for the tritium breeding ratio (TBR) in a Tokamak nuclear fusion reactor.
+Our expensive model was a Monte Carlo (MC) neutronics simulation, \textit{Paramak}\footnote{Provided by collaborator Jonathan Shimwell, at UKAEA.}, which returns a prediction of the TBR for a given configuration of a spherical Tokamak.
 
-For the remainder of Section 1, we will define the TBR and set the context of this work within the goals of the UKAEA.
-In Section 2 we will describe our datasets generated from the expensive model for training and validation purposes, and the dimensionality reduction methods employed to develop our understanding of the parameter domain.
-In Section 3 we will present our methodologies for the comparison testing of a wide variety of surrogate modelling techniques, as well as a novel adaptive sampling procedure suited to this application.
-After delivering the results of these approaches in Section 4, we will give our final conclusions and recommendations for further work.
+For the remainder of Section 1, we will define the TBR and further motivate our research.
+In Section 2 we will present our methodologies for the comparison testing of a wide variety of surrogate modelling techniques, as well as a novel adaptive sampling procedure suited to this application.
+After delivering the results of these approaches in Section 3, we will give our final conclusions and recommendations for further work.
 
@@
 Nuclear fusion technology relies on the production and containment of an
-extremely hot and dense plasma. In this environment, by design similar to that
-of a star, hydrogen atoms attain energies sufficient to overcome their usual
-electrostatic repulsion and fuse to form helium~\cite{Hernandez2018}. Early prototype reactors
-made use of the deuterium (\isotope[2]{H}, or \isotope{D}) isotope of hydrogen in order to
-achieve fusion under more accessible conditions, but lead to limited success.
-The current frontier generation of fusion reactors, such as the Joint European Torus (JET) and the
+extremely hot and dense plasma containing enriched Hydrogen isotopes. The current frontier generation of fusion reactors, such as the Joint European Torus (JET) and the
 under-construction International Thermonuclear Experimental Reactor (ITER), make
-use of tritium (\isotope[3]{H}, or \isotope{T}) fuel for further efficiency gain.
-Experimentation at JET dating back to 1997~\cite{Keilhacker1999} has made significant headway in
-validating deuterium-tritium (D-T) operations and constraining the technology
-which will be employed in ITER in a scaled-up form.
-
-However, tritium is much less readily available as a fuel source than deuterium.
-While at least one deuterium atom occurs for every \num{5000} molecules of
-naturally-sourced water, and may be easily distilled, tritium is extremely rare
-in nature. It may be produced indirectly through irradiation of heavy water
+use of both tritium and deuterium fuel.
+While at least one deuterium atom occurs for every \num{5000} molecules of naturally-sourced water, and may be easily distilled, tritium is extremely rare in nature.
+It may be produced indirectly through irradiation of heavy water
 (\DDO) during nuclear fission, but only at very low rates which could
@@
 \end{eqnarray}
-\begin{figure}
-  \centering
-  % TODO: \includegraphics[width=0.48\textwidth]{fig1_tokamakdiagram.png}
-  \caption{Typical single-null reactor configuration as specified by BLUEPRINT~\cite{Coleman2019}: 1 — plasma,
-2 — breeding blankets }
-\label{fig:tokamak}
-\end{figure}
+
 where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
-less frequently occurring isotopes of lithium, respectively. \isotope[6]{Li} has
-the greatest tritium breeding cross-section of all tested isotopes~\cite{Hernandez2018}, but due
-to magnetohydrodynamic instability of liquid lithium in the reactor environment,
-a variety of solid lithium compounds are preferred.
-
-The TBR is defined as the ratio between tritium generation in the breeding
-blanket per unit time and tritium fuel consumption in the reactor. The MC
-neutronics simulations previously mentioned therefore must account for both the
-internal plasma dynamics of the fusion reactor and the resultant interactions of
-neutrons with breeding blanket materials. Neutron paths are traced through a CAD
-model (e.g. Figure~\ref{fig:tokamak}) of a reactor with modifiable geometry.
-
-The input parameters of the computationally-expensive TBR model therefore fall
+less common isotopes of lithium, respectively.
+The TBR is defined as the ratio between tritium generation in the breeding blanket and consumption in the reactor, whose input parameters in the-expensive MC model fall
 into two classes. Continuous parameters, including material thicknesses and
 packing ratios, describe the geometry of a given reactor configuration. Discrete
-categorical parameters further specify all relevant material sections, including
-coolants, armours, and neutron multipliers. One notable exception is the
-enrichment ratio, a continuous parameter denoting the presence
-of~\isotope[6]{Li}. Our challenge, put simply, was to produce a fast TBR
+categorical parameters then specify material selections, including
+coolants, armours, and neutron multipliers. We set out to produce a fast TBR
 function which takes these same input parameters and approximates the MC TBR

### 2020-05-29 paper/methodology.tex
Reduce introduction and adaptive sampling sections.

@@
 surrogate training on sampled point sets. Listed in~\tref{tbl:surrogates}, these
-implementations define 9~surrogate families that are later reviewed in~\sref{sec:results}.
+implementations define nine surrogate families that are later reviewed in~\sref{sec:results}.
 We note that each presented algorithm defines hyperparameters that may influence its
@@
 \subsection{Adaptive Approach}\label{sec:adaptive}
-\todo{This section needs to be shortened}
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig4_qassplan.png}
+	\includegraphics[width=1.2\linewidth]{fig4_qassplan.png}
 	\caption{\label{fig:qassplan}Schematic of QASS algorithm}
@@
 
-All of the surrogate modelling techniques studied in this project face a common
-challenge: their accuracy is limited by the quantity of training samples which
-are available from the expensive MC TBR model. Adaptive sampling procedures can
-improve upon this limitation by taking advantage of statistical information
-which is accumulated during the training of any surrogate model. Rather than
-training the surrogate on a single sample set generated according to a fixed
-strategy, sample locations are chosen periodically during training so as to best suit the model
-under consideration.
-
-Adaptive sampling techniques appear frequently in the literature and have been
-specialised for surrogate modelling. Garud's~\cite{Garud2016} ``Smart Sampling
-Algorithm'' achieved notable success by incorporating surrogate quality and
+Adaptive sampling techniques appear frequently in the literature and have been specialised for surrogate modelling, where precision is implicitly limited by the quantity of training samples which are available from the expensive model.
+Garud's~\cite{Garud2016} ``Smart Sampling Algorithm'' achieved notable success by incorporating surrogate quality and
 crowding distance scoring to identify optimal new samples, but was only tested
@@
 fare better for high-dimensional models by more thoroughly exploring all local
-optima in the feature space. MCMC produces a progressive chain of sample points,
-each drawn according to the same symmetric proposal
-distribution\todo{Incorporate the footnote into the text.}\footnote{An
-adaptive MCMC procedure~\cite{Zhang2012}, which adjusts an ellipsoidal proposal
-distribution to fit the posterior, was also implemented but not fully tested.}
-from the prior point. These sample points will converge to a desired posterior
-distribution, so long as the acceptance probability for these draws has a
-particular functional dependence on that posterior value (see~\cite{Zhou2018}
-for a review).
+optima in the feature space. MCMC produces each sample points according to a shared proposal
+distribution from the prior point. These sample points will converge to a desired posterior
+distribution, so long as the acceptance probability meets certain statistical criteria (see~\cite{Zhou2018} for a review).
 
@@
 parameter optimisation~\cite{Zhang2020,Gong2017}, in particular the ASMO-PODE
-algorithm~\cite{Ginting2011} which makes use of MCMC-based adaptive sampling to
-attain greater surrogate precision around prospective optima. Our novel approach
-draws inspiration from ASMO-PODE, but instead uses MCMC to generate samples
+algorithm~\cite{Ginting2011} which makes use of MCMC-based adaptive sampling. Our approach draws inspiration from ASMO-PODE, but instead uses MCMC to generate samples
 which increase surrogate precision throughout the entire parameter space.
@@
 Validation was also performed during each iteration on independent, uniformly-random sample sets.
-
-% Adaptive multi-chain MCMC:~\cite{Zhang2012}

### 2020-05-29 paper/results.tex
Reduce introduction and adaptive sampling sections.

@@
-\todo{Need any introduction here?}
-
 \subsection{Decoupled Approach}
@@
 \subsection{Adaptive Approach}\label{sec:adaptiveres}
-\todo{This section needs to be shortened.}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\linewidth]{fig5_sintoy}
-	\caption{Sinusoidal toy TBR theory over 2 continuous parameters,
-	$n=1$.}
-	\label{fig:sintoy}
-\end{figure}
 
 In order to test our QASS prototype, several functional toy theories for TBR were developed as alternatives to the expensive MC model.
-By far the most robust of these was the following sinusoidal theory with adjustable wavenumber parameter $n$:
+By far the most robust of these was the following sinusoidal theory over continuous parameters $C$, with adjustable wavenumber parameter $n$:
 
@@
 
-plotted in~\fref{fig:sintoy} for $n=1$ and two continuous parameters $C$.
 ANNs trained on this model demonstrated similar performance to those on the expensive
@@
 the sinusoidal theory for varied quantities of initial, incremental, and MCMC
-candidate samples. Although the scope of this project did not include thorough
-searches of this hyperparameter domain, sufficient runs were made to identify
-some likely trends.
+candidate samples.
 
@@
 effect on final surrogate precision, suggesting that the runtime of MCMC on each
-iteration can be limited for increased efficiency. The most complex dynamics
-arose with the adjustment of sample increment, shown in~\fref{fig:qassincr}. For
-each tested initial sample quantity $N$, the optimal number of step samples was seen to be well-approximated by $\sqrt{N}$. The plotted error trends suggest that
-incremental samples larger than this optimum give slower model improvement on
-both the training and evaluation sets, and a larger minimum error on the
-evaluation set. This performance distinction is predicted to be even more
-significant when trained on the expensive MC model, where the number of sample
-evaluations will serve as the primary bottleneck for computation time.
+iteration could be limited for increased efficiency.
+We also found that an optimum increment exists and is monotonic with initial sample quantity, above or below which models showed slower improvement on both the training and evaluation sets, and a larger minimum error on the
+evaluation set. This performance distinction will be far more
+significant for an expensive model such as Paramak, where the number of sample
+evaluations is the primary computational bottleneck.
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{fig6a_qassincrsamp.pdf}
-	\includegraphics[width=\linewidth]{fig6b_qassincrtime.pdf}
-    \caption{QASS absolute training error over total sample quantity (left) and number of iterations (right).
-MAE represents surrogate error on the adaptively-sampled training/test set, and E\_MAE on the independent evaluation sets.}
-    \label{fig:qassincr}
-\end{figure}
-
-The plateau effect in surrogate error on the evaluation set, seen
-in~\fref{fig:qassincr}, was universal to all configurations and thought to
-warrant further investigation. At first this was suspected to be a residual
+A plateau effect in surrogate error on the evaluation set was universal to all configurations, and initially suspected to be a residual
 effect of retraining the same ANN instance without adjustment to data

### 2020-05-29 paper/ucl_tbr_paper.tex
more edits to the methodology section to comply with journal guidelines
shorten the first two results sections, transition to two-column layout
Reduce introduction and adaptive sampling sections.

@@
 \usepackage{url}
+\usepackage{graphicx}
 
@@
 \newcommand{\DDO}{D\textsubscript{2}O}
+
+\graphicspath{{./fig/}}
 
@@
 
-\author{G~Van Goffrier$^1$ and P~Mánek$^{1,2}$, V~Gopakumar$^3$, N~Nikolau$^1$, J~Shimwell$^3$, I~Waldmann$^1$}
+\author{P~Mánek$^{1,2}$, G~Van Goffrier$^1$, V~Gopakumar$^3$, N~Nikolau$^1$, J~Shimwell$^3$ and I~Waldmann$^1$}
 
@@
 
-\eads{\mailto{graham.vangoffrier.19@ucl.ac.uk}, \mailto{petr.manek.19@ucl.ac.uk}}
+\eads{\mailto{petr.manek.19@ucl.ac.uk}, \mailto{graham.vangoffrier.19@ucl.ac.uk}}
 
@@
 % TODO: revise these
-\keywords{magnetic moment, solar neutrinos, astrophysics}
-\submitto{\jpg}
+\keywords{machine learning, surrogate model, nuclear fusion, tritium breeding, adaptive sampling}
+\submitto{\NF}
 \maketitle
+\ioptwocol
 

### 2020-06-04 paper/introduction.tex
added figure and changed reactor type

@@
 
-We sought to develop an empirical surrogate model for the tritium breeding ratio (TBR) in a Tokamak nuclear fusion reactor.
-Our expensive model was a Monte Carlo (MC) neutronics simulation, \textit{Paramak}\footnote{Provided by collaborator Jonathan Shimwell, at UKAEA.}, which returns a prediction of the TBR for a given configuration of a spherical Tokamak.
+We sought to develop an empirical surrogate model for the tritium breeding ratio (TBR) in a Inertial confinement fusion (ICF) nuclear fusion reactor.
+Our expensive model was a Monte Carlo (MC) neutronics simulation, \textit{Paramak}\footnote{Provided by collaborator Jonathan Shimwell, at UKAEA.}, which returns a prediction of the TBR for a given configuration of a spherical (ICF) reactor.
+
+\begin{figure}[!ht]
+  \centering
+    \begin{tikzpicture}
+    \fill[green!40!white]  (0,0) circle (3cm);
+    \fill[blue!40!white]  (0,0) circle (2cm);
+    \fill[white!40!white]  (0,0) circle (1.9cm);
+    \fill[red!40!white]  (0,0) circle (0.1cm);
+    \end{tikzpicture}
+
+    \caption{Diagram of the simple sphere geometry (not to scale) where the blanket is \fcolorbox{white}{green}{\rule{0pt}{6pt}\rule{6pt}{0pt}}, the firstwall is \fcolorbox{white}{blue}{\rule{0pt}{6pt}\rule{6pt}{0pt}} and the neutron point source is \fcolorbox{white}{red}{\rule{0pt}{6pt}\rule{6pt}{0pt}}.}
+    \label{fig:model_diagram}
+\end{figure}
 
@@
 into two classes. Continuous parameters, including material thicknesses and
-packing ratios, describe the geometry of a given reactor configuration. Discrete
+packing fraction, describe the geometry of a given reactor configuration. Discrete
 categorical parameters then specify material selections, including

### 2020-06-04 paper/introduction.tex
added neutron source description and geometry size

@@
 \end{figure}
+
+A point source with a Muir energy distribution \cite{openmcmuir} around 14.06MeV was used to approximate a DT plasma neutron source. 
+The inner radius of the void region was 10m, the first wall thickness was 2.7cm and the blanket thickness was 2m.
 
@@
 into two classes. Continuous parameters, including material thicknesses and
-packing fraction, describe the geometry of a given reactor configuration. Discrete
+packing fraction, describe the geometry of a given reactor configuration **TODO**add all the parameters here*****. Discrete
 categorical parameters then specify material selections, including

### 2020-06-11 paper/introduction.tex
use \todo for Jon's comment

--- 2020-06-04 paper/introduction.tex
@@
 into two classes. Continuous parameters, including material thicknesses and
-packing fraction, describe the geometry of a given reactor configuration. Discrete
+packing fraction, describe the geometry of a given reactor configuration.
+\todo{add all the parameters here} Discrete
 categorical parameters then specify material selections, including

### 2020-06-11 paper/rasterize_figure.sh
rasterize figure 6 plots (reducing the paper PDF size 10x), add rasterization script

@@ -1,0 +1,15 @@
+#!/bin/bash
+
+set -e
+
+DPI=300
+INPUT_FILE=$1 ; shift
+OUTPUT_FILE=$1 ; shift
+
+gs -o /tmp/onlytxt.pdf -sDEVICE=pdfwrite -dFILTERVECTOR -dFILTERIMAGE $INPUT_FILE
+gs -o /tmp/graphics.pdf -sDEVICE=pdfwrite -dFILTERTEXT $INPUT_FILE
+convert -density $DPI -quality 100 /tmp/graphics.pdf /tmp/graphics.png
+convert -density $DPI -quality 100 /tmp/graphics.png /tmp/graphics.pdf
+pdftk /tmp/graphics.pdf stamp /tmp/onlytxt.pdf output $OUTPUT_FILE
+rm /tmp/onlytxt.pdf /tmp/graphics.pdf /tmp/graphics.png
+

### 2020-06-11 paper/rasterize_figure.sh
add SO url

@@ -1,4 +1,5 @@
 #!/bin/bash
+# courtesy of: https://stackoverflow.com/questions/9607687/replacing-vector-images-in-a-pdf-with-raster-images
 
 set -e
 

### 2020-06-11 paper/methodology.tex
capitalize figure and table references

@@
 For both methods, we selected state-of-the-art regression algorithms to perform
-surrogate training on sampled point sets. Listed in~\tref{tbl:surrogates}, these
+surrogate training on sampled point sets. Listed in~\Tref{tbl:surrogates}, these
 implementations define nine surrogate families that are later reviewed in~\sref{sec:results}.
@@
 To compare quality of produced surrogates, we define a number of metrics listed
-in~\tref{tbl:metrics}. For regression performance analysis, we include a
+in~\Tref{tbl:metrics}. For regression performance analysis, we include a
 selection of absolute metrics to assess their approximation capability and set
@@
 
-We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, \fref{fig:qassplan}) to iteratively increment the training/test set with sample
+We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, \Fref{fig:qassplan}) to iteratively increment the training/test set with sample
 points which maximise surrogate error and minimise a crowding distance metric

### 2020-06-11 paper/results.tex
rasterize figure 6 plots (reducing the paper PDF size 10x), add rasterization script
capitalize figure and table references

@@
 
-The results displayed in~\fref{fig:exp1-time-vs-reg} indicate that in the first,
+The results displayed in~\Fref{fig:exp1-time-vs-reg} indicate that in the first,
 simplified case GBTs clearly appear to be the most accurate as
@@
 Comparing these results with those of the second, unrestricted experiment (shown
-in~\fref{fig:exp2-time-vs-reg}), we observe that many surrogate families
+in~\Fref{fig:exp2-time-vs-reg}), we observe that many surrogate families
 consistently underperformed. The least
@@
 	\caption{\label{fig:exp2-time-vs-reg}Results of experiment~2, plotted analogously
-	to~\fref{fig:exp1-time-vs-reg}.}
+	to~\Fref{fig:exp1-time-vs-reg}.}
 \end{figure}
@@
 
-The results shown in~\fref{fig:scaling} suggest that in terms of regression
+The results shown in~\Fref{fig:scaling} suggest that in terms of regression
 performance the most accurate families from the previous experiments
@@
 prediction time, or (c)~acceptable performance with the smallest training set.
-To this end, we trained 8~surrogates that are presented in~\fref{fig:reg-performance}
-and~\tref{tbl:exp4-detailed-results}.
+To this end, we trained 8~surrogates that are presented in~\Fref{fig:reg-performance}
+and~\Tref{tbl:exp4-detailed-results}.
 Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
@@
 		$\overline{t}_{\text{eval.}}=\SI{7.777049573054314}{\second}$
-		measured in the MC TBR model during run~1 (see~\tref{tbl:sampling-runs}).
+		measured in the MC TBR model during run~1 (see~\Tref{tbl:sampling-runs}).
 		The best-performing metrics are highlighted in bold.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model6}
+		\includegraphics[width=\linewidth]{exp4_model6_rasterized}
 	\end{minipage}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model7}
+		\includegraphics[width=\linewidth]{exp4_model7_rasterized}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model1}
+		\includegraphics[width=\linewidth]{exp4_model1_rasterized}
 	\end{minipage}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model3}
+		\includegraphics[width=\linewidth]{exp4_model3_rasterized}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model4}
+		\includegraphics[width=\linewidth]{exp4_model4_rasterized}
 	\end{minipage}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model5}
+		\includegraphics[width=\linewidth]{exp4_model5_rasterized}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model2}
+		\includegraphics[width=\linewidth]{exp4_model2_rasterized}
 	\end{minipage}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model8}
+		\includegraphics[width=\linewidth]{exp4_model8_rasterized}
 	\end{minipage}
@@
 QASS and a baseline scheme with uniformly random incremental samples, shown
-in~\fref{fig:qasssampling}.
+in~\Fref{fig:qasssampling}.
 
@@
 samples and half uniformly random samples incremented on each iteration, which
-is also shown in~\fref{fig:qasssampling}. An increase in initial sample size was
+is also shown in~\Fref{fig:qasssampling}. An increase in initial sample size was
 observed to also resolve precision in these smooth regions of the toy theory, as
 the initial samples were obtained from a uniform random distribution. As shown
-in ~\fref{fig:qasssampling100k}, with~\num{100000} initial samples it was
+in ~\Fref{fig:qasssampling100k}, with~\num{100000} initial samples it was
 possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline

### 2020-06-11 paper/conclusion.tex
implement first batch of comments from Nikos

@@
 surrogates for the Paramak TBR model. After reviewing
-nine surrogate model families, examining their behaviour on constrained and
+nine surrogate model families, examining their behaviour on a constrained and
 unrestricted feature space, and studying their scaling properties, we retrained
@@
 practical use. The fastest surrogate, an artificial neural network trained
-on~\num{500000} datapoints, featured~$R^2=\num{0.985}$ with mean prediction time
+on~\num{500000} datapoints, attained an~$R^2=\num{0.985}$ with mean prediction time
 of~$\SI{0.898}{\micro\second}$, representing a relative
@@
 We further developed a novel adaptive
-sampling algorithm, QASS, capable of interfacing with any of the studied
-surrogates. Preliminary testing on a toy theory, qualitatively comparable to
+sampling algorithm, QASS, capable of interfacing with any surrogate model.
+Preliminary testing on a toy theory, qualitatively comparable to
 the MC TBR model, demonstrated the effectiveness of QASS and behavioural trends
-consistent with the design of the algorithm.
-With~\num{100000} initial samples and 100 incremental samples per iteration, QASS achieved a ${\sim}40\%$ decrease in surrogate error as compared with a baseline random sampling scheme.
+consistent with the design of the algorithm. With~\num{100000} initial samples
+and 100 incremental samples per iteration, QASS achieved a ${\sim}40\%$ decrease
+in surrogate error compared to a baseline random sampling scheme.
 Further optimisation over the hyperparameter space has strong potential to increase this performance, in particular by decreasing the required quantity of initial samples.

### 2020-06-11 paper/methodology.tex
implement first batch of comments from Nikos

@@
 
-To compare quality of produced surrogates, we define a number of metrics listed
+To compare the quality of the produced surrogates, we define a number of metrics listed
 in~\Tref{tbl:metrics}. For regression performance analysis, we include a
-selection of absolute metrics to assess their approximation capability and set
+selection of absolute metrics to assess the models' approximation capability and set
 practical bounds on the expected uncertainty of their predictions. In addition, we also track
 relative measures that are better-suited for comparison between this work and others as
-they maintain invariance with respect to the selected domain and image space.
+they are invariant with respect to the selected domain and image space.
 For complexity analysis, surrogates are assessed in terms of wall
@@
 Experiments related to the decoupled approach are organised in four parts,
-further described in this section. In summary, we aim to optimise hyperparameters of
+further described in this section. In summary, we aim to optimise the hyperparameters of
 each surrogate family separately and later use the best found results to compare surrogate
@@
 unrestricted feature space. In both cases, hyperparameter tuning is
-facilitated by Bayesian optimisation~\cite{movckus1975bayesian}. We set its
-objective to maximise $R^2$ and terminate the process after 1000~iterations or
+facilitated by Bayesian optimisation~\cite{movckus1975bayesian}. We select the
+hyperparameter configuration that produces the model that maximises $R^2$. The
+process is terminated after 1000~iterations or
 2~days, whichever condition is satisfied first.

### 2020-06-11 paper/results.tex
implement first batch of comments from Nikos

@@
 that, we note that ERTs, SVMs and ANNs also achieved satisfactory results with respect to both examined metrics.
-While the remainder of tested surrogate families does not exhibit problems in
+While the remainder of tested surrogate families does not exhibit prohibitive
 complexity, its regression performance falls below average.
@@
 in~\Fref{fig:exp2-time-vs-reg}), we observe that many surrogate families
-consistently underperformed. The least
+consistently underperform. The least
 affected models appear to be GBTs, ANNs and ERTs, which are known to be capable of capturing relationships
@@
 time. We observe that ERTs and RBFs also
-demonstrated satisfactory results, relatively outperforming the remaining surrogates in
+demonstrated satisfactory results, clearly outperforming the remaining surrogates in
 terms of regression performance, and in some cases also in prediction time.
@@
 restrictions employed in the first case have proven effective in improving the
-regression performance of some methods, this result has fluctuated considerably
+regression performance of some methods, their performance fluctuates considerably
 depending on the selected slices. Furthermore, in all instances the best
-results were achieved by families of surrogates that were nearly unaffected by
-this modification.
+results are achieved by families of surrogates that do not benefit from this
+restriction (GBTs, ANNs, ERTs).
 
@@
 more training points are introduced. While such families achieve nearly comparable
-performance on the largest dataset, in the opposite case tree-based approaches
+performance on the largest dataset, in the opposite case tree-based ensemble approaches
 clearly outperform ANNs. This can be observed
@@
 are trained trivially at the expense of increased lookup complexity later during prediction.
-Furthermore, we observe that the majority of tree-based algorithms also perform
+Furthermore, we observe that the majority of tree-based ensemble algorithms also perform
 and scale well, unlike RBFs and GPR which appear to behave superlinearly. We note that ANNs,
@@
 GBTs, ABTs and ANNs appear to be tied, as they not only exhibit
-comparable times but also similar scaling slopes. Following that, we note a
+comparable times but also similar scaling slopes. Following those, we note a
 clear hierarchy of ERTs, SVMs, GPR and RBFs, trailed by IDW and KNNs.
@@
 experiments~2-3, we utilised the best-performing hyperparameters.
-In pursuit of goal~(a), the best approximator (no.~1,
+In pursuit of goal~(a), the best approximator (Model~1,
 ANN) achieved~$R^2=\num{0.998}$ and mean prediction
@@
 with respect to the MC TBR evaluation baseline. Satisfying
-goal~(b), the fastest model (no.~2, ANN) achieved~$R^2=\num{0.985}$,
+goal~(b), the fastest model (Model~2, ANN) achieved~$R^2=\num{0.985}$,
 $\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
@@
 were trained on the entire available set of~\num{500000} datapoints, to satisfy
-goal~(c) we also trained a more simplified model (no.~4, GBT)
+goal~(c) we also trained a more simplified model (Model~4, GBT)
 that achieved~$R^2=\num{0.913}$,
@@
 	\sisetup{round-mode=places,round-precision=3,detect-weight=true,detect-family=true}
-	\caption{\label{tbl:exp4-detailed-results}Results of experiment~4. Here, figures are reported over 5~cross-validation folds,
+	\caption{\label{tbl:exp4-detailed-results}Results of experiment~4. Here,
+		average values and standard deviations are reported over 5~cross-validation folds,
 		$|\mathcal{T}|$~denotes cross-validation set size ($\times 10^3$)
@@
 		measured in the MC TBR model during run~1 (see~\Tref{tbl:sampling-runs}).
-		The best-performing metrics are highlighted in bold.}
+	The best-performing method(s) under each are highlighted in bold.}
 	\setlength\tabcolsep{4pt}
@@
 
-	\caption{Regression performance of models 1-8 (from left to right, top to
+	\caption{Regression performance of Models 1-8 (from left to right, top to
 		bottom) trained in the model comparison experiment, viewed

### 2020-06-12 paper/introduction.tex
integrate first batch of Vignesh's comments

@@
 The TBR is defined as the ratio between tritium generation in the breeding blanket and consumption in the reactor, whose input parameters in the-expensive MC model fall
-into two classes. Continuous parameters, including material thicknesses and
+into two classes. Continuous parameters, such as material thicknesses and
 packing fraction, describe the geometry of a given reactor configuration.
 \todo{add all the parameters here} Discrete
-categorical parameters then specify material selections, including
+categorical parameters then specify material selections, such as
 coolants, armours, and neutron multipliers. We set out to produce a fast TBR

### 2020-06-12 paper/introduction.tex
implement more of Nikos feedback in two passes

@@
 
-We sought to develop an empirical surrogate model for the tritium breeding ratio (TBR) in a Inertial confinement fusion (ICF) nuclear fusion reactor.
-Our expensive model was a Monte Carlo (MC) neutronics simulation, \textit{Paramak}\footnote{Provided by collaborator Jonathan Shimwell, at UKAEA.}, which returns a prediction of the TBR for a given configuration of a spherical (ICF) reactor.
+In this work, we develop an empirical surrogate model for the tritium breeding
+ratio (TBR) in a Inertial confinement fusion (ICF) nuclear fusion reactor. The
+expensive model (which our surrogate model approximates) is a Monte Carlo (MC)
+neutronics simulation, \textit{Paramak}\footnote{Provided by collaborator
+Jonathan Shimwell, at UKAEA.}\todo{IOP guidelines discourage footnotes}, which returns a prediction of the TBR for a given configuration of a spherical (ICF) reactor.
 
@@
 \todo{add all the parameters here} Discrete
-categorical parameters then specify material selections, such as
+categorical parameters specify material selections, such as
 coolants, armours, and neutron multipliers. We set out to produce a fast TBR

### 2020-06-12 paper/results.tex
implement more of Nikos feedback in two passes

@@
 	\includegraphics[width=0.9\linewidth]{exp2_time_vs_reg}
-	\caption{\label{fig:exp2-time-vs-reg}Results of experiment~2, plotted analogously
+	\caption{\label{fig:exp2-time-vs-reg}Results of Experiment~2, plotted analogously
 	to~\Fref{fig:exp1-time-vs-reg}.}
@@
 \subsubsection{Model Comparison}
-In the fourth experiment, we aim to create models that yield:
+In Experiment~4, we aim to create models that yield:
 (a)~the best regression performance regardless
@@
 Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
-experiments~2-3, we utilised the best-performing hyperparameters.
+Experiments~2 \&~3, we utilised the best-performing hyperparameters.
 In pursuit of goal~(a), the best approximator (Model~1,
@@
 	\sisetup{round-mode=places,round-precision=3,detect-weight=true,detect-family=true}
-	\caption{\label{tbl:exp4-detailed-results}Results of experiment~4. Here,
+	\caption{\label{tbl:exp4-detailed-results}Results of Experiment~4. Here,
 		average values and standard deviations are reported over 5~cross-validation folds,
@@
 		and $\omega$ is a relative speedup with respect to
-		$\overline{t}_{\text{eval.}}=\SI{7.777049573054314}{\second}$
-		measured in the MC TBR model during run~1 (see~\Tref{tbl:sampling-runs}).
+		$\overline{t}_{\text{eval.}}=\num{7.777049573054314} \pm
+		\num{2.8103592103930337} \text{ s}$
+		measured in the MC TBR model over~\num{500000} samples.
 	The best-performing method(s) under each are highlighted in bold.}
@@
 
-	\caption{Regression performance of Models 1-8 (from left to right, top to
-		bottom) trained in the model comparison experiment, viewed
+	\caption{Regression performance of Models~1-8 (from left to right, top to
+		bottom) trained in Experiment~4, viewed
 		as true vs.~predicted TBR on a test set of a selected cross-validation

### 2020-06-14 paper/introduction.tex
Graham edits to intro and adaptive sections.

--- 2020-06-12 paper/introduction.tex
@@
 
-We sought to develop an empirical surrogate model for the tritium breeding ratio (TBR) in a Inertial confinement fusion (ICF) nuclear fusion reactor.
-Our expensive model was a Monte Carlo (MC) neutronics simulation, \textit{Paramak}\footnote{Provided by collaborator Jonathan Shimwell, at UKAEA.}, which returns a prediction of the TBR for a given configuration of a spherical (ICF) reactor.
+In this work, we develop an empirical surrogate model for the tritium breeding
+ratio (TBR) in an inertial confinement fusion (ICF) reactor. The
+expensive model which our surrogate model approximates is a Monte Carlo (MC)
+neutronics simulation, \textit{Paramak} (provided by collaborator
+Jonathan Shimwell at UKAEA) which returns a prediction of the TBR for a given configuration of a spherical ICF reactor.
 
@@
 
-A point source with a Muir energy distribution \cite{openmcmuir} around 14.06MeV was used to approximate a DT plasma neutron source. 
+A point source with a Muir energy distribution \cite{openmcmuir} around 14.06MeV was used to approximate a Deuterium-Tritium (D-T) plasma neutron source. 
 The inner radius of the void region was 10m, the first wall thickness was 2.7cm and the blanket thickness was 2m.
@@
 less common isotopes of lithium, respectively.
-The TBR is defined as the ratio between tritium generation in the breeding blanket and consumption in the reactor, whose input parameters in the-expensive MC model fall
-into two classes. Continuous parameters, such as material thicknesses and
-packing fraction, describe the geometry of a given reactor configuration.
-\todo{add all the parameters here} Discrete
-categorical parameters then specify material selections, such as
-coolants, armours, and neutron multipliers. We set out to produce a fast TBR
+The TBR is defined as the ratio between tritium generation in the breeding blanket and consumption in the reactor, whose input parameters in the expensive MC model fall
+into two classes.
+The geometry of a given reactor is described by continuous parameters: the thicknesses of the firstwall and blanket; the proportions of armour, structural, and coolant materials in the firstwall proportions of multiplier, breeder, structural, and coolant materials in the blanket; and sphere-packing fractions for the blanket breeder and multiplier materials.
+Material selections for all firstwall and blanket materials listed above are specified by discrete
+categorical parameters. The enrichment ratio of $Li$ in the blanket breeder material is specified by an additional continuous parameter. We set out to produce a fast TBR
 function which takes these same input parameters and approximates the MC TBR

### 2020-06-14 paper/methodology.tex
implement more of Nikos feedback in two passes
implement more Nikos comments

@@
 surrogate training on sampled point sets. Listed in~\Tref{tbl:surrogates}, these
-implementations define nine surrogate families that are later reviewed in~\sref{sec:results}.
+implementations define 9~surrogate families that are later reviewed in~\Sref{sec:results}.
 We note that each presented algorithm defines hyperparameters that may influence its
-performance. Since their optimal values for this problem are unknown, we explore
-their assignments prior to other experiments.
+performance. Their problem-specific optimal values are searched within the scope
+of this work, in particular Experiments~1 \&~2 that are outlined
+in~\Sref{sec:experiment-methodology}.
 
@@
 		Extremely randomised trees~\cite{geurts2006extremely}	& ERT & SciKit & 7 \\
-		AdaBoosted decision trees~\cite{drucker1997improving}	& ABT & SciKit & 3 \\
+		AdaBoosted decision trees$^\text{a}$~\cite{drucker1997improving}	& ABT & SciKit & 3 \\
 		Gaussian process regression~\cite{williams2006gaussian}	& GPR & SciKit & 2 \\
@@
 		\bottomrule
-		\end{tabular}
+		\end{tabular}\\%
+		{\footnotesize $^\text{a}$Note that ABTs can be viewed as a subclass of GBTs.}
 	\end{indented}
@@
 they are invariant with respect to the selected domain and image space.
-For complexity analysis, surrogates are assessed in terms of wall
+For analysis of computational complexity, surrogates are assessed in terms of wall
 time (captured by the Python~\texttt{time} package). This is motivated by common practical use
 cases of our work, where models are trained and used as drop-in replacements for the
-expensive MC TBR model. Since training set sizes remain to be determined, all times are
-reported per a single datapoint. Even though some surrogates support acceleration
-by means of parallelisation, sequential processing of samples was ensured to
-achieve comparability between considered models. The only exception to this are
-ANNs, which require considerable amount of processing power for training on
-conventional CPU architectures. Lastly, to prevent undesirable bias by training set
-selection, all metrics are collected in the scheme of 5-fold cross-validation.
+expensive MC TBR model. All times reported (training, test, evaluation) are
+normalized by the corresponding dataset size, i.e.~correspond to ``time to
+process a single datapoint.''
+Even though some surrogates support acceleration by means of parallelisation, we
+used non-parallelized implementations. The only exception to this are ANNs,
+which require a considerable amount of processing power for training on
+conventional CPU architectures. Lastly, to prevent undesirable bias by training
+set selection, all reported metrics are obtained via 5-fold cross-validation.
+In this setting, a sample set is uniformly divided into 5 disjoint folds, each of which
+is used as a test set for models trained on the remaining 4. Having repeated the
+same experiment for each such run, the overall value of individual metrics is
+reported in terms of their mean and standard deviation over all folds.
 
@@
 		\midrule
-		Complexity metrics	& {}	& {} \\
+		Computational complexity metrics	& {}	& {} \\
 		\midrule
@@
 
-Experiments related to the decoupled approach are organised in four parts,
+Experiments related to the decoupled approach are organised in 4~parts,
 further described in this section. In summary, we aim to optimise the hyperparameters of
@@
 
-The objective of the first experiment is to simplify the regression task for
+The objective of the Experiment~1 is to simplify the regression task for
 surrogates prone to suboptimal performance in discontinuous spaces.
@@
 This is repeated for 4~distinct assignments to explore variances in behaviour.
-The second experiment conventionally measures surrogate performance on the full,
+Experiment~2 conventionally measures surrogate performance on the full,
 unrestricted feature space. In both cases, hyperparameter tuning is
@@
 
-In the third experiment, the 20~best-performing hyperparameter configurations
+In Experiment~3, the 20~best-performing hyperparameter configurations
 per each family are used to train surrogates on sets of various sizes to
-investigate their scaling properties. Following that, the fourth experiment aims
+investigate their scaling properties. Following that, Experiment~4 aims
 to produce surrogates suitable for practical use by retraining selected

### 2020-06-14 paper/results.tex
implement more Nikos comments

@@
 	\caption{\label{fig:exp1-time-vs-reg}20~best-performing surrogates per each considered family, plotted in
-		terms of complexity (as~$\overline{t}_{\text{pred.}}$) and regression
+		terms of computational complexity (as~$\overline{t}_{\text{pred.}}$) and regression
 		performance (as~$R^2$) with 3~selected discrete feature assignments.}
@@
 		{} & {} & \multicolumn{4}{c}{Regression performance} &
-		\multicolumn{3}{c}{Complexity}\\
+		\multicolumn{3}{c}{Computational complexity}\\
 		\cmidrule(lr){3-6}
@@
 ANNs trained on this model demonstrated similar performance to those on the expensive
-MC model. QASS performance was verified by training a $\text{1h3f}(256)$ ANN on
+MC model. QASS performance was verified by training an ANN on
 the sinusoidal theory for varied quantities of initial, incremental, and MCMC

### 2020-06-14 paper/conclusion.tex

@@
 surrogates for the Paramak TBR model. After reviewing
-nine surrogate model families, examining their behaviour on a constrained and
+9~surrogate model families, examining their behaviour on a constrained and
 unrestricted feature space, and studying their scaling properties, we retrained
@@
 This will allow for future deployment of QASS on the Paramak TBR model in coalition with any of the most effective identified surrogates.
+
+Relevant source code, model instances and datasets are freely
+available online as well as a more detailed technical
+report~\cite{github,finalreport}.

### 2020-06-14 paper/methodology.tex

@@
 	\item[]
-		\begin{tabular}{lrl}
+		\begin{tabularx}{\textwidth}{Xrl}
 		\toprule
@@
 		Mean absolute error	& MAE & $N^{-1}\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|$ \\
-		Standard error of regression & $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
+		Standard deviation of error & $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
 		\hat{y}^{(i)}| \right\} $ \\
@@
 			$\hat{f}(x)$})N^{-1}$ \\
-				Relative speedup & $\omega$	& $(\text{wall evaluation time of $f(x)$})
+				Relative speedup & $\omega$	& $(\text{wall evaluation$^\text{b}$ time of $f(x)$})
 				(N\overline{t}_{\text{pred.}})^{-1}$ \\
 		\bottomrule
-		\end{tabular}
+		\end{tabularx}\\%
+		{\footnotesize $^\text{b}$This corresponds to evaluation of the
+		expensive MC TBR model on all points of the test set. In surrogates, the
+		same time period is referred to as ``prediction time.''}
 	\end{indented}

### 2020-06-14 paper/results.tex

@@
 time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
-to a standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
+to a standard deviation of error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
 with respect to the MC TBR evaluation baseline. Satisfying
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig7_qasssampling.pdf}
+	\hspace*{-1.5em}\includegraphics[width=1.15\linewidth]{fig7_qasssampling.pdf}
 	\caption{\label{fig:qasssampling}Absolute training error for QASS, baseline scheme, and mixed scheme.}
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig8_qasssampling100k.pdf}
+	\hspace*{-1.5em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.pdf}
 	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and baseline scheme, with 100k initial samples.}

### 2020-06-14 paper/ucl_tbr_paper.tex
correct author name
added figure and changed reactor type
rasterize figure 6 plots (reducing the paper PDF size 10x), add rasterization script
more graphics tweaks

@@
 \usepackage{graphicx}
+\usepackage{tikz}
+\usepackage{tabularx}
 
@@
 
-\graphicspath{{./fig/}}
+\graphicspath{{./fig_final_report/}{./fig/}}
 
@@
 
-\author{P~Mánek$^{1,2}$, G~Van Goffrier$^1$, V~Gopakumar$^3$, N~Nikolau$^1$, J~Shimwell$^3$ and I~Waldmann$^1$}
+\author{P~Mánek$^{1,2}$, G~Van Goffrier$^1$, V~Gopakumar$^3$, N~Nikolaou$^1$, J~Shimwell$^3$ and I~Waldmann$^1$}
 
@@
 % TODO: revise these
-\keywords{machine learning, surrogate model, nuclear fusion, tritium breeding, adaptive sampling}
+\keywords{machine learning, surrogate model, regression, Monte Carlo simulation, tritium breeding, adaptive sampling}
 \submitto{\NF}

### 2020-06-14 paper/results.tex
implement more Nikos comments

@@
 \subsubsection{Hyperparameter Tuning}
+\label{sec:res-exp12}
 
@@
 	\includegraphics[width=0.9\linewidth]{exp1_slice2}
-	\caption{\label{fig:exp1-time-vs-reg}20~best-performing surrogates per each considered family, plotted in
+	\caption{\label{fig:exp1-time-vs-reg}Results of Experiment~1, 20~best-performing surrogates per each considered family, plotted in
 		terms of computational complexity (as~$\overline{t}_{\text{pred.}}$) and regression
-		performance (as~$R^2$) with 3~selected discrete feature assignments.}
+		performance (as~$R^2$) with 3~selected discrete feature assignments out
+		of~4.}
 \end{figure}
@@
 \subsubsection{Scaling Benchmark}
+\label{sec:res-exp3}
 
@@
 \subsubsection{Model Comparison}
+\label{sec:res-exp4}
+
 In Experiment~4, we aim to create models that yield:
@@
 	\centering
-	\hspace*{-1.5em}\includegraphics[width=1.15\linewidth]{fig7_qasssampling.pdf}
+	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig7_qasssampling.pdf}
 	\caption{\label{fig:qasssampling}Absolute training error for QASS, baseline scheme, and mixed scheme.}
@@
 	\centering
-	\hspace*{-1.5em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.pdf}
+	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.pdf}
 	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and baseline scheme, with 100k initial samples.}

### 2020-06-17 paper/results.tex
minor adjustments

--- 2020-06-14 paper/results.tex
@@
 	\caption{\label{fig:exp1-time-vs-reg}20~best-performing surrogates per each considered family, plotted in
-		terms of computational complexity (as~$\overline{t}_{\text{pred.}}$) and regression
+		terms of complexity (as~$\overline{t}_{\text{pred.}}$) and regression
 		performance (as~$R^2$) with 3~selected discrete feature assignments.}
@@
 		{} & {} & \multicolumn{4}{c}{Regression performance} &
-		\multicolumn{3}{c}{Computational complexity}\\
+		\multicolumn{3}{c}{Complexity}\\
 		\cmidrule(lr){3-6}

### 2020-06-17 paper/introduction.tex

@@
 numerous evaluations of an expensive procedure are required over the same or
-similar domains, e.g. in the parameter optimisation of a theoretical model. The
+similar domains, e.g.~in the parameter optimisation of a theoretical model. The
 term ``metamodel'' proves especially meaningful in this case, when the surrogate
@@
 
-A point source with a Muir energy distribution \cite{openmcmuir} around 14.06MeV was used to approximate a Deuterium-Tritium (D-T) plasma neutron source. 
-The inner radius of the void region was 10m, the first wall thickness was 2.7cm and the blanket thickness was 2m.
+A point source with a Muir energy distribution \cite{openmcmuir} around~\SI{14.06}{\mega\electronvolt} was used to approximate a Deuterium-Tritium (D-T) plasma neutron source. 
+The inner radius of the void region was~\SI{10}{\metre}, the first wall
+thickness was~\SI{2.7}{\centi\metre} and the blanket thickness
+was~\SI{2}{\metre}.
 
-For the remainder of Section 1, we will define the TBR and further motivate our research.
-In Section 2 we will present our methodologies for the comparison testing of a wide variety of surrogate modelling techniques, as well as a novel adaptive sampling procedure suited to this application.
-After delivering the results of these approaches in Section 3, we will give our final conclusions and recommendations for further work.
+For the remainder of Section~1, we will define the TBR and further motivate our
+research. In Section~2 we will present our methodologies for the comparison
+testing of a wide variety of surrogate modelling techniques, as well as a novel
+adaptive sampling procedure suited to this application. After delivering the
+results of these approaches in Section~3, we will give our final conclusions and recommendations for further work.
 
@@
 layers of material which partially line the reactor and produce tritium upon
-neutron bombardment, e.g. by 
+neutron bombardment, e.g.~by 
 \begin{eqnarray}
@@
 Material selections for all firstwall and blanket materials listed above are specified by discrete
-categorical parameters. The enrichment ratio of $Li$ in the blanket breeder material is specified by an additional continuous parameter. We set out to produce a fast TBR
+categorical parameters. The enrichment ratio of \isotope{Li} in the blanket breeder material is specified by an additional continuous parameter. We set out to produce a fast TBR
 function which takes these same input parameters and approximates the MC TBR

### 2020-06-17 paper/methodology.tex

@@
 
-The objective of the Experiment~1 is to simplify the regression task for
+The objective of Experiment~1 is to simplify the regression task for
 surrogates prone to suboptimal performance in discontinuous spaces.
@@
 assignment, and surrogates are trained only on the remaining continuous features.
-This is repeated for 4~distinct assignments to explore variances in behaviour.
-Experiment~2 conventionally measures surrogate performance on the full,
-unrestricted feature space. In both cases, hyperparameter tuning is
+This is repeated several times to explore variances in behaviour,
+particularly in 4~distinct assignments that are obtained by setting blanket and
+firstwall coolant materials to one
+of:~$\{\text{H\textsubscript{2}O},\isotope{He}\}$.
+Experiment~2 conventionally measures surrogate performance on the full feature
+space without any parameter restrictions. In both experiments, hyperparameter tuning is
 facilitated by Bayesian optimisation~\cite{movckus1975bayesian}. We select the
 hyperparameter configuration that produces the model that maximises $R^2$. The
-process is terminated after 1000~iterations or
-2~days, whichever condition is satisfied first.
+process is terminated after 1000~iterations or 2~days, whichever condition is satisfied first.
+The results of Experiments~1 \&~2 are depicted
+in Figures~\ref{fig:exp1-time-vs-reg} \&~\ref{fig:exp2-time-vs-reg}
+respectively, and described in~\Sref{sec:res-exp12}
 
 In Experiment~3, the 20~best-performing hyperparameter configurations
-per each family are used to train surrogates on sets of various sizes to
-investigate their scaling properties. Following that, Experiment~4 aims
+per each model family are used to train surrogates on sets of various sizes to
+investigate their scaling properties. In particular, we consider sets of
+sizes~$\{1,2,5,10,12,15,20\}$ in thousands of samples to better characterize the
+relationship of each family between sample count and the metrics of interest
+listed in~\Tref{tbl:metrics}.
+The results are shown in~\Fref{fig:scaling} and discussed in~\Sref{sec:res-exp3}
+
+Finally, Experiment~4 aims
 to produce surrogates suitable for practical use by retraining selected
 well-scaling instances on large training sets in order to satisfy the goals of this work.
+The results are displayed in~\Fref{fig:reg-performance} and
+in~\Tref{tbl:exp4-detailed-results}, and summarized in~\Sref{sec:res-exp4}
 

### 2020-06-17 paper/results.tex

--- 2020-06-14 paper/results.tex
@@
 time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
-to a standard deviation of error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
+to a standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
 with respect to the MC TBR evaluation baseline. Satisfying

### 2020-06-17 paper/ucl_tbr_paper.tex
add github reference back
remove the word 'Tokamak' from title and abstract

@@
 
-\title[Fast Regression of the Tritium Breeding Ratio in Tokamaks]{Fast Regression of the
-Tritium Breeding Ratio in Tokamak Fusion Reactors} % TODO: revise this
+\title[Fast Regression of the Tritium Breeding Ratio in Fusion Reactors]{Fast Regression of the
+Tritium Breeding Ratio in Fusion Reactors}
 
@@
 \begin{abstract}
-	% TODO: this has been taken as is from the report, revise this
 	The tritium breeding ratio (TBR) is an essential quantity for the design of
-	modern and next-generation Tokamak nuclear fusion reactors. Representing the
+	modern and next-generation D-T fueled nuclear fusion reactors. Representing the
 	ratio between tritium fuel generated in breeding blankets and fuel consumed

### 2020-06-17 paper/introduction.tex
add and reference parameter table

@@
 where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
-less common isotopes of lithium, respectively.
-The TBR is defined as the ratio between tritium generation in the breeding blanket and consumption in the reactor, whose input parameters in the expensive MC model fall
-into two classes.
-The geometry of a given reactor is described by continuous parameters: the thicknesses of the firstwall and blanket; the proportions of armour, structural, and coolant materials in the firstwall proportions of multiplier, breeder, structural, and coolant materials in the blanket; and sphere-packing fractions for the blanket breeder and multiplier materials.
-Material selections for all firstwall and blanket materials listed above are specified by discrete
-categorical parameters. The enrichment ratio of \isotope{Li} in the blanket breeder material is specified by an additional continuous parameter. We set out to produce a fast TBR
+less common isotopes of lithium, respectively. The TBR is defined as the ratio
+between tritium generation in the breeding blanket and consumption in the
+reactor, whose input parameters (exhaustively listed in~\Tref{tbl:params}) in the expensive MC model fall
+into 2~classes. While the geometry of a given reactor is described by continuous
+parameters, material selections are specified by discrete
+categorical parameters. We set out to produce a fast TBR
 function which takes these same input parameters and approximates the MC TBR
 model with the greatest achievable regression performance.
+
+\begin{table}[t]
+	\setlength\tabcolsep{2pt}
+	\caption{\label{tbl:params}Input parameters supplied to the MC TBR simulation in alphabetical
+		order. Groups of fractions marked\textsuperscript{\textdagger
+		\textdaggerdbl} are independently required to sum to 1.}
+	\begin{indented}
+	\item[]
+		\begin{tabular}{l|ll}
+		\toprule
+		{} & Parameter name & Domain\\
+		\midrule
+		\parbox[t]{2mm}{\hspace{-2pt}\multirow{12}{*}{\rotatebox[origin=c]{90}{Blanket}}}
+		   & Breeder fraction\textsuperscript{\textdagger} & $[0,1]$\\
+		   & Breeder \isotope[6]{Li} enrichment fraction & $[0,1]$\\
+		   & Breeder material & $\{\text{Li}_2\text{TiO}_3, \text{Li}_4\text{SiO}_4\}$\\
+		   & Breeder packing fraction & $[0,1]$\\
+		   & Coolant fraction\textsuperscript{\textdagger} & $[0,1]$\\
+		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
+		   & Multiplier fraction\textsuperscript{\textdagger} & $[0,1]$\\
+		   & Multiplier material & $\{\text{Be}, \text{Be}_{12}\text{Ti}\}$\\
+		   & Multiplier packing fraction & $[0,1]$\\
+		   & Structural fraction\textsuperscript{\textdagger} & $[0,1]$\\
+		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
+		   & Thickness & $[0,500]$\\
+		\midrule
+		\parbox[t]{2mm}{\hspace{-2pt}\multirow{6}{*}{\rotatebox[origin=c]{90}{First wall}}}
+		   & Armour fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
+		   & Coolant fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
+		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
+		   & Structural fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
+		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
+		   & Thickness & $[0,20]$\\
+		\bottomrule
+		\end{tabular}
+	\end{indented}
+\end{table}

### 2020-06-17 paper/methodology.tex
decrease table row spacing
add extra punctuation at the end of a sentence

@@
 	\setlength\tabcolsep{2pt}
+	\renewcommand{\arraystretch}{0.95}
 	\caption{\label{tbl:surrogates}Considered surrogate model families, their
@@
 \begin{table*}[t]
+	\renewcommand{\arraystretch}{0.95}
 	\caption{\label{tbl:metrics}Metrics recorded in experiments. In
@@
 in Figures~\ref{fig:exp1-time-vs-reg} \&~\ref{fig:exp2-time-vs-reg}
-respectively, and described in~\Sref{sec:res-exp12}
+respectively, and described in~\Sref{sec:res-exp12}.
 
@@
 listed in~\Tref{tbl:metrics}.
-The results are shown in~\Fref{fig:scaling} and discussed in~\Sref{sec:res-exp3}
+The results are shown in~\Fref{fig:scaling} and discussed
+in~\Sref{sec:res-exp3}.
 
@@
 The results are displayed in~\Fref{fig:reg-performance} and
-in~\Tref{tbl:exp4-detailed-results}, and summarized in~\Sref{sec:res-exp4}
+in~\Tref{tbl:exp4-detailed-results}, and summarized in~\Sref{sec:res-exp4}.
 

### 2020-06-17 paper/methodology.tex
add missing preposition

@@
 performance. Their problem-specific optimal values are searched within the scope
-of this work, in particular Experiments~1 \&~2 that are outlined
+of this work, in particular in Experiments~1 \&~2 that are outlined
 in~\Sref{sec:experiment-methodology}.

### 2020-06-18 paper/introduction.tex
decrease table row spacing
Minor changes

@@
 
-In this work, we develop an empirical surrogate model for the tritium breeding
-ratio (TBR) in an inertial confinement fusion (ICF) reactor. The
-expensive model which our surrogate model approximates is a Monte Carlo (MC)
-neutronics simulation, \textit{Paramak} (provided by collaborator
-Jonathan Shimwell at UKAEA) which returns a prediction of the TBR for a given configuration of a spherical ICF reactor.
+In this work, we develop an empirical
+surrogate model for the tritium breeding ratio
+(TBR) in an inertial confinement fusion (ICF)
+reactor. The expensive model which our
+surrogate model approximates is a Monte
+Carlo (MC) neutronics simulation, \textit{Paramak} which returns a prediction of the TBR for a given configuration of a spherical
+ICF reactor.
+This was achieved by containerizing (using Docker) the neutronics workflow and providing a (python flask based) API interface that returned TBR values for the provided inputs.
+The neutronics workflow used OpenMC, Fendl 3.1d nuclear data and a Python 3 environment for receiving the API inputs and for driving the model creation, simulation and results extraction.
 
@@
 
-    \caption{Diagram of the simple sphere geometry (not to scale) where the blanket is \fcolorbox{white}{green}{\rule{0pt}{6pt}\rule{6pt}{0pt}}, the firstwall is \fcolorbox{white}{blue}{\rule{0pt}{6pt}\rule{6pt}{0pt}} and the neutron point source is \fcolorbox{white}{red}{\rule{0pt}{6pt}\rule{6pt}{0pt}}.}
+    \caption{Diagram of the simple sphere geometry (not to scale) where the blanket is \fcolorbox{white}{green}{\rule{0pt}{6pt}\rule{6pt}{0pt}}, the first wall is \fcolorbox{white}{blue}{\rule{0pt}{6pt}\rule{6pt}{0pt}} and the neutron point source is \fcolorbox{white}{red}{\rule{0pt}{6pt}\rule{6pt}{0pt}}.}
     \label{fig:model_diagram}
@@
 	\setlength\tabcolsep{2pt}
+	\renewcommand{\arraystretch}{0.95}
 	\caption{\label{tbl:params}Input parameters supplied to the MC TBR simulation in alphabetical

### 2020-06-18 paper/methodology.tex
Minor changes

@@
 particularly in 4~distinct assignments that are obtained by setting blanket and
-firstwall coolant materials to one
+first wall coolant materials to one
 of:~$\{\text{H\textsubscript{2}O},\isotope{He}\}$.

### 2020-06-18 paper/conclusion.tex
minor content and typesetting adjustments

@@
 of~$\SI{0.898}{\micro\second}$, representing a relative
-speedup of $8\cdot 10^6$ with respect to the MC model. We demonstrated the possibility of achieving comparable results using only a
+speedup of $8\cdot 10^6$ with respect to Paramak. Furthermore, we demonstrated the possibility of achieving comparable results using only a
 training set of size~\num{10000}.
@@
 We further developed a novel adaptive
-sampling algorithm, QASS, capable of interfacing with any surrogate model.
+sampling algorithm, QASS, capable of interfacing with any of the presented
+surrogate models.
 Preliminary testing on a toy theory, qualitatively comparable to
-the MC TBR model, demonstrated the effectiveness of QASS and behavioural trends
+Paramak, demonstrated the effectiveness of QASS and behavioural trends
 consistent with the design of the algorithm. With~\num{100000} initial samples

### 2020-06-18 paper/introduction.tex
minor content and typesetting adjustments

@@
 
-In this work, we develop an empirical
-surrogate model for the tritium breeding ratio
-(TBR) in an inertial confinement fusion (ICF)
-reactor. The expensive model which our
-surrogate model approximates is a Monte
-Carlo (MC) neutronics simulation, \textit{Paramak} which returns a prediction of the TBR for a given configuration of a spherical
-ICF reactor.
-This was achieved by containerizing (using Docker) the neutronics workflow and providing a (python flask based) API interface that returned TBR values for the provided inputs.
-The neutronics workflow used OpenMC, Fendl 3.1d nuclear data and a Python 3 environment for receiving the API inputs and for driving the model creation, simulation and results extraction.
+In this work, we develop an empirical surrogate model for the tritium breeding
+ratio (TBR) in an inertial confinement fusion (ICF) reactor. The expensive model
+that our surrogate model approximates is a Monte Carlo (MC) neutronics
+simulation, Paramak~\cite{paramak}, which returns a prediction of the TBR for a given
+configuration of a spherical ICF reactor.
 
@@
 
-A point source with a Muir energy distribution \cite{openmcmuir} around~\SI{14.06}{\mega\electronvolt} was used to approximate a Deuterium-Tritium (D-T) plasma neutron source. 
-The inner radius of the void region was~\SI{10}{\metre}, the first wall
-thickness was~\SI{2.7}{\centi\metre} and the blanket thickness
-was~\SI{2}{\metre}.
+Paramak facitilates simulation via OpenMC neutronics workflow that is enclosed in
+a portable Docker container, which conveniently exposes an HTTP API using the
+Python~3 \texttt{flask} package. For the purposes of this work, we used this setup to
+simulate a point source with a Muir energy distribution \cite{openmcmuir}
+around~\SI{14.06}{\mega\electronvolt} to approximate a Deuterium-Tritium (D-T)
+plasma neutron source. Illustrated in~\Fref{fig:model_diagram}, the simulated
+geometry was deliberately left tunable, so that dependency of TBR on various
+parameters may be investigated.
 
-For the remainder of Section~1, we will define the TBR and further motivate our
-research. In Section~2 we will present our methodologies for the comparison
+For the remainder of~\Sref{sec:introduction}, we will define the TBR and further motivate our
+research. In~\Sref{sec:methodology} we will present our methodologies for the comparison
 testing of a wide variety of surrogate modelling techniques, as well as a novel
 adaptive sampling procedure suited to this application. After delivering the
-results of these approaches in Section~3, we will give our final conclusions and recommendations for further work.
+results of these approaches in~\Sref{sec:results}, we will give our final conclusions and
+recommendations in~\Sref{sec:conclusion}.
 
@@
 between tritium generation in the breeding blanket and consumption in the
-reactor, whose input parameters (exhaustively listed in~\Tref{tbl:params}) in the expensive MC model fall
-into 2~classes. While the geometry of a given reactor is described by continuous
-parameters, material selections are specified by discrete
-categorical parameters. We set out to produce a fast TBR
-function which takes these same input parameters and approximates the MC TBR
-model with the greatest achievable regression performance.
+reactor, whose description in Paramak is facilitated by 2~classes of parameters
+(exhaustively listed in~\Tref{tbl:params}). While the geometry of a given
+reactor is described by continuous parameters, material selections are specified
+by discrete categorical parameters.
+
+In our work, we set out to produce a fast TBR function which takes these same
+input parameters and approximates the MC model used in Paramak with the
+greatest achievable regression performance.
 
@@
 	\renewcommand{\arraystretch}{0.95}
-	\caption{\label{tbl:params}Input parameters supplied to the MC TBR simulation in alphabetical
-		order. Groups of fractions marked\textsuperscript{\textdagger
+	\caption{\label{tbl:params}Input parameters supplied to Paramak and surrogates in alphabetical order. Groups of fractions marked\textsuperscript{\textdagger
 		\textdaggerdbl} are independently required to sum to 1.}

### 2020-06-18 paper/methodology.tex
minor content and typesetting adjustments

@@
 achieve expected evaluation time lower than that of~$f(x)$. In this work, we
-consider two methods of producing viable surrogates: (1) a conventional decoupled
+consider 2~methods of producing viable surrogates: (1)~a conventional decoupled
 approach, which evaluates $f(x)$ on a set of randomly sampled points and
-trains surrogates in a supervised scheme, and (2) an adaptive approach, which attempts to
+trains surrogates in a supervised scheme, and (2)~an adaptive approach, which attempts to
 compensate for localised regression performance insuficiencies by interleaving
 multiple epochs of sampling and training.
-
-For both methods, we selected state-of-the-art regression algorithms to perform
-surrogate training on sampled point sets. Listed in~\Tref{tbl:surrogates}, these
-implementations define 9~surrogate families that are later reviewed in~\Sref{sec:results}.
-We note that each presented algorithm defines hyperparameters that may influence its
-performance. Their problem-specific optimal values are searched within the scope
-of this work, in particular in Experiments~1 \&~2 that are outlined
-in~\Sref{sec:experiment-methodology}.
 
@@
 \end{table}
-
-To compare the quality of the produced surrogates, we define a number of metrics listed
-in~\Tref{tbl:metrics}. For regression performance analysis, we include a
-selection of absolute metrics to assess the models' approximation capability and set
-practical bounds on the expected uncertainty of their predictions. In addition, we also track
-relative measures that are better-suited for comparison between this work and others as
-they are invariant with respect to the selected domain and image space.
-For analysis of computational complexity, surrogates are assessed in terms of wall
-time (captured by the Python~\texttt{time} package). This is motivated by common practical use
-cases of our work, where models are trained and used as drop-in replacements for the
-expensive MC TBR model. All times reported (training, test, evaluation) are
-normalized by the corresponding dataset size, i.e.~correspond to ``time to
-process a single datapoint.''
-Even though some surrogates support acceleration by means of parallelisation, we
-used non-parallelized implementations. The only exception to this are ANNs,
-which require a considerable amount of processing power for training on
-conventional CPU architectures. Lastly, to prevent undesirable bias by training
-set selection, all reported metrics are obtained via 5-fold cross-validation.
-In this setting, a sample set is uniformly divided into 5 disjoint folds, each of which
-is used as a test set for models trained on the remaining 4. Having repeated the
-same experiment for each such run, the overall value of individual metrics is
-reported in terms of their mean and standard deviation over all folds.
 
@@
 		\end{tabularx}\\%
-		{\footnotesize $^\text{b}$This corresponds to evaluation of the
-		expensive MC TBR model on all points of the test set. In surrogates, the
-		same time period is referred to as ``prediction time.''}
+		{\footnotesize $^\text{b}$This corresponds to evaluation of Paramak
+		 on all points of the test set. In surrogates, the equivalent
+		time period is referred to as ``prediction time.''}
 	\end{indented}
 \end{table*}
+
+For both methods, we selected state-of-the-art regression algorithms to perform
+surrogate training on sampled point sets. Listed in~\Tref{tbl:surrogates}, these
+implementations define 9~surrogate families that are later reviewed in~\Sref{sec:results}.
+We note that each presented algorithm defines hyperparameters that may influence its
+performance. Their problem-specific optimal values are searched within the scope
+of this work, in particular in Experiments~1 \&~2 that are outlined
+in~\Sref{sec:experiment-methodology}.
+
+To compare the quality of the produced surrogates, we define a number of metrics listed
+in~\Tref{tbl:metrics}. For regression performance analysis, we include a
+selection of absolute metrics to assess the models' approximation capability and set
+practical bounds on the expected uncertainty of their predictions. In addition, we also track
+relative measures that are better-suited for comparison between this work and others as
+they are invariant with respect to the selected domain and image space.
+For analysis of computational complexity, surrogates are assessed in terms of wall
+time (captured by the Python~3 \texttt{time} package). This is motivated by common practical use
+cases of our work, where models are trained and used as drop-in replacements for
+Paramak. All times reported (training, test, evaluation) are
+normalized by the corresponding dataset size, i.e.~correspond to ``time to
+process a single datapoint.''
+
+Even though some surrogates support acceleration by means of parallelisation, we
+used non-parallelized implementations. The only exception to this are ANNs,
+which require a considerable amount of processing power for training on
+conventional CPU architectures. Lastly, to prevent undesirable bias by training
+set selection, all reported metrics are obtained via 5-fold cross-validation.
+In this setting, a sample set is uniformly divided into 5 disjoint folds, each of which
+is used as a test set for models trained on the remaining 4. Having repeated the
+same experiment for each division, the overall value of individual metrics is
+reported in terms of their mean and standard deviation over all folds.
 
@@
 space without any parameter restrictions. In both experiments, hyperparameter tuning is
-facilitated by Bayesian optimisation~\cite{movckus1975bayesian}. We select the
+facilitated by Bayesian optimisation~\cite{movckus1975bayesian}, where we select the
 hyperparameter configuration that produces the model that maximises $R^2$. The
@@
 listed in~\Tref{tbl:metrics}.
-The results are shown in~\Fref{fig:scaling} and discussed
+The results of this experiment are shown in~\Fref{fig:scaling} and discussed
 in~\Sref{sec:res-exp3}.
@@
 well-scaling instances on large training sets in order to satisfy the goals of this work.
-The results are displayed in~\Fref{fig:reg-performance} and
+The results of this process are displayed in~\Fref{fig:reg-performance} and
 in~\Tref{tbl:exp4-detailed-results}, and summarized in~\Sref{sec:res-exp4}.
@@
 \subsection{Adaptive Approach}\label{sec:adaptive}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=1.2\linewidth]{fig4_qassplan.png}
-	\caption{\label{fig:qassplan}Schematic of QASS algorithm}
-\end{figure}
 
@@
 distribution, so long as the acceptance probability meets certain statistical criteria (see~\cite{Zhou2018} for a review).
+
+\begin{figure}
+	\centering
+	\hspace*{-5pt}\includegraphics[width=1.28\linewidth]{fig4_qassplan.png}
+	\caption{\label{fig:qassplan}Schematic of QASS algorithm}
+\end{figure}
 

### 2020-06-18 paper/acknowledgements.tex
reference online resources
re-enable STFC acknowledgement, add EUROfusion acknowledgement

@@
-PM was supported the STFC UCL Centre for Doctoral Training in Data Intensive
+{\footnotesize
+PM \& GVG were supported the STFC UCL Centre for Doctoral Training in Data Intensive
 Science (grant no. ST/P006736/1).
+This work has been carried out within the framework of the EUROfusion consortium and has received funding from the Euratom research and training programme 2014-2018 and 2019-2020 under grant agreement No 633053.
+The views and opinions expressed herein do not necessarily reflect those of the European Commission.
+}

### 2020-06-18 paper/results.tex
decrease table row spacing
add back 'computational' after it was mistakenly removed during a merge
minor content and typesetting adjustments
ran spell check, transformed -ise verbs to -ize as per IOP guidelines

@@
 and scale well, unlike RBFs and GPR which appear to behave superlinearly. We note that ANNs,
-which are the only family to utilise parallelisation during training, show an
+which are the only family to utilize parallelisation during training, show an
 inverse scaling characteristic. We suspect that this effect may be caused
@@
 Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
-Experiments~2 \&~3, we utilised the best-performing hyperparameters.
+Experiments~2 \&~3, we utilized the best-performing hyperparameters.
 In pursuit of goal~(a), the best approximator (Model~1,
@@
 	\setlength\tabcolsep{4pt}
+	\renewcommand{\arraystretch}{0.95}
 	\begin{indented}
@@
 	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.pdf}
-	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and baseline scheme, with 100k initial samples.}
+	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and
+	baseline scheme, with~\num{100000} initial samples.}
 \end{figure}

### 2020-06-18 paper/introduction.tex
swap this for our in introduction

@@
 
-Paramak facitilates simulation via OpenMC neutronics workflow that is enclosed in
+Paramak facilitates simulation via OpenMC neutronics workflow that is enclosed in
 a portable Docker container, which conveniently exposes an HTTP API using the
-Python~3 \texttt{flask} package. For the purposes of this work, we used this setup to
+Python~3 \texttt{flask} package. For the purposes of our work, we used this setup to
 simulate a point source with a Muir energy distribution \cite{openmcmuir}
@@
 plasma neutron source. Illustrated in~\Fref{fig:model_diagram}, the simulated
-geometry was deliberately left tunable, so that dependency of TBR on various
+geometry was deliberately left adjustable, so that dependency of TBR on various
 parameters may be investigated.
@@
 
-Instead, modern D-T reactors rely on tritium breeding blankets, specialised
+Instead, modern D-T reactors rely on tritium breeding blankets, specialized
 layers of material which partially line the reactor and produce tritium upon

### 2020-06-18 paper/introduction.tex
swap investigated for explored

@@
 geometry was deliberately left adjustable, so that dependency of TBR on various
-parameters may be investigated.
+parameters may be explored.
 

### 2020-06-19 talk_ucl_cdt_200622/adaptive.tex
add outline for CDT talk on Monday

\begin{frame}
	\frametitle{The QASS Algorithm}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Application on Toy Theory}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

% TODO Graham: add some more slides here depending on your preferences

### 2020-06-19 talk_ucl_cdt_200622/introduction.tex
add outline for CDT talk on Monday

\begin{frame}
	\frametitle{Tritium Breeding in ICF Reactors}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Problem Description}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Data Generation}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Dimensionality Reduction}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Methodology}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

### 2020-06-19 talk_ucl_cdt_200622/ucl_tbr_talk.tex
add outline for CDT talk on Monday

\documentclass{beamer}
\usetheme{ucl}
\useoutertheme[small]{ucltitlebanner}
\setbeamercolor{banner}{bg=darkblue}

%%%%%% Some other settings that can make things look nicer
%%% Set a smaller indent for description environment
\setbeamersize{description width=2em}
%%% Remove nav symbols (and shift any logo down to corner)
\setbeamertemplate{navigation symbols}{\vspace{-2ex}}

\setbeamertemplate{slide counter}[frameonly]

\title[Surrogate Modelling of the Tritium Breeding Ratio]{Surrogate Modelling of the Tritium Breeding Ratio}
\author[Petr Mánek \and Graham Van Goffrier]{Petr Mánek \and Graham Van Goffrier}
\institute[UCL]{%
	Centre for Doctoral Training in Data Intensive Science \\ %
	University College London
}
\date{22nd June 2020}

\begin{document}

\begin{frame}
  \titlepage%
\end{frame}

\section{Introduction}
\input{introduction}

\section{Decoupled Approach}
\input{decoupled}

\section{Adaptive Approach}
\input{adaptive}

\section{Conclusion}
\input{conclusion}

\end{document}

### 2020-06-19 talk_ucl_cdt_200622/introduction.tex
add methodology frame

@@
 	\frametitle{Methodology}
+			Conventional regression task -- search for a cheap surrogate $\hat{f}(x)$ that
+			minimizes dissimilarity with an expensive function $f(x)$:
+
 			\begin{itemize}
-		\item % TODO
+				\item
+					Regression performance (capability to approximate)
+					\begin{itemize}
+						\item Absolute: mean absolute error, $\sigma$ of error
+						\item Relative: $R^2$, $R^2_\text{adj.}$
 					\end{itemize}
+				\item
+					Computational complexity:
+					wall training \& prediction time / sample.
+			\end{itemize}
+
+			2 approaches for surrogate training:
+			\begin{enumerate}
+				\item
+					Decoupled -- trains models from previously sampled
+					$\mathcal{T}=\{(x,f(x))\}$.
+				\item
+					Adaptive -- repeats sampling \& model training, increases
+					sampling density in low-performance regions.
+			\end{enumerate}
 \end{frame}

### 2020-06-19 talk_ucl_cdt_200622/introduction.tex
First intro slide

@@
 \begin{frame}
-	\frametitle{Tritium Breeding in ICF Reactors}
+	\frametitle{Project Background}
+	Nuclear fusion -- the energy of the future!
+    \vspace{10pt}
 	\begin{itemize}
-		\item % TODO
+	    \item Must produce and contain an extremely hot and dense plasma
+	    \begin{itemize}
+		    \item Magnetic Confinement Fusion (MCF): toroidal circulation
+		    \item Inertial Confinement Fusion (ICF): spherical compression
 		\end{itemize}
+		\vspace{10pt}
+		\item Modern designs require enriched Hydrogen fuel of two varieties:
+	    \begin{itemize}
+		    \item Deuterium ($^2$H) -- abundant in naturally-sourced water
+		    \item Tritium ($^3$H) -- extremely rare, but can be produced \textit{in-reactor}
+		\end{itemize}
+	\end{itemize}
+	\vspace{10pt}
+	\centering{\includegraphics[height=3cm]{icf_diagram}}
 \end{frame}
@@
 
-\begin{frame}
-	\frametitle{Dimensionality Reduction}
-	\begin{itemize}
-		\item % TODO
-	\end{itemize}
-\end{frame}
+%\begin{frame}
+%	\frametitle{Dimensionality Reduction}
+%	\begin{itemize}
+%		\item % TODO
+%	\end{itemize}
+%\end{frame}
 

### 2020-06-19 talk_ucl_cdt_200622/introduction.tex
Intro slides

@@
 	\frametitle{Problem Description}
-	\begin{itemize}
-		\item % TODO
-	\end{itemize}
+	Tritium breeding blankets convert neutron radiation from the fusion plasma into a steady supply of tritium fuel.
+	\begin{center}
+	$^1_0n + ^6_3Li \rightarrow ^3_1H + ^4_2He$ \hspace{20pt} $^1_0n + ^7_3Li \rightarrow ^3_1H + ^4_2He + ^1_0n$
+	\end{center}
+	However, the tritium breeding ratio (TBR) depends on numerous geometric and material parameters.\newline
+
+	TBR evaluation \textit{Paramak} achieves very accurate results by OpenMC Monte Carlo neutronics simulation, but is computationally expensive.
+
+	\vspace{15pt}
+
+	\begin{center}
+	    \textbf{Our Challenge:}
+	\end{center}
+
+	\begin{center}
+	    \textbf{Produce a fast TBR function which strongly approximates Paramak, making use of the latest in surrogate modelling techniques.}
+	\end{center}
 \end{frame}
@@
 	\frametitle{Data Generation}
-	\begin{itemize}
-		\item % TODO
-	\end{itemize}
+	We designed the Approximate TBR Evaluator (ATE) package to generate training and test datasets from Paramak.\newline
+	 \begin{columns}[onlytextwidth,T]
+      \column{\dimexpr\linewidth-6cm-5mm}
+
+        UCL's Hypatia cluster provided the multithreading power for us to produce one million TBR samples, representing 27 days of runtime.\newline
+
+        These runs included full evaluations on the 18 continuous discrete parameters of Paramak, and "slice" evaluations with all discrete parameters frozen.
+
+      \column{6cm}
+      \vspace{0cm}
+      \includegraphics[trim={0 0 0 2mm},clip,width=6cm]{params}
+
+    \end{columns}
 \end{frame}

### 2020-06-20 talk_ucl_cdt_200622/adaptive.tex
QASS theory slide

@@
 \begin{frame}
-	\frametitle{The QASS Algorithm}
+	\frametitle{Adaptive Sampling: Theory}
+	 \begin{columns}[onlytextwidth,T]
+      \column{\dimexpr\linewidth-6cm-5mm}
+
+        Adaptive sampling takes advantage of surrogate information content \textit{during training} to reduce sample quantity.\newline
+
+        We developed a technique which is novel in the literature:
         \begin{itemize}
-		\item % TODO
+        \item Construct surrogate quality distribution by nearest- neighbour interpolation.
+        \item Draw candidate samples by quality using MCMC.
+        \item Include samples with high crowding distance.
+        \item Repeat!
         \end{itemize}
+      \column{6cm}
+      \includegraphics[width=8cm]{qassplan}
+
+    \end{columns}
 \end{frame}
@@
 \end{frame}
-
-% TODO Graham: add some more slides here depending on your preferences

### 2020-06-20 talk_ucl_cdt_200622/introduction.tex
QASS theory slide

@@
 
-        These runs included full evaluations on the 18 continuous discrete parameters of Paramak, and "slice" evaluations with all discrete parameters frozen.
+        These runs included full evaluations on the 18 continuous and discrete parameters of Paramak, and "slice" evaluations with all discrete parameters frozen.
 

### 2020-06-20 talk_ucl_cdt_200622/adaptive.tex

@@
 	\frametitle{Application on Toy Theory}
-	\begin{itemize}
-		\item % TODO
-	\end{itemize}
+	        Toy functional TBR theory with wavenumber n, and similar ANN performance to Paramak:\newline
+
+        \begin{center}
+        $\text{TBR} = \frac{1}{|C|}\sum_{i \in C} \left[1 + \sin(2\pi n (x_i - 1/2)) \right]$\newline
+        \end{center}
+    \begin{columns}[onlytextwidth,T]
+      \column{\dimexpr\linewidth-4cm-5mm}
+
+        Evaluation was performed both on the adaptively-sampled dataset and on a baseline uniform-random dataset.\newline
+
+        An baseline scheme with incremental but uniform-random samples was used as a placebo comparison.
+
+      \column{4cm}
+      \includegraphics[trim={1.3cm 1.3cm 0 0},clip,width=4cm]{sintoy}
+
+    \end{columns}
 \end{frame}
+
+\begin{frame}
+    \frametitle{Adaptive Sampling: Results}
+
+    \begin{center}
+    \includegraphics[width=12cm]{qassresult}
+    \end{center}
+
+\end{frame}

### 2020-06-20 talk_ucl_cdt_200622/introduction.tex
shorten methodology slide

@@
 				\item
-					Regression performance (capability to approximate)
-					\begin{itemize}
-						\item Absolute: mean absolute error, $\sigma$ of error
-						\item Relative: $R^2$, $R^2_\text{adj.}$
-					\end{itemize}
+					Regression performance: mean absolute error, $\sigma$ of
+					error, $R^2$, $R^2_\text{adj.}$
 				\item
@@
 					Decoupled -- trains models from previously sampled
-					$\mathcal{T}=\{(x,f(x))\}$.
+					datapoints.
 				\item

### 2020-06-20 talk_ucl_cdt_200622/introduction.tex
drop wall
use the isotope package to typeset nuclear reactions

@@
 	Tritium breeding blankets convert neutron radiation from the fusion plasma into a steady supply of tritium fuel.
-	\begin{center}
-	$^1_0n + ^6_3Li \rightarrow ^3_1H + ^4_2He$ \hspace{20pt} $^1_0n + ^7_3Li \rightarrow ^3_1H + ^4_2He + ^1_0n$
-	\end{center}
+	\begin{align*}
+		\isotope[1][0]{n} + \isotope[6][3]{Li} \rightarrow \isotope[3][1]{H} +
+		\isotope[4][2]{He}
+		\qquad\qquad
+		\isotope[1][0]{n} + \isotope[7][3]{Li} \rightarrow \isotope[3][1]{H} +
+		\isotope[4][2]{He} + \isotope[1][0]{n}
+	\end{align*}
 	However, the tritium breeding ratio (TBR) depends on numerous geometric and material parameters.\newline
@@
 					Computational complexity:
-					wall training \& prediction time / sample.
+					training \& prediction time / sample.
 			\end{itemize}

### 2020-06-21 talk_ucl_cdt_200622/adaptive.tex
improve toy theory slide typesetting

--- 2020-06-20 talk_ucl_cdt_200622/adaptive.tex
@@
 	\frametitle{Application on Toy Theory}
-	\begin{itemize}
-		\item % TODO
-	\end{itemize}
+	Toy functional TBR theory with wavenumber n, and similar ANN performance to Paramak:
+	\begin{align*}
+		\text{TBR} = \frac{1}{|C|}\sum_{i \in C} \left[1 + \sin(2\pi n (x_i - 1/2)) \right]
+	\end{align*}
+
+	\vspace{1em}
+
+	\begin{columns}[T]
+		\column{0.5\paperwidth}
+		\vspace{0.5em}
+		Evaluation performed both on the adaptively-sampled dataset and on a baseline uniform-random dataset.\newline
+
+		An baseline scheme with incremental but uniform-random samples used as a placebo comparison.
+
+		\column{0.4\paperwidth}
+		\includegraphics[width=0.4\paperwidth]{sintoy}
+
+	\end{columns}
 \end{frame}
+
+\begin{frame}
+    \frametitle{Adaptive Sampling: Results}
+
+    \begin{center}
+    \includegraphics[width=12cm]{qassresult}
+    \end{center}
+
+\end{frame}

### 2020-06-21 talk_ucl_cdt_200622/conclusion.tex
add outline for CDT talk on Monday

--- 2020-06-19 talk_ucl_cdt_200622/adaptive.tex
@@
 \begin{frame}
-	\frametitle{The QASS Algorithm}
+	\frametitle{Conclusion}
+
+	Decoupled approach:
+
 	\begin{itemize}
-		\item % TODO
+		\item
+			Tuned and compared surrogates from 9~state-of-the-art families.
+		\item
+			Found heuristic: GBTs for $<10^4$~points and
+			ANNs for $\geq10^5$~points.
+		\item
+			Fastest found surrogate predicts TBR with standard deviation of
+			error~$\num{0.033}$ in~\SI{0.898}{\micro\second}, which is~$8\cdot
+			10^6\times$~faster than Paramak.
+		\item
+			While this used 500K~datapoints, we found surrogates with
+			comparable properties with as little as 10K~datapoints.
 	\end{itemize}
+
+	\vspace{0.5em}
+
+	Adaptive approach:
+	\begin{itemize}
+		\item 
+			TODO % TODO Graham
+		\item
+			TODO % TODO Graham
+		\item
+			TODO % TODO Graham
+		\item
+			TODO % TODO Graham
+	\end{itemize}
+
+	\vspace{0.5em}
+
+	Presented methods portable $\rightarrow$ can be used as cheap
+	approximation of any simulation or black box function.
 \end{frame}
-
-\begin{frame}
-	\frametitle{Application on Toy Theory}
-	\begin{itemize}
-		\item % TODO
-	\end{itemize}
-\end{frame}
-
-% TODO Graham: add some more slides here depending on your preferences

### 2020-06-21 talk_ucl_cdt_200622/introduction.tex
use beamer block for problem description
add model list to outline slide
Call updates

@@
+%TODO: make all more concise, bullet points
+
 \begin{frame}
@@
 	\frametitle{Problem Description}
-	Tritium breeding blankets convert neutron radiation from the fusion plasma into a steady supply of tritium fuel.
+	Breeding blankets convert neutron radiation from the fusion plasma into a steady supply of tritium fuel.
 	\begin{align*}
@@
 
+	\begin{block}{Our Challenge:}
 		\begin{center}
-	    \textbf{Our Challenge:}
+			Produce a fast TBR function that strongly approximates Paramak, making use of the latest in surrogate modelling techniques.
 		\end{center}
-
-	\begin{center}
-	    \textbf{Produce a fast TBR function which strongly approximates Paramak, making use of the latest in surrogate modelling techniques.}
-	\end{center}
+	\end{block}
 \end{frame}
@@
 
+		\vspace{2em}
+
 		2 approaches for surrogate training:

### 2020-06-21 talk_ucl_cdt_200622/ucl_tbr_talk.tex
set graphics path, include UKAEA logo on the title slide
add CDT logo to the title page
add a slide on experiment 4
use title slide at section beginning
use the isotope package to typeset nuclear reactions

@@
 \documentclass{beamer}
+
+% Main theme configuration
 \usetheme{ucl}
@@
 
-%%%%%% Some other settings that can make things look nicer
-%%% Set a smaller indent for description environment
+% Packages and settings
+\usepackage{siunitx}
+\usepackage{isotope}
+\usepackage{hyperref}
+\graphicspath{{./fig_final_report/}{./fig_paper/}{./fig/}}
+
+\newcommand{\email}[1]{\href{mailto:#1}{\texttt{#1}}}
+
+% Set a smaller indent for description environment
 \setbeamersize{description width=2em}
-%%% Remove nav symbols (and shift any logo down to corner)
+
+% Remove nav symbols (and shift any logo down to corner)
 \setbeamertemplate{navigation symbols}{\vspace{-2ex}}
 
-\setbeamertemplate{slide counter}[frameonly]
+% Title slide logos
+\newlength{\titlegraphicheight}
+\setlength{\titlegraphicheight}{0.15\paperheight}
+\titlegraphic{%
+	\includegraphics[height=\titlegraphicheight]{cdt_dis_logo}%
+	\hspace{15pt}%
+	\includegraphics[height=\titlegraphicheight]{ukaea_logo}%
+}
 
+% Use title slide at section beginning
+\AtBeginSection[]{
+  \begin{frame}
+  \vfill
+  \centering
+  \begin{beamercolorbox}[sep=8pt,center]{title}
+    \usebeamerfont{title}\insertsectionhead\par%
+  \end{beamercolorbox}
+  \vfill
+  \end{frame}
+}
+
+% Metadata
 \title[Surrogate Modelling of the Tritium Breeding Ratio]{Surrogate Modelling of the Tritium Breeding Ratio}
@@
 
+% Title slide
 \begin{frame}
@@
 
-\section{Introduction}
+% Body of the presentation is organized in separate files
 \input{introduction}
@@
 
-\section{Conclusion}
 \input{conclusion}
 
+\begin{frame}
+	\vspace{2em}
+
+	{\centering
+		\begin{beamercolorbox}[sep=8pt,center]{title}
+			\usebeamerfont{title} Thank you for listening! \par%
+		\end{beamercolorbox}
+	}
+
+	\vspace{2em}
+
+	Petr Mánek \dotfill \email{petr.manek.19@ucl.ac.uk}
+
+	Graham Van~Goffrier \dotfill \email{graham.vangoffrier.19@ucl.ac.uk}
+
+	\vspace{2em}
+
+	{\footnotesize
+	Further reading:
+	\begin{itemize}
+		\item
+			\href{https://github.com/ucl-tbr-group-project/documentation/raw/pinboards-submitted/elevator_pitch/elevator_pitch.pdf}{Single page abstract (available online)}.
+		\item
+			\href{https://github.com/ucl-tbr-group-project/documentation/raw/pinboards-submitted/paper/ucl_tbr_paper.pdf}{Journal article, currently in internal pre-submission review (available online):\\
+			\textit{Fast Regression of the Tritium Breeding Ratio in Fusion
+		Reactors}}.
+		\item
+			\href{https://github.com/ucl-tbr-group-project/documentation/raw/published/final_report/tbr_final_report.pdf}{Industry group project final report (available online)}.
+		\item
+			All models, plots, training data, source code and technical documentation.
+			\url{https://github.com/ucl-tbr-group-project}
+	\end{itemize}
+	}
+
+\end{frame}
+
 \end{document}

### 2020-06-21 talk_ucl_cdt_200622/adaptive.tex
Updates to adaptive slides.

@@
 
-        We developed a technique which is novel in the literature:
-        \begin{itemize}
+        We developed a new technique:
+        \vspace{-5pt}
+        \begin{enumerate}
         \item Construct surrogate quality distribution by nearest- neighbour interpolation.
@@
         \item Repeat!
-        \end{itemize}
+        \end{enumerate}
       \column{6cm}
@@
 		\vspace{0.5em}
-		Evaluation performed both on the adaptively-sampled dataset and on a baseline uniform-random dataset.\newline
+		Two evaluation sets:
+		\begin{itemize}
+		    \item Adaptively-sampled dataset
+		    \item Independent random dataset
+		\end{itemize}
+		\vspace{15pt}
 
-		An baseline scheme with incremental but uniform-random samples used as a placebo comparison.
+		Placebo comparison -- a baseline scheme without MCMC, incremental uniform-random samples.
 
@@
     \frametitle{Adaptive Sampling: Results}
-
+    \vspace{-10pt}
     \begin{center}
@@
 
+    $60\%$ decrease in MAE for independent evaluation (dashed) \newline
+    Equivalently, $6\%$ decrease in samples needed for same accuracy
+
 \end{frame}
+
+\begin{frame}
+    \frametitle{Adaptive Sampling: Results}
+    \vspace{-10pt}
+    \begin{center}
+    \includegraphics[width=12cm]{qassresult}
+    \end{center}
+
+    $60\%$ decrease in MAE for independent evaluation (dashed lines) \newline
+    Equivalently, $6\%$ decrease in samples needed for same accuracy
+
+\end{frame}
+
+\begin{frame}
+    \frametitle{Adaptive Sampling: Results}
+    \vspace{-10pt}
+    \begin{center}
+    \includegraphics[width=12cm]{qassincr}
+    \end{center}
+
+    Fewer incremented samples can lead to better accuracy! \newline
+    But depends on initial samples, specific model -- further study needed.
+
+\end{frame}

### 2020-06-21 talk_ucl_cdt_200622/introduction.tex
Updates to adaptive slides.

@@
 	\frametitle{Problem Description}
-	Breeding blankets convert neutron radiation from the fusion plasma into a steady supply of tritium fuel.
+	Tritium breeding blankets convert neutron radiation to tritium fuel:
 	\begin{align*}
@@
 	\end{align*}
-	However, the tritium breeding ratio (TBR) depends on numerous geometric and material parameters.\newline
+	Tritium breeding ratio (TBR) = fuel bred / fuel consumed
 
-	TBR evaluation \textit{Paramak} achieves very accurate results by OpenMC Monte Carlo neutronics simulation, but is computationally expensive.
+	\begin{itemize}
+	    \item Depends on numerous geometric and material parameters.
+	    \item Evaluated precisely by OpenMC neutronics simulation \textit{Paramak}, but is computationally expensive. 
+	\end{itemize}
 
@@
 	 \begin{columns}[onlytextwidth,T]
-      \column{\dimexpr\linewidth-6cm-5mm}
+      \column{\dimexpr\linewidth-7cm-5mm}
 
-        UCL's Hypatia cluster provided the multithreading power for us to produce one million TBR samples, representing 27 days of runtime.\newline
+        Deployed Paramak on UCL's Hypatia cluster:
+        \begin{itemize}
+            \item Generated 1M samples
+            \item 27 days of runtime
+        \end{itemize}
 
-        These runs included full evaluations on the 18 continuous and discrete parameters of Paramak, and "slice" evaluations with all discrete parameters frozen.
+        	\vspace{10pt}
 
-      \column{6cm}
-      \vspace{0cm}
-      \includegraphics[trim={0 0 0 2mm},clip,width=6cm]{params}
+        Two classes of runs:
+        \begin{itemize}
+            \item Full -- 18 discrete and continuous parameters
+            \item Slice -- 11 continuous parameters
+        \end{itemize}
+
+      \column{7cm}
+      \vspace{-0.5cm}
+      \includegraphics[trim={0 0 0 2mm},clip,width=7cm]{params}
 

### 2020-06-21 talk_ucl_cdt_200622/introduction.tex
remove dot from methodology slide
Data generation slide updated.

@@
 	    \begin{itemize}
-		    \item Deuterium ($^2$H) -- abundant in naturally-sourced water
-		    \item Tritium ($^3$H) -- extremely rare, but can be produced \textit{in-reactor}
+		    \item Deuterium ($^2$H) -- abundant in naturally-sourced water.
+		    \item Tritium ($^3$H) -- extremely rare, but can be produced \textit{in-reactor}.
 		\end{itemize}
@@
 	\frametitle{Data Generation}
-	We designed the Approximate TBR Evaluator (ATE) package to generate training and test datasets from Paramak.\newline
+	We produced training and test datasets by uniform random sampling over the 7 discrete and 11 continuous parameters of Paramak.\newline
 	 \begin{columns}[onlytextwidth,T]
@@
 
-        Deployed Paramak on UCL's Hypatia cluster:
+        Paramak was deployed on UCL's Hypatia cluster:
         \begin{itemize}
-            \item Generated 1M samples
-            \item 27 days of runtime
+            \item Generated 1M samples.
+            \item 27 days of runtime.
         \end{itemize}
@@
         \begin{itemize}
-            \item Full -- 18 discrete and continuous parameters
-            \item Slice -- 11 continuous parameters
+            \item All parameters free.
+            \item Discrete fixed, continuous free.
         \end{itemize}

### 2020-06-21 talk_ucl_cdt_200622/adaptive.tex
removed duplicate slide
Data generation slide updated.
Adaptive update

@@
 
-        Adaptive sampling takes advantage of surrogate information content \textit{during training} to reduce sample quantity.\newline
+        How can we take advantage of surrogate information content \textit{during training} to reduce sample quantity?\newline
 
@@
 \end{frame}
-
-\begin{frame}
-    \frametitle{Adaptive Sampling: Results}
-    \vspace{-10pt}
-    \begin{center}
-    \includegraphics[width=12cm]{qassresult}
-    \end{center}
-
-    $60\%$ decrease in MAE for independent evaluation (dashed lines) \newline
-    Equivalently, $6\%$ decrease in samples needed for same accuracy
-
-\end{frame}
+1
 

### 2020-06-21 talk_ucl_cdt_200622/conclusion.tex
Updates to adaptive slides.
replace points and samples in the conclusion slide

@@
 		\item
-			Found heuristic: GBTs for $<10^4$~points and
-			ANNs for $\geq10^5$~points.
+			Found heuristic: GBTs for $<10^4$~samples,
+			ANNs for $\geq10^5$~samples.
 		\item
@@
 		\item
-			While this used 500K~datapoints, we found surrogates with
-			comparable properties with as little as 10K~datapoints.
+			While this used 500K~samples, we found surrogates with
+			comparable properties with as little as 10K~samples.
 	\end{itemize}
@@
 
-	Adaptive approach:
+	Adaptive approach (on toy theory):
 	\begin{itemize}
 	    \item
-			TODO % TODO Graham
+	        New theoretical approach developed based on MCMC.
 		\item 
-			TODO % TODO Graham
+			$60\%$ decrease in evaluation MAE demonstrated.
 		\item
-			TODO % TODO Graham
+			$6\%$ decrease in expensive TBR samples needed.
 		\item
-			TODO % TODO Graham
+			Strong potential for further reduction through hyperparameter optimization.
 	\end{itemize}

### 2020-06-21 talk_ucl_cdt_200622/adaptive.tex
Conclusion updates

@@
 
-        How can we take advantage of surrogate information content \textit{during training} to reduce sample quantity?\newline
+        How can we take advantage of surrogate information content \textit{during training} to reduce sample quantity? \newline
 
@@
         \item Draw candidate samples by quality using MCMC.
-        \item Include samples with high crowding distance.
+        \item Include samples with greatest separation from neighbours.
         \item Repeat!
@@
 	\frametitle{Application on Toy Theory}
-	Toy functional TBR theory with wavenumber n, and similar ANN performance to Paramak:
+	Toy functional TBR theory with wavenumber n, and qualitatively comparable ANN performance to Paramak:
 	\begin{align*}
@@
 \end{frame}
-1
 

### 2020-06-22 talk_ucl_cdt_200622/introduction.tex
update table and typesetting in the data generation slide

@@
 	\frametitle{Data Generation}
-	We produced training and test datasets by uniform random sampling over the 7 discrete and 11 continuous parameters of Paramak.\newline
-	 \begin{columns}[onlytextwidth,T]
-      \column{\dimexpr\linewidth-7cm-5mm}
+	We produced training and test datasets by uniform random sampling over the 7
+	discrete and 11 continuous parameters of Paramak.
+
+	\begin{columns}[T]
+		\column{0.34\textwidth}
+
+		\vspace{5pt}
 
@@
 
-        	\vspace{10pt}
+		\vspace{5pt}
 
-        Two classes of runs:
+		2~classes of runs:
 		\begin{itemize}
@@
 
-      \column{7cm}
-      \vspace{-0.5cm}
-      \includegraphics[trim={0 0 0 2mm},clip,width=7cm]{params}
+		\vspace{5pt}
+
+		{\footnotesize
+		Groups of fractions marked\textsuperscript{\textdagger\textdaggerdbl} are required to sum to 1.
+		}
+
+		\column{0.62\textwidth}
+		\vspace{5pt}
+
+		{\fontsize{8pt}{8pt}\selectfont
+		\setlength\tabcolsep{3pt}
+		\begin{tabular}{l|ll}
+		\toprule
+		{} & Parameter name & Domain\\
+		\midrule
+		\parbox[t]{2mm}{\hspace{-2pt}\multirow{12}{*}{\rotatebox[origin=c]{90}{Blanket}}}
+		   & Breeder fraction\textsuperscript{\textdagger} & $[0,1]$\\
+		   & Breeder \isotope[6]{Li} enrichment fraction & $[0,1]$\\
+		   & Breeder material & $\{\text{Li}_2\text{TiO}_3, \text{Li}_4\text{SiO}_4\}$\\
+		   & Breeder packing fraction & $[0,1]$\\
+		   & Coolant fraction\textsuperscript{\textdagger} & $[0,1]$\\
+		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
+		   & Multiplier fraction\textsuperscript{\textdagger} & $[0,1]$\\
+		   & Multiplier material & $\{\text{Be}, \text{Be}_{12}\text{Ti}\}$\\
+		   & Multiplier packing fraction & $[0,1]$\\
+		   & Structural fraction\textsuperscript{\textdagger} & $[0,1]$\\
+		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
+		   & Thickness & $[0,500]$\\
+		\midrule
+		\parbox[t]{2mm}{\hspace{-2pt}\multirow{6}{*}{\rotatebox[origin=c]{90}{First wall}}}
+		   & Armour fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
+		   & Coolant fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
+		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
+		   & Structural fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
+		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
+		   & Thickness & $[0,20]$\\
+		\bottomrule
+		\end{tabular}
+		}
 
@@
 				Computational complexity:
-				training \& prediction time / sample.
+				training \& prediction time / sample
 		\end{itemize}

### 2020-06-22 talk_ucl_cdt_200622/adaptive.tex
update typesetting in the toy theory slide
Adaptive phrasing changes, validation set

@@
 
+	\vspace{-1em}
+	{\footnotesize
+		\hfill(where $C$~enumerates all continuous variables)
+	}
+
 	\vspace{1em}
@@
 		\vspace{0.5em}
-		Two evaluation sets:
+		Evaluation set:
 		\begin{itemize}
-		    \item Adaptively-sampled dataset
-		    \item Independent random dataset
+		    \item Adaptive samples
+		    \item Generated during runtime
+		\end{itemize}
+		Validation set:
+		\begin{itemize}
+		    \item Uniform random samples
+		    \item Generated independently
 		\end{itemize}
@@
 
-		Placebo comparison -- a baseline scheme without MCMC, incremental uniform-random samples.
+		Placebo comparison -- incremental uniform-random samples, no MCMC.
 
 		\column{0.4\paperwidth}
-		\includegraphics[width=0.4\paperwidth]{sintoy}
+		\hspace{-20pt}\includegraphics[width=0.45\paperwidth]{sintoy}
 
@@
 
-    $60\%$ decrease in MAE for independent evaluation (dashed) \newline
+    $60\%$ decrease in MAE for validation set (dashed) \newline
     Equivalently, $6\%$ decrease in samples needed for same accuracy

### 2020-06-28 paper/acknowledgements.tex
add RCUK grant acknowledgement
add Nikos acknowledgement
add UTEF acknowledgement

@@
 Science (grant no. ST/P006736/1).
+
+This project was supported by the EU Horizon 2020 research \& innovation
+programme [grant No 758892, ExoAI]. N.~Nikolaou acknowledges the support of the NVIDIA Corporation’s GPU grant.
+
 This work has been carried out within the framework of the EUROfusion consortium and has received funding from the Euratom research and training programme 2014-2018 and 2019-2020 under grant agreement No 633053.
 The views and opinions expressed herein do not necessarily reflect those of the European Commission.
+
+This work has been partly funded by the Institutional support for the
+development of a research organization (DKRVO, Czech Republic).
+
+This work has also been part-funded by the RCUK Energy Programme (grant number EP/I501045/1).
 }

### 2020-10-05 talk_ucl_cdt_201008/conclusion.tex
clone June's talk in preparation for October 8

\begin{frame}
	\frametitle{Conclusion}

	Decoupled approach:

	\begin{itemize}
		\item
			Tuned and compared surrogates from \alert{9~state-of-the-art
			families}.
		\item
			Found heuristic: \alert{GBTs} for $<10^4$~samples,
			\alert{ANNs} for $\geq10^5$~samples.
		\item
			Fastest found surrogate predicts TBR with standard deviation of
			error~$\num{0.033}$ in~\SI{0.898}{\micro\second}, which is~\alert{$8\cdot
			10^6\times$~faster} than Paramak.
		\item
			While this used 500K~samples, we found surrogates with
			comparable properties with \alert{as little as 10K~samples}.
	\end{itemize}

	\vspace{0.5em}

	Adaptive approach (on toy theory):
	\begin{itemize}
	    \item
	        New theoretical approach QASS developed, based on MCMC.
		\item 
			\alert{$60\%$ decrease} in evaluation MAE demonstrated.
		\item
			\alert{$6\%$ decrease} in expensive TBR samples needed.
		\item
			Strong potential for further reduction via hyperparameter tuning.
	\end{itemize}

	\vspace{0.5em}

	All presented methods \alert{portable} $\longrightarrow$ can be used as cheap
	approximation of any simulation or black box function.
\end{frame}

### 2020-10-07 talk_ucl_cdt_201008/conclusion.tex
simplify typesetting 2nd half of the presentation

@@
 
-	Decoupled approach:
-
+	\begin{block}{Decoupled Approach}
 		\begin{itemize}
 			\item
-			Tuned and compared surrogates from \alert{9~state-of-the-art
-			families}.
-		\item
-			Found heuristic: \alert{GBTs} for $<10^4$~samples,
+				Heuristic: \alert{GBTs} for $<10^4$~samples,
 				\alert{ANNs} for $\geq10^5$~samples.
 			\item
-			Fastest found surrogate predicts TBR with standard deviation of
-			error~$\num{0.033}$ in~\SI{0.898}{\micro\second}, which is~\alert{$8\cdot
+				Fastest found surrogate evaluates TBR in~\SI{0.898}{\micro\second}
+				with error~$\num{0.033}$. This is roughly~\alert{$8\cdot
 				10^6\times$~faster} than Paramak.
 			\item
-			While this used 500K~samples, we found surrogates with
-			comparable properties with \alert{as little as 10K~samples}.
+				Found surrogates with comparable properties with
+				\alert{$\approx$10K~samples}.
 		\end{itemize}
+	\end{block}
 
-	\vspace{0.5em}
-
-	Adaptive approach (on toy theory):
+	\begin{block}{Adaptive Approach}
 		\begin{itemize}
@@
 				\alert{$6\%$ decrease} in expensive TBR samples needed.
+		\end{itemize}
+	\end{block}
+
+	\begin{itemize}
 		\item 
-			Strong potential for further reduction via hyperparameter tuning.
+			All methods \alert{portable} $\rightarrow$ cheap approximation of any simulation.
+		\item
+			Article in IOP \alert{Journal of Nuclear Fusion} (pending).
+		\item
+			Included as a benchmark in the \alert{SciML Collaboration}.
 	\end{itemize}
 
-	\vspace{0.5em}
-
-	All presented methods \alert{portable} $\longrightarrow$ can be used as cheap
-	approximation of any simulation or black box function.
 \end{frame}

### 2020-10-07 talk_ucl_cdt_201008/adaptive.tex
rework background slide, add neat illustration
add slide numbers

--- 2020-06-22 talk_ucl_cdt_200622/adaptive.tex
@@
 
-        How can we take advantage of surrogate information content \textit{during training} to reduce sample quantity? \newline
+        How to take advantage of surrogate information content \textit{during training} to reduce sample quantity? \newline
 
-        We developed a new technique:
-        \vspace{-5pt}
+		We developed \alert{a new technique:}
+        \vspace{-1em}
         \begin{enumerate}
@@
 	\frametitle{Application on Toy Theory}
-	Toy functional TBR theory with wavenumber n, and qualitatively comparable ANN performance to Paramak:
+	Toy functional TBR theory with wavenumber $n$, and qualitatively comparable ANN performance to Paramak:
 	\begin{align*}
-		\text{TBR} = \frac{1}{|C|}\sum_{i \in C} \left[1 + \sin(2\pi n (x_i - 1/2)) \right]
+		\text{TBR}_\text{toy} = \frac{1}{|C|}\sum_{i \in C} \left[1 + \sin(2\pi n (x_i - 1/2)) \right]
 	\end{align*}
@@
 		\column{0.5\paperwidth}
-		\vspace{0.5em}
+		\vspace{-0.5em}
 		Evaluation set:
@@
 		\end{itemize}
+		\vspace{0.5em}
 		Validation set:
@@
     \frametitle{Adaptive Sampling: Results}
-    \vspace{-10pt}
+    \vspace{-20pt}
     \begin{center}
@@
 
-    $60\%$ decrease in MAE for validation set (dashed) \newline
-    Equivalently, $6\%$ decrease in samples needed for same accuracy
+	\alert{$60\%$ decrease} in MAE for validation set (dashed) \newline
+	Equivalently, \alert{$6\%$ decrease} in samples needed for same accuracy
 

### 2020-11-18 paper/conclusion.tex
Updated following UKAEA feedback, largely Paramak discussion

@@
 in surrogate error compared to a baseline random sampling scheme.
-Further optimisation over the hyperparameter space has strong potential to increase this performance, in particular by decreasing the required quantity of initial samples.
+Further optimisation over the hyperparameter space has strong potential to increase this performance by further reduction of necessary expensive samples, in particular by decreasing the required quantity of initial samples.
 This will allow for future deployment of QASS on the Paramak TBR model in coalition with any of the most effective identified surrogates.

### 2020-11-18 paper/introduction.tex
do not break paragraph after nuclear equations
Updated following UKAEA feedback, largely Paramak discussion

@@
 configuration of a spherical ICF reactor.
+Although more expensive 3D parametric models exist, we chose the Paramak simulation for its preferable speed in dataset generation in order to most fully demonstrate our methods.
 
@@
 Python~3 \texttt{flask} package. For the purposes of our work, we used this setup to
-simulate a point source with a Muir energy distribution \cite{openmcmuir}
+simulate a point source with a Muir energy distribution \cite{openmcmuir}\footnotemark[1]
 around~\SI{14.06}{\mega\electronvolt} to approximate a Deuterium-Tritium (D-T)
@@
 parameters may be explored.
+Nuclear data for simulation was extracted from the following sources, in order of preference: Fendl 3.1d \cite{fendl31d}; Jeff 3.3 \cite{jeff33}; and ENDF 7.1 \cite{2011ii}.
 
@@
 recommendations in~\Sref{sec:conclusion}.
+
+\footnotetext[1]{A bug in the Muir distribution involving erronous normal sampling was recently uncovered (see https://github.com/openmc-dev/openmc/pull/1670), but is disregarded in the present approach-focused work.}
 
@@
 	\isotope[3][1]{T} + \hspace{3pt} \isotope[4][2]{He} + \hspace{3pt} \isotope[1][0]{n}
-\end{eqnarray}
-
+\end{eqnarray}%
 where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
@@
 by discrete categorical parameters.
+For all parameters, we have attempted to cover the full theoretical range of values even where those values are practically infeasible with current technology (e.g.
+packing fractions close to 1).
+Simulating broadly around typical values of parameters is necessary to construct the most accurate model of the typical range, and also aids in demonstrating the robustness of constructed models.
 
@@
 input parameters and approximates the MC model used in Paramak with the
-greatest achievable regression performance.
+greatest achievable regression performance, while also minimising the required quantity of expensive samples.
 

### 2020-12-01 paper/methodology.tex
add explicit explanation of baseline for speed-ups

@@
-Labeling the expensive MC TBR model $f(x)$, a surrogate is a mapping
-$\hat{f}(x)$ such that $f(x)$ and $\hat{f}(x)$ minimise a selected dissimilarity
+Labeling the expensive Paramak model $f(x)$, a surrogate is a mapping
+$\hat{f}(x)$ such that $f(x)$ and $\hat{f}(x)$ minimize a selected dissimilarity
 metric. In order to be considered \textit{viable}, $\hat{f}(x)$ is required to
@@
 trains surrogates in a supervised scheme, and (2)~an adaptive approach, which attempts to
-compensate for localised regression performance insuficiencies by interleaving
+compensate for localized regression performance insufficiency's by interleaving
 multiple epochs of sampling and training.
@@
 \begin{table}[t]
-	\setlength\tabcolsep{2pt}
+	\setlength\tabcolsep{1pt}
 	\renewcommand{\arraystretch}{0.95}
@@
 		Gradient boosted trees~\cite{friedman2001greedy,friedman1999stochastic,hastie2009elements}	& GBT & SciKit & 11 \\
-		Extremely randomised trees~\cite{geurts2006extremely}	& ERT & SciKit & 7 \\
+		Extremely randomized trees~\cite{geurts2006extremely}	& ERT & SciKit & 7 \\
 		AdaBoosted decision trees$^\text{a}$~\cite{drucker1997improving}	& ABT & SciKit & 3 \\
@@
 size $N$, values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
-denote images of the $i$th testing sample in the MC TBR model and the surrogate
+denote images of the $i$th testing sample in Paramak and the surrogate
 respectively. The mean $\overline{y}=N^{-1}\sum_{i=1}^N y^{(i)}$ and $P$ is the
@@
 
-Experiments related to the decoupled approach are organised in 4~parts,
-further described in this section. In summary, we aim to optimise the hyperparameters of
+Experiments related to the decoupled approach are organized in 4~parts,
+further described in this section. In summary, we aim to optimize the hyperparameters of
 each surrogate family separately and later use the best found results to compare surrogate
@@
 facilitated by Bayesian optimisation~\cite{movckus1975bayesian}, where we select the
-hyperparameter configuration that produces the model that maximises $R^2$. The
+hyperparameter configuration that produces the model that maximizes $R^2$. The
 process is terminated after 1000~iterations or 2~days, whichever condition is satisfied first.
@@
 
-Adaptive sampling techniques appear frequently in the literature and have been specialised for surrogate modelling, where precision is implicitly limited by the quantity of training samples which are available from the expensive model.
+Adaptive sampling techniques appear frequently in the literature and have been
+specialized for surrogate modelling, where precision is implicitly limited by the quantity of training samples which are available from the expensive model.
 Garud's~\cite{Garud2016} ``Smart Sampling Algorithm'' achieved notable success by incorporating surrogate quality and
 crowding distance scoring to identify optimal new samples, but was only tested
-on a single-parameter domain. We theorised that a nondeterministic sample
+on a single-parameter domain. We theorized that a nondeterministic sample
 generation approach, built around Markov Chain Monte Carlo methods (MCMC), would
@@
 We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, \Fref{fig:qassplan}) to iteratively increment the training/test set with sample
-points which maximise surrogate error and minimise a crowding distance metric
+points which maximize surrogate error and minimize a crowding distance metric
 (CDM)~\cite{Solonen2012} in feature space.

### 2020-12-01 paper/results.tex
Updated following UKAEA feedback, largely Paramak discussion
add explicit explanation of baseline for speed-ups

@@
 \label{sec:res-exp4}
-
+{
+\sisetup{round-mode=places,round-precision=3,detect-weight=true,detect-family=true}
 In Experiment~4, we aim to create models that yield:
@@
 To this end, we trained 8~surrogates that are presented in~\Fref{fig:reg-performance}
-and~\Tref{tbl:exp4-detailed-results}.
+and~\Tref{tbl:exp4-detailed-results}. We compared these
+surrogates with the baseline represented by Paramak per-sample evaluation time $\overline{t}_{\text{eval.}}=\num{7.777049573054314} \pm
+\num{2.8103592103930337} \text{ s}$, which was measured earlier on a set of~\num{500000} samples.
+}
+
 Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
@@
 to a standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
-with respect to the MC TBR evaluation baseline. Satisfying
+with respect to Paramak. Satisfying
 goal~(b), the fastest model (Model~2, ANN) achieved~$R^2=\num{0.985}$,
@@
 		\num{2.8103592103930337} \text{ s}$
-		measured in the MC TBR model over~\num{500000} samples.
+		measured in Paramak over~\num{500000} samples.
 	The best-performing method(s) under each are highlighted in bold.}
@@
 	\centering
-	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig7_qasssampling.pdf}
+	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig7_qasssampling.png}
 	\caption{\label{fig:qasssampling}Absolute training error for QASS, baseline scheme, and mixed scheme.}
@@
 	\centering
-	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.pdf}
+	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.png}
 	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and

### 2020-12-02 paper/ucl_tbr_paper.tex
minor content and typesetting adjustments
increase size of captions in fig. 6 plots

@@
 \usepackage{booktabs}
+\usepackage{xcolor}
 \usepackage{multirow}
@@
 \newcommand{\DDO}{D\textsubscript{2}O}
+\definecolor{datacolor}{RGB}{72,36,117}
 
 \graphicspath{{./fig_final_report/}{./fig/}}
+
+\newcommand{\surrogateplot}[6]{
+\begin{tikzpicture}
+	\node[anchor=south west,inner sep=0] at (0,0){\includegraphics[width=\textwidth]{#1}};
+	\draw[black,fill=white,line
+		width=0.05mm,align=right,font=\fontsize{5.5}{6.5}\selectfont]
+		(0.42,#6) rectangle
+		(2.45,2.5) node[pos=.5] {
+			\\[0.1ex]
+			$\mathrm{MAE} = \num{#2}$\\
+			$S = \num{#3}$\\
+			$R^2 = \num{#4}$\\
+			$R^2_{\text{adj.}} = \num{#5}$
+		};
+	\draw[black,fill=white,line
+		width=0.05mm,align=left,font=\fontsize{5.5}{7.5}\selectfont]
+		(2.02,1.43) rectangle
+		(4.05,0.38) node[pos=.5] {
+			{\color{red}
+			\leavevmode\leaders\hrule height 0.7ex
+			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
+			\hskip1pt
+			\leavevmode\leaders\hrule height 0.7ex
+			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
+			} Ideal model\\
+			{\leavevmode\leaders\hrule height 0.7ex
+			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
+			\hskip1pt
+			\leavevmode\leaders\hrule height 0.7ex
+			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
+			} Trained model\\
+			\hskip3pt\raisebox{0.25ex}{\scalebox{0.75}{\color{datacolor}\textbullet}}\hskip4pt Data
+		};
+\end{tikzpicture}}
 
@@
 
-% TODO: revise these
-\keywords{machine learning, surrogate model, regression, Monte Carlo simulation, tritium breeding, adaptive sampling}
+\keywords{machine learning, surrogate model, regression, fast approximation,
+Monte Carlo simulation, OpenMC, Paramak, tritium breeding, adaptive sampling}
 \submitto{\NF}
@@
 \section{Methodology}
-\label{sec:methodoglogy}
+\label{sec:methodology}
 \input{methodology}

### 2020-12-02 paper/results.tex
increase size of captions in fig. 6 plots
increase size of fig. 3-5

@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{exp1_slice0}
-	\includegraphics[width=0.9\linewidth]{exp1_slice1}
-	\includegraphics[width=0.9\linewidth]{exp1_slice2}
-	\caption{\label{fig:exp1-time-vs-reg}Results of Experiment~1, 20~best-performing surrogates per each considered family, plotted in
-		terms of computational complexity (as~$\overline{t}_{\text{pred.}}$) and regression
-		performance (as~$R^2$) with 3~selected discrete feature assignments out
+	\hspace*{-0.1\columnwidth}
+	\includegraphics[trim=10pt 50pt 10pt 10pt,clip,width=1.1\linewidth]{exp1_slice0}
+
+	\vfill
+
+	\hspace*{-0.1\columnwidth}
+	\includegraphics[trim=10pt 50pt 10pt 10pt,clip,width=1.1\linewidth]{exp1_slice1}
+
+	\vfill
+
+	\hspace*{-0.1\columnwidth}
+	\includegraphics[trim=10pt 15pt 10pt 10pt,clip,width=1.1\linewidth]{exp1_slice2}
+
+	\caption{\label{fig:exp1-time-vs-reg}Experiment~1 results. 20~best surrogates per each considered family, plotted in
+		terms of~$\overline{t}_{\text{pred.}}$ and~$R^2$ with 3~selected slices out
 		of~4.}
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{exp2_time_vs_reg}
-	\caption{\label{fig:exp2-time-vs-reg}Results of Experiment~2, plotted analogously
+
+	\hspace*{-0.1\columnwidth}
+	\includegraphics[trim=10pt 15pt 10pt 10pt,clip,width=1.1\linewidth]{exp2_time_vs_reg_edited}
+	\caption{\label{fig:exp2-time-vs-reg}Experiment~2 results, plotted analogously
 	to~\Fref{fig:exp1-time-vs-reg}.}
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{scaling_metric_r2}
-	\includegraphics[width=0.9\linewidth]{scaling_time_train}
-	\includegraphics[width=0.9\linewidth]{scaling_time_pred}
-	\caption{Results of the scaling benchmark displayed as a function of
-	training set size. From top to bottom, regression performance (as $R^2$),
-	mean training time and mean prediction time.}
+	\hspace*{-0.1\columnwidth}
+	\includegraphics[trim=10pt 50pt 10pt 10pt,clip,width=1.1\columnwidth]{scaling_metric_r2}
+
+	\vfill
+
+	\hspace*{-0.1\columnwidth}
+	\includegraphics[trim=5pt 50pt 10pt 10pt,clip,width=1.1\columnwidth]{scaling_time_train}
+
+	\vfill
+
+	\hspace*{-0.1\columnwidth}
+	\includegraphics[trim=0pt 15pt 10pt 15pt,clip,width=1.1\columnwidth]{scaling_time_pred}
+	\caption{Experiment~3 results, displayed as a function of $N_0$. From top to bottom, $R^2$,
+	$\overline{t}_{\text{trn.}}$, $\overline{t}_{\text{pred.}}$.}
 	\label{fig:scaling}
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model6_rasterized}
+		\surrogateplot{exp4_model6_rasterized}{0.008585}{0.011885}{0.998152}{0.998152}{3.55}
 	\end{minipage}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model7_rasterized}
+		\surrogateplot{exp4_model7_rasterized}{0.024634}{0.031499}{0.986202}{0.986198}{3.58}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model1_rasterized}
+		\surrogateplot{exp4_model1_rasterized}{0.057670}{0.058917}{0.942217}{0.942178}{3.58}
 	\end{minipage}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model3_rasterized}
+		\surrogateplot{exp4_model3_rasterized}{0.070818}{0.066410}{0.920779}{0.919694}{3.58}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model4_rasterized}
+		\surrogateplot{exp4_model4_rasterized}{0.051033}{0.055558}{0.951106}{0.951073}{3.58}
 	\end{minipage}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model5_rasterized}
+		\surrogateplot{exp4_model5_rasterized}{0.067856}{0.071096}{0.918668}{0.918393}{3.58}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model2_rasterized}
+		\surrogateplot{exp4_model2_rasterized}{0.067836}{0.074189}{0.913457}{0.913223}{3.58}
 	\end{minipage}\hfill%
@@
 		\centering
-		\includegraphics[width=\linewidth]{exp4_model8_rasterized}
+		\surrogateplot{exp4_model8_rasterized}{0.061678}{0.091997}{0.894604}{0.894533}{3.58}
 	\end{minipage}

### 2020-12-02 paper/results.tex
more typesetting improvements in fig. 6

@@
 	\centering
-	\begin{minipage}{0.5\linewidth}
+
+	\hspace*{-0.06\linewidth}
+	\begin{minipage}{0.53\linewidth}
 		\centering
-		\surrogateplot{exp4_model6_rasterized}{0.008585}{0.011885}{0.998152}{0.998152}{3.55}
-	\end{minipage}\hfill%
-	\begin{minipage}{0.5\linewidth}
+		\surrogateplot{exp4_model6_rasterized}{0.008585}{0.011885}{0.998152}{0.998152}{3.79}
+	\end{minipage}%
+	\begin{minipage}{0.53\linewidth}
 		\centering
-		\surrogateplot{exp4_model7_rasterized}{0.024634}{0.031499}{0.986202}{0.986198}{3.58}
+		\surrogateplot{exp4_model7_rasterized}{0.024634}{0.031499}{0.986202}{0.986198}{3.82}
 	\end{minipage}
 
-	\begin{minipage}{0.5\linewidth}
+	\hspace*{-0.06\linewidth}
+	\begin{minipage}{0.53\linewidth}
 		\centering
-		\surrogateplot{exp4_model1_rasterized}{0.057670}{0.058917}{0.942217}{0.942178}{3.58}
-	\end{minipage}\hfill%
-	\begin{minipage}{0.5\linewidth}
+		\surrogateplot{exp4_model1_rasterized}{0.057670}{0.058917}{0.942217}{0.942178}{3.82}
+	\end{minipage}%
+	\begin{minipage}{0.53\linewidth}
 		\centering
-		\surrogateplot{exp4_model3_rasterized}{0.070818}{0.066410}{0.920779}{0.919694}{3.58}
+		\surrogateplot{exp4_model3_rasterized}{0.070818}{0.066410}{0.920779}{0.919694}{3.82}
 	\end{minipage}
 
-	\begin{minipage}{0.5\linewidth}
+	\hspace*{-0.06\linewidth}
+	\begin{minipage}{0.53\linewidth}
 		\centering
-		\surrogateplot{exp4_model4_rasterized}{0.051033}{0.055558}{0.951106}{0.951073}{3.58}
-	\end{minipage}\hfill%
-	\begin{minipage}{0.5\linewidth}
+		\surrogateplot{exp4_model4_rasterized}{0.051033}{0.055558}{0.951106}{0.951073}{3.82}
+	\end{minipage}%
+	\begin{minipage}{0.53\linewidth}
 		\centering
-		\surrogateplot{exp4_model5_rasterized}{0.067856}{0.071096}{0.918668}{0.918393}{3.58}
+		\surrogateplot{exp4_model5_rasterized}{0.067856}{0.071096}{0.918668}{0.918393}{3.82}
 	\end{minipage}
 
-	\begin{minipage}{0.5\linewidth}
+	\hspace*{-0.06\linewidth}
+	\begin{minipage}{0.53\linewidth}
 		\centering
-		\surrogateplot{exp4_model2_rasterized}{0.067836}{0.074189}{0.913457}{0.913223}{3.58}
-	\end{minipage}\hfill%
-	\begin{minipage}{0.5\linewidth}
+		\surrogateplot{exp4_model2_rasterized}{0.067836}{0.074189}{0.913457}{0.913223}{3.82}
+	\end{minipage}%
+	\begin{minipage}{0.53\linewidth}
 		\centering
-		\surrogateplot{exp4_model8_rasterized}{0.061678}{0.091997}{0.894604}{0.894533}{3.58}
+		\surrogateplot{exp4_model8_rasterized}{0.061678}{0.091997}{0.894604}{0.894533}{3.82}
 	\end{minipage}
@@
 	\caption{Regression performance of Models~1-8 (from left to right, top to
-		bottom) trained in Experiment~4, viewed
+		bottom) in Experiment~4, viewed
 		as true vs.~predicted TBR on a test set of a selected cross-validation

### 2020-12-02 paper/ucl_tbr_paper.tex
increase size of fig. 3-5
more typesetting improvements in fig. 6

@@
 		(0.42,#6) rectangle
-		(2.45,2.5) node[pos=.5] {
+		(2.55,2.7) node[pos=.5] {
 			\\[0.1ex]
@@
 		width=0.05mm,align=left,font=\fontsize{5.5}{7.5}\selectfont]
-		(2.02,1.43) rectangle
-		(4.05,0.38) node[pos=.5] {
+		(2.02,1.3) rectangle
+		(4.3,0.38) node[pos=.5] {
 			{\color{red}

### 2020-12-02 paper/introduction.tex
add VR reference

@@
 Nuclear data for simulation was extracted from the following sources, in order of preference: Fendl 3.1d \cite{fendl31d}; Jeff 3.3 \cite{jeff33}; and ENDF 7.1 \cite{2011ii}.
+To maintain model-agnostic approach, variance reduction (VR) techniques
+were not used to accelerate the MC neutronics simulation~\cite{Kleijnen2013}.
+It should be noted that depending on application, VR may constitute a viable
+alternative to the presented work.
 
@@
 
-\footnotetext[1]{A bug in the Muir distribution involving erronous normal sampling was recently uncovered (see https://github.com/openmc-dev/openmc/pull/1670), but is disregarded in the present approach-focused work.}
+\footnotetext[1]{A bug in the Muir distribution involving erronous normal
+sampling was recently uncovered (see
+\url{https://github.com/openmc-dev/openmc/pull/1670}), but is disregarded in the present approach-focused work.}
 

### 2021-04-06 paper/ucl_tbr_paper.tex
nicer typesetting with the savetrees package
reduce keyword count

@@
 \usepackage{siunitx}
-\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % TODO: remove me before submitting
 \usepackage{isotope}
@@
 \usepackage{tabularx}
+\usepackage[all=normal,bibbreaks=tight,floats=tight,mathspacing=tight,wordspacing=tight]{savetrees}
 
@@
 
-\keywords{machine learning, surrogate model, regression, fast approximation,
-Monte Carlo simulation, OpenMC, Paramak, tritium breeding, adaptive sampling}
+\keywords{Machine Learning, Surrogate Model, Tritium Breeding, Regression, Fast Approximation, Adaptive Sampling}
 \submitto{\NF}

### 2021-04-08 paper/results.tex
fix table error
nicer typesetting with the savetrees package
modify to correct for arXiv errors

@@
 		\midrule
-		\input{tbl/table11}
+		\input{table11} \\
 		\bottomrule
@@
 
-In order to test our QASS prototype, several functional toy theories for TBR were developed as alternatives to the expensive MC model.
-By far the most robust of these was the following sinusoidal theory over continuous parameters $C$, with adjustable wavenumber parameter $n$:
+In order to test our QASS prototype, several functional toy theories for TBR
+were developed as alternatives to the expensive MC model. By far the most robust
+of these was the following sinusoidal theory over continuous parameters~$C$,
+with adjustable wavenumber parameter~$n$:
 
@@
 	\centering
-	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig7_qasssampling.png}
+	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig7_qasssampling_new.pdf}
 	\caption{\label{fig:qasssampling}Absolute training error for QASS, baseline scheme, and mixed scheme.}
@@
 	\centering
-	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.png}
+	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k_new.pdf}
 	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and

### 2022-01-31 paper/introduction.tex
Second round of revisions to paper submission.

@@
 
-In this work, we develop an empirical surrogate model for the tritium breeding
+In this work, we develop a family of empirical surrogate models for the tritium breeding
 ratio (TBR) in an inertial confinement fusion (ICF) reactor. The expensive model
@@
 Although more expensive 3D parametric models exist, we chose the Paramak simulation for its preferable speed in dataset generation in order to most fully demonstrate our methods.
+We further propose an adaptive sampling algorithm (QASS) suitable for reducing the quantity of expensive samples needed to train our surrogate models.
 
@@
 parameters may be explored.
-Nuclear data for simulation was extracted from the following sources, in order of preference: Fendl 3.1d \cite{fendl31d}; Jeff 3.3 \cite{jeff33}; and ENDF 7.1 \cite{2011ii}.
+Nuclear data for simulation was extracted from the following sources, in order of preference: FENDL 3.1d \cite{fendl31d}; JEFF 3.3 \cite{jeff33}; and ENDF/B-VII.1 \cite{2011ii}.
 To maintain model-agnostic approach, variance reduction (VR) techniques
@@
 research. In~\Sref{sec:methodology} we will present our methodologies for the comparison
-testing of a wide variety of surrogate modelling techniques, as well as a novel
-adaptive sampling procedure suited to this application. After delivering the
+testing of a wide variety of surrogate modelling techniques, as well as defining the adaptive sampling procedure QASS. After delivering the
 results of these approaches in~\Sref{sec:results}, we will give our final conclusions and
@@
 
-In our work, we set out to produce a fast TBR function which takes these same
-input parameters and approximates the MC model used in Paramak with the
-greatest achievable regression performance, while also minimising the required quantity of expensive samples.
+In our work, we set out to produce a fast TBR surrogate model, which takes the same input parameters as the MC model used in Paramak and approximates its output with the greatest achievable regression performance, while also minimising the required quantity of expensive-model samples needed for training.
 

### 2022-01-31 paper/results.tex
Second round of revisions to paper submission.

--- 2020-12-02 paper/results.tex
@@
 	\hspace*{-0.1\columnwidth}
-	\includegraphics[trim=10pt 50pt 10pt 10pt,clip,width=1.1\columnwidth]{scaling_metric_r2}
+	\includegraphics[trim=10pt 50pt 10pt 10pt,clip,width=1\columnwidth]{scaling_metric_r2}
 
@@
 	\hspace*{-0.1\columnwidth}
-	\includegraphics[trim=5pt 50pt 10pt 10pt,clip,width=1.1\columnwidth]{scaling_time_train}
+	\includegraphics[trim=5pt 50pt 10pt 10pt,clip,width=1\columnwidth]{scaling_time_train}
 
@@
 	\hspace*{-0.1\columnwidth}
-	\includegraphics[trim=0pt 15pt 10pt 15pt,clip,width=1.1\columnwidth]{scaling_time_pred}
+	\includegraphics[trim=0pt 15pt 10pt 15pt,clip,width=1\columnwidth]{scaling_time_pred}
 	\caption{Experiment~3 results, displayed as a function of $N_0$. From top to bottom, $R^2$,
@@
 time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
-to a standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
+to a standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6.92} \times {10^6}$
 with respect to Paramak. Satisfying
@@
 $\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
-and~$\omega=\num{8659251} \times$.
+and~$\omega=\num{8.66} \times {10^6}$.
 While these surrogates
@@
 that achieved~$R^2=\num{0.913}$,
-$\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
+$\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1.27} \times {10^6}$
 with a set of size only~\num{10000}.
@@
 		\midrule
-		\input{tbl/table11}
+		\input{tbl/table11} \\
 		\bottomrule
@@
 
-In order to test our QASS prototype, several functional toy theories for TBR were developed as alternatives to the expensive MC model.
-By far the most robust of these was the following sinusoidal theory over continuous parameters $C$, with adjustable wavenumber parameter $n$:
+In order to test our QASS prototype, several functional toy theories for TBR were developed as alternatives to the expensive MC model. QASS performance was verified by training an ANN on
+these theories for varied quantities of initial, incremental, and MCMC
+candidate samples. By far the most useful
+of these was the following sinusoidal theory, as ANNs trained on this model demonstrated similar performance to those on the expensive
+MC model:
 
@@
 
-ANNs trained on this model demonstrated similar performance to those on the expensive
-MC model. QASS performance was verified by training an ANN on
-the sinusoidal theory for varied quantities of initial, incremental, and MCMC
-candidate samples.
+where $C$ denotes the continuous parameter space, and $n$ is an adjustable wavenumber parameter.
 
@@
 	\centering
-	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig7_qasssampling.png}
+	\hspace*{-0.5em}\includegraphics[width=1.1\linewidth]{fig7_qasssampling.png}
 	\caption{\label{fig:qasssampling}Absolute training error for QASS, baseline scheme, and mixed scheme.}
@@
 	\centering
-	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.png}
+	\hspace*{-0.5em}\includegraphics[width=1.1\linewidth]{fig8_qasssampling100k.png}
 	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and
@@
 samples and half uniformly random samples incremented on each iteration, which
-is also shown in~\Fref{fig:qasssampling}. An increase in initial sample size was
-observed to also resolve precision in these smooth regions of the toy theory, as
+is also shown in~\Fref{fig:qasssampling}. An increase in initial sample size was also observed to improve precision in these smooth regions of the toy theory, as
 the initial samples were obtained from a uniform random distribution. As shown
@@
 termination for QASS, this corresponds to a ${\sim}6\%$ decrease in the number
-of total samples needed to train a surrogate with the same error.
+of total samples needed to train a surrogate model while achieving the same error.

### 2022-03-11 paper/introduction.tex
second round of revisions handled by PM

@@
 
-    \caption{Diagram of the simple sphere geometry (not to scale) where the blanket is \fcolorbox{white}{green}{\rule{0pt}{6pt}\rule{6pt}{0pt}}, the first wall is \fcolorbox{white}{blue}{\rule{0pt}{6pt}\rule{6pt}{0pt}} and the neutron point source is \fcolorbox{white}{red}{\rule{0pt}{6pt}\rule{6pt}{0pt}}.}
+    \caption{Diagram of the simple sphere geometry (not to scale) where the
+	blanket is \fcolorbox{white}{green}{\rule{0pt}{6pt}\rule{6pt}{0pt}}, the
+first wall is \fcolorbox{white}{blue}{\rule{0pt}{6pt}\rule{6pt}{0pt}} and the
+neutron point source is \fcolorbox{white}{red}{\rule{0pt}{6pt}\rule{6pt}{0pt}}.
+Blanket and first wall thickness, as well as their material and structural
+properties, are adjustable parameters of the simulation that are later optimized
+(see~\Tref{tbl:params} for complete parameter listing).}
     \label{fig:model_diagram}
@@
 extremely hot and dense plasma containing enriched Hydrogen isotopes. The current frontier generation of fusion reactors, such as the Joint European Torus (JET) and the
-under-construction International Thermonuclear Experimental Reactor (ITER), make
+under-construction ITER, make
 use of both tritium and deuterium fuel.
@@
 
-Instead, modern D-T reactors rely on tritium breeding blankets, specialized
+Modern D-T reactors rely on tritium breeding blankets, specialized
 layers of material which partially line the reactor and produce tritium upon
@@
 		\toprule
-		{} & Parameter name & Domain\\
+		{} & Parameter name (abbreviation) & Domain\\
 		\midrule
@@
 		   & Breeder \isotope[6]{Li} enrichment fraction & $[0,1]$\\
-		   & Breeder material & $\{\text{Li}_2\text{TiO}_3, \text{Li}_4\text{SiO}_4\}$\\
+		   & Breeder material (BBM) & $\{\text{Li}_2\text{TiO}_3, \text{Li}_4\text{SiO}_4\}$\\
 		   & Breeder packing fraction & $[0,1]$\\
 		   & Coolant fraction\textsuperscript{\textdagger} & $[0,1]$\\
-		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
+		   & Coolant material (BCM) & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
 		   & Multiplier fraction\textsuperscript{\textdagger} & $[0,1]$\\
-		   & Multiplier material & $\{\text{Be}, \text{Be}_{12}\text{Ti}\}$\\
+		   & Multiplier material (BMM) & $\{\text{Be}, \text{Be}_{12}\text{Ti}\}$\\
 		   & Multiplier packing fraction & $[0,1]$\\
-		   & Structural fraction\textsuperscript{\textdagger} & $[0,1]$\\
+		   & Structural fraction\textsuperscript{\textdagger} (BSM) & $[0,1]$\\
 		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
-		   & Thickness & $[0,500]$\\
+		   & Thickness & $[0,500]\text{ cm}$\\
 		\midrule
@@
 		   & Coolant fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
-		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
+		   & Coolant material (FCM) & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
 		   & Structural fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
-		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
-		   & Thickness & $[0,20]$\\
+		   & Structural material (FSM) & $\{\text{SiC}, \text{eurofer}\}$\\
+		   & Thickness & $[0,20]\text{ cm}$\\
 		\bottomrule
@@
 	\end{indented}
+	% TODO: verify with JS that thickness unit is indeed cm
 \end{table}

### 2022-03-11 paper/methodology.tex
modify to correct for arXiv errors
Second round of revisions to paper submission.
second round of revisions handled by PM

@@
 		selected abbreviations and implementations. $\mathcal{H}$~denotes the
-		set of hyperparameters.}
+		set of hyperparameters, family-dependent priors that control the
+		learning process, and are tuned separately. Families with fewer
+		hyperparameter represents a smaller surogate domain to explore.}
 	\begin{indented}
@@
 in~\Tref{tbl:metrics}. For regression performance analysis, we include a
-selection of absolute metrics to assess the models' approximation capability and set
-practical bounds on the expected uncertainty of their predictions. In addition, we also track
-relative measures that are better-suited for comparison between this work and others as
+selection of absolute metrics (MAE, $S$) to assess the models' approximation capability
+and set practical bounds on the expected uncertainty of their predictions. In addition, we also track
+relative measures ($R^2$, $R^2_\text{adj.}$) that are better-suited for comparison between this work and others as
 they are invariant with respect to the selected domain and image space.
@@
 per each model family are used to train surrogates on sets of various sizes to
-investigate their scaling properties. In particular, we consider sets of
-sizes~$\{1,2,5,10,12,15,20\}$ in thousands of samples to better characterize the
-relationship of each family between sample count and the metrics of interest
-listed in~\Tref{tbl:metrics}.
+investigate their scaling properties. In particular, we track the metrics
+from~\Tref{tbl:metrics} as functions of training set size (1, 2, 5, 10, 12, 15 and 20 thousands
+of samples) individually for each family. This allows their comparison based on
+observed trends, and estimation of optimal training set sizes.
 The results of this experiment are shown in~\Fref{fig:scaling} and discussed
@@
 (CDM)~\cite{Solonen2012} in feature space.
+Error maximization is desirable for these sample points because it identifies regions of parameter space where the surrogate most needs to be improved.
 On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and absolute error calculated.

### 2022-03-11 paper/results.tex
second round of revisions handled by PM

@@
 The results displayed in~\Fref{fig:exp1-time-vs-reg} indicate that in the first,
-simplified case GBTs clearly appear to be the most accurate as
-well as the fastest surrogate family in terms of mean prediction time. Following
-that, we note that ERTs, SVMs and ANNs also achieved satisfactory results with respect to both examined metrics.
-While the remainder of tested surrogate families does not exhibit prohibitive
-complexity, its regression performance falls below average.
+simplified case GBTs clearly appear to be the most accurate as well as the
+fastest surrogate family in terms of mean prediction time. Following that, we
+note that ERTs, SVMs and ANNs also achieved satisfactory results with respect to
+both examined metrics. In addition, prediction times of GBTs and SVMs show
+relatively lower variance than those of ERTs and ANNs. Even though the remainder
+of tested surrogate families does not exhibit prohibitive complexity, its
+regression performance falls below average.
 
@@
 		terms of~$\overline{t}_{\text{pred.}}$ and~$R^2$ with 3~selected slices out
-		of~4.}
+	of~4 (defined in~\Tref{tbl:slices}).}
 \end{figure}
+
+\begin{table}[h]
+	\centering
+	\setlength\tabcolsep{5pt}
+	\renewcommand{\arraystretch}{0.95}
+	{\footnotesize
+		\begin{tabular}{llllll}
+		\toprule
+		BBM & BCM & BMM & BSM & FCM & FSM \\
+		\midrule
+		$\text{Li}_4\text{SiO}_4$ & $\text{H}_2\text{O}$ & $\text{Be}_{12}\text{Ti}$ & eurofer & $\text{H}_2\text{O}$ & eurofer\\
+		$\text{Li}_4\text{SiO}_4$ & He & $\text{Be}_{12}\text{Ti}$ & eurofer & $\text{H}_2\text{O}$ & eurofer\\
+		$\text{Li}_4\text{SiO}_4$ & $\text{H}_2\text{O}$ & $\text{Be}_{12}\text{Ti}$ & eurofer & He & eurofer\\
+		$\text{Li}_4\text{SiO}_4$ & He & $\text{Be}_{12}\text{Ti}$ & eurofer & He & eurofer\\
+		\bottomrule
+		\end{tabular}
+	}
+	\caption{Slices 1-4 of the domain space (discrete parameter
+	assignments) explored in Experiment~1. Columns correspond to abbreviated
+	parameter names listed in~\Tref{tbl:params}.}
+	\label{tbl:slices}
+\end{table}
 
@@
 in~\Fref{fig:exp2-time-vs-reg}), we observe that many surrogate families
-consistently underperform. The least
-affected models appear to be GBTs, ANNs and ERTs, which are known to be capable of capturing relationships
-involving mixed feature types that were deliberately withheld in the first
-experiment. With only negligible differences, the first two of these families
-appear to be tied for the best performance as well as the shortest prediction
-time. We observe that ERTs and RBFs also
-demonstrated satisfactory results, clearly outperforming the remaining surrogates in
-terms of regression performance, and in some cases also in prediction time.
+consistently underperform. The least affected models appear to be GBTs, ANNs and
+ERTs, which are known to be capable of capturing relationships involving mixed
+feature types that were deliberately withheld in the first experiment. With only
+negligible differences, the first two of these families appear to be tied for
+the best performance as well as the shortest prediction time. We observe that
+ERTs and RBFs also demonstrated satisfactory results, clearly outperforming the
+remaining surrogates in terms of regression performance, and in some cases also
+in prediction time.
 
@@
 regression performance of some methods, their performance fluctuates considerably
-depending on the selected slices. Furthermore, in all instances the best
+depending on the selected slices. For instance, the variance in SVM performance
+in slice 1 is much lower than in slices 2-3, and both KNNs and ABTs perform much
+better in slices 1-2 than in slice 3. Furthermore, in all instances the best
 results are achieved by families of surrogates that do not benefit from this
@@
 more training points are introduced. While such families achieve nearly comparable
-performance on the largest dataset, in the opposite case tree-based ensemble approaches
-clearly outperform ANNs. This can be observed
-particularly on sets of sizes up to~\num{6000}.
+performance on the largest dataset, in the opposite case tree-based ensemble
+approaches clearly outperform ANNs. For instance, GBTs achieve
+$\text{MAE}=\num{0.107}$ that is nearly half of the $\text{MAE}=\num{0.186}$
+reached by ANNs, representing a clear benefit given vastly disparate training
+and prediction times. This trend continues to set sizes up to~\num{6000}.
 
@@
 	\caption{\label{tbl:exp4-detailed-results}Results of Experiment~4. Here,
-		average values and standard deviations are reported over 5~cross-validation folds,
+		means and standard deviations are reported over 5~cross-validation folds,
 		$|\mathcal{T}|$~denotes cross-validation set size ($\times 10^3$)
@@
 		\num{2.8103592103930337} \text{ s}$
-		measured in Paramak over~\num{500000} samples.
-	The best-performing method(s) under each are highlighted in bold.}
+		measured in Paramak over~\num[round-precision=0]{500000} samples.
+	The best-performing method(s) under each metric are highlighted in bold.}
 	\setlength\tabcolsep{4pt}

### 2022-03-11 paper/introduction.tex

@@
 where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
-less common isotopes of lithium, respectively. The TBR is defined as the ratio
-between tritium generation in the breeding blanket and consumption in the
-reactor, whose description in Paramak is facilitated by 2~classes of parameters
+less common isotopes of lithium, respectively. The TBR is defined as the ratio of tritium produced per source neutron
+, whose description in Paramak is facilitated by 2~classes of parameters
 (exhaustively listed in~\Tref{tbl:params}). While the geometry of a given

### 2022-03-14 paper/referees/response-1.tex
Created referee response document.

\documentclass[12pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath,amssymb}
\usepackage{color}
\usepackage{graphicx}

\topmargin = 1mm
\headsep = 1mm
\textheight = 228mm
\textwidth = 167.0mm
\oddsidemargin = 1.1mm
\evensidemargin = 1.1mm
\date{\today}

% Set the format for notes on in-progress responses
\newcommand\myNotes[1]{\textcolor{red}{#1}}
\newcommand\myTodo[1]{\textcolor{blue}{#1}}

\begin{document}

\begin{center}
\bf Reviewer Response for Manuscript NF-104470
\end{center}

\bigskip

\noindent
Dear Editor,

\bigskip
\noindent
We thank the referees for their careful consideration and their useful comments. Please find below our detailed responses. We have also made the corresponding changes in the text.

\bigskip
\noindent
Best Regards,\\
Petr Mánek (for the authors)

\bigskip
\noindent
{\bf Report of Referee 1}

\begin{enumerate}
\item The paper presents a comparison of different families of surrogate methods for the calculation of the Tritium Breeding Ration (TBR) in a fusion reactor, claiming major focus to be on Inertial Confinement. In the paper, a ”surrogate” method is defined as a cheaper approximation of a much expensive calculation procedure like, for example, a Monte Carlo calculation. Often surrogate methods involve using Artificial Intelligence techniques like, e.g., Artificial Neural Networks.

The paper compares different families of surrogate methods checking both accuracy and computational complexity, and presents a novel adaptive method for sampling the relevant parameter space, called Quality-Adaptive Surrogate Sampling (QASS), aiming at optimizing the prediction accuracy
for a given size of the sampling set or, alternatively, minimizing the number of training points required for a given accuracy. If finally shows that the QASS method is effective at improving the efficiency of a large variety of surrogate methods.

Although I found the paper interesting to read and acknowledge it can produce a valuable contribution to the development of future fusion technologies, I feel it to be a bit out of the scope of the Nuclear Fusion journal. Numerical techniques are obviously a mission-critical for the development of a scientific and technological task as complex as controlled tehrmonuclear fusion, but a paper with such a strong pitch on computational sciences should be directed more properly, I would suggest, to a journal like, e.g., Journal of Computational Physics or Computer Physics Communications, to which I would recommend to re-direct the submission. I understand, however, that it is up to the editor to take a final decision on the paper acceptability based upon its subject. In the following, I will list my comments as if the paper were to be processed by Nuclear Fusion: I hope they could be useful to improve its quality, whatever journal it will finally be submitted to.

{\bf }

\newpage
\bigskip
\noindent
{\bf Comments}

\item Title:
I think the title is a bit misleading. At least to me, it generated first the feeling that the paper were to discuss predictions of the TBR in fusion reactors. I think something more descriptive could be Fast Regression Methods for the Evaluation of the Tritium Breeding Ratio in Fusion Reactors, or something similar.

{\bf }

\item Page 2, line 29, left column:
It is stated that the paper presents an empirical surrogate model for the tritium dreeding ratio (TBR) in an inertial confinement fusion (ICF) reactor. This sentence is puzzling to me. If I read correctly the paper later, it compares a family of surrogate methods and develop a strategy for adaptive sampling (QASS). I suspect this is what really the sentence refers to. If it is so, I think the authors should change the sentence, pointing more clearly to QASS.

{\bf }

\item Page 2, line 53, left column:
It is stated that the energy distribution for the neutrons considered in the paper is the one called Miur. Actually, a quick serach revealed that this is just a gaussian distribution with certain free parameters. I guess it would be more informative rewording this sentence as a gaussian energy distribution with some user-selected free parameters, re-directing to the relevant literature for more details.

{\bf }

\item  Page 2, line 24, right column:
While commenting figure 1, it is stated that the geometry of the system were intentionally left adjustable. I suspect that the free parameters are those listed later in Table 1, but this is not stated explicitly. I would appreciate if an explicit comment on which parameters are actually left adjustable could be made at this point.

{\bf }

\item Page 2, line 45, right column:
At this point, the paper mentions a novel adaptive sampling procedure suited to this application. I suspect this is what was previously meant (see my comment 2). I think the authors should try to resolve as much as possible this ambiguity between novel surrogate method and novel sampling procedure.

{\bf }

\item Page 3, line 6, left column:
It is stated that nuclear fusion technology relies on the production and containement of an extremely hot and dense plasma containing enriched Hydrogen isotopes. While this is certainly true for ICF applications, it is not true for magnetic confinement applications, where the fuel density is approximately $10^{-5}$ the atmospheric level. It is true that the paper claims to focus on ICF applications, which would make the statement correct. However, in the next few lines it discusses explicitly JET and ITER, which are magnetic fusion experiments. In these few lines there is an oscillation between inertial and magnetic fusion experiments, which make this paper segment ambiguous. I would appreciate if the authors could resolve such ambiguity.

{\bf }

\item Page 3, line 25, left column:
It is stated that modern D-T reactors rely on tritium breeding blanket. This sentence seem to be linked to the previous mentioning of JET and ITER. I would appreciate if the authors could be a bit more explicit and precise. It should be noted that JET does not have a blanket, while only test modules will be installed in ITER. It is true that such component is expected to be eventually installed in a reactor. Maybe, an example taken from ICF technology could also be added.

{\bf }

\item Page 3, line 32-39, right column:
The authors mention a fast TBR function which takes these same input parameters and approximates the MC model.... It is not clear, to me, what the term function means here. I feel there is again the ambiguity between surrogate methods and sampling technique. Could the authors resolve it?

{\bf }

\item Page 4, line 52, left column:
The authors state that they track relative measures that are better suited for comparison between this work and others, because they are invariant... I think it would be better to mention explicitly which ones are the relative metrics and the absolutes (mentioned a few lines earlier).

{\bf }

\item Page 5, line 5, right column:
The definition given the for standard deviation does not correspond to the one usually reported in statistics. Could the authors please check it?

{\bf }

\item Page 5, line 51, left column:
... to better characterize the relationship of each family between sample count and the metrics of interest... This sentence is a bit obscure to me. Maybe the authors could re-phrase it?

{\bf }

\item Figure 5:
The font-size of the labels is really small and makes it difficult to read. Could the authors increase it?

{\bf }

\item Page 6, lines 25-31, right column:
The authors comment the results displayed in figure 3. I understand that the figure was produced by keeping fixed some discrete parameters, but I have no clue which one (or which ones, in case different parameters were kept fixed for different subsets of the data shown). Could the authors explicitly show which one(s)?

{\bf }

\item Page 6, lines 34, right column:
It is stated that ERTs, SVMs, and ANNs also achieved satisfactory results with respect to both examined metrics, where I understand the considered metrics are regression performance and prediction time per sample. Actually, the figure suggests that ANNs could be relatively slow. Could the authors elaborate a bit more on that?

{\bf }

\item Page 6, lines 43, right column:
It is stated that GBTs, ANNs and ERTs ... are known to be capable of capturing relationships involving mixed feature types that were deliberately withheld in the first experiment. I think it would be appropriate to add a reference to the relevant literature to substantiate this statement.

{\bf }

\item Page 7, lines 30-37, right column:
Following both hyperparameter tuning experiments, we conclude that while domain restrictions employed in the first case have proven effective in improving the regression performance of some methods, their performance fluctuates considerably depending on the selected slices. The mentioned fluctuations are not obvious to me. Maybe the authors could elaborate a bit more on this to make them more apparent to the reader.

{\bf }

\item Page 7, lines 54, right column:
Commenting the dependence of the performance of the surrogate method families on the dataset size, it is stated that: While such families achieve nearly comparable performance on the largest dataset, in the opposite case tree-based ensemble approaches clearly outperform ANNs. To me, this sentence is only partially meaningful, because it should be complemented by a comment on the accuracy level that can be attained by whatever methods on the smallest dataset. If it appeared that the achievable accuracy is too low for practical applications, even the speed advantage would be useless. Could the authors add a line of comment/clarification on that?

{\bf }

\item Page 8, right column:
The figures inserted in the column are a bit too large. They cover the margin of the left column and some words are chopped. Could the authors fix this?

{\bf }

\item Page 9, lines 8 and 12, left column:
The speedups obtained with the surrogate methods are written as $\omega = 6916416 \times$ and $\omega = 8659251 \times$. I think that writing the acceleration obtained using standard scientific notation $6.92 \times 10^6$ and $8.66 \times 10^6$ would be far more immediate to read.

{\bf }

\item Page 9, line 41, left column:
The authors introduce a sinusoidal theory as an alternative to the expensive MC Paramak model used to assess the efficiency of the surrogate methods and sampling techniques they analyze. They qualify this theory as robust. It is by far not clear to be what the word robust means in this context. Could the authors clarify this?

{\bf }

\item Page 10, line 4:
The best-performing method(s) under each are highlighted in bolt I do not fully understand this sentence. Perhaps a word is missing (under each ... what ... ? )

{\bf }

\item Page 10, figure 7 and 8:
They are too large and covers some letters of the opposite left column. I think they should be resized.

{\bf }

\item Page 11, line 7, left column:
An increase in initial sample size was observed to also resolve precision in these smooth regions... I do not understand what the wording resolve precision means in this context. Maybe the authors could elaborate a bit more on that?

{\bf }

\item Page 11, line 26-31, left column:
The authors claim they developed fast and high-quality surrogates for the Paramak TBR model. I suspect that here again there is an ambiguity between surrogate models and sampling strategies. If the authors really developed a novel surrogate model, this is not clear to me. Could the authors elaborate more on that?

{\bf }

\item Page 12, line 32, left column:
When following the url reported in the citation, I reach a publication with title The components of the Wired Spanning Forest are recurrent, which looks different from the declared one. Maybe is the link wrong?

{\bf }

\end{enumerate}

\newpage
\bigskip
\noindent
{\bf Report of Referee 2}

\begin{enumerate}
\item Highly interesting work on empirical surrogate modelling for an integral 3D Monte-Carlo radiation transport problem (TBR).

{\bf }

\bigskip
\noindent
{\bf Comments}

\item Introduction: use capital letters for FENDL and JEFF projects; ENDF/B-VII.1.

{\bf }

\item Introduction: I am not fully convinced that VR is a competitor of your work or perhaps in other applications. The concept is very different, the objective is similar: to achieve significant speedups.

{\bf }

\item 1.1: The acronym ITER should be used without the abandoned explanation. Just say "ITER".

{\bf }

\item 1.1: 2nd paragraph starts with "instead". However, the tritium self-sufficiency is a paramount requirement for viable nuclear fusion energy production (DT reaction). Therefore the tritium breeding is an inherent feature of DT fusion reactors; there is no way to rely, even partially, on external supply, except of start-up inventories.

{\bf }

\item 1.1: TBR definition is ok, if "consumption" is well understood. Better to use the standard definiton tritium produced per source neutron (or tritium fused in plasma).

{\bf }

\item 1.1: Table 1: Thickness in mm; Armour material I suppose is W.

{\bf }

\item 1.1: It seems to me that the accessible domains could be narrowed down for a reasonable design space. Would this impact the assessment made in the paper? This obviously applies most prominently to parameters like armour fraction and blanket thickness.

{\bf }

\item 2: Table 2: it might be useful to briefly introduce the rationale of hyperparameter sets (how they are built from the Paramak input). What could be said about the size, e.g. using only 1-2 parameters vs. 11?

{\bf }

\item 2.2: Regarding QASS, I am confused about the objective to maximize surrogate eorr (page 6). Is this a typo?

{\bf }

\item 2.2: The CDM is not introduced through ref. 26. I would anyway suggest to describe the core of the metric in your article.

{\bf }

\item 3.2: what does "most robust" mean for the selected TBR toy theory? Is "robustness" a requirement for the functionality or success of QASS?

{\bf }

\item 3.2: Fig. 7/8: explain E-MAE in the article and how it relates to the introduced MAE.

{\bf }

\end{enumerate}

\bigskip
\noindent
{\bf Report of Board of Editors}

\begin{enumerate}
\item The reviewer believes to publish this paper in the Nuclear Fusion, the authors should interpret or correlate finding/result/significance with the fusion terminology/knowledge/practice. In this case, what is the final design composition (the set of input parameters listed in Table 1) derived from the proposed methodology that would provide an adequate TBR, and how are the derived design compositions compared with the available designs? Without such a comparison, it is hard to evaluate the contribution of the paper toward the advancement of fusion nuclear science and technology (FNST). Furthermore, even TBR is a critical parameter in the design, the blanket design has to satisfy other constraints such as temperature, stress, MHD pressure drop, etc. How does the proposed method incorporate additional yet necessary constraints in searching for a required TBR?

The goal of the proposed methodology is not clearly stated. If the goal is only to produce a fast TBR function as stated below “In our work, we set out to produce a fast TBR function which takes these same input parameters and approximates the MC model used in Paramak with the greatest achievable regression performance, while also minimizing the required quantity of expensive samples,” the reviewer would consider this work is in its primitive stage of the application of artificial intelligence/machine learning to FNST, and a too narrow fusion relevant scope to be published in Nuclear Fusion. More thoughts should be given to the identifications of the space/critical design needs from an integrated perspective (versus a single parameter such as TBR), where AI/the proposed methodology can help ensure tritium fuel self-sufficiency for the fusion energy development.

{\bf }

\end{enumerate}

\end{document}

### 2022-03-14 paper/conclusion.tex
Added red text coloring for referee edits.

@@
 We employed a broad spectrum of data
-analysis and machine learning techniques to develop fast and high-quality
-surrogates for the Paramak TBR model. After reviewing
+analysis and machine learning techniques to develop a library of fast and high-quality
+surrogate models for the expensive Paramak TBR model. After reviewing
 9~surrogate model families, examining their behaviour on a constrained and
@@
 
-We further developed a novel adaptive
-sampling algorithm, QASS, capable of interfacing with any of the presented
-surrogate models.
+We additionally developed a novel adaptive
+sampling algorithm, QASS, capable of interfacing with any of the \textcolor{red}{surrogate models presented in this work}.
 Preliminary testing on a toy theory, qualitatively comparable to
-Paramak, demonstrated the effectiveness of QASS and behavioural trends
-consistent with the design of the algorithm. With~\num{100000} initial samples
+Paramak, demonstrated the effectiveness of QASS and \textcolor{red}{key} behavioral trends. With~\num{100000} initial samples
 and 100 incremental samples per iteration, QASS achieved a ${\sim}40\%$ decrease
@@
 Further optimisation over the hyperparameter space has strong potential to increase this performance by further reduction of necessary expensive samples, in particular by decreasing the required quantity of initial samples.
-This will allow for future deployment of QASS on the Paramak TBR model in coalition with any of the most effective identified surrogates.
+This will allow for future deployment of QASS on top of any of \textcolor{red}{our most effective identified TBR surrogate models}.
 

### 2022-03-14 paper/introduction.tex
Added red text coloring for referee edits.

@@
 
-In this work, we develop a family of empirical surrogate models for the tritium breeding
+In this work, we develop \textcolor{red}{a family of empirical surrogate models} for the tritium breeding
 ratio (TBR) in an inertial confinement fusion (ICF) reactor. The expensive model
@@
 Although more expensive 3D parametric models exist, we chose the Paramak simulation for its preferable speed in dataset generation in order to most fully demonstrate our methods.
-We further propose an adaptive sampling algorithm (QASS) suitable for reducing the quantity of expensive samples needed to train our surrogate models.
+\textcolor{red}{We further propose an adaptive sampling algorithm (QASS) suitable for reducing the quantity of expensive samples needed to train our surrogate models.}
 
@@
 first wall is \fcolorbox{white}{blue}{\rule{0pt}{6pt}\rule{6pt}{0pt}} and the
-neutron point source is \fcolorbox{white}{red}{\rule{0pt}{6pt}\rule{6pt}{0pt}}.
+neutron point source is \fcolorbox{white}{red}{\rule{0pt}{6pt}\rule{6pt}{0pt}}. \textcolor{red}{
 Blanket and first wall thickness, as well as their material and structural
 properties, are adjustable parameters of the simulation that are later optimized
-(see~\Tref{tbl:params} for complete parameter listing).}
+(see~\Tref{tbl:params} for complete parameter listing).}}
     \label{fig:model_diagram}
@@
 parameters may be explored.
-Nuclear data for simulation was extracted from the following sources, in order of preference: FENDL 3.1d \cite{fendl31d}; JEFF 3.3 \cite{jeff33}; and ENDF/B-VII.1 \cite{2011ii}.
+Nuclear data for simulation was extracted from the following sources, in order of preference: \textcolor{red}{FENDL 3.1d \cite{fendl31d}; JEFF 3.3 \cite{jeff33}; and ENDF/B-VII.1 \cite{2011ii}}.
 To maintain model-agnostic approach, variance reduction (VR) techniques
@@
 extremely hot and dense plasma containing enriched Hydrogen isotopes. The current frontier generation of fusion reactors, such as the Joint European Torus (JET) and the
-under-construction ITER, make
+under-construction \textcolor{red}{ITER}, make
 use of both tritium and deuterium fuel.
@@
 
-Modern D-T reactors rely on tritium breeding blankets, specialized
+\textcolor{red}{Modern} D-T reactors rely on tritium breeding blankets, specialized
 layers of material which partially line the reactor and produce tritium upon
@@
 where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
-less common isotopes of lithium, respectively. The TBR is defined as the ratio of tritium produced per source neutron
+less common isotopes of lithium, respectively. \textcolor{red}{The TBR is defined as the ratio of tritium produced per source neutron}
 , whose description in Paramak is facilitated by 2~classes of parameters
@@
 
-In our work, we set out to produce a fast TBR surrogate model, which takes the same input parameters as the MC model used in Paramak and approximates its output with the greatest achievable regression performance, while also minimising the required quantity of expensive-model samples needed for training.
+In our work, we set out to produce a \textcolor{red}{fast TBR surrogate model}, which takes the same input parameters \textcolor{red}{as the MC model used in Paramak and approximates its output} with the greatest achievable regression performance, while also minimising the required quantity of expensive-model samples \textcolor{red}{needed for training}.
 
@@
 		\toprule
-		{} & Parameter name (abbreviation) & Domain\\
+		{} & Parameter name \textcolor{red}{(abbreviation)} & Domain\\
 		\midrule
@@
 		   & Breeder \isotope[6]{Li} enrichment fraction & $[0,1]$\\
-		   & Breeder material (BBM) & $\{\text{Li}_2\text{TiO}_3, \text{Li}_4\text{SiO}_4\}$\\
+		   & Breeder material \textcolor{red}{(BBM)} & $\{\text{Li}_2\text{TiO}_3, \text{Li}_4\text{SiO}_4\}$\\
 		   & Breeder packing fraction & $[0,1]$\\
 		   & Coolant fraction\textsuperscript{\textdagger} & $[0,1]$\\
-		   & Coolant material (BCM) & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
+		   & Coolant material \textcolor{red}{(BCM)} & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
 		   & Multiplier fraction\textsuperscript{\textdagger} & $[0,1]$\\
-		   & Multiplier material (BMM) & $\{\text{Be}, \text{Be}_{12}\text{Ti}\}$\\
+		   & Multiplier material \textcolor{red}{(BMM)} & $\{\text{Be}, \text{Be}_{12}\text{Ti}\}$\\
 		   & Multiplier packing fraction & $[0,1]$\\
-		   & Structural fraction\textsuperscript{\textdagger} (BSM) & $[0,1]$\\
+		   & Structural fraction\textsuperscript{\textdagger} \textcolor{red}{(BSM)} & $[0,1]$\\
 		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
@@
 		   & Coolant fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
-		   & Coolant material (FCM) & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
+		   & Coolant material \textcolor{red}{(FCM)} & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
 		   & Structural fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
-		   & Structural material (FSM) & $\{\text{SiC}, \text{eurofer}\}$\\
+		   & Structural material \textcolor{red}{(FSM)} & $\{\text{SiC}, \text{eurofer}\}$\\
 		   & Thickness & $[0,20]\text{ cm}$\\
@@
 	\end{indented}
-	% TODO: verify with JS that thickness unit is indeed cm
 \end{table}

### 2022-03-14 paper/methodology.tex
Added red text coloring for referee edits.

@@
 		selected abbreviations and implementations. $\mathcal{H}$~denotes the
-		set of hyperparameters, family-dependent priors that control the
+		set of hyperparameters, \textcolor{red}{family-dependent priors that control the
 		learning process, and are tuned separately. Families with fewer
-		hyperparameter represents a smaller surogate domain to explore.}
+		hyperparameter represents a smaller surogate domain to explore.}}
 	\begin{indented}
@@
 in~\Tref{tbl:metrics}. For regression performance analysis, we include a
-selection of absolute metrics (MAE, $S$) to assess the models' approximation capability
+selection of absolute metrics \textcolor{red}{(MAE, $S$)} to assess the models' approximation capability
 and set practical bounds on the expected uncertainty of their predictions. In addition, we also track
-relative measures ($R^2$, $R^2_\text{adj.}$) that are better-suited for comparison between this work and others as
+relative measures \textcolor{red}{($R^2$, $R^2_\text{adj.}$)} that are better-suited for comparison between this work and others as
 they are invariant with respect to the selected domain and image space.
@@
 
-Even though some surrogates support acceleration by means of parallelisation, we
-used non-parallelized implementations. The only exception to this are ANNs,
-which require a considerable amount of processing power for training on
+Even though some surrogates support acceleration by means of \textcolor{red}{parallelization}, we
+used non-parallelized implementations. The only exception to this \textcolor{red}{is the ANN family},
+which \textcolor{red}{requires} a considerable amount of processing power for training on
 conventional CPU architectures. Lastly, to prevent undesirable bias by training
@@
 In Experiment~3, the 20~best-performing hyperparameter configurations
-per each model family are used to train surrogates on sets of various sizes to
+\textcolor{red}{for} each model family are used to train surrogates on sets of various sizes to
 investigate their scaling properties. In particular, we track the metrics
@@
 fare better for high-dimensional models by more thoroughly exploring all local
-optima in the feature space. MCMC produces each sample points according to a shared proposal
-distribution from the prior point. These sample points will converge to a desired posterior
+optima in the feature space. MCMC produces each sample \textcolor{red}{point} according to a \textcolor{red}{jump step drawn from a} shared proposal
+distribution. These sample points will converge to a desired posterior
 distribution, so long as the acceptance probability meets certain statistical criteria (see~\cite{Zhou2018} for a review).
@@
 (CDM)~\cite{Solonen2012} in feature space.
-Error maximization is desirable for these sample points because it identifies regions of parameter space where the surrogate most needs to be improved.
-On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and absolute error calculated.
+\textcolor{red}{Error maximization is desirable for these sample points because it identifies regions of parameter space where the surrogate most needs to be improved.} On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and absolute error calculated.
 MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points.

### 2022-03-14 paper/results.tex
Added red text coloring for referee edits.

@@
 note that ERTs, SVMs and ANNs also achieved satisfactory results with respect to
-both examined metrics. In addition, prediction times of GBTs and SVMs show
-relatively lower variance than those of ERTs and ANNs. Even though the remainder
+both examined metrics. \textcolor{red}{In addition, prediction times of GBTs and SVMs show
+relatively lower variance than those of ERTs and ANNs. Even though} the remainder
 of tested surrogate families does not exhibit prohibitive complexity, its
@@
 		terms of~$\overline{t}_{\text{pred.}}$ and~$R^2$ with 3~selected slices out
-	of~4 (defined in~\Tref{tbl:slices}).}
+	of~4 \textcolor{red}{(defined in~\Tref{tbl:slices})}.}
 \end{figure}
@@
 	}
-	\caption{Slices 1-4 of the domain space (discrete parameter
+	\caption{\textcolor{red}{Slices 1-4 of the domain space (discrete parameter
 	assignments) explored in Experiment~1. Columns correspond to abbreviated
-	parameter names listed in~\Tref{tbl:params}.}
+	parameter names listed in~\Tref{tbl:params}.}}
 	\label{tbl:slices}
@@
 regression performance of some methods, their performance fluctuates considerably
-depending on the selected slices. For instance, the variance in SVM performance
+depending on the selected slices. \textcolor{red}{For instance, the variance in SVM performance
 in slice 1 is much lower than in slices 2-3, and both KNNs and ABTs perform much
-better in slices 1-2 than in slice 3. Furthermore, in all instances the best
+better in slices 1-2 than in slice 3.} Furthermore, in all instances the best
 results are achieved by families of surrogates that do not benefit from this
@@
 performance on the largest dataset, in the opposite case tree-based ensemble
-approaches clearly outperform ANNs. For instance, GBTs achieve
+approaches clearly outperform ANNs. \textcolor{red}{For instance, GBTs achieve
 $\text{MAE}=\num{0.107}$ that is nearly half of the $\text{MAE}=\num{0.186}$
 reached by ANNs, representing a clear benefit given vastly disparate training
-and prediction times. This trend continues to set sizes up to~\num{6000}.
+and prediction times. This trend continues to set sizes up to~\num{6000}.}
 
@@
 
-Consistent with our expectation, the shortest training times were achieved by
+Consistent with our \textcolor{red}{expectations}, the shortest training times were achieved by
 instance-based learning methods (KNN, IDW) that
@@
 	\sisetup{round-mode=places,round-precision=3,detect-weight=true,detect-family=true}
-	\caption{\label{tbl:exp4-detailed-results}Results of Experiment~4. Here,
+	\caption{\label{tbl:exp4-detailed-results}\textcolor{red}{Results of Experiment~4. Here,
 		means and standard deviations are reported over 5~cross-validation folds,
@@
 		measured in Paramak over~\num[round-precision=0]{500000} samples.
-	The best-performing method(s) under each metric are highlighted in bold.}
+	The best-performing method(s) under each metric are highlighted in bold.}}
 	\setlength\tabcolsep{4pt}
@@
 		bottom) in Experiment~4, viewed
-		as true vs.~predicted TBR on a test set of a selected cross-validation
-		fold. Points are coloured by density.}
+		as true vs.~predicted TBR on a test set of a selected cross-validation fold. Points are \textcolor{red}{colored} by density.}
 	\label{fig:reg-performance}
@@
 
-In order to test our QASS prototype, several functional toy theories for TBR were developed as alternatives to the expensive MC model. QASS performance was verified by training an ANN on
+In order to test our QASS prototype, several functional toy theories for TBR were developed as alternatives to the expensive MC model.
+\textcolor{red}{QASS performance was verified by training an ANN on
 these theories for varied quantities of initial, incremental, and MCMC
@@
 of these was the following sinusoidal theory, as ANNs trained on this model demonstrated similar performance to those on the expensive
-MC model:
+MC model:}
 
@@
 
-where $C$ denotes the continuous parameter space, and $n$ is an adjustable wavenumber parameter.
+\textcolor{red}{where $C$ denotes the continuous parameter space, and $n$ is an adjustable wavenumber parameter.}
 
@@
 adaptively-sampled training set, it is outperformed by the baseline scheme on
-uniformly-random evaluation sets. We suspected that while QASS excels in
+uniformly-random evaluation sets. We \textcolor{red}{inferred} that while QASS excels in
 learning the most strongly peaked regions of the TBR theory, this comes at the
@@
 sampling suffices. Therefore a mixed scheme was implemented, with half MCMC
-samples and half uniformly random samples incremented on each iteration, which
+samples and half uniformly-random samples incremented on each iteration, which
 is also shown in~\Fref{fig:qasssampling}. An increase in initial sample size was also observed to improve precision in these smooth regions of the toy theory, as
-the initial samples were obtained from a uniform random distribution. As shown
-in ~\Fref{fig:qasssampling100k}, with~\num{100000} initial samples it was
+the initial samples were \textcolor{red}{uniformly-random}. As shown
+in~\Fref{fig:qasssampling100k}, with~\num{100000} initial samples it was
 possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline

### 2022-03-14 paper/introduction.tex
Small writing changes in first two sections.

@@
 Although more expensive 3D parametric models exist, we chose the Paramak simulation for its preferable speed in dataset generation in order to most fully demonstrate our methods.
-\textcolor{red}{We further propose an adaptive sampling algorithm (QASS) suitable for reducing the quantity of expensive samples needed to train our surrogate models.}
+\textcolor{red}{We quantify the success of several of our best-performing surrogate models by studying their accuracy and prediction time.
+We further propose an adaptive sampling algorithm (QASS) suitable for reducing the quantity of expensive samples needed to train our surrogate models.}
 
@@
 
-Paramak facilitates simulation via OpenMC neutronics workflow that is enclosed in
+Paramak facilitates simulation via \textcolor{red}{an} OpenMC neutronics workflow that is enclosed in
 a portable Docker container, which conveniently exposes an HTTP API using the
-Python~3 \texttt{flask} package. For the purposes of our work, we used this setup to
-simulate a point source with a Muir energy distribution \cite{openmcmuir}\footnotemark[1]
+Python~3 \texttt{flask} package. \textcolor{red}{Within this setup, we employ} a Muir energy distribution \cite{openmcmuir}\footnotemark[1]
 around~\SI{14.06}{\mega\electronvolt} to approximate a Deuterium-Tritium (D-T)
-plasma neutron source. Illustrated in~\Fref{fig:model_diagram}, the simulated
-geometry was deliberately left adjustable, so that dependency of TBR on various
-parameters may be explored.
+plasma neutron source. Illustrated in~\Fref{fig:model_diagram}, the simulated \textcolor{red}{reactor}
+geometry was left adjustable \textcolor{red}{in order to study its influence on the TBR}.
 Nuclear data for simulation was extracted from the following sources, in order of preference: \textcolor{red}{FENDL 3.1d \cite{fendl31d}; JEFF 3.3 \cite{jeff33}; and ENDF/B-VII.1 \cite{2011ii}}.
@@
 research. In~\Sref{sec:methodology} we will present our methodologies for the comparison
-testing of a wide variety of surrogate modelling techniques, as well as defining the adaptive sampling procedure QASS. After delivering the
+testing of a wide variety of surrogate modelling techniques, as well as defining \textcolor{red}{an add-on} adaptive sampling procedure QASS. After delivering the
 results of these approaches in~\Sref{sec:results}, we will give our final conclusions and
@@
 sampling was recently uncovered (see
-\url{https://github.com/openmc-dev/openmc/pull/1670}), but is disregarded in the present approach-focused work.}
+\url{https://github.com/openmc-dev/openmc/pull/1670}), but is disregarded in the present \textcolor{red}{methods-focused} work.}
 
@@
 While at least one deuterium atom occurs for every \num{5000} molecules of naturally-sourced water, and may be easily distilled, tritium is extremely rare in nature.
-It may be produced indirectly through irradiation of heavy water
+\textcolor{red}{Tritium} may be produced indirectly through irradiation of heavy water
 (\DDO) during nuclear fission, but only at very low rates which could
@@
 	&\longrightarrow \hspace{3pt} 
-	\isotope[3][1]{T} + \hspace{3pt} \isotope[4][2]{He} + \hspace{3pt} \isotope[1][0]{n}
+	\isotope[3][1]{T} + \hspace{3pt} \isotope[4][2]{He} + \hspace{3pt} \isotope[1][0]{n}.
 \end{eqnarray}%
-where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
-less common isotopes of lithium, respectively. \textcolor{red}{The TBR is defined as the ratio of tritium produced per source neutron}
-, whose description in Paramak is facilitated by 2~classes of parameters
+%
+\textcolor{red}{The TBR is defined as the ratio of tritium produced per source neutron}, whose description in Paramak is facilitated by \textcolor{red}{two} classes of parameters
 (exhaustively listed in~\Tref{tbl:params}). While the geometry of a given
@@
 packing fractions close to 1).
-Simulating broadly around typical values of parameters is necessary to construct the most accurate model of the typical range, and also aids in demonstrating the robustness of constructed models.
+Simulating broadly around typical values of parameters \textcolor{red}{improves the accuracy of the model nearer to typical values}, and also aids in demonstrating the robustness of constructed models.
 
 In our work, we set out to produce a \textcolor{red}{fast TBR surrogate model}, which takes the same input parameters \textcolor{red}{as the MC model used in Paramak and approximates its output} with the greatest achievable regression performance, while also minimising the required quantity of expensive-model samples \textcolor{red}{needed for training}.
+\textcolor{red}{This represents a significant step forwards in computational fusion-reactor design, as any speed-up achieved in TBR evaluation directly informs a speed-up in numerical optimization of reactor parameters, although such optimization is beyond the scope of the present work.}
 

### 2022-03-14 paper/methodology.tex
Small writing changes in first two sections.

@@
-Labeling the expensive Paramak model $f(x)$, a surrogate is a mapping
+Labeling the expensive Paramak model $f(x)$, a surrogate \textcolor{red}{model is a function}
 $\hat{f}(x)$ such that $f(x)$ and $\hat{f}(x)$ minimize a selected dissimilarity
 metric. In order to be considered \textit{viable}, $\hat{f}(x)$ is required to
-achieve expected evaluation time lower than that of~$f(x)$. In this work, we
-consider 2~methods of producing viable surrogates: (1)~a conventional decoupled
-approach, which evaluates $f(x)$ on a set of randomly sampled points and
+achieve \textcolor{red}{an} expected evaluation time lower than that of~$f(x)$. In this work, we
+consider \textcolor{red}{two} methods of producing viable surrogates: (1)~a conventional decoupled
+approach, which evaluates $f(x)$ on a set of \textcolor{red}{uniformly-random samples} and
 trains surrogates in a supervised scheme, and (2)~an adaptive approach, which attempts to
-compensate for localized regression performance insufficiency's by interleaving
+compensate for localized regression performance \textcolor{red}{insufficiencies} by interleaving
 multiple epochs of sampling and training.
+\textcolor{red}{Several high-accuracy and deployment-ready surrogate models are developed using the decoupled approach, and their performance characterized numerically, while the adaptive approach is studied as a proof-of-concept.}
 
@@
 		 on all points of the test set. In surrogates, the equivalent
-		time period is referred to as ``prediction time.''}
+		time period is referred to as \textcolor{red}{the} ``prediction time.''}
 	\end{indented}
@@
 
-For both methods, we selected state-of-the-art regression algorithms to perform
+We selected several state-of-the-art regression algorithms to perform
 surrogate training on sampled point sets. Listed in~\Tref{tbl:surrogates}, these
-implementations define 9~surrogate families that are later reviewed in~\Sref{sec:results}.
+implementations define \textcolor{red}{nine} surrogate families \textcolor{red}{which are detailed} in~\Sref{sec:results}.
 We note that each presented algorithm defines hyperparameters that may influence its
@@
 
-To compare the quality of the produced surrogates, we define a number of metrics listed
+To compare the quality of the produced surrogates, we define a \textcolor{red}{variety} of metrics listed
 in~\Tref{tbl:metrics}. For regression performance analysis, we include a
@@
 For analysis of computational complexity, surrogates are assessed in terms of wall
-time (captured by the Python~3 \texttt{time} package). This is motivated by common practical use
-cases of our work, where models are trained and used as drop-in replacements for
+time (captured by the Python~3 \texttt{time} package). This is motivated by common practical \textcolor{red}{use-cases} of our work, where surrogate models are trained as replacements for
 Paramak. All times reported (training, test, evaluation) are
@@
 set selection, all reported metrics are obtained via 5-fold cross-validation.
-In this setting, a sample set is uniformly divided into 5 disjoint folds, each of which
-is used as a test set for models trained on the remaining 4. Having repeated the
-same experiment for each division, the overall value of individual metrics is
-reported in terms of their mean and standard deviation over all folds.
+In this setting, a sample set is uniformly divided into \textcolor{red}{five} disjoint folds, each of which
+is used as a test set for models trained on the remaining \textcolor{red}{four}. Having repeated the
+same experiment for each division, the overall value of individual metrics is reported in terms of their mean and standard deviation over all folds.
 
@@
 
-Experiments related to the decoupled approach are organized in 4~parts,
+Experiments related to the decoupled approach are organized in \textcolor{red}{four} parts,
 further described in this section. In summary, we aim to optimize the hyperparameters of
-each surrogate family separately and later use the best found results to compare surrogate
-families among themselves.
+each surrogate family separately, \textcolor{red}{and later compare the best results between
+families.}
 
 The objective of Experiment~1 is to simplify the regression task for
-surrogates prone to suboptimal performance in discontinuous spaces.
+surrogates prone to suboptimal performance in \textcolor{red}{discrete} spaces.
 To this end, training points are filtered to a single selected discrete feature
 assignment, and surrogates are trained only on the remaining continuous features.
-This is repeated several times to explore variances in behaviour,
-particularly in 4~distinct assignments that are obtained by setting blanket and
+This is repeated several times to explore variances in behavior,
+particularly in \textcolor{red}{four} distinct assignments that are obtained by setting blanket and
 first wall coolant materials to one
@@
 hyperparameter configuration that produces the model that maximizes $R^2$. The
-process is terminated after 1000~iterations or 2~days, whichever condition is satisfied first.
+process is terminated after 1000~iterations or \textcolor{red}{two} days, whichever condition is satisfied first.
 The results of Experiments~1 \&~2 are depicted
@@
 
-In Experiment~3, the 20~best-performing hyperparameter configurations
+In Experiment~3, the \textcolor{red}{twenty} best-performing hyperparameter configurations
 \textcolor{red}{for} each model family are used to train surrogates on sets of various sizes to
@@
 from~\Tref{tbl:metrics} as functions of training set size (1, 2, 5, 10, 12, 15 and 20 thousands
-of samples) individually for each family. This allows their comparison based on
+of samples) individually \textcolor{red}{for} each family. This allows their comparison based on
 observed trends, and estimation of optimal training set sizes.
@@
 to produce surrogates suitable for practical use by retraining selected
-well-scaling instances on large training sets in order to satisfy the goals of this work.
+well-scaling instances on large training sets\textcolor{red}{.}
 The results of this process are displayed in~\Fref{fig:reg-performance} and
@@
 \textcolor{red}{Error maximization is desirable for these sample points because it identifies regions of parameter space where the surrogate most needs to be improved.} On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and absolute error calculated.
-MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points.
+MCMC was then performed to sample the error function generated by performing nearest-neighbor interpolation on these test error points.
 The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the training/test set, beginning another training epoch.

### 2022-08-08 paper/acknowledgements.tex
nicer typesetting with the savetrees package
Removed textcolor and minor grammar adjustments.

@@
-{\footnotesize
-PM \& GVG were supported the STFC UCL Centre for Doctoral Training in Data Intensive
-Science (grant no. ST/P006736/1).
+PM \& GVG were supported by the STFC UCL Centre for Doctoral Training in Data Intensive
+Science (grant no. ST/P006736/1). GVG was funded by the UCL Graduate Research and Overseas Research Scholarships.
 
@@
 This work has also been part-funded by the RCUK Energy Programme (grant number EP/I501045/1).
-}

### 2022-08-08 paper/conclusion.tex
Removed textcolor and minor grammar adjustments.

@@
 We additionally developed a novel adaptive
-sampling algorithm, QASS, capable of interfacing with any of the \textcolor{red}{surrogate models presented in this work}.
+sampling algorithm, QASS, capable of interfacing with any of the surrogate models presented in this work.
 Preliminary testing on a toy theory, qualitatively comparable to
-Paramak, demonstrated the effectiveness of QASS and \textcolor{red}{key} behavioral trends. With~\num{100000} initial samples
+Paramak, demonstrated the effectiveness of QASS and key behavioral trends. With~\num{100000} initial samples
 and 100 incremental samples per iteration, QASS achieved a ${\sim}40\%$ decrease
@@
 Further optimisation over the hyperparameter space has strong potential to increase this performance by further reduction of necessary expensive samples, in particular by decreasing the required quantity of initial samples.
-This will allow for future deployment of QASS on top of any of \textcolor{red}{our most effective identified TBR surrogate models}.
+This will allow for future deployment of QASS on top of any of our most effective identified TBR surrogate models.
 

### 2022-08-08 paper/introduction.tex
Removed textcolor and minor grammar adjustments.

--- 2022-03-11 paper/introduction.tex
@@
 Although more expensive 3D parametric models exist, we chose the Paramak simulation for its preferable speed in dataset generation in order to most fully demonstrate our methods.
+We quantify the success of several of our best-performing surrogate models by studying their accuracy and prediction time.
 We further propose an adaptive sampling algorithm (QASS) suitable for reducing the quantity of expensive samples needed to train our surrogate models.
@@
 
-Paramak facilitates simulation via OpenMC neutronics workflow that is enclosed in
+Paramak facilitates simulation via an OpenMC neutronics workflow that is enclosed in
 a portable Docker container, which conveniently exposes an HTTP API using the
-Python~3 \texttt{flask} package. For the purposes of our work, we used this setup to
-simulate a point source with a Muir energy distribution \cite{openmcmuir}\footnotemark[1]
+Python~3 \texttt{flask} package. Within this setup, we employ a Muir energy distribution \cite{openmcmuir}\footnotemark[1]
 around~\SI{14.06}{\mega\electronvolt} to approximate a Deuterium-Tritium (D-T)
-plasma neutron source. Illustrated in~\Fref{fig:model_diagram}, the simulated
-geometry was deliberately left adjustable, so that dependency of TBR on various
-parameters may be explored.
-Nuclear data for simulation was extracted from the following sources, in order of preference: FENDL 3.1d \cite{fendl31d}; JEFF 3.3 \cite{jeff33}; and ENDF/B-VII.1 \cite{2011ii}.
-To maintain model-agnostic approach, variance reduction (VR) techniques
+plasma neutron source. As illustrated in~\Fref{fig:model_diagram}, the simulated reactor
+geometry was made adjustable in order to study its influence on the TBR.
+Nuclear data for simulation were extracted from the following sources, in order of preference: FENDL 3.1d \cite{fendl31d}; JEFF 3.3 \cite{jeff33}; and ENDF/B-VII.1 \cite{2011ii}.
+To maintain a model-agnostic approach, variance reduction (VR) techniques
 were not used to accelerate the MC neutronics simulation~\cite{Kleijnen2013}.
@@
 research. In~\Sref{sec:methodology} we will present our methodologies for the comparison
-testing of a wide variety of surrogate modelling techniques, as well as defining the adaptive sampling procedure QASS. After delivering the
+testing of a wide variety of surrogate modelling techniques, as well as defining an add-on adaptive sampling procedure QASS. After delivering the
 results of these approaches in~\Sref{sec:results}, we will give our final conclusions and
@@
 sampling was recently uncovered (see
-\url{https://github.com/openmc-dev/openmc/pull/1670}), but is disregarded in the present approach-focused work.}
+\url{https://github.com/openmc-dev/openmc/pull/1670}), but is disregarded in the present methods-focused work.}
 
@@
 While at least one deuterium atom occurs for every \num{5000} molecules of naturally-sourced water, and may be easily distilled, tritium is extremely rare in nature.
-It may be produced indirectly through irradiation of heavy water
+Tritium may be produced indirectly through irradiation of heavy water
 (\DDO) during nuclear fission, but only at very low rates which could
@@
 	&\longrightarrow \hspace{3pt} 
-	\isotope[3][1]{T} + \hspace{3pt} \isotope[4][2]{He} + \hspace{3pt} \isotope[1][0]{n}
+	\isotope[3][1]{T} + \hspace{3pt} \isotope[4][2]{He} + \hspace{3pt} \isotope[1][0]{n}.
 \end{eqnarray}%
-where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
-less common isotopes of lithium, respectively. The TBR is defined as the ratio of tritium produced per source neutron
-, whose description in Paramak is facilitated by 2~classes of parameters
+%
+The TBR is defined as the ratio of tritium produced per source neutron}, whose description in Paramak is facilitated by two classes of parameters
 (exhaustively listed in~\Tref{tbl:params}). While the geometry of a given
@@
 packing fractions close to 1).
-Simulating broadly around typical values of parameters is necessary to construct the most accurate model of the typical range, and also aids in demonstrating the robustness of constructed models.
+Simulating broadly around typical values of parameters also improves the accuracy of the model nearer to typical values, and further aids in demonstrating the robustness of constructed models.
 
 In our work, we set out to produce a fast TBR surrogate model, which takes the same input parameters as the MC model used in Paramak and approximates its output with the greatest achievable regression performance, while also minimising the required quantity of expensive-model samples needed for training.
+This represents a significant step forwards in computational fusion-reactor design, as any speed-up achieved in TBR evaluation directly informs a speed-up in numerical optimization of reactor parameters, although such optimization is beyond the scope of the present work.
 

### 2022-08-08 paper/methodology.tex
Removed textcolor and minor grammar adjustments.

--- 2022-03-11 paper/methodology.tex
@@
-Labeling the expensive Paramak model $f(x)$, a surrogate is a mapping
+Labeling the expensive Paramak model $f(x)$, a surrogate model is a function
 $\hat{f}(x)$ such that $f(x)$ and $\hat{f}(x)$ minimize a selected dissimilarity
 metric. In order to be considered \textit{viable}, $\hat{f}(x)$ is required to
-achieve expected evaluation time lower than that of~$f(x)$. In this work, we
-consider 2~methods of producing viable surrogates: (1)~a conventional decoupled
-approach, which evaluates $f(x)$ on a set of randomly sampled points and
+achieve an expected evaluation time lower than that of~$f(x)$. In this work, we
+consider two methods of producing viable surrogates: (1)~a conventional decoupled
+approach, which evaluates $f(x)$ on a set of uniformly-random samples and
 trains surrogates in a supervised scheme, and (2)~an adaptive approach, which attempts to
-compensate for localized regression performance insufficiency's by interleaving
+compensate for localized regression performance insufficiencies by interleaving
 multiple epochs of sampling and training.
+Several high-accuracy and deployment-ready surrogate models are developed using the decoupled approach, and their performance characterized numerically, while the adaptive approach is studied exclusively as a proof-of-concept.
 
@@
 		 on all points of the test set. In surrogates, the equivalent
-		time period is referred to as ``prediction time.''}
+		time period is referred to as the ``prediction time.''}
 	\end{indented}
@@
 
-For both methods, we selected state-of-the-art regression algorithms to perform
+We selected several state-of-the-art regression algorithms to perform
 surrogate training on sampled point sets. Listed in~\Tref{tbl:surrogates}, these
-implementations define 9~surrogate families that are later reviewed in~\Sref{sec:results}.
+implementations define nine surrogate families which are detailed in~\Sref{sec:results}.
 We note that each presented algorithm defines hyperparameters that may influence its
@@
 
-To compare the quality of the produced surrogates, we define a number of metrics listed
+To compare the quality of the produced surrogates, we define a variety of metrics listed
 in~\Tref{tbl:metrics}. For regression performance analysis, we include a
 selection of absolute metrics (MAE, $S$) to assess the models' approximation capability
-and set practical bounds on the expected uncertainty of their predictions. In addition, we also track
-relative measures ($R^2$, $R^2_\text{adj.}$) that are better-suited for comparison between this work and others as
+and to set practical bounds on the expected uncertainty of their predictions. In addition, we also track
+relative measures ($R^2$, $R^2_\text{adj.}$) that are better-suited for comparison between this work and others, as
 they are invariant with respect to the selected domain and image space.
 For analysis of computational complexity, surrogates are assessed in terms of wall
-time (captured by the Python~3 \texttt{time} package). This is motivated by common practical use
-cases of our work, where models are trained and used as drop-in replacements for
+time (captured by the Python~3 \texttt{time} package). This is motivated by common practical use-cases of our work, where surrogate models are trained as replacements for
 Paramak. All times reported (training, test, evaluation) are
@@
 
-Even though some surrogates support acceleration by means of parallelisation, we
-used non-parallelized implementations. The only exception to this are ANNs,
-which require a considerable amount of processing power for training on
+Even though some surrogates support acceleration by means of parallelization, we
+used non-parallelized implementations. The only exception to this is the ANN family,
+which requires a considerable amount of processing power for training on
 conventional CPU architectures. Lastly, to prevent undesirable bias by training
-set selection, all reported metrics are obtained via 5-fold cross-validation.
-In this setting, a sample set is uniformly divided into 5 disjoint folds, each of which
-is used as a test set for models trained on the remaining 4. Having repeated the
-same experiment for each division, the overall value of individual metrics is
-reported in terms of their mean and standard deviation over all folds.
+set selection, all reported metrics are obtained via five-fold cross-validation.
+In this setting, a sample set is uniformly divided into five disjoint folds, each of which
+is used as a test set for models trained on the remaining four. Having repeated the
+same experiment for each division, the overall value of individual metrics is reported in terms of their mean and standard deviation over all folds.
 
@@
 
-Experiments related to the decoupled approach are organized in 4~parts,
+Experiments related to the decoupled approach are organized in four parts,
 further described in this section. In summary, we aim to optimize the hyperparameters of
-each surrogate family separately and later use the best found results to compare surrogate
-families among themselves.
+each surrogate family separately, and later compare the best results between
+families.
 
 The objective of Experiment~1 is to simplify the regression task for
-surrogates prone to suboptimal performance in discontinuous spaces.
+surrogates prone to suboptimal performance in discrete spaces.
 To this end, training points are filtered to a single selected discrete feature
 assignment, and surrogates are trained only on the remaining continuous features.
-This is repeated several times to explore variances in behaviour,
-particularly in 4~distinct assignments that are obtained by setting blanket and
+This is repeated several times to explore variances in behavior,
+particularly in four distinct assignments that are obtained by setting blanket and
 first wall coolant materials to one
@@
 hyperparameter configuration that produces the model that maximizes $R^2$. The
-process is terminated after 1000~iterations or 2~days, whichever condition is satisfied first.
+process is terminated after 1000~iterations or two days, whichever condition is satisfied first.
 The results of Experiments~1 \&~2 are depicted
@@
 
-In Experiment~3, the 20~best-performing hyperparameter configurations
-per each model family are used to train surrogates on sets of various sizes to
+In Experiment~3, the twenty best-performing hyperparameter configurations
+for each model family are used to train surrogates on sets of various sizes to
 investigate their scaling properties. In particular, we track the metrics
@@
 to produce surrogates suitable for practical use by retraining selected
-well-scaling instances on large training sets in order to satisfy the goals of this work.
+well-scaling instances on large training sets.
 The results of this process are displayed in~\Fref{fig:reg-performance} and
@@
 fare better for high-dimensional models by more thoroughly exploring all local
-optima in the feature space. MCMC produces each sample points according to a shared proposal
-distribution from the prior point. These sample points will converge to a desired posterior
+optima in the feature space. MCMC produces each sample point according to a jump step drawn from a shared proposal
+distribution. These sample points will converge to a desired posterior
 distribution, so long as the acceptance probability meets certain statistical criteria (see~\cite{Zhou2018} for a review).
@@
 On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and absolute error calculated.
-MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points.
+MCMC was then performed to sample the error function generated by performing nearest-neighbor interpolation on these test error points.
 The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the training/test set, beginning another training epoch.

### 2022-08-08 paper/results.tex
Removed textcolor and minor grammar adjustments.

--- 2022-03-11 paper/results.tex
@@
 relatively lower variance than those of ERTs and ANNs. Even though the remainder
-of tested surrogate families does not exhibit prohibitive complexity, its
-regression performance falls below average.
+of tested surrogate families do not exhibit prohibitive complexity, their
+regression performance fall below the average.
 
@@
 ERTs and RBFs also demonstrated satisfactory results, clearly outperforming the
-remaining surrogates in terms of regression performance, and in some cases also
-in prediction time.
+remaining surrogates in terms of regression performance, and in some cases also prediction time.
 
@@
 approaches clearly outperform ANNs. For instance, GBTs achieve
-$\text{MAE}=\num{0.107}$ that is nearly half of the $\text{MAE}=\num{0.186}$
-reached by ANNs, representing a clear benefit given vastly disparate training
-and prediction times. This trend continues to set sizes up to~\num{6000}.
+$\text{MAE}=\num{0.107}$, nearly half of the $\text{MAE}=\num{0.186}$
+achieved by ANNs, representing a clear benefit given vastly disparate training
+and prediction times. This trend continues for set sizes up to~\num{6000}.
 
@@
 
-Consistent with our expectation, the shortest training times were achieved by
+Consistent with our expectations, the shortest training times were achieved by
 instance-based learning methods (KNN, IDW) that
@@
 Finally, all tested families with the exception of previously mentioned instance-based
-models offer desirable prediction times. Analogous to previous experiments,
-GBTs, ABTs and ANNs appear to be tied, as they not only exhibit
-comparable times but also similar scaling slopes. Following those, we note a
+models offered desirable prediction times. Analogous to previous experiments,
+GBTs, ABTs and ANNs appeared to be tied, as they not only exhibited
+comparable times but also similar scaling slopes. After those, we note a
 clear hierarchy of ERTs, SVMs, GPR and RBFs, trailed by IDW and KNNs.
@@
 		bottom) in Experiment~4, viewed
-		as true vs.~predicted TBR on a test set of a selected cross-validation
-		fold. Points are coloured by density.}
+		as true vs.~predicted TBR on a test set of a selected cross-validation fold. Points are colored by density.}
 	\label{fig:reg-performance}
@@
 adaptively-sampled training set, it is outperformed by the baseline scheme on
-uniformly-random evaluation sets. We suspected that while QASS excels in
+uniformly-random evaluation sets. We inferred that while QASS excels in
 learning the most strongly peaked regions of the TBR theory, this comes at the
@@
 sampling suffices. Therefore a mixed scheme was implemented, with half MCMC
-samples and half uniformly random samples incremented on each iteration, which
+samples and half uniformly-random samples incremented on each iteration, which
 is also shown in~\Fref{fig:qasssampling}. An increase in initial sample size was also observed to improve precision in these smooth regions of the toy theory, as
-the initial samples were obtained from a uniform random distribution. As shown
-in ~\Fref{fig:qasssampling100k}, with~\num{100000} initial samples it was
+the initial samples were uniformly-random. As shown
+in~\Fref{fig:qasssampling100k}, with~\num{100000} initial samples it was
 possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline

### 2022-08-13 paper/introduction.tex
fix extra brace that prevented rendering

@@
 %
-The TBR is defined as the ratio of tritium produced per source neutron}, whose description in Paramak is facilitated by two classes of parameters
+The TBR is defined as the ratio of tritium produced per source neutron, whose description in Paramak is facilitated by two classes of parameters
 (exhaustively listed in~\Tref{tbl:params}). While the geometry of a given

### 2023-01-08 paper/introduction.tex
move BSM acronym to the correct parameter

@@
 		   & Multiplier packing fraction & $[0,1]$\\
-		   & Structural fraction\textsuperscript{\textdagger} (BSM) & $[0,1]$\\
-		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
+		   & Structural fraction\textsuperscript{\textdagger} & $[0,1]$\\
+		   & Structural material (BSM) & $\{\text{SiC}, \text{eurofer}\}$\\
 		   & Thickness & $[0,500]\text{ cm}$\\

### 2023-01-08 paper/introduction.tex
implement Nikos's suggestion to rephrase sentence in introduction section

@@
 
-In our work, we set out to produce a fast TBR surrogate model, which takes the same input parameters as the MC model used in Paramak and approximates its output with the greatest achievable regression performance, while also minimising the required quantity of expensive-model samples needed for training.
-This represents a significant step forwards in computational fusion-reactor design, as any speed-up achieved in TBR evaluation directly informs a speed-up in numerical optimization of reactor parameters, although such optimization is beyond the scope of the present work.
+In our work, we set out to produce a fast TBR surrogate model, which takes the
+same input parameters as the MC model used in Paramak and approximates its
+output with the greatest achievable regression performance, while also
+minimising the required quantity of expensive-model samples needed for training.
+This represents a significant step forward in computational fusion-reactor
+design, as speed-ups achieved in TBR evaluation can lead to a speed-up in
+numerical optimization of reactor parameters, although such optimization is
+beyond the scope of the present work.
 

### 2023-01-08 paper/referees/response-2.tex
add referee response

\documentclass[12pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath,amssymb}
\usepackage{color}
\usepackage{graphicx}

\topmargin = 1mm
\headsep = 1mm
\textheight = 228mm
\textwidth = 167.0mm
\oddsidemargin = 1.1mm
\evensidemargin = 1.1mm
\date{\today}

% Set the format for notes on in-progress responses
\newcommand\myNotes[1]{\textcolor{red}{#1}}
\newcommand\myTodo[1]{\textcolor{blue}{#1}}

\begin{document}

\begin{center}
\bf Reviewer Response for Manuscript MLST-100670
\end{center}

\bigskip

\noindent
Dear Editor,

\bigskip
\noindent
We thank the referee for his or her careful consideration and useful comments.
Please find below our detailed responses. We have also made the corresponding
changes in the text.

\bigskip
\noindent
Best Regards,\\
Petr Mánek (for the authors)

\bigskip
\bigskip
\bigskip
\noindent
{\bf Comments of Referee 1}

\begin{enumerate}

\item Page 3, Section 1.1, Table 1: Please correct abbreviation \textit{Blanket
	Structural Fraction (BSM)} defined in Table 1. It should be BSF. While BSM
	corresponds to \textit{``Blanket Structural Material''}.

{\bf
	The ``BSM'' abbreviation was indeed intended to denote ``Blanket
	Structural Material'', as can be seen further on in Table 4, where it is
	associated with ``eurofer''. In the submitted manuscript, the abbreviation
	was incorrectly misplaced in Table 1 by one row. We have corrected this
	error.
}

\item Page 3, Section 1.1, lines 47-54: Please clarify the meaning of the
	sentence which currently is trivial and does not convey much sense:
	\textit{``This represents a significant step forwards in computational
		fusion-reactor design, as any speed-up achieved in TBR evaluation
		directly informs a speed-up in numerical optimization of reactor
		parameters, although such optimization is beyond the scope of the
		present work.''} Particularly, I suspect that its second clause is very
		doubtful: \textit{``as any speed-up achieved in TBR evaluation directly
		informs a speed-up in numerical optimization of reactor parameters,''}
		Maybe, the problems in understanding are related with the phrases
		\textit{``any speed-up''} -- this is too general expression, the second
		phrase is \textit{``directly informs''} -- maybe you wanted to say
		\textit{``directly connected''}?

{\bf
	It is true that the wording of this sentence is perhaps unnecessarily
	complex. Its purpose is to motivate our work in the following sense: if a
	computationally expensive Monte Carlo (MC) simulation is required in order
	to evaluate a single instance of reactor parameters (i.e.~a single data
	point of some phase space), it may act as a performance bottleneck
	prohibiting efficient exploration of that domain. Our surrogate models can
	be viewed as a possible improvement of this paradigm. If a surrogate model
	is trained to be sufficiently accurate, it could perhaps completely
	substitute MC simulations in this process (note that MC would still be
	needed to train the model). Or alternatively, one could envision a hybrid
	optimization process where a surrogate model acts as a heuristic that guides
	the optimization algorithm, prunes the parameter space and reduces the
	number of calls to the MC. For instance, such approach would be consistent
	with Branch \& Bound strategy. Since the prediction time of the presented
	surrogate models is significantly smaller than the runtime of the MC, in
	both cases we would observe a relative speed-up of the optimization process.

	We have rephrased the referenced sentence to better convey this meaning.
}

\end{enumerate}

\end{document}
